### 2020-02-17 Paper%20draft/apssamp.tex
Add files via upload

% ****** Start of file apssamp.tex ******
%
%   This file is part of the APS files in the REVTeX 4.2 distribution.
%   Version 4.2a of REVTeX, December 2014
%
%   Copyright (c) 2014 The American Physical Society.
%
%   See the REVTeX 4 README file for restrictions and more information.
%
% TeX'ing this file requires that you have AMS-LaTeX 2.0 installed
% as well as the rest of the prerequisites for REVTeX 4.2
%
% See the REVTeX 4 README file
% It also requires running BibTeX. The commands are as follows:
%
%  1)  latex apssamp.tex
%  2)  bibtex apssamp
%  3)  latex apssamp.tex
%  4)  latex apssamp.tex
%
\documentclass[%
 reprint,
%superscriptaddress,
%groupedaddress,
%unsortedaddress,
%runinaddress,
%frontmatterverbose, 
%preprint,
%preprintnumbers,
%nofootinbib,
%nobibnotes,
%bibnotes,
 amsmath,amssymb,
 aps,
%pra,
%prb,
%rmp,
%prstab,
%prstper,
%floatfix,
]{revtex4-2}

\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
%\usepackage{hyperref}% add hypertext capabilities
%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
%\linenumbers\relax % Commence numbering lines

%\usepackage[showframe,%Uncomment any one of the following lines to test 
%%scale=0.7, marginratio={1:1, 2:3}, ignoreall,% default settings
%%text={7in,10in},centering,
%%margin=1.5in,
%%total={6.5in,8.75in}, top=1.2in, left=0.9in, includefoot,
%%height=10in,a5paper,hmargin={3cm,0.8in},
%]{geometry}

\begin{document}

\preprint{APS/123-QED}

\title{Generalised gravitational burst searches \\with Generative Adverserial Networks}% Force line breaks with \\
\thanks{A footnote to the article title}%

%\author{Jordan McGinn, Chris Messenger, Ik Siong Heng}
 \altaffiliation[Also at ]{Physics Department, XYZ University.}%Lines break automatically or can be forced with \\

 \email{}
\affiliation{%
School of Physics \& Astronomy\\
University of Glasgow \\
Glasgow G12 8QQ, United Kingdom
}%

\date{\today}% It is always \today, today,
             %  but any date may be explicitly specified

\begin{abstract}
As the field of gravitational wave astronomy expands and as detectors become more sensitive, there is a need for fast and efficient detection of various sources. Gravitational wave bursts are a family of signals that remain unmodeled, therefore, they have a low detection sensitivity to standard detection schemes. This report examines the use of Generative Adversarial Networks as a detection pipeline for gravitational wave burst signals. BurstGAN is trained to detect three classes of burst signals: sine-Gaussian, Ring-downs and white-noise bursts contained in white Gaussian noise. The resulting sensitivity curves show that sine-Gaussian and Ring-downs are confidently detectable at SNRs > while white-noise bursts require SNRs of >.
%\begin{description}
%\item[Usage]
%Secondary publications and information retrieval purposes.
%\item[Structure]
%You may use the \texttt{description} environment to structure your abstract;
%use the optional argument of the \verb+\item+ command to give the category of each item. 
%\end{description}
\end{abstract}

%\keywords{Suggested keywords}%Use showkeys class option if keyword
                              %display desired
\maketitle

%\tableofcontents

\section{Introduction}

The detections of gravitational waves by Advanced Laser Interferometer Gravitational wave Observatory (aLIGO) and Advanced Virgo [1–5], have opened up new avenues to explore the Universe. Astrophysical sources of transient gravitational waves include the merging of compact binary star systems like black holes and/or neutron stars [6], core-collapse supernova [7], pulsar glitches [8] and other events involving accelerating massive objects.
Gravitational wave bursts (GWBs) are an exciting area of research as the emissions process of such waves is not well understood. The waveforms often depend on complicated orbital dynamics and equations of state which limit the sensitivity on searching for burst sources. Typically, the duration of burst signals are short with amplitudes that can be greater than the detector noise. Burst searches look for excess power contained in a time-frequency plot and rely on consistent arrival times, waveform shapes and frequencies between detectors. We focus on utilising an unsupervised form of machine learning called Generative Adversarial Networks [9] as a generalised GW transient search. A two detector case is considered such that the signals retain their form between detections and a defined time delay between detections relating to the sky orientation of the source.

\section{Background}
Generative adversarial networks (GANs) have seen considerable success in recent years as a generative machine learning model. GANs work to train two competing neural networks, consisting of a discriminator D that is trained to distinguish between real and fake data and a generator G that produces synthetic reproductions of the real data. The original GAN method has G perform a mapping from an input noise vector z to its representation of the data and D maps its input x to a probability [0,1] that the input came form either the training data or G. Both networks compete in turn to trick the other and after training, G produces accurate distributions and D can detect forgeries. During training, D s given a batch of samples that contains one half real data (labelled as 1) and one half fake data (labelled as 0) which it then makes predictions on. The loss on D is calculated by comparing its predictions to the labels through a defined loss function. (talk about binary cross entropy). The training process of a GAN alternatively updates the weights of the D and G based on information on its competitors loss function. This loss of D is used to update the weights of G to produce more realistic samples of the input distribution, the loss of G encourages the D to update its classification abilities. Both networks compete in a minimax game that is tied to a value function V (D, G) which G is trying minimise and D is trying to maximise:
\begin{multline}
\mathop{\text{min}}_{G}  \mathop{\text{max}}_{D} V(D,G) = \mathbb{E}_{\bold{x} \sim p_{\text{r}}(\bold{x})} [\text{log} D(\bold{x})] \\ + \mathbb{E}_{\bold{z} \sim p_{\text{z}}(\bold{z})} [\text{log}(1-D(G(\bold{z})))]
\label{equation:GANloss}
\end{multline}
In theory this will eventually lead to the local Nash equilibrium [18] where both neural networks are trained optimally. In practice, however, GANs are notoriously difficult to train. Such difficulties include: Non-convergence, where the model parameters oscillate and the loss never converges. Mode collapse where G produces a limited diversity of samples, and the diminishing gradient problem when applying the gradient descent algorithm to a non-continuous function. 
\\ To overcome some of these difficulties [blank] proposed adding structure to the latent space by providing G with a class label. This has the effect of making a point in latent space conditional on a provided class. [blank] extends this idea further by requiring D to output a probability of the data belonging to each class.

\section{Method}
To simulate gravitational burst sources, three GW signal morphologies, spanning a range of frequencies, duration and time delays were tested. The three families are:\\

time delay/antenna pattern/lalsuite etc \\

archetecture/hyperparameters

\section{Results}

\bibliography{apssamp}% Produces the bibliography via BibTeX.

\end{document}
%
% ****** End of file apssamp.tex ******

### 2020-02-17 Paper%20draft/apssamp.tex
Added some bullet points to address.

@@
 \usepackage{bm}% bold math
+\usepackage{color}
+\usepackage{acronym}
 %\usepackage{hyperref}% add hypertext capabilities
@@
 
+\newcommand{\jordan}[1]{\textbf{\textcolor{red}{JORDAN: #1}}}
+\newcommand{\siong}[1]{\textbf{\textcolor{blue}{SIONG: #1}}}
+\newcommand{\chris}[1]{\textbf{\textcolor{green}{CHRIS: #1}}}
+
 \begin{document}
@@
 
-\title{Generalised gravitational burst searches \\with Generative Adverserial Networks}% Force line breaks with \\
+\title{Generalised gravitational burst searches with Generative Adverserial
+Networks~\chris{Need to change the title if we don't search}}% Force line breaks with \\
 \thanks{A footnote to the article title}%
@@
 \begin{abstract}
-As the field of gravitational wave astronomy expands and as detectors become more sensitive, there is a need for fast and efficient detection of various sources.
-Gravitational wave bursts are a family of signals that remain unmodeled, therefore, they have a low detection sensitivity to standard detection schemes.
-This report examines the use of Generative Adversarial Networks as a detection pipeline for gravitational wave burst signals.
-BurstGAN is trained to detect three classes of burst signals: sine-Gaussian, Ring-downs and white-noise bursts contained in white Gaussian noise.
-The resulting sensitivity curves show that sine-Gaussian and Ring-downs are confidently detectable at SNRs > while white-noise bursts require SNRs of >.
-%\begin{description}
-%\item[Usage]
-%Secondary publications and information retrieval purposes.
-%\item[Structure]
-%You may use the \texttt{description} environment to structure your abstract;
-%use the optional argument of the \verb+\item+ command to give the category of each item. 
-%\end{description}
+As the field of gravitational wave astronomy expands and as detectors become
+more sensitive, there is a need for fast and efficient detection of various
+sources. Gravitational wave bursts are a family of signals that remain
+unmodeled, therefore, they have a low detection sensitivity to standard
+detection schemes. This report examines the use of Generative Adversarial
+Networks as a detection pipeline for gravitational wave burst signals. BurstGAN
+is trained to detect three classes of burst signals: sine-Gaussian, Ring-downs
+and white-noise bursts contained in white Gaussian noise. The resulting
+sensitivity curves show that sine-Gaussian and Ring-downs are confidently
+detectable at SNRs > while white-noise bursts require SNRs of >.~\chris{we'll
+fix the abstract at the end}
+%\begin{description} \item[Usage] Secondary publications and information
+%retrieval purposes.  \item[Structure] You may use the \texttt{description}
+%environment to structure your abstract; use the optional argument of the
+%\verb+\item+ command to give the category of each item.  \end{description}
 \end{abstract}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Introduction}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-The detections of gravitational waves by Advanced Laser Interferometer Gravitational wave Observatory (aLIGO) and Advanced Virgo [1–5], have opened up new avenues to explore the Universe.
-Astrophysical sources of transient gravitational waves include the merging of compact binary star systems like black holes and/or neutron stars [6], core-collapse supernova [7], pulsar glitches [8] and other events involving accelerating massive objects.
-Gravitational wave bursts (GWBs) are an exciting area of research as the emissions process of such waves is not well understood.
-The waveforms often depend on complicated orbital dynamics and equations of state which limit the sensitivity on searching for burst sources.
-Typically, the duration of burst signals are short with amplitudes that can be greater than the detector noise.
-Burst searches look for excess power contained in a time-frequency plot and rely on consistent arrival times, waveform shapes and frequencies between detectors.
-We focus on utilising an unsupervised form of machine learning called Generative Adversarial Networks [9] as a generalised GW transient search.
-A two detector case is considered such that the signals retain their form between detections and a defined time delay between detections relating to the sky orientation of the source.
+\begin{itemize}
+\item Need to introduce GWs - the current state of the field e.g. detections
+and LVC papers
+\item Introduce burst searches - what's the point of burst searches - lots of references
+\item Discuss the family of burst waveforms currently used and why - not in detail, just
+an introduction
+\item Introduce ML techniques in GWs - lots of references
+\item What this paper does on GANs in 1 paragraph
+\item Describe the structure of the paper 
+\end{itemize}
 
-\section{Background}
-Generative adversarial networks (GANs) have seen considerable success in recent years as a generative machine learning model.
-GANs work to train two competing neural networks, consisting of a discriminator D that is trained to distinguish between real and fake data and a generator G that produces synthetic reproductions of the real data.
-The original GAN method has G perform a mapping from an input noise vector z to its representation of the data and D maps its input x to a probability [0,1] that the input came form either the training data or G.
-Both networks compete in turn to trick the other and after training, G produces accurate distributions and D can detect forgeries.
-During training, D s given a batch of samples that contains one half real data (labelled as 1) and one half fake data (labelled as 0) which it then makes predictions on.
-The loss on D is calculated by comparing its predictions to the labels through a defined loss function.
-(talk about binary cross entropy).
-The training process of a GAN alternatively updates the weights of the D and G based on information on its competitors loss function.
-This loss of D is used to update the weights of G to produce more realistic samples of the input distribution, the loss of G encourages the D to update its classification abilities.
-Both networks compete in a minimax game that is tied to a value function V (D, G) which G is trying minimise and D is trying to maximise:
+The detections of gravitational waves by Advanced Laser Interferometer
+Gravitational wave Observatory (aLIGO) and Advanced Virgo [1–5], have opened up
+new avenues to explore the Universe. Astrophysical sources of transient
+gravitational waves include the merging of compact binary star systems like
+black holes and/or neutron stars [6], core-collapse supernova [7], pulsar
+glitches [8] and other events involving accelerating massive objects.
+Gravitational wave bursts (GWBs) are an exciting area of research as the
+emissions process of such waves is not well understood. The waveforms often
+depend on complicated orbital dynamics and equations of state which limit the
+sensitivity on searching for burst sources. Typically, the duration of burst
+signals are short with amplitudes that can be greater than the detector noise.
+Burst searches look for excess power contained in a time-frequency plot and
+rely on consistent arrival times, waveform shapes and frequencies between
+detectors. We focus on utilising an unsupervised form of machine learning
+called Generative Adversarial Networks [9] as a generalised GW transient
+search. A two detector case is considered such that the signals retain their
+form between detections and a defined time delay between detections relating to
+the sky orientation of the source.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Generative Adversarial Networks}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{itemize}
+\item Describe GANs in detail but really focus on the fact that the reader is a
+GW data analyst - not a computer scientist
+\item A diagram would be very useful
+\item Do not discuss our specific case here - just stay general
+\item A subsection on the specific advanced flavour of GAN that you are using
+here - motivate this choice.
+\end{itemize}
+
+Generative adversarial networks (GANs) have seen considerable success in recent
+years as a generative machine learning model. GANs work to train two competing
+neural networks, consisting of a discriminator D that is trained to distinguish
+between real and fake data and a generator G that produces synthetic
+reproductions of the real data. The original GAN method has G perform a mapping
+from an input noise vector z to its representation of the data and D maps its
+input x to a probability [0,1] that the input came form either the training
+data or G. Both networks compete in turn to trick the other and after training,
+G produces accurate distributions and D can detect forgeries. During training,
+D s given a batch of samples that contains one half real data (labelled as 1)
+and one half fake data (labelled as 0) which it then makes predictions on. The
+loss on D is calculated by comparing its predictions to the labels through a
+defined loss function. (talk about binary cross entropy). The training process
+of a GAN alternatively updates the weights of the D and G based on information
+on its competitors loss function. This loss of D is used to update the weights
+of G to produce more realistic samples of the input distribution, the loss of G
+encourages the D to update its classification abilities. Both networks compete
+in a minimax game that is tied to a value function V (D, G) which G is trying
+minimise and D is trying to maximise:
+
 \begin{multline}
@@
 \end{multline}
-In theory this will eventually lead to the local Nash equilibrium [18] where both neural networks are trained optimally.
-In practice, however, GANs are notoriously difficult to train.
-Such difficulties include: Non-convergence, where the model parameters oscillate and the loss never converges.
-Mode collapse where G produces a limited diversity of samples, and the diminishing gradient problem when applying the gradient descent algorithm to a non-continuous function.
-\\ To overcome some of these difficulties [blank] proposed adding structure to the latent space by providing G with a class label.
-This has the effect of making a point in latent space conditional on a provided class.
-[blank] extends this idea further by requiring D to output a probability of the data belonging to each class.
 
+In theory this will eventually lead to the local Nash equilibrium [18] where
+both neural networks are trained optimally. In practice, however, GANs are
+notoriously difficult to train. Such difficulties include: Non-convergence,
+where the model parameters oscillate and the loss never converges. Mode
+collapse where G produces a limited diversity of samples, and the diminishing
+gradient problem when applying the gradient descent algorithm to a
+non-continuous function.  \\ To overcome some of these difficulties [blank]
+proposed adding structure to the latent space by providing G with a class
+label. This has the effect of making a point in latent space conditional on a
+provided class. [blank] extends this idea further by requiring D to output a
+probability of the data belonging to each class.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Method}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{itemize}
+\item Need to introduce the scheme you propose to use
+\item A paragraph or subsection on the data generation being very clear on all
+5 waveform models and the prior parameter space for each
+\item A subsection on the design of the network architecture
+\item A subsection on the "box" and why we implement it
+\item A subsection on the training of the network - give rough timings and rule
+of thumb decisions made
+\item Do not discuss the results here 
+\end{itemize}
+
 To simulate gravitational burst sources, three GW signal morphologies, spanning a range of frequencies, duration and time delays were tested. The three families are:\\
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Results}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{itemize}
+\item Begin by outlining the type of results you will be presenting
+\item A subsection on the general quality of generated waveforms - we may need
+to have overlaps between generated wavefoms and training data (maybe)
+\item A subsection on the descriminator - maybe a confusion matrix?
+\item a subsection on the latent space varaition within each class - fixed
+class, sliding in latent space.
+\item A subsection on the class space variation - fixed latent space and
+sliding in the class space.
+\item A final subsection on the general waveform model based on random latent
+and class space locations.
+\item Make no conclusions.
+\end{itemize}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Conclusions}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{itemize}
+\item Summarise the paper
+\item Dedicate a paragraph to each of the key results discussed in the previous
+section
+\item Have at least one paragraph on the future directions of this work
+\item Conclude with a positive paragrpah about the potential uses and impact of
+the approach.
+\end{itemize}
 

### 2020-02-26 GAN_paper.tex
new file:   GAN_paper.tex

--- 2020-02-17 Paper%20draft/apssamp.tex
@@
 \usepackage{acronym}
+\usepackage{comment}
 %\usepackage{hyperref}% add hypertext capabilities
@@
 \newcommand{\chris}[1]{\textbf{\textcolor{green}{CHRIS: #1}}}
+\newcommand{\michael}[1]{\textbf{\textcolor{orange}{MICHAEL: #1}}}
 
@@
 
+Gravitational-wave (GW) astronomy is now an established field, starting with the first detection of a binary black hole merger \cite{} on September 2015.
+Following this, the first and second observations runs (O1 and O2) of Advanced LIGO and Advanced Virgo reported several more mergers \cite{}.
+On August 2017 a binary neutron star merger was observed alongside its electron-magnetic counterpart for the first time, giving rise to multimessenger gravitational wave astronomy.
+
+GW bursts are transient signals of typically short duration ($<$ 1s) whose waveforms are not accurately modelled or are complex to re-produce.
+Astrophysical sources for such transients include: \jordan{should i include a list of these?}.
+Since GW bursts are un-modelled they are not sensitive to template based detection schemes such as matched-filtering \cite{}, instead, detection involves distinguishing the signal from detector noise.
+This is only possible if the detector noise is well characterised and the candidate signal can be differentiated from system or environmental glitches.
+As such, GW burst searches rely on an astrophysical burst signature appearing in multiple detectors.
+\jordan{how deep should i go?
+with coherent WaveBurst etc?}
+
+Many GW burst algorithms \cite{cite the shit outta this} are tested and tuned using model waveforms that may or may not have astrophysical significance but have easy to define parameters and share characteristics of real bursts that is enough to simulate coincident non-stationary deviations between detectors.
+Such waveforms may have long-duration, short bandwidth (ringdowns), long-duration, large bandwidth (inspirals) and many algorithms make use of sine-Gaussians: a Gaussian modulated sine wave that is characterised by it's central frequency and narrow bandwidth.
+This makes it a great tool for diagnosing LIGOs sensitivity to frequency.
+
+We aim to explore the use of machine learning in generating and interpreting these mock GW burst signals.
+Neural networks have shown to replicate the sensitivities of matched filtering in GW detection \cite{} and rapid parameter estimation \cite{}, however these methods have primarily been focused on binary black hole signals and have not yet expanded to burst examples.
+A subset of deep learning that has seen fruitful development in recent years \cite{} is Generative Adversarial Networks (GANs).
+These unsupervised algorithms learn patterns in a given training data set using an adversarial process.
+The generations from GANs are state-of-the-art in fields such as high quality image fidelity, image and text-to-image translation and video prediciton \cite{} and there is notable works on time series generations /cite.
+
+\begin{comment}
 The detections of gravitational waves by Advanced Laser Interferometer
@@
 the sky orientation of the source.
+\end{comment}
 

### 2020-02-26 Paper_draft/GAN_paper.tex
Update GAN_paper.tex

--- 2020-02-26 GAN_paper.tex
@@
 \begin{abstract}
-As the field of gravitational wave astronomy expands and as detectors become
-more sensitive, there is a need for fast and efficient detection of various
-sources. Gravitational wave bursts are a family of signals that remain
-unmodeled, therefore, they have a low detection sensitivity to standard
-detection schemes. This report examines the use of Generative Adversarial
-Networks as a detection pipeline for gravitational wave burst signals. BurstGAN
-is trained to detect three classes of burst signals: sine-Gaussian, Ring-downs
-and white-noise bursts contained in white Gaussian noise. The resulting
-sensitivity curves show that sine-Gaussian and Ring-downs are confidently
-detectable at SNRs > while white-noise bursts require SNRs of >.~\chris{we'll
+f >.~\chris{we'll
 fix the abstract at the end}
@@
 
-Gravitational-wave (GW) astronomy is now an established field, starting with the first detection of a binary black hole merger \cite{} on September 2015.
-Following this, the first and second observations runs (O1 and O2) of Advanced LIGO and Advanced Virgo reported several more mergers \cite{}.
-On August 2017 a binary neutron star merger was observed alongside its electron-magnetic counterpart for the first time, giving rise to multimessenger gravitational wave astronomy.
+Gravitational-wave (GW) astronomy is now an established field, starting with the first detection 
+of a binary black hole merger \cite{} on September 2015. Following this, the first and second 
+observations runs (O1 and O2) of Advanced LIGO and Advanced Virgo reported several more mergers \cite{}. 
+On August 2017 a binary neutron star merger was observed alongside its electron-magnetic counterpart for 
+the first time, giving rise to multimessenger gravitational wave astronomy.
 
-GW bursts are transient signals of typically short duration ($<$ 1s) whose waveforms are not accurately modelled or are complex to re-produce.
-Astrophysical sources for such transients include: \jordan{should i include a list of these?}.
-Since GW bursts are un-modelled they are not sensitive to template based detection schemes such as matched-filtering \cite{}, instead, detection involves distinguishing the signal from detector noise.
-This is only possible if the detector noise is well characterised and the candidate signal can be differentiated from system or environmental glitches.
-As such, GW burst searches rely on an astrophysical burst signature appearing in multiple detectors.
-\jordan{how deep should i go?
-with coherent WaveBurst etc?}
+GW bursts are transient signals of typically short duration ($<$ 1s) whose waveforms are not accurately 
+modelled or are complex to re-produce. Astrophysical sources for such transients include:
+\jordan{should i include a list of these?}. Since GW bursts are un-modelled they are not sensitive to 
+template based detection schemes such as matched-filtering \cite{}, instead, detection involves distinguishing 
+the signal from detector noise. This is only possible if the detector noise is well characterised and the candidate 
+signal can be differentiated from system or environmental glitches. As such, GW burst searches rely on an astrophysical 
+burst signature appearing in multiple detectors. \jordan{how deep should i go? with coherent WaveBurst etc?}
 
-Many GW burst algorithms \cite{cite the shit outta this} are tested and tuned using model waveforms that may or may not have astrophysical significance but have easy to define parameters and share characteristics of real bursts that is enough to simulate coincident non-stationary deviations between detectors.
-Such waveforms may have long-duration, short bandwidth (ringdowns), long-duration, large bandwidth (inspirals) and many algorithms make use of sine-Gaussians: a Gaussian modulated sine wave that is characterised by it's central frequency and narrow bandwidth.
-This makes it a great tool for diagnosing LIGOs sensitivity to frequency.
+Many GW burst algorithms \cite{cite the shit outta this} are tested and tuned using model waveforms that may or may not 
+have astrophysical significance but have easy to define parameters and share characteristics of real bursts that is enough
+to simulate coincident non-stationary deviations between detectors. Such waveforms may have long-duration,
+short bandwidth (ringdowns), long-duration, large bandwidth (inspirals) and many algorithms make use of sine-Gaussians: 
+a Gaussian modulated sine wave that is characterised by it's central frequency and narrow bandwidth. This makes it a great
+tool for diagnosing LIGOs sensitivity to frequency.
 
 We aim to explore the use of machine learning in generating and interpreting these mock GW burst signals. 
-Neural networks have shown to replicate the sensitivities of matched filtering in GW detection \cite{} and rapid parameter estimation \cite{}, however these methods have primarily been focused on binary black hole signals and have not yet expanded to burst examples.
-A subset of deep learning that has seen fruitful development in recent years \cite{} is Generative Adversarial Networks (GANs).
-These unsupervised algorithms learn patterns in a given training data set using an adversarial process.
-The generations from GANs are state-of-the-art in fields such as high quality image fidelity, image and text-to-image translation and video prediciton \cite{} and there is notable works on time series generations /cite.
+Neural networks have shown to replicate the sensitivities of matched filtering in GW detection \cite{} and 
+rapid parameter estimation \cite{}, however these methods have primarily been focused on binary black hole 
+signals and have not yet expanded to burst examples. A subset of deep learning that has seen fruitful development 
+in recent years \cite{} is Generative Adversarial Networks (GANs). These unsupervised algorithms learn patterns in
+a given training data set using an adversarial process. The generations from GANs are state-of-the-art in fields such 
+as high quality image fidelity, image and text-to-image translation and video prediciton \cite{} and there is notable
+works on time series generations /cite.
 

### 2020-03-05 Paper_draft/GAN_paper.tex
Update GAN_paper.tex

--- 2020-02-26 GAN_paper.tex
@@
 
-\usepackage{graphicx}% Include figure files
+\usepackage[draft]{graphicx}% Include figure files
+\graphicspath{images}
 \usepackage{dcolumn}% Align table columns on decimal point
@@
 \usepackage{comment}
+\usepackage{standalone}
+\usepackage{tikz}
+\usepackage{caption}
+\usepackage{subcaption}
+\usepackage{amssymb}
+\usepackage{pifont}
 %\usepackage{hyperref}% add hypertext capabilities
@@
 
+\begin{comment}
+
 \begin{itemize}
@@
 \end{itemize}
+\end{comment}
 
@@
 
+\begin{comment}
 \begin{itemize}
@@
 \end{itemize}
+\end{comment}
+
+\begin{figure}
+    \centering
+    \begin{subfigure}[t]{0.45\columnwidth}
+        \centering
+        \input{GAN_diagram_vertical}%     without .tex extension
+        \caption{Vanilla GAN}
+        \label{fig:GAN}
+    \end{subfigure}\hfill
+    \begin{subfigure}[t]{0.55\columnwidth}
+        \centering
+        \input{ACGAN_diagram_vertical}%     without .tex extension
+        \caption{AC-GAN}
+        \label{fig:ACGAN}
+    \end{subfigure}\hfill
+    \caption{Comparison of the original GAN method and the Auxiliary Conditional-GAN method }
+\end{figure}
 
@@
 years as a generative machine learning model. GANs work to train two competing
-neural networks, consisting of a discriminator D that is trained to distinguish
-between real and fake data and a generator G that produces synthetic
-reproductions of the real data. The original GAN method has G perform a mapping
-from an input noise vector z to its representation of the data and D maps its
-input x to a probability [0,1] that the input came form either the training
-data or G. Both networks compete in turn to trick the other and after training,
-G produces accurate distributions and D can detect forgeries. During training,
-D s given a batch of samples that contains one half real data (labelled as 1)
+neural networks, consisting of a discriminator \textbf{D} that is trained to distinguish
+between real and fake data and a generator \textbf{G} that produces synthetic
+reproductions of the real data. The GAN method has \textbf{G} perform a mapping
+from an input noise vector \textbf{z} to its representation of the data and \textbf{D} maps its
+input \textbf{x} to a probability that the input came form either the training
+data or \textbf{G}.  During training, \textbf{D} is given a batch of samples that contains one half real data (labelled as 1)
 and one half fake data (labelled as 0) which it then makes predictions on. The
-loss on D is calculated by comparing its predictions to the labels through a
-defined loss function. (talk about binary cross entropy). The training process
-of a GAN alternatively updates the weights of the D and G based on information
-on its competitors loss function. This loss of D is used to update the weights
-of G to produce more realistic samples of the input distribution, the loss of G
-encourages the D to update its classification abilities. Both networks compete
-in a minimax game that is tied to a value function V (D, G) which G is trying
-minimise and D is trying to maximise:
+loss for \textbf{D} is calculated by comparing its predictions to the labelled data through the binary cross-entropy function. The training process
+of a GAN alternatively updates the weights of the \textbf{D} and \textbf{G} based on information
+on its competitors loss function. This loss of \textbf{D} is used to update the weights
+of \textbf{G} to produce more realistic samples of the input distribution, the loss of G
+encourages \textbf{D} to update its classification abilities. Both networks compete
+in a minimax game that is tied to a value function V (D, G) which \textbf{G} is trying
+minimise and \textbf{D} is trying to maximise:
 
@@
 \end{multline}
-
+\subsection{Auxiliary conditional GANs}
 In theory this will eventually lead to the local Nash equilibrium [18] where
@@
 collapse where G produces a limited diversity of samples, and the diminishing
-gradient problem when applying the gradient descent algorithm to a
+gradient problem when applying gradient descent to a
 non-continuous function.  \\ To overcome some of these difficulties [blank]
@@
 
+\begin{figure}
+    \centering
+    \includegraphics[scale=0.1]{images/real_fake_sample.png}
+    \caption{Caption}
+    \label{fig:my_label}
+\end{figure}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+\Appendix
+
+\begin{table*}[t]
+\begin{center}
+\begin{tabular}{ r  l  l  l  l  l  l}  
+ \hline
+ Operation & Kernel & Strides & Output Shape & BN & Dropout & Activation \\ 
+ \hline
+ G(\textbf{z}): Input \textbf{z} $\sim$ Normal(0,0.02) & N/A & N/A & (100,) & \ding{55} & 0 & N/A \\  
+ Dense & N/A & N/A & (32768,) & \ding{55} & 0 & ReLU \\  
+ Class input c & N/A & N/A & (1,) & \ding{55} & 0 & N/A \\
+ Embedding & N/A & N/A & (1, 120) & \ding{55} & 0 & N/A \\
+ Dense & N/A & N/A & (1,128) & \ding{55} & 0 & ReLU \\ 
+ Reshape \textbf{z} & N/A & N/A & (128, 256) & \ding{55} & 0 & N/A \\
+ Reshape c & N/A & N/A & (128, 1) & \ding{55} & 0 & N/A \\
+ Concatenate & N/A & N/A & (128, 257) & \ding{55} & 0 & N/A \\
+ Reshape & N/A & N/A & (64, 514) & \ding{55} & 0 & N/A \\
+ Transposed Convolution & 18x1 & 2 & (256, 256) & \ding{51} & 0 & ReLU\\
+ Transposed Convolution & 18x1 & 2 & (512, 128) & \ding{55} & 0 & ReLU\\
+ Transposed Convolution & 18x1 & 2 & (1024, 64) & \ding{55} & 0 & ReLU\\
+ Convolution & 18x1 & 1 & (1024, 1) & \ding{55} & 0 & Tanh \\
+ Sky input & N/A & N/A & (3,) & \ding{55} & 0 & N/A \\
+ Concatenate & N/A & N/A & (1027,) &  \ding{55} & 0 & N/A \\
+ Lambda & N/A & N/A & (1024, 2) & \ding{55} & 0 & N/A \\
+ D(\textbf{x}): Input \textbf{x} & N/A & N/A & (1024, 2) & \ding{55} & 0 & N/A \\
+ Convolution & 14x1 & 2 & (512, 64) & \ding{55} & 0.5 & Leaky ReLU \\
+ Convolution & 14x1 & 2 & (256, 128) & \ding{55} & 0.5 & Leaky ReLU \\
+ Convolution & 14x1 & 2 & (128, 256) & \ding{55} & 0.5 & Leaky ReLU \\
+ Convolution & 14x1 & 2 & (64, 512) & \ding{55} & 0.5 & Leaky ReLU \\
+ Flatten & N/A & N/A & (32768,) & \ding{55} & 0 & N/A \\
+ Dense & N/A & N/A & (1,) & \ding{55} & 0 & Sigmoid \\
+ Dense & N/A & N/A & (5,) & \ding{55} & 0 & Softmax \\
+ \hline
+ Optimizer & \multicolumn{6}{l}{Adam($\alpha$ = 0.0002, $\beta_{1}$ = 0.5)} \\
+ Batch size & \multicolumn{6}{l}{100}  \\
+ Iterations & \multicolumn{6}{l}{60000}  \\
+ Leaky ReLU slope & \multicolumn{6}{l}{0.2} \\
+ Weight initialization & \multicolumn{6}{l}{Gaussian($\mu$ = 0, $\sigma$ = 0.02)} \\
+ Generator loss & \multicolumn{6}{l}{Binary cross-entropy} \\
+ Discriminator loss & \multicolumn{6}{l}{Binary cross-entropy \& sparse categorical cross-entropy} \\ 
+ \hline
+\end{tabular}
+\end{center}
+\end{table*}
+
 \end{document}

### 2020-03-19 Paper_draft/IOPLaTeXGuidelines.tex
Add files via upload

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%    INSTITUTE OF PHYSICS PUBLISHING                                   %
%                                                                      %
%   `Preparing an article for publication in an Institute of Physics   %
%    Publishing journal using LaTeX'                                   %
%                                                                      %
%    LaTeX source code `ioplau2e.tex' used to generate `author         %
%    guidelines', the documentation explaining and demonstrating use   %
%    of the Institute of Physics Publishing LaTeX preprint files       %
%    `iopart.cls, iopart12.clo and iopart10.clo'.                      %
%                                                                      %
%    `ioplau2e.tex' itself uses LaTeX with `iopart.cls'                %
%                                                                      %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
% First we have a character check
%
% ! exclamation mark    " double quote  
% # hash                ` opening quote (grave)
% & ampersand           ' closing quote (acute)
% $ dollar              % percent       
% ( open parenthesis    ) close paren.  
% - hyphen              = equals sign
% | vertical bar        ~ tilde         
% @ at sign             _ underscore
% { open curly brace    } close curly   
% [ open square         ] close square bracket
% + plus sign           ; semi-colon    
% * asterisk            : colon
% < open angle bracket  > close angle   
% , comma               . full stop
% ? question mark       / forward slash 
% \ backslash           ^ circumflex
%
% ABCDEFGHIJKLMNOPQRSTUVWXYZ 
% abcdefghijklmnopqrstuvwxyz 
% 1234567890
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\documentclass[12pt]{iopart}
\newcommand{\gguide}{{\it Preparing graphics for IOP Publishing journals}}
%Uncomment next line if AMS fonts required
%\usepackage{iopams}  
\begin{document}

\title[Author guidelines for IOP Publishing journals in  \LaTeXe]{How to prepare and submit an article for 
publication in an IOP Publishing journal using \LaTeXe}

\author{Content \& Services Team}

\address{IOP Publishing, Temple Circus, Temple Way, Bristol BS1 6HG, UK}
\ead{submissions@iop.org}
\vspace{10pt}
\begin{indented}
\item[]August 2017
\end{indented}

\begin{abstract}
This document describes the  preparation of an article using \LaTeXe\ and 
\verb"iopart.cls" (the IOP Publishing \LaTeXe\ preprint class file).
This class file is designed to help 
authors produce preprints in a form suitable for submission to any of the
journals listed in table~\ref{jlab1} on the next page.  You are not obliged to use this class file---we accept
submissions using all common \LaTeX\ class and style files.  The \verb"iopart.cls"
class file is supplied merely as a convenience for those authors who find it useful.
This document gives both general advice that applies whatever class file you use, and specific advice
that applies if you choose to use \verb"iopart.cls".

We also accept submissions in Word format.  See elsewhere on this site for guidelines on Word submissions.

If you have any queries about this document or any aspect of preparing your article for submission please contact us at the e-mail address given above.
\end{abstract}

%
% Uncomment for keywords
%\vspace{2pc}
%\noindent{\it Keywords}: XXXXXX, YYYYYYYY, ZZZZZZZZZ
%
% Uncomment for Submitted to journal title message
%\submitto{\JPA}
%
% Uncomment if a separate title page is required
%\maketitle
% 
% For two-column output uncomment the next line and choose [10pt] rather than [12pt] in the \documentclass declaration
%\ioptwocol
%

\section{Introduction: file preparation and submission}

The \verb"iopart" \LaTeXe\ article class file is provided to help authors prepare articles for submission to IOP Publishing journals.
  This document gives advice on preparing your submission, and specific instructions on how to use \verb"iopart.cls" to follow this advice.  You
  do not have to use \verb"iopart.cls"; articles prepared using any other common class and style files can also be submitted.
    It is not necessary to mimic the appearance of a published article.

The advice
on \LaTeX\ file preparation in this document applies to
the journals listed in table~\ref{jlab1}.  If your journal is not listed please go to the journal website via \verb"http://iopscience.iop.org/journals" for specific
submission instructions.

\begin{table}
\caption{\label{jlab1}Journals to which this document applies, and macros for the abbreviated journal names in {\tt iopart.cls}. Macros for other journal titles are listed in appendix\,A.}
\footnotesize
\begin{tabular}{@{}llll}
\br
Short form of journal title&Macro name&Short form of journal title&Macro name\\
\mr
2D Mater.&\verb"\TDM"&Mater. Res. Express&\verb"\MRE"\\
Biofabrication&\verb"\BF"&Meas. Sci. Technol.$^c$&\verb"\MST"\\
Bioinspir. Biomim.&\verb"\BB"&Methods Appl. Fluoresc.&\verb"\MAF"\\
Biomed. Mater.&\verb"\BMM"&Modelling Simul. Mater. Sci. Eng.&\verb"\MSMSE"\\
Class. Quantum Grav.&\verb"\CQG"&Nucl. Fusion&\verb"\NF"\\
Comput. Sci. Disc.&\verb"\CSD"&New J. Phys.&\verb"\NJP"\\
Environ. Res. Lett.&\verb"\ERL"&Nonlinearity$^{a,b}$&\verb"\NL"\\
Eur. J. Phys.&\verb"\EJP"&Nanotechnology&\verb"\NT"\\
Inverse Problems&\verb"\IP"&Phys. Biol.$^c$&\verb"\PB"\\
J. Breath Res.&\verb"\JBR"&Phys. Educ.$^a$&\verb"\PED"\\
J. Geophys. Eng.$^d$&\verb"\JGE"&Physiol. Meas.$^{c,d,e}$&\verb"\PM"\\
J. Micromech. Microeng.&\verb"\JMM"&Phys. Med. Biol.$^{c,d,e}$&\verb"\PMB"\\
J. Neural Eng.$^c$&\verb"\JNE"&Plasma Phys. Control. Fusion&\verb"\PPCF"\\
J. Opt.&\verb"\JOPT"&Phys. Scr.&\verb"\PS"\\
J. Phys. A: Math. Theor.&\verb"\jpa"&Plasma Sources Sci. Technol.&\verb"\PSST"\\
J. Phys. B: At. Mol. Opt. Phys.&\verb"\jpb"&Rep. Prog. Phys.$^{e}$&\verb"\RPP"\\
J. Phys: Condens. Matter&\verb"\JPCM"&Semicond. Sci. Technol.&\verb"\SST"\\
J. Phys. D: Appl. Phys.&\verb"\JPD"&Smart Mater. Struct.&\verb"\SMS"\\
J. Phys. G: Nucl. Part. Phys.&\verb"\jpg"&Supercond. Sci. Technol.&\verb"\SUST"\\
J. Radiol. Prot.$^a$&\verb"\JRP"&Surf. Topogr.: Metrol. Prop.&\verb"\STMP"\\
Metrologia&\verb"\MET"&Transl. Mater. Res.&\verb"\TMR"\\
\br
\end{tabular}\\
$^{a}$UK spelling is required; $^{b}$MSC classification numbers are required; $^{c}$titles of articles are required in journal references; $^{d}$Harvard-style references must be used (see section \ref{except}); $^{e}$final page numbers of articles are required in journal references.

\end{table}
\normalsize

Any special submission requirements for the journals are indicated with footnotes in table~\ref{jlab1}.
Journals which require references in a particular format will need special care if you are using BibTeX, and you might need to use a \verb".bst" file
that gives slightly non-standard output in order to supply any extra information required.  It is not
necessary to give references in the exact style of references used in published articles, as long as all of
the required information is present.

Also note that there is an incompatibility
between \verb"amsmath.sty" and \verb"iopart.cls" which cannot be completely worked around.  If your article relies
on commands in \verb"amsmath.sty" that are not available in \verb"iopart.cls", you may wish to consider using a different
class file.

Whatever journal you are submitting to, please look at recent published articles (preferably
articles in your subject area) to familiarize yourself with the features of the journal.  We do not demand
that your \LaTeX\ file closely resembles a published article---a generic `preprint' appearance of the sort
commonly seen on \verb"arXiv.org" is fine---but your submission should be presented
in a way that makes it easy for the referees to form an opinion of whether it is suitable for the journal.
The generic advice in this document---on what to include in an abstract, how best to present complicated
mathematical expressions, and so on---applies whatever class file you are using.

\subsection{What you will need to supply}
Submissions to our journals are handled via the ScholarOne web-based submission system.  When you submit
a new article to us you need only submit a PDF of your article.  When you submit a revised version,
we ask you to submit the source files as well.  Upon acceptance for publication we will use the source files to produce a proof of your article in the journal style.

\subsubsection{Text.}When you send us the source files for a revised version of your submission,
you should send us the \LaTeX\ source code of your paper with all figures read in by 
the source code (see section \ref{figinc}).  Articles can be prepared using almost any version of \TeX\ or \LaTeX{},
not just \LaTeX\ with the class file \verb"iopart.cls".  You may split your \LaTeX\ file into several parts, but please show
which is the `master' \LaTeX\ file that reads in all of the other ones by naming it appropriately.  The `master'
\LaTeX\ file must read in all other \LaTeX\ and figure files from the current directory.  {\it Do not read in files from a different directory, e.g. \verb"\includegraphics{/figures/figure1.eps}" or
\verb"\include{../usr/home/smith/myfiles/macros.tex}"---we store submitted files
all together in a single directory with no subdirectories}.
\begin{itemize}
\item {\bf Using \LaTeX\ packages.} Most \LaTeXe\ packages can be used if they are 
available in common distributions of \LaTeXe; however, if it is essential to use 
a non-standard package then any extra files needed to process the article must 
also be supplied.  Try to avoid using any packages that manipulate or change the standard
\LaTeX\ fonts: published articles use fonts in the Times family, but we prefer that you 
use \LaTeX\ default Computer Modern fonts in your submission.  The use of \LaTeX\ 2.09, and of plain
\TeX\ and variants such as AMSTeX is acceptable, but a complete PDF of your submission should be supplied in these cases.
\end{itemize}
\subsubsection{Figures.} Figures should ideally be included in an article as encapsulated PostScript files
(see section \ref{figinc}) or created using standard \LaTeX\ drawing commands. 
 Please name all figure files using the guidelines in section \ref{fname}.
We accept submissions that use pdf\TeX\ to include
PDF or bitmap figures, but please ensure that you send us a PDF that uses PDF version 1.4 or lower
(to avoid problems in the ScholarOne system).
You can do this by putting \verb"\pdfminorversion=4" at the very start of your TeX file.

\label{fig1}All figures should be included within the body of the text 
at an appropriate point or grouped together with their captions at the end of the article. A standard graphics inclusion package such as \verb"graphicx" should be used for figure inclusion, and the package should be declared in the usual
way, for example with \verb"\usepackage{graphicx}", after the \verb"\documentclass" command.
Authors should avoid using special effects generated by including verbatim
PostScript code in the submitted \LaTeX\ file. Wherever possible, please try to use standard \LaTeX\ tools 
and packages.

\subsubsection{References.\label{bibby}}
You can produce your bibliography in the standard \LaTeX\ way using the \verb"\bibitem" command. Alternatively
you can use BibTeX: our preferred  \verb".bst" styles are:

\begin{itemize}
\item For the numerical (Vancouver) reference style we recommend that authors use 
 \verb"unsrt.bst"; this does not quite follow the style of published articles in our
 journals but this is not a problem.  Alternatively \verb"iopart-num.bst" created by Mark A Caprio
 produces a reference style that closely matches that in published articles.  The file is available from
\verb"http://ctan.org/tex-archive/biblio/bibtex/contrib/iopart-num/" .
\item For alphabetical (Harvard) style references we recommend that authors use the \verb"harvard.sty"
in conjunction with the \verb"jphysicsB.bst" BibTeX style file.  These, and accompanying documentation, can be downloaded
from \penalty-10000 \verb"http://www.ctan.org/tex-archive/macros/latex/contrib/harvard/".
Note that the \verb"jphysicsB.bst" bibliography style does not include article titles
in references to journal articles.
To include the titles of journal articles you can use the style \verb"dcu.bst" which is included
in the \verb"harvard.sty" package.  The output differs a little from the final journal reference
style, but all of the necessary information is present and the reference list will be formatted
into journal house style as part of the production process if your article is accepted for publication.
\end{itemize}

\noindent Please make sure that you include your \verb".bib" bibliographic database file(s) and any 
\verb".bst" style file(s) you have used.

\subsection{\label{copyright}Copyrighted material and ethical policy} If you wish to make use of previously published material for which you do not own the copyright then you must seek permission from the copyright holder, usually both the author and the publisher.  It is your responsibility to obtain copyright permissions and this should be done prior to submitting your article. If you have obtained permission, please provide full details of the permission granted---for example, copies of the text of any e-mails or a copy of any letters you may have received. Figure captions must include an acknowledgment of the original source of the material even when permission to reuse has been obtained.  Please read our ethical policy before writing your article.

\subsection{Naming your files}
\subsubsection{General.}
Please name all your files, both figures and text, as follows:
\begin{itemize}
\item Use only characters from the set a to z, A to Z, 0 to 9 and underscore (\_).
\item Do not use spaces or punctuation characters in file names.
\item Do not use any accented characters such as
\'a, \^e, \~n, \"o.
\item Include an extension to indicate the file type (e.g., \verb".tex", \verb".eps", \verb".txt", etc).
\item Use consistent upper and lower case in filenames and in your \LaTeX\ file.
If your \LaTeX\ file contains the line \verb"\includegraphics{fig1.eps}" the figure file must be called
\verb"fig1.eps" and not \verb"Fig1.eps" or \verb"fig1.EPS".  If you are on a Unix system, please ensure that
there are no pairs of figures whose names differ only in capitalization, such as \verb"fig_2a.eps" and \verb"fig_2A.eps",
as Windows systems will be unable to keep the two files in the same directory.
\end{itemize}
When you submit your article files, they are manipulated
and copied many times across multiple databases and file systems. Including non-standard
characters in your filenames will cause problems when processing your article.
\subsubsection{\label{fname}Naming your figure files.} In addition to the above points, please give each figure file a name which indicates the number of the figure it contains; for example, \verb"figure1.eps", \verb"figure2a.eps", etc. If the figure file contains a figure with multiple parts, for example figure 2(a) to 2(e), give it a name such as \verb"figure2a_2e.eps", and so forth.
\subsection{How to send your files}
Please send your submission via the ScholarOne submission system.  Go to the journal home
page, and use the `Submit an article' link on the right-hand side.

\section{Preparing your article}

\subsection{Sample coding for the start of an article}
\label{startsample}
The code for the start of a title page of a typical paper in the \verb"iopart.cls" style might read:
%%begin novalidate
\small\begin{verbatim}
\documentclass[12pt]{iopart}
\begin{document}
\title[The anomalous magnetic moment of the 
neutrino]{The anomalous magnetic moment of the 
neutrino and its relation to the solar neutrino problem}

\author{P J Smith$^1$, T M Collins$^2$, 
R J Jones$^3$\footnote{Present address:
Department of Physics, University of Bristol, Tyndalls Park Road, 
Bristol BS8 1TS, UK.} and Janet Williams$^3$}

\address{$^1$ Mathematics Faculty, Open University, 
Milton Keynes MK7~6AA, UK}
\address{$^2$ Department of Mathematics, 
Imperial College, Prince Consort Road, London SW7~2BZ, UK}
\address{$^3$ Department of Computer Science, 
University College London, Gower Street, London WC1E~6BT, UK}
\ead{williams@ucl.ac.uk}

\begin{abstract}
...
\end{abstract}
\keywords{magnetic moment, solar neutrinos, astrophysics}
\submitto{\jpg}
\maketitle
\end{verbatim}
\normalsize

At the start of the \LaTeX\ source code please include 
commented material to identify the journal, author, and (if you are sending a revised
version or a resubmission) the reference number that the journal
has given to the submission. The first non-commented line should be 
\verb"\documentclass[12pt]{iopart}"  to load the preprint class 
file.  The normal text will be in the Computer Modern 12pt font.
It is possible to specify 10pt font size by passing the option \verb"[10pt]" to the class file.
Although it is possible to choose a font other than Computer Modern by loading external packages, this is not recommended.

The article text begins after \verb"\begin{document}".
Authors of very long articles may find it convenient to separate 
their article into a series of \LaTeX\ files each containing one section, and each of which is called 
in turn by the primary file.  The files for each section should be read in from the current directory;
please name the primary file clearly so that we know to run \LaTeX\ on this file.

Authors may use any common \LaTeX\ \verb".sty" files.
Authors may also define their own macros and definitions either in the main article \LaTeX\ file
or in a separate \verb".tex" or \verb".sty" file that is read in by the
main file, provided they do not overwrite existing definitions.
It is helpful to the production staff if complicated author-defined macros are explained in a \LaTeX\ comment.
The article class \verb"iopart.cls" can be used with other package files such
as those loading the AMS extension fonts 
\verb"msam" and \verb"msbm", which provide the 
blackboard bold alphabet and various extra maths symbols as well as symbols useful in figure 
captions.  An extra style file \verb"iopams.sty" is provided to load these
packages and provide extra definitions for bold Greek letters.

\subsection{\label{dblcol}Double-column layout}
The \verb"iopart.cls" class file produces single-column output by default, but a two-column layout can be obtained by
using \verb"\documentclass[10pt]" at the start of the file and \verb"\ioptwocol" after the \verb"\maketitle" command.  Two-column output will begin
on a new page (unlike in published double-column articles, where the two-column material
starts on the same page as the abstract).

In general we prefer to receive submissions in single-column format even for journals
published in double-column style; however, the \verb"\ioptwocol" option may be useful to test figure sizes
and equation breaks for these journals.  When setting material
in two columns you can use the asterisked versions of \LaTeX\ commands such as \verb"\begin{figure*} ... \end{figure*}"
to set figures and tables across two columns.  If you have any problems or any queries about producing two-column output, please contact us at \verb"submissions@iop.org".

\section{The title and abstract page} 
If you use \verb"iopart.cls", the code for setting the title page information is slightly different from
the normal default in \LaTeX.  If you are using a different class file, you do not need to mimic the appearance of
an \verb"iopart.cls" title page, but please ensure that all of the necessary information is present.

\subsection{Titles and article types}
The title is set using the command
\verb"\title{#1}", where \verb"#1" is the title of the article. The
first letter 
of the title should be capitalized with the rest in lower case. 
The title appears in bold case, but mathematical expressions within the title may be left in light-face type.

If the title is too long to use as a running head at the top of each page (apart from the
first) a short
form can be provided as an optional argument (in square brackets)
before the full title, i.e.\ \verb"\title[Short title]{Full title}".

For article types other than papers, \verb"iopart.cls"
has a generic heading \verb"\article[Short title]{TYPE}{Full title}" 
and some specific definitions given in table~\ref{arttype}. In each case (apart from Letters
to the Editor and Fast Track Communications) an 
optional argument can be used immediately after the control sequence name
to specify the short title; where no short title is given, the full title
will be used as the running head.  Not every article type has its own macro---use \verb"\article" for
any not listed.  A full list of the types of articles published by a journal is given
in the submission information available via the journal home page.
%For Letters use \verb"\letter{Full title}"; no short title is required as 
%the running head is automatically defined to be {\it Letter to the Editor}.
The generic heading could be used for 
articles such as those presented at a conference or workshop, e.g.
\small\begin{verbatim}
\article[Short title]{Workshop on High-Energy Physics}{Title}
\end{verbatim}\normalsize
Footnotes to titles may be given by using \verb"\footnote{Text of footnote.}" immediately after the title.
Acknowledgment of funding should be included in the acknowledgments section rather than in a footnote.

\begin{table}
\caption{\label{arttype}Types of article defined in the {\tt iopart.cls} 
class file.}
\footnotesize\rm
\begin{tabular*}{\textwidth}{@{}l*{15}{@{\extracolsep{0pt plus12pt}}l}}
\br
Command& Article type\\
\mr
\verb"\title{#1}"&Paper (no surtitle on first page)\\
\verb"\ftc{#1}"&Fast Track Communication\\
\verb"\review{#1}"&Review\\
\verb"\topical{#1}"&Topical Review\\
\verb"\comment{#1}"&Comment\\
\verb"\note{#1}"&Note\\
\verb"\paper{#1}"&Paper (no surtitle on first page)\\
\verb"\prelim{#1}"&Preliminary Communication\\
\verb"\rapid{#1}"&Rapid Communication\\
\verb"\letter{#1}"&Letter to the Editor\\
\verb"\article{#1}{#2}"&Other articles\\\ & (use this for any other type of article; surtitle is whatever is entered as {\tt 
\#1})\\
\br
\end{tabular*}
\end{table}

\subsection{Authors' names and addresses}
For the authors' names type \verb"\author{#1}", 
where \verb"#1" is the 
list of all authors' names. Western-style names should be written as initials then
family name, with a comma after all but the last 
two names, which are separated by `and'. Initials should {\it not} be followed by full stops. First (given) names may be used if 
desired.  Names in Chinese, Japanese and Korean styles should be written as you want them to appear in the published article. Authors in all IOP Publishing journals have the option to include their names in Chinese, Japanese or Korean characters in addition to the English name: see appendix B for details.

If the authors are at different addresses a superscripted number, e.g. $^1$, \verb"$^1$", should be used after each 
name to reference the author to his/her address.
If an author has additional information to appear as a footnote, such as 
a permanent address, a normal \LaTeX\ footnote command
should be given after the family name and address marker 
with this extra information.

The authors' affiliations follow the list of authors. 
Each address is set by using
\verb"\address{#1}" with the address as the single parameter in braces. 
If there is more 
than one address then the appropriate superscripted number, followed by a space, should come at the start of
the address.

E-mail addresses are added by inserting the 
command \verb"\ead{#1}" after the postal address(es) where \verb"#1" is the e-mail address.  
See section~\ref{startsample} for sample coding. For more than one e-mail address, please use the command 
\verb"\eads{\mailto{#1}, \mailto{#2}}" with \verb"\mailto" surrounding each e-mail address.  Please ensure
that, at the very least, you state the e-mail address of the corresponding author.

\subsection{The abstract}
The abstract follows the addresses and
should give readers concise information about the content 
of the article and indicate the main results obtained and conclusions 
drawn. It should be self-contained---there should be no references to 
figures, tables, equations, bibliographic references etc.  It should be enclosed between \verb"\begin{abstract}"
and \verb"\end{abstract}" commands.  The abstract should normally be restricted 
to a single paragraph of around 200 words.

\subsection{Subject classification numbers}
We no longer ask authors to supply Physics and Astronomy Classification System (PACS)
classification numbers.  For submissions to {\it Nonlinearity}\/ we ask that you should
supply Mathematics Subject Classification (MSC) codes.  MSC numbers are included after the abstract 
using \verb"\ams{#1}".

The command
\verb"\submitto{#1}" can be inserted, where \verb"#1" is the journal name written in full or the appropriate control sequence as
given in table~\ref{jlab1}. This command is not essential to the running of the file and can be omitted.

\subsection{Keywords}
Keywords are required for all submissions. Authors should supply a minimum of three (maximum seven) keywords appropriate to their article as a new paragraph starting \verb"\noindent{\it Keywords\/}:" after the end of the abstract.

\subsection{Making a separate title page}
To keep the header material on a separate page from the
body of the text insert \verb"\maketitle" (or \verb"\newpage") before the start of the text. 
If \verb"\maketitle" is not included the text of the
article will start immediately after the abstract.

\section{The text}
\subsection{Sections, subsections and subsubsections}
The text of articles may be divided into sections, subsections and, where necessary, 
subsubsections. To start a new section, end the previous paragraph and 
then include \verb"\section" followed by the section heading within braces. 
Numbering of sections is done {\it automatically} in the headings: 
sections will be numbered 1, 2, 3, etc, subsections will be numbered 
2.1, 2.2,  3.1, etc, and subsubsections will be numbered 2.3.1, 2.3.2, 
etc.  Cross references to other sections in the text should, where
possible, be made using 
labels (see section~\ref{xrefs}) but can also
be made manually. See section~\ref{eqnum} for information on the numbering of displayed equations. Subsections and subsubsections are 
similar to sections but 
the commands are \verb"\subsection" and \verb"\subsubsection" respectively. 
Sections have a bold heading, subsections an italic heading and 
subsubsections an italic heading with the text following on directly.
\small\begin{verbatim}
\section{This is the section title}
\subsection{This is the subsection title}
\end{verbatim}\normalsize

The first section is normally an introduction,  which should state clearly 
the object of the work, its scope and the main advances reported, with 
brief references to relevant results by other workers. In long papers it is 
helpful to indicate the way in which the paper is arranged and the results 
presented.

Footnotes should be avoided whenever possible and can often be included in the text as phrases or sentences in parentheses. If required, they should be used only for brief notes that do not fit conveniently into the text. The use of 
displayed mathematics in footnotes should be avoided wherever possible and no equations within a footnote should be numbered. 
The standard \LaTeX\ macro \verb"\footnote" should be used.  Note that in \verb"iopart.cls" the \verb"\footnote" command
produces footnotes indexed by a variety of different symbols,
whereas in published articles we use numbered footnotes.  This
is not a problem: we will convert symbol-indexed footnotes to numbered ones during the production process.

\subsection{Acknowledgments}
Authors wishing to acknowledge assistance or encouragement from 
colleagues, special work by technical staff or financial support from 
organizations should do so in an unnumbered `Acknowledgments' section 
immediately following the last numbered section of the paper. In \verb"iopart.cls" the 
command \verb"\ack" sets the acknowledgments heading as an unnumbered
section.

Please ensure that you include all of the sources of funding and the funding contract reference numbers that you are contractually obliged to acknowledge. We often receive requests to add such information very late in the production process, or even after the article is published, and we cannot always do this. Please collect all of the necessary information from your co-authors and sponsors as early as possible.

\subsection{Appendices}
Technical detail that it is necessary to include, but that interrupts 
the flow of the article, may be consigned to an appendix. 
Any appendices should be included at the end of the main text of the paper, after the acknowledgments section (if any) but before the reference list.
If there are 
two or more appendices they should be called Appendix A, Appendix B, etc. 
Numbered equations will be in the form (A.1), (A.2), etc,
figures will appear as figure A1, figure B1, etc and tables as table A1,
table B1, etc.

The command \verb"\appendix" is used to signify the start of the
appendices. Thereafter \verb"\section", \verb"\subsection", etc, will 
give headings appropriate for an appendix. To obtain a simple heading of 
`Appendix' use the code \verb"\section*{Appendix}". If it contains
numbered equations, figures or tables the command \verb"\appendix" should
precede it and \verb"\setcounter{section}{1}" must follow it.

\subsection{Some matters of style}
It will help the readers if your article is written in a clear,
consistent and concise manner. During the production process
we will try to make sure that your work is presented to its
readers in the best possible way without sacrificing the individuality of
your writing. Some recommended 
points to note, however, are the following.  These apply to all of the journals listed
in table~\ref{jlab1}.
\begin{enumerate}
\item Authors are often inconsistent in the use of `ize' and `ise' endings.
We recommend using `-ize' spellings (diagonalize, 
renormalization, minimization, etc) but there are some common 
exceptions to this, for example: devise, 
promise and advise.

\item The words table and figure should be written 
in full and {\bf not} abbreviaged to tab. and fig. Do not include `eq.', `equation' etc before an equation number or `ref.'\, `reference' etc before a reference number.
\end{enumerate}

Please check your article carefully for accuracy, consistency and clarity before
submission. Remember that your article will probably be read by many
people whose native language is not English and who may not  
be aware of many of the subtle meanings of words or idiomatic phases
present in the English language. It therefore helps if you try to keep
sentences as short and simple as possible.  If you are not a native English speaker,
please ask a native English speaker to read your paper and check its grammar.

\section{Mathematics}
\subsection{Two-line constructions}
The great advantage of \LaTeX\ 
over other text processing systems is its 
ability to handle mathematics of almost any degree of complexity. However, 
in order to produce an article suitable for publication both within a print journal and online, 
authors should exercise some restraint on the constructions used. Some equations using very small characters which are clear in a preprint style article may be difficult read in a smaller format.

For simple fractions in the text the solidus \verb"/", as in 
$\lambda/2\pi$, should be used instead of \verb"\frac" or \verb"\over", 
using parentheses where necessary to avoid ambiguity, 
for example to distinguish between $1/(n-1)$ and $1/n-1$. Exceptions to 
this are the proper fractions $\frac12$, $\frac13$, $\frac34$, 
etc, which are better left in this form. In displayed equations 
horizontal lines are preferable to solidi provided the equation is 
kept within a height of two lines. A two-line solidus should be 
avoided where possible; the construction $(\ldots)^{-1}$ should be 
used instead. For example use:
\begin{equation*}
\frac{1}{M_{\rm a}}\left(\int^\infty_0{\rm d}
\omega\;\frac{|S_o|^2}{N}\right)^{-1}\qquad\mbox{instead of}\qquad
\frac{1}{M_{\rm a}}\biggl/\int^\infty_0{\rm d}
\omega\;\frac{|S_o|^2}{N}.
\end{equation*}

\subsection{Roman and italic in mathematics}
In mathematics mode \LaTeX\ automatically sets variables in an italic 
font. In most cases authors should accept this italicization. However, 
there are some cases where it is preferable to use a Roman font; for 
instance, a Roman d for a differential d, a Roman e 
for an exponential e and a Roman i for the square root of $-1$. To 
accommodate this and to simplify the  typing of equations, \verb"iopart.cls" provides
some extra definitions. \verb"\rmd", \verb"\rme" and \verb"\rmi" 
now give Roman d, e and i respectively for use in equations, 
e.g.\ $\rmi x\rme^{2x}\rmd x/\rmd y$ 
is obtained by typing \verb"$\rmi x\rme^{2x}\rmd x/\rmd y$".

Certain other common mathematical functions, such as cos, sin, det and 
ker, should appear in Roman type. Standard \LaTeX\ provides macros for 
most of these functions 
(in the cases above, \verb"\cos", \verb"\sin", \verb"\det" and \verb"\ker" 
respectively); \verb"iopart.cls" also provides 
additional definitions for $\Tr$, $\tr$ and 
$\Or$ (\verb"\Tr", \verb"\tr" and \verb"\Or", respectively).

Subscripts and superscripts should be in Roman type if they are labels 
rather than variables or characters that take values. For example in the 
equation
\[
\epsilon_m=-g\mu_{\rm n}Bm
\]
$m$, the $z$ component of the nuclear spin, is italic because it can have 
different values whereas n is Roman because it 
is a label meaning nuclear ($\mu_{\rm n}$ 
is the nuclear magneton).

\subsection{Displayed equations in double-column journals}
Authors should bear in mind that all mathematical formulae in double-column journals will need to fit
into the width of a single column.  You may find it helpful to use a two-column layout (such as the two-column
option in \verb"iopart.cls") in your submission so that you can check the width of equations.

\subsection{Special characters for mathematics}
Bold italic characters can be used in our journals to signify vectors (rather
than using an upright bold or an over arrow). To obtain this effect when using \verb"iopart.cls",
use \verb"\bi{#1}" within maths mode, e.g. $\bi{ABCdef}$. Similarly, in \verb"iopart.cls", if upright 
bold characters are required in maths, use \verb"\mathbf{#1}" within maths
mode, e.g. $\mathbf{XYZabc}$. The calligraphic (script) uppercase alphabet
is obtained with \verb"\mathcal{AB}" or \verb"\cal{CD}" 
($\mathcal{AB}\cal{CD}$).

The American Mathematical Society provides a series of extra symbol fonts
to use with \LaTeX\ and packages containing the character definitions to
use these fonts. Authors wishing to use Fraktur 
\ifiopams$\mathfrak{ABC}$ \fi
or Blackboard Bold \ifiopams$\mathbb{XYZ}$ \fi can include the appropriate
AMS package (e.g. \verb"amsgen.sty", \verb"amsfonts.sty", \verb"amsbsy.sty", \verb"amssymb.sty") with a 
\verb"\usepackage" command or add the command \verb"\usepackage{iopams}"
which loads the four AMS packages mentioned above and also provides
definitions for extra bold characters (all Greek letters and some other
additional symbols).

The package \verb"iopams.sty" uses the definition \verb"\boldsymbol" in \verb"amsbsy.sty"
which allows individual non-alphabetical symbols and Greek letters to be 
made bold within equations.
The bold Greek lowercase letters \ifiopams$\balpha \ldots\bomega$,\fi 
are obtained with the commands 
\verb"\balpha" \dots\ \verb"\bomega" (but note that
bold eta\ifiopams, $\bfeta$,\fi\ is \verb"\bfeta" rather than \verb"\beta")
and the capitals\ifiopams, $\bGamma\ldots\bOmega$,\fi\ with commands 
\verb"\bGamma" \dots\
\verb"\bOmega". Bold versions of the following symbols are
predefined in \verb"iopams.sty": 
bold partial\ifiopams, $\bpartial$,\fi\ \verb"\bpartial",
bold `ell'\ifiopams, $\bell$,\fi\  \verb"\bell", 
bold imath\ifiopams, $\bimath$,\fi\  \verb"\bimath", 
bold jmath\ifiopams, $\bjmath$,\fi\  \verb"\bjmath", 
bold infinity\ifiopams, $\binfty$,\fi\ \verb"\binfty", 
bold nabla\ifiopams, $\bnabla$,\fi\ \verb"\bnabla", 
bold centred dot\ifiopams, $\bdot$,\fi\  \verb"\bdot". Other 
characters are made bold using 
\verb"\boldsymbol{\symbolname}".

Please do not use the style file \verb"amsmath.sty" (part of the AMSTeX package) in conjunction with \verb"iopart.cls". This will result in several errors. To make use of the macros defined in \verb"amsmath.sty", \verb"iopart.cls" provides the file \verb"setstack.sty" which reproduces the following useful macros from \verb"amsmath.sty":
\small\begin{verbatim}
\overset \underset \sideset \substack \boxed   \leftroot
\uproot  \dddot    \ddddot  \varrow   \harrow
\end{verbatim}\normalsize

If the mathematical notation
that you need is best handled in \verb"amsmath.sty" you might want to consider using an article class
other than \verb"iopart.cls". We accept submissions using any class or style files.

Table~\ref{math-tab2} lists some other macros for use in 
mathematics with a brief description of their purpose.

\begin{table}
\caption{\label{math-tab2}Other macros defined in {\tt iopart.cls} for use in maths.}
\begin{tabular*}{\textwidth}{@{}l*{15}{@{\extracolsep{0pt plus
12pt}}l}}
\br
Macro&Result&Description\\
\mr
\verb"\fl"&&Start line of equation full left\\
\verb"\case{#1}{#2}"&$\case{\#1}{\#2}$&Text style fraction in display\\
\verb"\Tr"&$\Tr$&Roman Tr (Trace)\\
\verb"\tr"&$\tr$&Roman tr (trace)\\
\verb"\Or"&$\Or$&Roman O (of order of)\\
\verb"\tdot{#1}"&$\tdot{x}$&Triple dot over character\\
\verb"\lshad"&$\lshad$&Text size left shadow bracket\\
\verb"\rshad"&$\rshad$&Text size right shadow bracket\\
\br
\end{tabular*}
\end{table}

\subsection{Alignment of displayed equations}

The normal style for aligning displayed equations in our published journal articles is to align them left rather than centre. The \verb"iopart.cls" class file automatically does this and indents each line of a display.  In \verb"iopart.cls", to make any line start at the left margin of the page, add \verb"\fl" at start of the line (to indicate full left).

Using the \verb"eqnarray" environment equations will naturally be aligned left and indented without the use of any ampersands for alignment, see equations (\ref{eq1}) and (\ref{eq2})
\begin{eqnarray}
\alpha + \beta =\gamma^2, \label{eq1}\\
\alpha^2 + 2\gamma + \cos\theta = \delta. \label{eq2} 
\end{eqnarray}
This is the normal equation style for our journals.

Where some secondary alignment is needed, for instance a second part of an equation on a second line, a single ampersand is added at the point of alignment in each line  (see  (\ref{eq3}) and (\ref{eq4})).
\begin{eqnarray}
\alpha &=2\gamma^2 + \cos\theta + \frac{XY \sin\theta}{X+ Y\cos\theta} \label{eq3}\\
 & = \delta\theta PQ \cos\gamma. \label{eq4} 
\end{eqnarray}

Two points of alignment are possible using two ampersands for alignment (see  (\ref{eq5}) and (\ref{eq6})).  Note in this case extra space \verb"\qquad" is added before the second ampersand in the longest line (the top one) to separate the condition from the equation. 
\begin{eqnarray}
\alpha &=2\gamma^2 + \cos\theta + \frac{XY \sin\theta}{X+ Y\cos\theta}\qquad& \theta > 1 \label{eq5}\\
 & = \delta\theta PQ \cos\gamma &\theta \leq 1.\label{eq6} 
\end{eqnarray}

For a long equation which has to be split over more than one line the first line should start at the left margin, this is achieved by inserting \verb"\fl" (full left) at the start of the line. The use of the alignment parameter \verb"&" is not necessary unless some secondary alignment is needed.
\begin{eqnarray}
\fl \alpha + 2\gamma^2 = \cos\theta + \frac{XY \sin\theta}{X+ Y\cos\theta} +  \frac{XY \sin\theta}{X- Y\cos\theta} +
+ \left(\frac{XY \sin\theta}{X+ Y\cos\theta}\right)^2 \nonumber\\
+  \left(\frac{XY \sin\theta}{X- Y\cos\theta}\right)^2.\label{eq7} 
\end{eqnarray}

The plain \TeX\ command \verb"\eqalign" can be used within an \verb"equation" environment to obtain a multiline equation with a single centred number, for example
\begin{equation}
\eqalign{\alpha + \beta =\gamma^2 \cr
\alpha^2 + 2\gamma + \cos\theta = \delta.} 
\end{equation}

During the production process we will break equations as appropriate for the page layout of the journal. If you are submitting to a double-column journal and wish to review how your equations will break, you may find the double-column layout described in section \ref{dblcol} useful.

\subsection{Miscellaneous points}
The following points on the layout of mathematics apply whichever class file you use.

Exponential expressions, especially those containing subscripts or 
superscripts, are clearer if the notation $\exp(\ldots)$ is used, except for 
simple examples. For instance $\exp[\rmi(kx-\omega t)]$ and $\exp(z^2)$ are 
preferred to $\e^{\rmi(kx-\omega t)}$ and $\e^{z^2}$, but 
$\e^x$ 
is acceptable.

Similarly the square root sign $\sqrt{\phantom{b}}$ should 
only be used with relatively
simple expressions, e.g.\ $\sqrt2$ and $\sqrt{a^2+b^2}$;
in other cases the 
power $1/2$ should be used; for example, $[(x^2+y^2)/xy(x-y)]^{1/2}$.

It is important to distinguish between $\ln = \log_\e$ and $\lg 
=\log_{10}$. Braces, brackets and parentheses should be used in the 
following order: $\{[(\;)]\}$. The same ordering of brackets should be 
used within each size. However, this ordering can be ignored if the
brackets have a 
special meaning (e.g.\ if they denote an average or a function).

Decimal fractions should always be preceded by a zero: for example 0.123 {\bf not} .123.
For long numbers use thin spaces after every third character away from the position of the decimal point, unless 
this leaves a single separated character: e.g.\ $60\,000$, $0.123\,456\,78$ 
but 4321 and 0.7325.

Equations should be followed by a full stop (periods) when at the end
of a sentence.

\subsection{Equation numbering and layout in {\tt iopart.cls}}
\label{eqnum}
\LaTeX\ provides facilities for automatically numbering equations 
and these should be used where possible. Sequential numbering (1), (2), 
etc, is the default numbering system although in \verb"iopart.cls", if the command
\verb"\eqnobysec" is included in the preamble, equation numbering
by section is obtained, e.g.\ 
(2.1), (2.2), etc. Equation numbering by section is used in appendices automatically when the \verb"\appendix" command is used, even if sequential numbering has been used in the rest of the article. 
Refer to equations in the text using the equation number in parentheses. It is not normally necessary to include the word equation before the number; and abbreviations such as eqn or eq should not be used.
In \verb"iopart.cls", there are alternatives to the standard \verb"\ref" command that you might
find useful---see \tref{abrefs}.

Sometimes it is useful to number equations as parts of the same
basic equation. This can be accomplished in \verb"iopart.cls" by inserting the 
commands \verb"\numparts" before the equations concerned and 
\verb"\endnumparts" when reverting to the normal sequential numbering.
For example using \verb"\numparts \begin{eqnarray}" ... \verb"\end{eqnarray} \endnumparts":

\numparts
\begin{eqnarray}
T_{11}&=(1+P_\e)I_{\uparrow\uparrow}-(1-P_\e)
I_{\uparrow\downarrow},\label{second}\\
T_{-1-1}&=(1+P_\e)I_{\downarrow\downarrow}-(1-P_\e)I_{\uparrow\downarrow},\\
S_{11}&=(3+P_\e)I_{\downarrow\uparrow}-(3-P_e)I_{\uparrow\uparrow},\\
S_{-1-1}&=(3+P_\e)I_{\uparrow\downarrow}-(3-P_\e)
I_{\downarrow\downarrow}.
\end{eqnarray}
\endnumparts

Equation labels within the \verb"\eqnarray" environment will be referenced
as subequations, e.g. (\ref{second}).

\subsection{Miscellaneous extra commands for displayed equations}
The \verb"\cases" command has been amended slightly in \verb"iopart.cls" to 
increase the space between the equation and the condition. 
\Eref{cases} 
demonstrates simply the output from the \verb"\cases" command
\begin{equation}
\label{cases}
X=\cases{1&for $x \ge 0$\\
-1&for $x<0$\\}
\end{equation}
%The code used was:
%\small\begin{verbatim}
%\begin{equation}
%\label{cases}
%X=\cases{1&for $x \ge 0$\\
%-1&for $x<0$\\}
%\end{equation}
%\end{verbatim}
%\normalsize

To obtain text style fractions within displayed maths the command 
\verb"\case{#1}{#2}" can be used instead
of the usual \verb"\frac{#1}{#2}" command or \verb"{#1 \over #2}".

When two or more short equations are on the same line they should be 
separated by a `qquad space' (\verb"\qquad"), rather than
\verb"\quad" or any combination of \verb"\,", \verb"\>", \verb"\;" 
and \verb"\ ".

\section{Referencing\label{except}}
Two different styles of referencing are in common use: 
the Harvard alphabetical system and the Vancouver numerical system. 
All journals to which this document applies allow the use of either the Harvard or Vancouver system, 
except for {\it Physics in Medicine and Biology} and {\it Physiological Measurement}
for which authors {\it must\/} use the Harvard referencing style (with the titles of journal
articles given, and final page numbers given).

\subsection{Harvard (alphabetical) system}
In the Harvard system the name of the author appears in the text together 
with the year of publication. As appropriate, either the date or the name 
and date are included within parentheses. Where there are only two authors 
both names should be given in the text; if there are more than two 
authors only the first name should appear followed by `{\it et al}' 
(which can be obtained in \verb"iopart.cls" by typing \verb"\etal"). When two or 
more references to work by one author or group of authors occur for the 
same year they should be identified by including a, b, etc after the date 
(e.g.\ 2012a). If several references to different pages of the same article 
occur the appropriate page number may be given in the text, e.g.\ Kitchen 
(2011, p 39).

The reference list at the end of an article consists of an 
unnumbered `References' section containing an
alphabetical listing by authors' names. References with the same author list are ordered by date, oldest first.
The reference list in the 
preprint style is started in \verb"iopart.cls" by including the command \verb"\section*{References}" and then
\verb"\begin{harvard}".
Individual references start with \verb"\item[]" and the reference list is completed with \verb"\end{harvard}".
There is also a shortened form of the coding: \verb"\section*{References}"
and \verb"\begin{harvard}" can be replaced by the single command
\verb"\References", and \verb"\end{harvard}" can be shortened to
\verb"\endrefs".

\subsection{Vancouver (numerical) system}
In the Vancouver system references are numbered sequentially 
throughout the text. The numbers occur within square brackets and one 
number can be used to designate several references. A numerical 
reference list in the \verb"iopart" style is started by including the 
command \verb"\section*{References}" and then
\verb"\begin{thebibliography}{<num>}", where \verb"<num>" is the largest
number in the reference list (or any other number with the same number
of digits).  The 
reference list gives the references in 
numerical order, individual references start with \verb"\bibitem{label}". The list is completed by
\verb"\end{thebibliography}". Short forms of the commands are again
available: \verb"\Bibliography{<num>}" can be used at the start of the
references section and \verb"\endbib" at the end.

A variant of this system is to use labels instead of numbers within 
square brackets, in this case references in the list should start with \verb"\bibitem[label-text]". This method is allowed for all journals that accept numerical references.

\subsection{BibTeX\label{bibtex}}
If you are using BibTeX, see the earlier section \ref{bibby} for information on what \verb".bst" file to use.
The output that you get will differ slightly from that specified in the rest of this section,
but this is not a problem as long as all the relevant information is present.

\subsection{References, general}
A complete reference should provide the reader with enough information to 
locate the item concerned. Up to ten authors may be given in a particular reference; where 
there are more than ten only the first should be given followed by 
`{\it et al}'.  If you are using BibTeX
and the \verb".bst" file that you are using includes more than 10 authors, do not worry about this:
we can correct this during the production process.  Abbreviate a journal name only in accordance with the journal's
own recommendations for abbreviation---if in doubt, leave it unabbreviated.

The terms {\it loc.\ cit.}\ and {\it ibid}.\ should not be used. 
Unpublished conferences and reports should generally not be included 
in the reference list if a published version of the work exists. Articles in the course of publication should 
include the article title and the journal of publication, if known. 
A reference to a thesis submitted for a higher degree may be included 
if it has not been superseded by a published 
paper---please state the institution where the work was submitted.

The basic structure of a reference in the reference list is the same in both the alphabetical and numerical systems, the only difference being the code at the start of the reference. Alphabetical references are preceded by \verb"\item[]", numerical by \verb"\bibitem{label}" or just \verb"\item" to generate a number or \verb"\nonum" where a reference is not the first in a group of references under the same number.

Note that footnotes to the text should not be 
included in the reference list, but should appear at the bottom of the relevant page by using the \verb"\footnote" command.

\subsection{References to journal articles}
The following guidance applies if you are producing your reference list `by hand'; that is,
without the help of BibTeX.  See section~\ref{bibby} for BibTeX help.

Article references in published articles in our journals contain three changes of 
font:
the authors and date appear in Roman type, the journal title in 
italic, the volume number in bold and the page numbers in Roman again. 
A typical journal entry would be:

\smallskip
\begin{harvard}
\item[] Spicer P E, Nijhoff F W and van der Kamp P H 2011 {\it Nonlinearity} {\bf 24} 2229
\end{harvard}
\smallskip

\noindent which would be obtained by typing, within the references
environment 
\small\begin{verbatim}
\item[] Spicer P E, Nijhoff F W and van der Kamp P H 2011 {\it Nonlinearity} 
{\bf 24} 2229
\end{verbatim}\normalsize

\noindent Features to note are the following.

\begin{enumerate}
\item The authors should be in the form of surname (with only the first 
letter capitalized) followed by the initials with no 
periods after the initials. Authors should be separated by a comma 
except for the last two which should be separated by `and' with no 
comma preceding it.

\item The year of publication follows the authors and is not in parentheses.

\item Titles of journal articles can also be included (in Roman (upright) text after the year). Article titles are required in reference lists for {\it Inverse Problems, Journal of Neural Engineering, Measurement Science and Technology, Physical Biology, Physics in Medicine and Biology\/} and {\it Physiological Measurement}.

\item The journal is in italic and is abbreviated. If a journal has several parts denoted by 
different letters the part letter should be inserted after the journal in Roman type (e.g.\ 
{\it Phys.\ Rev.\ \rm A}). \verb"iopart.cls" includes macros for abbreviated titles of all journals handled by IOP Publishing (see table~\ref{jlab2}) and some other common titles (table \ref{jlab3}).

\item The volume number is bold; the page number is Roman.
 Both the initial and final page numbers should be given where possible---note that for {\it Reports on Progress in Physics\/}, {\it Physiological Measurement} and {\it Physics in Medicine and Biology}
 the final page number is {\it required}. The final page number should be in 
the shortest possible form and separated from the initial page number by an en rule (\verb"--"), e.g.\ 1203--14.

\item Where there are two or more references with identical authors, 
the authors' names should be repeated for the second and subsequent references. Each individual publication should be presented as a separate reference, although in the numerical system one number can be used for several references. This facilitates linking in the online journal. 
\end{enumerate}

\subsubsection{Article numbering.}
Many journals now use article-numbering systems that do not fit the conventional {\it year-journal-volume-page numbers} pattern. Some examples are:

\numrefs{1}
\item Carlip S and Vera R 1998 {\it Phys. Rev.} D {\bf 58} 011345 
\item Davies K and Brown G 1997 {\it J. High Energy Phys.} JHEP12(1997)002
\item Hannestad S 2005 {\it J. Cosmol. Astropart. Phys.} JCAP02(2005)011
\item Hilhorst H J 2005 {\it J. Stat. Mech.} L02003
\item Gundlach C 1999 {\it Liv. Rev. Rel.} 1994-4
\endnumrefs

\noindent The website of the journal you are citing should state the correct format for citations.

\subsection{Preprint references}
Preprints may be referenced but if the article concerned has been published in a peer-reviewed journal, that reference should take precedence. If only a preprint reference can be given, it is helpful to include the article title. Examples are:
\vskip6pt
\numrefs{1}
\item Neilson D and Choptuik M 2000 {\it Class. Quantum Grav.} {\bf 17} 761 (arXiv:gr-qc/9812053)
\item Sundu H, Azizi K, S\"ung\"u J Y and Yinelek N 2013 Properties of $D_{s2}^*(2573)$ charmed-strange tensor meson arXiv:1307.6058
\endnumrefs

\noindent For preprints added to arXiv.org after April 2007 it is not necessary to include the subject area, however this information can be included in square brackets after the number if desired, e.g.
\numrefs{1}
\item Sundu H, Azizi K, S\"ung\"u J Y and Yinelek N 2013 Properties of $D_{s2}^*(2573)$ charmed-strange tensor meson arXiv:1307.6058 [hep-ph]
\endnumrefs

\subsection{References to books, conference proceedings and reports}

References to books, proceedings and reports are similar, but have only two
changes of font. The authors and date of publication are in Roman, the 
title of the book is in italic, and the editors, publisher, 
town of publication 
and page number are in Roman. A typical reference to a book and a
conference paper might be

\smallskip
\begin{harvard}
\item[] Dorman L I 1975 {\it Variations of Galactic Cosmic Rays} 
(Moscow: Moscow State University Press) p~103
\item[] Caplar R and Kulisic P 1973 {\it Proc.\
Int.\ Conf.\ on Nuclear Physics (Munich)} vol~1 (Amsterdam:  
North-Holland/American Elsevier) p~517
\end{harvard}
\smallskip

\noindent which would be obtained by with the code
\small\begin{verbatim}
\item[] Dorman L I 1975 {\it Variations of Galactic Cosmic Rays} 
(Moscow: Moscow State University Press) p~103
\item[] Caplar R and Kulisic P 1973 {\it Proc. Int. Conf. on Nuclear 
Physics (Munich)} vol~1 (Amsterdam: North-Holland/American 
Elsevier) p~517
\end{verbatim}\normalsize
\noindent

\noindent Features to note are the following.
\begin{enumerate}
\item Book titles are in italic and should be spelt out in full with 
initial capital letters for all except minor words. Words such as 
Proceedings, Symposium, International, Conference, Second, etc should 
be abbreviated to Proc., Symp., Int., Conf., 2nd, 
respectively, but the rest of the title should be given in full, 
followed by the date of the conference and the 
town or city where the conference was held. For 
laboratory reports the laboratory should be spelt out wherever 
possible, e.g.\ {\it Argonne National Laboratory Report}.

\item The volume number, for example, vol~2, should be followed by 
the editors, if any, in the form ed~A~J~Smith and P~R~Jones. Use 
\etal if there are more than two editors. Next comes the town of 
publication and publisher, within brackets and separated by a colon, 
and finally the page numbers preceded by p if only one number is given 
or pp if both the initial and final numbers are given.

\item If a book is part of a series (for examples, {\it Springer Tracts in Modern Physics\/}), the series title and volume number is given in parentheses after the book title. Whereas for an individual volume in a multivolume set, the set title is given first, then the volume title. 
\end{enumerate}
\smallskip
\begin{harvard}
\item[]Morse M 1996 Supersonic beam sources {\it Atomic Molecular and Optical Physics\/} ({\it Experimental Methods in the Physical Sciences\/} vol 29) ed F B Dunning and R Hulet (San Diego, CA: Academic)  
\item[]Fulco C E, Liverman C T and Sox H C (eds) 2000 {\it Gulf War and Health\/} vol 1 {\it Depleted Uranium, Pyridostigmine Bromide, Sarin, and Vaccines\/} (Washington, DC: The National Academies Press)
\end{harvard}

\section{Cross-referencing\label{xrefs}}
The facility to cross reference items in the text is very useful when 
composing articles as the precise form of the article may be uncertain at the start 
and  revisions and amendments may subsequently be made. 
\LaTeX\ provides excellent facilities for doing cross-referencing
and these can be very useful in preparing articles.

\subsection{References}
\label{refs}
Cross referencing is useful for numeric reference lists because, if it 
is used, adding 
another reference to the list does not then involve renumbering all 
subsequent references. It is not necessary for referencing 
in the Harvard system where the final reference list is alphabetical 
and normally no other changes are necessary when a reference is added or
deleted.
When using \LaTeX , two passes (under certain circumstances, three passes)
are necessary initially to get the cross references right 
but once they are correct a single run is usually sufficient provided an 
\verb".aux" file is available and the file 
is run to the end each time.
If the 
reference list contains an entry \verb"\bibitem{label}", 
this command 
will produce the correct number in the reference list and 
\verb"\cite{label}" will produce the number within square brackets in the 
text. \verb"label" may contain letters, numbers 
or punctuation characters but must not contain spaces or commas. It is also
recommended that the underscore character \_{} is not used in cross
referencing. 
Thus labels of the form 
\verb"eq:partial", \verb"fig:run1", \verb"eq:dy'", 
etc, may be used. When several 
references occur together in the text \verb"\cite" may be used with 
multiple labels with commas but no spaces separating them; 
the output will be the 
numbers within a single pair of square brackets with a comma and a 
thin space separating the numbers. Thus \verb"\cite{label1,label2,label4}"
would give [1,\,2,\,4]. Note that no attempt is made by the style file to sort the 
labels and no shortening of groups of consecutive numbers is done.
Authors should therefore either try to use multiple labels in the correct 
order, or use a package such as \verb"cite.sty" that reorders labels
correctly.

The numbers for the cross referencing are generated in the order the 
references appear in the reference list, so that if the entries in the 
list are not in the order in which the references appear in the text 
then the 
numbering within the text will not be sequential. To correct this 
change the ordering of the entries in the reference list and then 
rerun the \LaTeX\ file {\it twice}.  Please ensure that all references resolve correctly: check the \verb".log" file
for undefined or multiply-defined citations, and check that the output does not contain question
marks that indicate unresolved references.

\subsection{Equation numbers, sections, subsections, figures and 
tables}
Labels for equation numbers, sections, subsections, figures and tables 
are all defined with the \verb"\label{label}" command and cross references 
to them are made with the \verb"\ref{label}" command.

Any section, subsection, subsubsection, appendix or subappendix 
command defines a section type label, e.g. 1, 2.2, A2, A1.2 depending 
on context. A typical article might have in the code of its introduction 
`The results are discussed in section\verb"~\ref{disc}".' and
the heading for the discussion section would be:
\small\begin{verbatim}
\section{Results}\label{disc}
\end{verbatim}\normalsize
Labels to sections, etc, may occur anywhere within that section except
within another numbered environment. 
Within a maths environment labels can be used to tag equations which are 
referred to within the text.

In addition to the standard \verb"\ref{<label>}", in \verb"iopart.cls" the abbreviated
forms given in \tref{abrefs}
are available for reference to standard parts of the text.

\Table{\label{abrefs}Alternatives to the normal references command {\tt $\backslash$ref} available in {\tt iopart.cls},
and the text generated by
them. Note it is not normally necessary to include the word equation
before an equation number except where the number starts a sentence. The
versions producing an initial capital should only be used at the start of
sentences.} 
\br
Reference&Text produced\\
\mr
\verb"\eref{<label>}"&(\verb"<num>")\\
\verb"\Eref{<label>}"&Equation (\verb"<num>")\\
\verb"\fref{<label>}"&figure \verb"<num>"\\
\verb"\Fref{<label>}"&Figure \verb"<num>"\\
\verb"\sref{<label>}"&section \verb"<num>"\\
\verb"\Sref{<label>}"&Section \verb"<num>"\\
\verb"\tref{<label>}"&table \verb"<num>"\\
\verb"\Tref{<label>}"&Table \verb"<num>"\\
\br
\endTable

\section{Tables and table captions}
Tables are numbered serially and referred to in the text 
by number (table 1, etc, {\bf not} tab. 1). Each table should have an 
explanatory caption which should be as concise as possible. If a table 
is divided into parts these should be labelled \pt(a), \pt(b), 
\pt(c), etc but there should be only one caption for the whole 
table, not separate ones for each part.

In the preprint style the tables may be included in the text 
or listed separately after the reference list 
starting on a new page.

\subsection{The basic table format}
The standard form for a table in \verb"iopart.cls" is:
\small\begin{verbatim}
\begin{table}
\caption{\label{label}Table caption.}
\begin{indented}
\item[]\begin{tabular}{@{}llll}
\br
Head 1&Head 2&Head 3&Head 4\\
\mr
1.1&1.2&1.3&1.4\\
2.1&2.2&2.3&2.4\\
\br
\end{tabular}
\end{indented}
\end{table}
\end{verbatim}\normalsize

\noindent Points to note are:
\begin{enumerate}
\item The caption comes before the table. It should have a period at
the end.

\item Tables are normally set in a smaller type than the text.
The normal style is for tables to be indented. This is accomplished
by using \verb"\begin{indented}" \dots\ \verb"\end{indented}"
and putting \verb"\item[]" before the start of the tabular environment.
Omit these
commands for any tables which will not fit on the page when indented.

\item The default is for columns to be aligned left and 
adding \verb"@{}" omits the extra space before the first column.

\item Tables have only horizontal rules and no vertical ones. The rules at
the top and bottom are thicker than internal rules and are set with
\verb"\br" (bold rule). 
The rule separating the headings from the entries is set with
\verb"\mr" (medium rule).  These are special \verb"iopart.cls" commands.

\item Numbers in columns should be aligned on the decimal point;
to help do this a control sequence \verb"\lineup" has been defined
in \verb"iopart.cls"
which sets \verb"\0" equal to a space the size of a digit, \verb"\m"
to be a space the width of a minus sign, and \verb"\-" to be a left
overlapping minus sign. \verb"\-" is for use in text mode while the other
two commands may be used in maths or text.
(\verb"\lineup" should only be used within a table
environment after the caption so that \verb"\-" has its normal meaning
elsewhere.) See table~\ref{tabone} for an example of a table where
\verb"\lineup" has been used.
\end{enumerate}

\begin{table}
\caption{\label{tabone}A simple example produced using the standard table commands 
and $\backslash${\tt lineup} to assist in aligning columns on the 
decimal point. The width of the 
table and rules is set automatically by the 
preamble.}

\begin{indented}
\lineup
\item[]\begin{tabular}{@{}*{7}{l}}
\br                              
$\0\0A$&$B$&$C$&\m$D$&\m$E$&$F$&$\0G$\cr 
\mr
\0\023.5&60  &0.53&$-20.2$&$-0.22$ &\01.7&\014.5\cr
\0\039.7&\-60&0.74&$-51.9$&$-0.208$&47.2 &146\cr 
\0123.7 &\00 &0.75&$-57.2$&\m---   &---  &---\cr 
3241.56 &60  &0.60&$-48.1$&$-0.29$ &41   &\015\cr 
\br
\end{tabular}
\end{indented}
\end{table}

\subsection{Simplified coding and extra features for tables}
The basic coding format can be simplified using extra commands provided in
the \verb"iopart" class file. The commands up to and including 
the start of the tabular environment
can be replaced by
\small\begin{verbatim}
\Table{\label{label}Table caption}
\end{verbatim}\normalsize
and this also activates the definitions within \verb"\lineup".
The final three lines can also be reduced to \verb"\endTable" or
\verb"\endtab". Similarly for a table which does not fit on the page when indented
\verb"\fulltable{\label{label}caption}" \dots\ \verb"\endfulltable"
can be used. \LaTeX\ optional positional parameters can, if desired, be added after 
\verb"\Table{\label{label}caption}" and \verb"\fulltable{\label{label}caption}".

\verb"\centre{#1}{#2}" can be used to centre a heading 
\verb"#2" over \verb"#1" 
columns and \verb"\crule{#1}" puts a rule across 
\verb"#1" columns. A negative 
space \verb"\ns" is usually useful to reduce the space between a centred 
heading and a centred rule. \verb"\ns" should occur immediately after the 
\verb"\\" of the row containing the centred heading (see code for
\tref{tabl3}). A small space can be 
inserted between rows of the table 
with \verb"\ms" and a half line space with \verb"\bs" 
(both must follow a \verb"\\" but should not have a 
\verb"\\" following them).

\Table{\label{tabl3}A table with headings spanning two columns and containing notes. 
To improve the 
visual effect a negative skip ($\backslash${\tt ns})
has been put in between the lines of the 
headings. Commands set-up by $\backslash${\tt lineup} are used to aid 
alignment in columns. $\backslash${\tt lineup} is defined within
the $\backslash${\tt Table} definition.}
\br
&&&\centre{2}{Separation energies}\\
\ns
&Thickness&&\crule{2}\\
Nucleus&(mg\,cm$^{-2}$)&Composition&$\gamma$, n (MeV)&$\gamma$, 2n (MeV)\\
\mr
$^{181}$Ta&$19.3\0\pm 0.1^{\rm a}$&Natural&7.6&14.2\\
$^{208}$Pb&$\03.8\0\pm 0.8^{\rm b}$&99\%\ enriched&7.4&14.1\\
$^{209}$Bi&$\02.86\pm 0.01^{\rm b}$&Natural&7.5&14.4\\
\br
\end{tabular}
\item[] $^{\rm a}$ Self-supporting.
\item[] $^{\rm b}$ Deposited over Al backing.
\end{indented}
\end{table}

Units should not normally be given within the body of a table but 
given in brackets following the column heading; however, they can be 
included in the caption for long column headings or complicated units. 
Where possible tables should not be broken over pages. 
If a table has related notes these should appear directly below the table
rather than at the bottom of the page. Notes can be designated with
footnote symbols (preferable when there are only a few notes) or
superscripted small roman letters. The notes are set to the same width as
the table and in normal tables follow after \verb"\end{tabular}", each
note preceded by \verb"\item[]". For a full width table \verb"\noindent"
should precede the note rather than \verb"\item[]". To simplify the coding 
\verb"\tabnotes" can, if desired, replace \verb"\end{tabular}" and 
\verb"\endtabnotes" replaces
\verb"\end{indented}\end{table}".

If all the tables are grouped at the end of a document
the command \verb"\Tables" is used to start a new page and 
set a heading `Tables and table captions'. If the tables follow an appendix then add the command \verb"\noappendix" to revert to normal style numbering.

\section{Figures and figure captions}

Figures (with their captions) can be incorporated into the text at the appropriate position or grouped together
at the end of the article. If the figures are at the end of the article and follow an appendix then in \verb"iopart.cls" you can add the command \verb"\noappendix" to revert to normal style numbering.  We remind you that you must seek permission
to reuse any previously-published figures, and acknowledge their use correctly---see section \ref{copyright}.

\subsection{Inclusion of graphics files\label{figinc}}
Using the \verb"graphicx" package graphics files can 
be included within figure and center environments at an 
appropriate point within the text using code such as:
\small\begin{verbatim}
\includegraphics{file.eps}
\end{verbatim}\normalsize
The \verb"graphicx" package supports various optional arguments
to control the appearance of the figure. Other similar 
packages can also be used (e.g. \verb"graphics", \verb"epsf").   Whatever package you use,
you must include it explicitly after the \verb"\documentclass" declaration using (say)
\verb"\usepackage{graphicx}".

For more detail about graphics inclusion see the documentation 
of the \verb"graphicx" package, refer to one of the books on \LaTeX , e.g. Goosens M, Rahtz S and Mittelbach F 1997 {\it The }\LaTeX\ {\it Graphics Companion\/} 
(Reading, MA: Addison-Wesley),
or download some of the excellent free documentation available via the Comprehensive
TeX Archive Network (CTAN) \verb"http://www.ctan.org"---{in particular see Reckdahl K 2006 {\it Using Imported Graphics in }\LaTeX\ {\it and }pdf\LaTeX\ \verb"http://www.ctan.org/tex-archive/info/epslatex".

IOP Publishing's graphics guidelines provide further information on preparing \verb".eps" files.

We prefer you to use \verb".eps" files for your graphics, but we realise that converting other
formats of graphics to \verb".eps" format can be troublesome.  If you use PDF or bitmap-format graphics
such as JPG or PNG that need to be included using the pdf\TeX\ package, this is OK, but please bear
in mind that the PDF you submit should use PDF standard 1.4 or lower (use \verb"\pdfminorversion=4" at the
start of the file).

The main \LaTeX\ file must read in graphics files and subsidiary \LaTeX\ files from the current directory,
{\it not} from a subdirectory.  Your submission files are stored on our systems in a single location and we will not be able to process your
TeX file automatically if it relies on organization of the files into subdirectories.

\subsection{Captions}
Below each figure should be a brief caption describing it and, if 
necessary, interpreting the various lines and symbols on the figure. 
As much lettering as possible should be removed from the figure itself 
and included in the caption. If a figure has parts, these should be 
labelled ($a$), ($b$), ($c$), etc and all parts should be described 
within a single caption. \Tref{blobs} gives the definitions for describing 
symbols and lines often used within figure captions (more symbols are 
available when using the optional packages loading the AMS extension fonts).

\subsection{Supplementary Data}
All of our journals encourage authors to submit supplementary data attachments to 
enhance the online versions of published research articles. Supplementary data 
enhancements typically consist of video clips, animations or
data files, tables of extra information or extra figures. They can 
add to the reader's understanding and present results in attractive ways that go 
beyond what can be presented in the PDF version of the article. 
See our supplementary data guidelines for further details.

Software, in the form of input scripts for mathematical packages (such as Mathematica notebook files), or
source code that can be interpreted or compiled (such as Python scripts or Fortran or C programs), or executable
files, can sometimes be accepted as supplementary data, but the journal may ask you for assurances about
the software and distribute them from the article web page only subject to a disclaimer.  Contact the journal
in the first instance if you want to submit software.

\begin{table}[t]
\caption{\label{blobs}Control sequences to describe lines and symbols in figure 
captions.}
\begin{indented}
\item[]\begin{tabular}{@{}lllll}
\br
Control sequence&Output&&Control sequence&Output\\
\mr
\verb"\dotted"&\dotted        &&\verb"\opencircle"&\opencircle\\
\verb"\dashed"&\dashed        &&\verb"\opentriangle"&\opentriangle\\
\verb"\broken"&\broken&&\verb"\opentriangledown"&\opentriangledown\\
\verb"\longbroken"&\longbroken&&\verb"\fullsquare"&\fullsquare\\
\verb"\chain"&\chain          &&\verb"\opensquare"&\opensquare\\
\verb"\dashddot"&\dashddot    &&\verb"\fullcircle"&\fullcircle\\
\verb"\full"&\full            &&\verb"\opendiamond"&\opendiamond\\
\br
\end{tabular}
\end{indented}
\end{table}

\clearpage

\appendix

\section{List of macros for formatting text, figures and tables}

\begin{table}[hb]
\caption{Macros available for use in text in {\tt iopart.cls}. Parameters in square brackets are optional.}
\footnotesize\rm
\begin{tabular}{@{}*{7}{l}}
\br
Macro name&Purpose\\
\mr
\verb"\title[#1]{#2}"&Title of article and short title (optional)\\
\verb"\paper[#1]{#2}"&Title of paper and short title (optional)\\
\verb"\letter{#1}"&Title of Letter to the Editor\\
\verb"\ftc{#1}"&Title of Fast Track Communication\\
\verb"\rapid[#1]{#2}"&Title of Rapid Communication and short title (optional)\\
\verb"\comment[#1]{#2}"&Title of Comment and short title (optional)\\
\verb"\topical[#1]{#2}"&Title of Topical Review and short title 
(optional)\\
\verb"\review[#1]{#2}"&Title of review article and short title (optional)\\
\verb"\note[#1]{#2}"&Title of Note and short title (optional)\\
\verb"\prelim[#1]{#2}"&Title of Preliminary Communication \& short title\\
\verb"\author{#1}"&List of all authors\\
\verb"\article[#1]{#2}{#3}"&Type and title of other articles and 
short title (optional)\\
\verb"\address{#1}"&Address of author\\
\verb"\ams{#1}"&Mathematics Classification Scheme\\
\verb"\submitto{#1}"&`Submitted to' message\\
\verb"\maketitle"&Creates title page\\
\verb"\begin{abstract}"&Start of abstract\\
\verb"\end{abstract}"&End of abstract\\
\verb"\nosections"&Inserts space before text when no sections\\
\verb"\section{#1}"&Section heading\\
\verb"\subsection{#1}"&Subsection heading\\
\verb"\subsubsection{#1}"&Subsubsection heading\\
\verb"\appendix"&Start of appendixes\\
\verb"\ack"&Acknowledgments heading\\
\verb"\References"&Heading for reference list\\
\verb"\begin{harvard}"&Start of alphabetic reference list\\
\verb"\end{harvard}"&End of alphabetic reference list\\
\verb"\begin{thebibliography}{#1}"&Start of numeric reference list\\
\verb"\end{thebibliography}"&End of numeric reference list\\
\verb"\etal"&\etal for text and reference lists\\
\verb"\nonum"&Unnumbered entry in numerical reference list\\
\br
\end{tabular}
\end{table}

\clearpage

\begin{table}
\caption{Macros defined within {\tt iopart.cls}
for use with figures and tables.}
\begin{indented}
\item[]\begin{tabular}{@{}l*{15}{l}}
\br
Macro name&Purpose\\
\mr
\verb"\Figures"&Heading for list of figure captions\\
\verb"\Figure{#1}"&Figure caption\\
\verb"\Tables"&Heading for tables and table captions\\
\verb"\Table{#1}"&Table caption\\
\verb"\fulltable{#1}"&Table caption for full width table\\
\verb"\endTable"&End of table created with \verb"\Table"\\
\verb"\endfulltab"&End of table created with \verb"\fulltable"\\
\verb"\endtab"&End of table\\
\verb"\br"&Bold rule for tables\\
\verb"\mr"&Medium rule for tables\\
\verb"\ns"&Small negative space for use in table\\
\verb"\centre{#1}{#2}"&Centre heading over columns\\
\verb"\crule{#1}"&Centre rule over columns\\
\verb"\lineup"&Set macros for alignment in columns\\
\verb"\m"&Space equal to width of minus sign\\
\verb"\-"&Left overhanging minus sign\\
\verb"\0"&Space equal to width of a digit\\
\br
\end{tabular}
\end{indented}
\end{table}

\clearpage

\begin{table}[hb]
\caption{\label{jlab2}Abbreviations in {\tt iopart.cls} for journals handled by IOP Publishing.}
\footnotesize
\begin{tabular}{@{}llll}
\br
{\rm Short form of journal title} & Macro & {\rm Short form of journal title} & Macro \\
\mr
2D Mater.&\verb"\TDM"&J. Radiol. Prot.&\verb"\JRP"\\
AJ&\verb"\AJ"&J. Semicond.&\verb"\JOS"\\
ApJ&\verb"\APJ"&J. Stat. Mech.&\verb"\JSTAT"\\
ApJL&\verb"\APJL"&Laser Phys.&\verb"\LP"\\
ApJS&\verb"\APJS"&Laser Phys. Lett.&\verb"\LPL"\\
Adv. Nat. Sci: Nanosci. Nanotechnol.&\verb"\ANSN"&Metrologia&\verb"\MET"\\
Appl. Phys. Express&\verb"\APEX"&Mater. Res. Express&\verb"\MRE"\\
Biofabrication&\verb"\BF"&Meas. Sci. Technol.&\verb"\MST"\\
Bioinspir. Biomim.&\verb"\BB"&Methods Appl. Fluoresc.&\verb"\MAF"\\
Biomed. Mater.&\verb"\BMM"&Modelling Simul. Mater. Sci. Eng.&\verb"\MSMSE"\\
Chin. J. Chem. Phys.&\verb"\CJCP"&Nucl. Fusion&\verb"\NF"\\
Chinese Phys. B&\verb"\CPB"&New J. Phys.&\verb"\NJP"\\
Chinese Phys. C&\verb"\CPC"&Nonlinearity&\verb"\NL"\\
Chinese Phys. Lett.&\verb"\CPL"&Nanotechnology&\verb"\NT"\\
Class. Quantum Grav.&\verb"\CQG"&Phys. Biol.&\verb"\PB"\\
Commun. Theor. Phys.&\verb"\CTP"&Phys. Educ.&\verb"\PED"\\
Comput. Sci. Disc.&\verb"\CSD"&Phys.-Usp.&\verb"\PHU"\\
Environ. Res. Lett.&\verb"\ERL"&Physiol. Meas.&\verb"\PM"\\
EPL&\verb"\EPL"&Phys. Med. Biol.&\verb"\PMB"\\
Eur. J. Phys.&\verb"\EJP"&Phys. Scr.&\verb"\PS"\\
Fluid Dyn. Res.&\verb"\FDR"&Plasma Phys. Control. Fusion&\verb"\PPCF"\\
Inverse Problems&\verb"\IP"&Plasma Sci. Technol.&\verb"\PST"\\
Izv. Math.&\verb"\IZV"&Plasma Sources Sci. Technol.&\verb"\PSST"\\
Jpn. J. Appl. Phys.&\verb"\JJAP"&Quantum Electron.&\verb"\QEL"\\
J. Breath Res.&\verb"\JBR"&Rep. Prog. Phys.&\verb"\RPP"\\
JCAP&\verb"\JCAP"&Res. Astron. Astrophys.&\verb"\RAA"\\
J. Geophys. Eng.&\verb"\JGE"&Russ. Chem. Rev.&\verb"\RCR"\\
JINST&\verb"\JINST"&Russ. Math. Surv.&\verb"\RMS"\\
J. Micromech. Microeng.&\verb"\JMM"&Sb. Math.&\verb"\MSB"\\
J. Neural Eng.&\verb"\JNE"&Science Foundation in China&\verb"\SFC"\\
J. Opt.&\verb"\JOPT"&Sci. Technol. Adv. Mater.&\verb"\STAM"\\
J. Phys. A: Math. Theor.&\verb"\jpa"&Semicond. Sci. Technol.&\verb"\SST"\\
J. Phys. B: At. Mol. Opt. Phys.&\verb"\jpb"&Smart Mater. Struct.&\verb"\SMS"\\
J. Phys: Condens. Matter&\verb"\JPCM"&Supercond. Sci. Technol.&\verb"\SUST"\\
J. Phys. D: Appl. Phys.&\verb"\JPD"&Surf. Topogr.: Metrol. Prop.&\verb"\STMP"\\
J. Phys. G: Nucl. Part. Phys.&\verb"\jpg"&Transl. Mater. Res.&\verb"\TMR"\\
\mr
{\it IOP Conference Series journals}\\
\mr
J. Phys.: Conf. Ser.&\verb"\JPCS"\\
IOP Conf. Ser.: Earth Environ. Sci.&\verb"\EES"\\
IOP Conf. Ser.: Mater. Sci. Eng.&\verb"\MSE"\\

\br
\end{tabular}

\end{table}

\clearpage

\begin{table}

\caption{\label{jlab2b}Abbreviations for IOP Publishing journals that are no longer published.}
\begin{indented}
\item[]\begin{tabular}{@{}lll}
\br
{\rm Short form of journal title} & Macro name & Years relevant\\
\mr
J. Phys. A: Math. Gen.&\verb"\JPA"&1975--2006\\
J. Phys. B: At. Mol. Phys.&\verb"\JPB"&1968--1987\\
J. Phys. C: Solid State Phys.&\verb"\JPC"&1968--1988\\
J. Phys. E: Sci. Instrum.&\verb"\JPE"&1968--1989\\
J. Phys. F: Met. Phys.&\verb"\JPF"&1971--1988\\
J. Phys. G: Nucl. Phys.&\verb"\JPG"&1975--1988\\
Pure Appl. Opt.&\verb"\PAO"&1992--1998\\
Quantum Opt.&\verb"\QO"&1989--1994\\
Quantum Semiclass. Opt.&\verb"\QSO"&1995--1998\\
J. Opt. A: Pure Appl. Opt.&\verb"\JOA"&1999--2009\\
J. Opt. B: Quantum Semiclass. Opt.&\verb"\JOB"&1999--2005\\
\br
\end{tabular}
\end{indented}
\end{table}

\begin{table}[h]

\caption{\label{jlab3}Abbreviations in {\tt iopart.cls} for some 
common journals not handled by IOP Publishing.}
\begin{indented}
\item[]\begin{tabular}{@{}llll}
\br
Short form of journal & Macro & Short form of Journal & Macro\\
\mr
Acta Crystallogr.&\verb"\AC"&J. Quant. Spectrosc. Radiat. Transfer&\verb"\JQSRT"\\
Acta Metall.&\verb"\AM"&Nuovo Cimento&\verb"\NC"\\
Ann. Phys., Lpz&\verb"\AP"&Nucl. Instrum. Methods&\verb"\NIM"\\
Ann. Phys., NY&\verb"\APNY"&Nucl. Phys.&\verb"\NP"\\
Ann. Phys., Paris&\verb"\APP"&Phys. Fluids&\verb"\PF"\\
Can. J. Phys.&\verb"\CJP"&Phys. Lett.&\verb"\PL"\\
Gen. Rel. Grav.&\verb"\GRG"&Phys. Rev.&\verb"\PR"\\
J. Appl. Phys.&\verb"\JAP"&Phys. Rev. Lett.&\verb"\PRL"\\
J. Chem. Phys.&\verb"\JCP"&Proc. R. Soc.&\verb"\PRS"\\
J. High Energy Phys.&\verb"\JHEP"&Phys. Status Solidi&\verb"\PSS"\\
J. Magn. Magn. Mater.&\verb"\JMMM"&Phil. Trans. R. Soc.&\verb"\PTRS"\\
J. Math. Phys.&\verb"\JMP"&Rev. Mod. Phys.&\verb"\RMP"\\
J. Opt. Soc. Am.&\verb"\JOSA"&Rev. Sci. Instrum.&\verb"\RSI"\\
J. Physique&\verb"\JP"&Solid State Commun.&\verb"\SSC"\\
J. Phys. Chem.&\verb"\JPhCh"&Sov. Phys.--JETP&\verb"\SPJ"\\
J. Phys. Soc. Jpn.&\verb"\JPSJ"&Z. Phys.&\verb"\ZP"\\

\br
\end{tabular}
\end{indented}
\end{table}

\clearpage

\section{Including author names using Chinese, Japanese and Korean characters in submissions to IOP Publishing journals}
Authors in all IOP Publishing journals have the option to include names in Chinese, Japanese or Korean (CJK) characters in addition to the English name. The names will be displayed in the print issue and the online PDF, abstract and table of contents, in parentheses after the English name.

It is the decision of the individual authors whether or not to include a CJK version of their names; for a single article it is not necessary for all authors to include a CJK name if only one author wishes to do so. It is the responsibility of the authors to check the accuracy and formatting of the names in the final proofs that they receive prior to publication.

To include names in CJK characters, authors should use the \verb"cjk.sty" package, available from \verb"http://www.ctan.org/tex-archive/language/chinese/CJK/". Users should be aware that this is a very large and complicated package which relies on a large number of fonts.  We recommend using a TeX package that includes this package and all of the fonts by default, so that manual configuration is not required (e.g. the TeXLive distribution, which is available on all platforms (Macintosh, Windows and Linux)).

The documentation for the \verb"cjk.sty" package gives information on how CJK characters can be included in TeX files.  Most authors will find it convenient to include the characters in one of the standard encodings such as UTF-8, GB or JIS, if they have access to a text editor that supports such encodings.

Example TeX coding might be:
\begin{verbatim}
\documentclass[12pt]{iopart}
\usepackage{CJK}
.
.
.
\begin{document}
\begin{CJK*}{GBK}{ }

\title[]{Title of article}
\author{Author Name (CJK characters)}
\address{Department, University, City, Country}
.
.
.
\end{CJK*}
\end{verbatim}
%%end novalidate
To avoid potential problems in handling the CJK characters in submissions, authors should always include a PDF of the full version of their papers (including all figure files, tables, references etc) with the CJK characters in it.

\end{document}

### 2020-03-19 Paper_draft/main.tex
Add files via upload

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%    INSTITUTE OF PHYSICS PUBLISHING                                   %
%                                                                      %
%   `Preparing an article for publication in an Institute of Physics   %
%    Publishing journal using LaTeX'                                   %
%                                                                      %
%    LaTeX source code `ioplau2e.tex' used to generate `author         %
%    guidelines', the documentation explaining and demonstrating use   %
%    of the Institute of Physics Publishing LaTeX preprint files       %
%    `iopart.cls, iopart12.clo and iopart10.clo'.                      %
%                                                                      %
%    `ioplau2e.tex' itself uses LaTeX with `iopart.cls'                %
%                                                                      %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
% First we have a character check
%
% ! exclamation mark    " double quote  
% # hash                ` opening quote (grave)
% & ampersand           ' closing quote (acute)
% $ dollar              % percent       
% ( open parenthesis    ) close paren.  
% - hyphen              = equals sign
% | vertical bar        ~ tilde         
% @ at sign             _ underscore
% { open curly brace    } close curly   
% [ open square         ] close square bracket
% + plus sign           ; semi-colon    
% * asterisk            : colon
% < open angle bracket  > close angle   
% , comma               . full stop
% ? question mark       / forward slash 
% \ backslash           ^ circumflex
%
% ABCDEFGHIJKLMNOPQRSTUVWXYZ 
% abcdefghijklmnopqrstuvwxyz 
% 1234567890
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\documentclass[12pt]{iopart}
\usepackage{xcolor}
\usepackage{pifont}
\usepackage{comment}
\usepackage{subcaption}
\usepackage{tikz}
\usetikzlibrary{shapes.geometric, arrows, calc}
\usepackage{amsmath}
\usepackage{amssymb}
\newcommand{\gguide}{{\it Preparing graphics for IOP Publishing journals}}
%Uncomment next line if AMS fonts required
%\usepackage{iopams}  
\newcommand{\jordan}[1]{\textbf{\textcolor{red}{JORDAN: #1}}}
\newcommand{\siong}[1]{\textbf{\textcolor{blue}{SIONG: #1}}}
\newcommand{\chris}[1]{\textbf{\textcolor{green}{CHRIS: #1}}}
\newcommand{\michael}[1]{\textbf{\textcolor{orange}{MICHAEL: #1}}}
\begin{document}

\title{Generative Adversarial Networks and Gravitational Waves}

\author{J. McGinn}

\address{University of Glasgow, Physics \& Astronomy Department, Glasgow G12 8QQ, UK}
%\ead{jordan.mcginn@glasgow.ac.uk}
\vspace{10pt}
\begin{indented}
\item[]March 2020
\end{indented}

\begin{abstract}

\end{abstract}

%
% Uncomment for keywords
%\vspace{2pc}
%\noindent{\it Keywords}: XXXXXX, YYYYYYYY, ZZZZZZZZZ
%
% Uncomment for Submitted to journal title message
%\submitto{\JPA}
%
% Uncomment if a separate title page is required
%\maketitle
% 
% For two-column output uncomment the next line and choose [10pt] rather than [12pt] in the \documentclass declaration
%\ioptwocol
%

\section{Introduction}
\begin{itemize}
\item Need to introduce GWs - the current state of the field e.g. detections
and LVC papers \ding{51}
\item Introduce burst searches - what's the point of burst searches \ding{51} - lots of references 
\item Discuss the family of burst waveforms currently used and why - not in detail, just
an introduction \ding{51}
\item Introduce ML techniques in GWs \ding{51} - lots of references
\item What this paper does on GANs in 1 paragraph \ding{51}
\item Describe the structure of the paper 
\end{itemize}

Gravitational-wave (GW) astronomy is now an established field, starting with the first detection of a binary black hole merger \cite{} on September 2015. Following this, the first and second observations runs (O1 and O2) of Advanced LIGO and Advanced Virgo reported several more mergers \cite{}. On August 2017 a binary neutron star merger was observed alongside its electron-magnetic counterpart for the first time, giving rise to multimessenger gravitational wave astronomy. 
GW bursts are transient signals of typically short duration ($<$ 1s) whose waveforms are not accurately modelled or are complex to re-produce. Astrophysical sources for such transients include: \jordan{should i include a list of these?}. Since GW bursts are un-modelled they are not sensitive to template based detection schemes such as matched-filtering \cite{}, instead, detection involves distinguishing the signal from detector noise. This is only possible if the detector noise is well characterised and the candidate signal can be differentiated from system or environmental glitches. As such, GW burst searches rely on an astrophysical burst signature appearing in multiple detectors. \jordan{how deep should i go? with coherent WaveBurst etc?}
Many GW burst algorithms \cite{cite the shit outta this} are tested and tuned using model waveforms that may or may not have astrophysical significance but have easy to define parameters and share characteristics of real bursts that is enough to simulate coincident non-stationary deviations between detectors. Such waveforms may have long-duration, short bandwidth (ringdowns), long-duration, large bandwidth (inspirals) and many algorithms make use of sine-Gaussians: a Gaussian modulated sine wave that is characterised by it's central frequency and narrow bandwidth. This makes it a great tool for diagnosing LIGOs sensitivity to frequency. 
We aim to explore the use of machine learning in generating and interpreting these mock GW burst signals. Neural networks have shown to replicate the sensitivities of matched filtering in GW detection \cite{} and rapid parameter estimation \cite{}, however these methods have primarily been focused on binary black hole signals and have not yet expanded to burst examples.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Generative Adversarial Networks}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}
\item Describe GANs in detail but really focus on the fact that the reader is a
GW data analyst - not a computer scientist \ding{51}
\item A diagram would be very useful \ding{51}
\item Do not discuss our specific case here - just stay general \ding{51}
\item A subsection on the specific advanced flavour of GAN that you are using
here - motivate this choice. \ding{51}
\end{itemize}

A subset of deep learning that has seen fruitful development in recent years \cite{} is Generative Adversarial Networks (GANs). These unsupervised algorithms learn patterns in a given training data set using an adversarial process. The generations from GANs are state-of-the-art in fields such as high quality image fidelity, image and text-to-image translation and video prediciton \cite{} and there is notable works on time series generations /cite. 
GANs work to train two competing neural networks, consisting of a discriminator  that is trained to distinguish
between real and fake data and a generator that produces synthetic
reproductions of the real data. The GAN method has generator perform a mapping
from an input noise vector \textbf{z} to its representation of the data and discriminator  maps its
input \textbf{x} to a probability that the input came form either the training
data or generator.  During training, discriminator  is given a batch of samples that contains one half real data (labelled as 1)
and one half fake data (labelled as 0) which it then makes predictions on. The
loss for discriminator  is calculated by comparing its predictions to the labelled data through the binary cross-entropy function. The training process
of a GAN alternatively updates the weights of the discriminator  and generator based on information
on its competitors loss function. This loss of discriminator  is used to update the weights
of generator to produce more realistic samples of the input distribution, the loss of G
encourages discriminator  to update its classification abilities. Both networks compete
in a minimax game that is tied to a value function V (D, G) which generator is trying
minimise and discriminator  is trying to maximise:

\begin{equation}
\mathop{\text{min}}_{G}  \mathop{\text{max}}_{D} V(D,G) = \mathbb{E}_{\bold{x} \sim p_{\text{r}}(\bold{x})} [\text{log} D(\bold{x})] \\ + \mathbb{E}_{\bold{z} \sim p_{\text{z}}(\bold{z})} [\text{log}(1-D(G(\bold{z})))]
\label{equation:GANloss}
\end{equation}
\subsection{Auxiliary conditional GANs}
In theory this will eventually lead to the local Nash equilibrium [18] where
both neural networks are trained optimally. In practice, however, GANs are
notoriously difficult to train. Such difficulties include: Non-convergence,
where the model parameters oscillate and the loss never converges, mode
collapse where G produces a limited diversity of samples, and diminishing
gradients when applying gradient descent to a
non-continuous function. To overcome some of these difficulties [blank]
proposed adding structure to the latent space by providing G with a class
label. This has the effect of making a point in latent space conditional on a
provided class. [blank] extends this idea further by requiring D to output a
probability of the data belonging to each class.

\begin{figure}
    \centering
    \begin{subfigure}[h]{0.5\textwidth}
        \centering
        \input{GAN_diagram_vertical}%     without .tex extension
        \caption{Vanilla GAN}
        \label{fig:GAN}
    \end{subfigure}\hfill
    \begin{subfigure}[h]{0.5\textwidth}
        \centering
        \input{ACGAN_diagram_vertical}%     without .tex extension
        \caption{AC-GAN}
        \label{fig:ACGAN}
    \end{subfigure}\hfill
    \caption{Comparison of the original GAN method and the Auxiliary Conditional-GAN method }
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Method}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}
\item Need to introduce the scheme you propose to use
\item A paragraph or subsection on the data generation being very clear on all
5 waveform models and the prior parameter space for each \ding{51}
\item A subsection on the design of the network architecture
\item A subsection on the "box" and why we implement it
\item A subsection on the training of the network - give rough timings and rule
of thumb decisions made
\item Do not discuss the results here 
\end{itemize}

To simulate gravitational burst sources, five GW signal morphologies, spanning a range of frequencies, duration and time delays were tested. The families are:
\begin{itemize}
	\item Sine-Gaussian:
		\begin{equation}
		\label{eqn:sg}
			h(t) = A \exp\bigg[ - \frac{(t-t_{0})^2}{\tau^2} \bigg] \sin (2 \pi f_0 (t-t_0))
		\end{equation}	
		where $f_0$ is the central frequency that takes values between 30 Hz - 50 Hz. $\tau$ is the decay parameter chosen to be between 1/60s  and 1/15s and the starting epoch chosen between 0.2s - 0.8s. Sine-Gaussian waveforms have a similar form to those produced by the merger of two black holes. Although binary mergers tend to be longer in duration.  		
	\item Ring-down waveforms:
		\begin{equation}
			h(t) = A \exp \bigg[-\frac{(t-t_0)}{\tau}\bigg]\sin(2 \pi f_0 (t-t_0))
		\end{equation}
		For ring-down signals the parameters for $f_0, \tau, t_0$ are chosen between; 30 Hz-50Hz, 0.02-0.1 and 0.1s-0.8s respectfully. These signals aim to replicate the post-merger late stages of binary coalescence.
	\item White-noise bursts:\hfill \\
	These signals are produced by inserting samples of random Gaussian noise with zero mean and a variance of 0.1 at a random point between 0.2s - 0.8s. The source of this signal type can be attributed to core-collapse supernova. 
	\item Gaussian:\\
	parameters for Gaussian pulse is: $t_0$ = [0.2s,0.8s] and $\tau = [100^{-1},20^{-1}]$
	\item BBH Inspiral: \\
	talk about bbh gen, lalsimulatino package Timedoman waveform. Priors like mass range and f min. 
\end{itemize}
\jordan{Could be a table rather than a list?}
\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{images/train.png}
    \caption{Examples of burst training signals from left to right: sine-gaussian, ringdown, white-noise burst, Gaussian, binary-black hole merger}
    \label{fig:my_label}
\end{figure}

\subsection{Architecture details}
We base the architecture on (cite DCGANS) and adopt the suggestions of (cite wavegan paper) lengthening one-dimensional convolution kernels on both the generator and discriminator. The class label is interpreted as an additional channel early in the generator model. This is achieved by projecting the class inputs as a learned embedding layer, into a fully connected layer which can then be concatenated channel-wise to $\textbf{z}$. The rest of the model is fully convolutional, upsampled using strided transposed convolutions with batchnormalisation in the first layer and ReLU activations throughout with the exception of Tanh for the output layer. Each transposed convolutional layer uses a kernel size of 18x1 and stride 2.
The discriminator network mirrors that of the generator without batch normalization, using LeakyReLU activations, SpatialDropout, and a 2-stride convolution for downsampling. The main difference is that the discriminator has two output layers. The first output is a single node activated by a Sigmoid that can be interpreted as the realness of the the signal. The second output is 5 nodes activated using the softmax function predicting the class of the input. This model is trained with binary cross entropy for the first output and sparse categorical cross-entropy for the second output. \jordan{Diagram of generator with box and showing the concate procedure}

\subsection{Applying Antenna responses}
We consider a two detector case where the generator should be trained to output two identical signals with a physical time shift representing the time of flight between detectors and the suppression of amplitudes due to interaction with the detector. To achieve this, the generator is trained to generate a single waveform that is then manipulated through a non-trainable ``response" layer. This layer creates a copy of its input, shifts it along in time and applies antenna responses to both the input and shifted signal. The result is a 2x1024 times series waveform representing an overlay data stream from two detector outputs.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}
\item Begin by outlining the type of results you will be presenting
\item A subsection on the general quality of generated waveforms - we may need
to have overlaps between generated wavefoms and training data (maybe)
\item A subsection on the descriminator - maybe a confusion matrix?
\item a subsection on the latent space varaition within each class - fixed
class, sliding in latent space.
\item A subsection on the class space variation - fixed latent space and
sliding in the class space.
\item A final subsection on the general waveform model based on random latent
and class space locations.
\item Make no conclusions.
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}
\item Summarise the paper
\item Dedicate a paragraph to each of the key results discussed in the previous
section
\item Have at least one paragraph on the future directions of this work
\item Conclude with a positive paragrpah about the potential uses and impact of
the approach.
\end{itemize}

\clearpage

\appendix
\section{List of hyperparameters}
\begin{table}[hb]
\caption{ACGAN architecture}
\footnotesize
\begin{tabular}{@{}lllllll}
\br
 Operation & Kernel & Strides & Output Shape & BN & Dropout & Activation \\
\mr
 G(\textbf{z}): Input \textbf{z} $\sim$ Normal(0,0.02) & N/A & N/A & (100,) & \ding{55} & 0 & N/A \\  
 Dense & N/A & N/A & (32768,) & \ding{55} & 0 & ReLU \\  
 Class input c & N/A & N/A & (1,) & \ding{55} & 0 & N/A \\
 Embedding & N/A & N/A & (1, 120) & \ding{55} & 0 & N/A \\
 Dense & N/A & N/A & (1,128) & \ding{55} & 0 & ReLU \\ 
 Reshape \textbf{z} & N/A & N/A & (128, 256) & \ding{55} & 0 & N/A \\
 Reshape c & N/A & N/A & (128, 1) & \ding{55} & 0 & N/A \\
 Concatenate & N/A & N/A & (128, 257) & \ding{55} & 0 & N/A \\
 Reshape & N/A & N/A & (64, 514) & \ding{55} & 0 & N/A \\
 Transposed Convolution & 18x1 & 2 & (256, 256) & \ding{51} & 0 & ReLU\\
 Transposed Convolution & 18x1 & 2 & (512, 128) & \ding{55} & 0 & ReLU\\
 Transposed Convolution & 18x1 & 2 & (1024, 64) & \ding{55} & 0 & ReLU\\
 Convolution & 18x1 & 1 & (1024, 1) & \ding{55} & 0 & Tanh \\
 Sky input & N/A & N/A & (3,) & \ding{55} & 0 & N/A \\
 Concatenate & N/A & N/A & (1027,) &  \ding{55} & 0 & N/A \\
 Lambda & N/A & N/A & (1024, 2) & \ding{55} & 0 & N/A \\
 D(\textbf{x}): Input \textbf{x} & N/A & N/A & (1024, 2) & \ding{55} & 0 & N/A \\
 Convolution & 14x1 & 2 & (512, 64) & \ding{55} & 0.5 & Leaky ReLU \\
 Convolution & 14x1 & 2 & (256, 128) & \ding{55} & 0.5 & Leaky ReLU \\
 Convolution & 14x1 & 2 & (128, 256) & \ding{55} & 0.5 & Leaky ReLU \\
 Convolution & 14x1 & 2 & (64, 512) & \ding{55} & 0.5 & Leaky ReLU \\
 Flatten & N/A & N/A & (32768,) & \ding{55} & 0 & N/A \\
 Dense & N/A & N/A & (1,) & \ding{55} & 0 & Sigmoid \\
 Dense & N/A & N/A & (5,) & \ding{55} & 0 & Softmax \\
\br
 Optimizer & \multicolumn{6}{l}{Adam($\alpha$ = 0.0002, $\beta_{1}$ = 0.5)} \\
 Batch size & \multicolumn{6}{l}{128}  \\
 Iterations & \multicolumn{6}{l}{60000}  \\
 Leaky ReLU slope & \multicolumn{6}{l}{0.2} \\
 Weight initialization & \multicolumn{6}{l}{Gaussian($\mu$ = 0, $\sigma$ = 0.02)} \\
 Generator loss & \multicolumn{6}{l}{Binary cross-entropy} \\
 Discriminator loss & \multicolumn{6}{l}{Binary cross-entropy \& sparse categorical cross-entropy} \\ 
 \br
\end{tabular}\\

\end{table}
\normalsize

\end{document}

### 2020-03-20 Paper_draft/figures/ACGAN_diagram_vertical.tex
Fixed style file

\begin{tikzpicture}[node distance=2cm]

\tikzstyle{zinput} = [rectangle, rounded corners, text centered, draw=black]%, fill=red!30]
\tikzstyle{generator} = [rectangle, rounded corners, text centered, draw=black]%, fill=red!30]
\tikzstyle{X real} = [rectangle, rounded corners, text centered, draw=black]%, fill=red!30]
\tikzstyle{X fake} = [rectangle, rounded corners, text centered, draw=black]%, fill=red!30]
\tikzstyle{X real} = [rectangle, rounded corners, text centered, draw=black]%, fill=red!30]
\tikzstyle{discriminator} = [rectangle, rounded corners, text centered, draw=black]%, fill=red!30]
\tikzstyle{real/fake} = [rectangle, rounded corners, text centered, draw=black]%, fill=red!30]
\tikzstyle{coutput} = [rectangle, rounded corners, text centered, draw=black]%, fill=red!30]

\tikzstyle{arrow} = [thick,->,>=stealth]

\node (r) [X real] {\textbf{X} real};
\node (f) [X fake, right of = r] {\textbf{X} fake};
\node (G) [generator,above of = f, scale = 2] {\textbf{G}};
\node (z) [zinput] [zinput, above of = G, xshift = 1cm] {\textbf{z} (noise)};
\node (c) [coutput, left of = z] {\textbf{c} (class)};
\node (D) [discriminator, below of = f, xshift = -1cm, scale = 2] {\textbf{D}};
\node (rf) [real/fake, below of = D, xshift = 1.2cm] {real/fake};
\node (co) [coutput, left of = rf, xshift = -0.5cm] {c = 1, 2, ...};

\draw [arrow] (z) edge[out=270,in=90] (G);
\draw [arrow] (c) edge[out=270,in=90] (G);
\draw [arrow] (c) edge[out=270,in=90] (r);
\draw [arrow] (G) -- (f);
\draw [arrow] (r) edge[out=270,in=90] (D);
\draw [arrow] (f) edge[out=270,in=90] (D);
\draw [arrow] (D) edge[out=270,in=90] (rf);
\draw [arrow] (D) edge[out=270,in=90] (co);

\end{tikzpicture}

### 2020-03-20 Paper_draft/figures/GAN_diagram_vertical.tex
Fixed style file

--- 2020-03-20 Paper_draft/figures/ACGAN_diagram_vertical.tex
@@
+%\documentclass{article}
+%\usepackage{comment}
+%\usepackage{tikz}
+%\usetikzlibrary{shapes.geometric, arrows, calc}
+
+%\begin{document}
+
 \begin{tikzpicture}[node distance=2cm]
@@
 \tikzstyle{real/fake} = [rectangle, rounded corners, text centered, draw=black]%, fill=red!30]
-\tikzstyle{coutput} = [rectangle, rounded corners, text centered, draw=black]%, fill=red!30]
 
@@
 \node (G) [generator,above of = f, scale = 2] {\textbf{G}};
-\node (z) [zinput] [zinput, above of = G, xshift = 1cm] {\textbf{z} (noise)};
-\node (c) [coutput, left of = z] {\textbf{c} (class)};
+\node (z) [zinput] [zinput, above of = G] {\textbf{z} (noise)};
 \node (D) [discriminator, below of = f, xshift = -1cm, scale = 2] {\textbf{D}};
-\node (rf) [real/fake, below of = D, xshift = 1.2cm] {real/fake};
-\node (co) [coutput, left of = rf, xshift = -0.5cm] {c = 1, 2, ...};
+\node (rf) [real/fake, below of = D] {real/fake};
 
-\draw [arrow] (z) edge[out=270,in=90] (G);
-\draw [arrow] (c) edge[out=270,in=90] (G);
-\draw [arrow] (c) edge[out=270,in=90] (r);
+\draw [arrow] (z) -- (G);
 \draw [arrow] (G) -- (f);
@@
 \draw [arrow] (f) edge[out=270,in=90] (D);
-\draw [arrow] (D) edge[out=270,in=90] (rf);
-\draw [arrow] (D) edge[out=270,in=90] (co);
+\draw [arrow] (D) -- (rf);
 
 \end{tikzpicture}
+%\end{document}

### 2020-03-20 Paper_draft/main.tex
Fixed style file

@@
 \usepackage{comment}
-\usepackage{subcaption}
+%\usepackage{subcaption}
 \usepackage{tikz}
 \usetikzlibrary{shapes.geometric, arrows, calc}
+\expandafter\let\csname equation*\endcsname\relax 
+\expandafter\let\csname endequation*\endcsname\relax 
 \usepackage{amsmath}
@@
 
-\begin{figure}
+\begin{figure}[h!]
     \centering
-    \begin{subfigure}[h]{0.5\textwidth}
-        \centering
-        \input{GAN_diagram_vertical}%     without .tex extension
-        \caption{Vanilla GAN}
-        \label{fig:GAN}
-    \end{subfigure}\hfill
-    \begin{subfigure}[h]{0.5\textwidth}
-        \centering
-        \input{ACGAN_diagram_vertical}%     without .tex extension
-        \caption{AC-GAN}
-        \label{fig:ACGAN}
-    \end{subfigure}\hfill
+    %\begin{subfigure}[h]{0.5\textwidth}
+        %\centering
+        \input{figures/GAN_diagram_vertical}%     without .tex extension
+    %\end{subfigure}\hfill
+    %\begin{subfigure}[h]{0.5\textwidth}
+       % \centering
+        \input{figures/ACGAN_diagram_vertical}%     without .tex extension
+    %\end{subfigure}\hfill
     \caption{Comparison of the original GAN method and the Auxiliary Conditional-GAN method }
@@
 5 waveform models and the prior parameter space for each \ding{51}
-\item A subsection on the design of the network architecture
-\item A subsection on the "box" and why we implement it
+\item A subsection on the design of the network architecture \ding{51}
+\item A subsection on the "box" and why we implement it \ding{51}
 \item A subsection on the training of the network - give rough timings and rule
@@
 \jordan{Could be a table rather than a list?}
+
 \begin{figure}
     \centering
-    \includegraphics[width=\textwidth]{images/train.png}
+    \includegraphics[width=\textwidth]{figures/train.png}
     \caption{Examples of burst training signals from left to right: sine-gaussian, ringdown, white-noise burst, Gaussian, binary-black hole merger}
-    \label{fig:my_label}
+    \label{fig:train}
 \end{figure}
@@
 \end{itemize}
+
+\subsection{Waveform quality}
+\begin{figure}
+    \centering
+    \includegraphics[width=\textwidth]{figures/gen_zoom_signals.png}
+    \caption{Top row: Output of generator when given latent vector and class integer. Bottom row: Detailed view of the same output}
+    \label{fig:gen_signals}
+\end{figure}
+\subsection{Classifier}
+\subsection{Latent space interpolation}
+\subsection{Class space interpolation}
 

### 2020-03-25 Paper_draft/main.tex
3/4 of a draft

@@
 \section{Introduction}
+\begin{comment}
 \begin{itemize}
@@
 GW bursts are transient signals of typically short duration ($<$ 1s) whose waveforms are not accurately modelled or are complex to re-produce.
-Astrophysical sources for such transients include: \jordan{should i include a list of these?}.
+Astrophysical sources for such transients include: Core collapse supernova, Neutron star instabilities, Fallback accretion onto a neutron star, Non axisymetric deformation in magnetars, Pulsar glitches, Neutron star post-mergers.
+Black hole accretion disk fragmentation..
 Since GW bursts are un-modelled they are not sensitive to template based detection schemes such as matched-filtering \cite{}, instead, detection involves distinguishing the signal from detector noise.
@@
 As such, GW burst searches rely on an astrophysical burst signature appearing in multiple detectors.
-\jordan{how deep should i go?
-with coherent WaveBurst etc?}
-Many GW burst algorithms \cite{cite the shit outta this} are tested and tuned using model waveforms that may or may not have astrophysical significance but have easy to define parameters and share characteristics of real bursts that is enough to simulate coincident non-stationary deviations between detectors.
+Many GW burst algorithms \cite{} are tested and tuned using model waveforms that may or may not have astrophysical significance but have easy to define parameters and share characteristics of real bursts that is enough to simulate coincident non-stationary deviations between detectors.
 Such waveforms may have long-duration, short bandwidth (ringdowns), long-duration, large bandwidth (inspirals) and many algorithms make use of sine-Gaussians: a Gaussian modulated sine wave that is characterised by it's central frequency and narrow bandwidth.
@@
 between real and fake data and a generator that produces synthetic
-reproductions of the real data. The GAN method has generator perform a mapping
+reproductions of the real data. The generator perform a mapping
 from an input noise vector \textbf{z} to its representation of the data and discriminator  maps its
@@
 \begin{equation}
-\mathop{\text{min}}_{G}  \mathop{\text{max}}_{D} V(D,G) = \mathbb{E}_{\bold{x} \sim p_{\text{r}}(\bold{x})} [\text{log} D(\bold{x})] \\ + \mathbb{E}_{\bold{z} \sim p_{\text{z}}(\bold{z})} [\text{log}(1-D(G(\bold{z})))]
+\mathop{\text{min}}_{G}  \mathop{\text{max}}_{D} V(D,G) = \mathbb{E}_{\mathbf{x} \sim p_{\text{r}}(\mathbf{x})} [\text{log} D(\mathbf{x})] \\ + \mathbb{E}_{\mathbf{z} \sim p_{\text{z}}(\mathbf{z})} [\text{log}(1-D(G(\mathbf{z})))]
 \label{equation:GANloss}
@@
 \subsection{Auxiliary conditional GANs}
-In theory this will eventually lead to the local Nash equilibrium [18] where
+In theory, the adversarial process will eventually lead to the local Nash equilibrium [18] where
 both neural networks are trained optimally. In practice, however, GANs are
@@
 provided class. [blank] extends this idea further by requiring D to output a
-probability of the data belonging to each class.
+probability of the data belonging to each class. A pictorial representation on the differences between these approaches is show below.
 
@@
     %\end{subfigure}\hfill
-    \caption{Comparison of the original GAN method and the Auxiliary Conditional-GAN method }
+    \caption{Comparison of the original GAN method and the Auxiliary Conditional-GAN method.
+For ACGANs the training data requires a label denoting its class that is also fed to the generator which then learns to generate waveforms based on the input label.
+Additionaly, the discrminator learns to classify which class the signal belongs to.}
 \end{figure}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Method}
+\section{Methodology}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+GW burst signals remain an unmodelled phenomenon, as such, current detection algorithms focus on waveform reconstruction reliant on coincident signals within multiple detectors.
+We propose a signal generation scheme utilizing GANs trained on burst-like waveforms.
+The GAN is trained on five signal morphology's spanning a range of prior parameters.
+The families are:
 
+\begin{comment}
 \begin{itemize}
@@
 \end{itemize}
+\end{comment}
 
-To simulate gravitational burst sources, five GW signal morphologies, spanning a range of frequencies, duration and time delays were tested. The families are:
 \begin{itemize}
@@
 		where $f_0$ is the central frequency that takes values between 30 Hz - 50 Hz.
-$\tau$ is the decay parameter chosen to be between 1/60s  and 1/15s and the starting epoch chosen between 0.2s - 0.8s.
+$\tau$ is the decay parameter chosen to be between 60s$^{-1}$  and 15s$^{-1}$ and the starting epoch chosen between 0.2s - 0.8s.
 Sine-Gaussian waveforms have a similar form to those produced by the merger of two black holes.
 Although binary mergers tend to be longer in duration.
-	\item Ring-down waveforms:
+	\item Ring-down:
 		\begin{equation}
@@
 	\item Gaussian:\\
-	parameters for Gaussian pulse is: $t_0$ = [0.2s,0.8s] and $\tau = [100^{-1},20^{-1}]$
-	\item BBH Inspiral: \\
-	talk about bbh gen, lalsimulatino package Timedoman waveform. Priors like mass range and f min. 
+	A simple Gasssian waveform with $t_0$ ranging from 0.2s to 0.8s and $\tau$ between  100$^{-1}$ and 20$^{-1}$
+	\item Binary black holes (BBH): \\
+	BBH signals are simulated using IMRPhenomD waveform routine from LALSuite which models the inspiral, merger and ringdown of a BBH waveform.
+The component masses lie in the range of [5,70]M$_0$ with zero spins and we fix m$_1$1$>$m$_2$.
+The mass distribution is approximated by a power law with index of 1.6 https://arxiv.org/abs/1811.12940.
+The signals are generated using random right ascensions and declinations uniform over the sky and the inclinations are drawn from the cosine of a uniform distribution in the range [-1,1].
+The peaks of the waveforms are set to be within [0.75,0.95]s of the 1s time interval.
 \end{itemize}
-\jordan{Could be a table rather than a list?}
 
@@
     \centering
-    \includegraphics[width=\textwidth]{figures/train.png}
-    \caption{Examples of burst training signals from left to right: sine-gaussian, ringdown, white-noise burst, Gaussian, binary-black hole merger}
+    \includegraphics[width=\textwidth]{figures/train.pdf}
+    \caption{Examples of burst training signals. From left to right: sine-gaussian, ringdown, white-noise burst, Gaussian, binary-black hole merger.}
     \label{fig:train}
 \end{figure}
+
+\subsection{Applying Antenna responses}
+We consider a two detector case where the generator should be trained to output two identical signals with a physical time shift representing the time of flight between detectors and the suppression of amplitudes due to interaction with the detector.
+To achieve this, the generator is trained to output a single waveform that is then put through a non-trainable ``response" layer as the final layer of the generator.
+This layer creates a copy of its input, shifts it along in time and applies antenna responses to both the input and shifted signal.
+The result is a 2x1024 times series waveform representing an overlay data stream from two detector outputs.
+An example of each signal family is shown in Fig.
+\ref{fig:train}.
 
@@
 The discriminator network mirrors that of the generator without batch normalization, using LeakyReLU activations, SpatialDropout, and a 2-stride convolution for downsampling.
-The main difference is that the discriminator has two output layers.
-The first output is a single node activated by a Sigmoid that can be interpreted as the realness of the the signal.
-The second output is 5 nodes activated using the softmax function predicting the class of the input.
+The main difference is that the discriminator has two output layers: the first output is a single node activated by a Sigmoid that can be interpreted as the realness of the the signal, the second output is 5 nodes activated using the softmax function predicting the class of the input.
 This model is trained with binary cross entropy for the first output and sparse categorical cross-entropy for the second output.
-\jordan{Diagram of generator with box and showing the concate procedure}
-
-\subsection{Applying Antenna responses}
-We consider a two detector case where the generator should be trained to output two identical signals with a physical time shift representing the time of flight between detectors and the suppression of amplitudes due to interaction with the detector.
-To achieve this, the generator is trained to generate a single waveform that is then manipulated through a non-trainable ``response" layer.
-This layer creates a copy of its input, shifts it along in time and applies antenna responses to both the input and shifted signal.
-The result is a 2x1024 times series waveform representing an overlay data stream from two detector outputs.
+Neural networks and subsequently GANs have multiple parameters a developer can tune when designing the model referred to as hyperparameters.
+The final network design used in this work comes from the use of trial and error and the initial designs influenced by the available literature.
+After tuning the multiple hyperparamters (Table \ref{Tab:hyperparameters}), the GAN is trained for 600000 iterations which in real time is $\Or$(1) day.
+\begin{comment}
+include Plot_NN to show generator architecture
+\end{comment}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{comment}
 
@@
 \end{itemize}
+\end{comment}
+
+Given a 100 dimensional vector drawn from a normal distribution, an integer class label and sky localisation information, the GAN is able to generate burst-like waveforms  generalised from the training set.
+We set out by describing the quality of generated waveforms and how they compare to the training set.
+We then explore the structure of the latent and class spaces by interpolating between points in these spaces.
+We test vector arithmetic that can be used to generate a new breed of signal by merging two or more families together.
+Finally, we discuss the capacity of the discriminator as a GW burst classifier and the auxiliary component of this work.
 
 \subsection{Waveform quality}
+The generator network is a function G : $\mathbf{z},\mathbf{c},\mathbb{\textbf{s}}$ $\in$ $\mathbb{R}^{100}$ $\to$ $\mathbb{R}^{1024\times2}$, where $\mathbf{z},\mathbf{c},\mathbb{\textbf{s}}$ are the latent vector, class vector and sky positions respectively.
+Given a latent vector randomly sampled from a normal distribution with zero mean and unit variance, a class label which is represented by a 120 dimensional vector for each class and antenna responses, the results from the generator can be seen in Fig.
+\ref{fig:gen_signals}.
+Each plot shows the output of the generator after given randomised $z$, $s$ and one of the five class vectors.
+
 \begin{figure}
     \centering
-    \includegraphics[width=\textwidth]{figures/gen_zoom_signals.png}
-    \caption{Top row: Output of generator when given latent vector and class integer. Bottom row: Detailed view of the same output}
+    \includegraphics[width=\textwidth]{figures/gen_sigs.png}
+    \caption{Generated waveforms after training and conditioning on five classes.
+The generator is able to capture the characteristics of each waveform and structure the class space to give control over which waveform to generate.
+Depending on the orientation of the detector with respect to a hypothetical signal in the sky, the waveforms may appear inverted, shifted in time and their strain attenuated.}
     \label{fig:gen_signals}
 \end{figure}
+\subsection{Latent space interpolation}
+In this section we explore the latent space formed by the generator by interpolation.
+Keeping the class space fixed and interpolating between to points in z we can see the full effect shown in Fig.
+\ref{fig:z_interp}.
+We can see that each plot shows plausible waveforms suggesting that the generator has constructed a smooth space unlike the discrete training case.
+Additionally as each class is given the same latent points to interpolate over, we can see that the waveforms cluster together with respect to their parameters.
+Visually, the sing-gaussian and ring-down waveforms share similar frequencies and the other signals show similar decays and starting epochs.
+The only exception is BBH waveforms, which is expected as they were trained with more variety of parameters and coinsitently have their peaks in the last quarter of the time series.
+\begin{figure}
+    \centering
+    \includegraphics[width=\textwidth]{figures/fixed_class_slerp.png}
+    \caption{Interpolations between two random latent points in z.
+Moving right along the columns moves a step in z while holding c fixed.
+Each row changes the class vector while maintaining the same interpolations in z.}
+    \label{fig:z_interp}
+\end{figure}
+\subsection{Class space interpolation}
+In order to explore the class space we keep the latent vector held constant and interpolate through the 5 classes.
+We construct a path between the 5 waveforms and show that the space is populated enough to allow for smooth transitions between classes.
+\begin{figure}
+    \centering
+    \includegraphics[width=\textwidth]{figures/fixed_z_slerp.png}
+    \caption{Class space interpolation with latent space held constant throughout.}
+    \label{fig:c_interp}
+\end{figure}
+
+\subsection{Vector Arithmetic}
 \subsection{Classifier}
-\subsection{Latent space interpolation}
-\subsection{Class space interpolation}
 
@@
 \end{tabular}\\
-
+\label{Tab:hyperparameters}
 \end{table}

### 2020-03-30 Paper_draft/main.tex
modified:   .DS_Store# 	new file:   Paper_draft/figures/adding.png 	new file:   Paper_draft/iopart-num.bib 	new file:   Paper_draft/iopart-num.bst 	new file:   Paper_draft/iopart-num_custom.bst 	modified:   Paper_draft/main.tex

@@
 \documentclass[12pt]{iopart}
+\bibliographystyle{iopart-num_custom}
 \usepackage{xcolor}
@@
 
-Gravitational-wave (GW) astronomy is now an established field, starting with the first detection of a binary black hole merger \cite{} on September 2015.
-Following this, the first and second observations runs (O1 and O2) of Advanced LIGO and Advanced Virgo reported several more mergers \cite{}.
+Gravitational-wave (GW) astronomy is now an established field, starting with the first detection of a binary black hole merger \cite{Abbott2016} on September 2015.
+Following this, the first and second observations runs (O1 and O2) of Advanced LIGO and Advanced Virgo reported several more mergers \cite{Abbott2016a, Abbott2017, Abbott2017a, Abbott2017b}.
 On August 2017 a binary neutron star merger was observed alongside its electron-magnetic counterpart for the first time, giving rise to multimessenger gravitational wave astronomy.
@@
 Astrophysical sources for such transients include: Core collapse supernova, Neutron star instabilities, Fallback accretion onto a neutron star, Non axisymetric deformation in magnetars, Pulsar glitches, Neutron star post-mergers.
-Black hole accretion disk fragmentation..
-Since GW bursts are un-modelled they are not sensitive to template based detection schemes such as matched-filtering \cite{}, instead, detection involves distinguishing the signal from detector noise.
+As GW bursts are un-modelled they are not sensitive to template based detection schemes such as matched-filtering \cite{Owen1998}, instead, detection involves distinguishing the signal from detector noise.
 This is only possible if the detector noise is well characterised and the candidate signal can be differentiated from system or environmental glitches.
 As such, GW burst searches rely on an astrophysical burst signature appearing in multiple detectors.
-Many GW burst algorithms \cite{} are tested and tuned using model waveforms that may or may not have astrophysical significance but have easy to define parameters and share characteristics of real bursts that is enough to simulate coincident non-stationary deviations between detectors.
+Many GW burst algorithms \cite{Klimenko_2008, Aso_2008} are tested and tuned using model waveforms that may or may not have astrophysical significance but have easy to define parameters and share characteristics of real bursts that is enough to simulate coincident non-stationary deviations between detectors.
 Such waveforms may have long-duration, short bandwidth (ringdowns), long-duration, large bandwidth (inspirals) and many algorithms make use of sine-Gaussians: a Gaussian modulated sine wave that is characterised by it's central frequency and narrow bandwidth.
@@
 We aim to explore the use of machine learning in generating and interpreting these mock GW burst signals.
-Neural networks have shown to replicate the sensitivities of matched filtering in GW detection \cite{} and rapid parameter estimation \cite{}, however these methods have primarily been focused on binary black hole signals and have not yet expanded to burst examples.
+Neural networks have shown to replicate the sensitivities of matched filtering in GW detection \cite{Gabbard2017} and rapid parameter estimation \cite{gabbard2019bayesian}, however these methods have primarily been focused on binary black hole signals and have not yet expanded to burst examples.
 
@@
 
-A subset of deep learning that has seen fruitful development in recent years \cite{} is Generative Adversarial Networks (GANs).
+A subset of deep learning that has seen fruitful development in recent years \cite{Goodfellow2014} is Generative Adversarial Networks (GANs).
 These unsupervised algorithms learn patterns in a given training data set using an adversarial process.
-The generations from GANs are state-of-the-art in fields such as high quality image fidelity, image and text-to-image translation and video prediciton \cite{} and there is notable works on time series generations /cite.
-GANs work to train two competing neural networks, consisting of a discriminator  that is trained to distinguish
+The generations from GANs are state-of-the-art in fields such as high quality image fidelity \cite{brock2018large,karras2019analyzing}, text-to-image translation \cite{reed2016generative} and video prediction \cite{liang2017dual} as well as time series generations \cite{esteban2017realvalued}.
+GANs train two competing neural networks, consisting of a discriminator that is set up to distinguish
 between real and fake data and a generator that produces synthetic
-reproductions of the real data. The generator perform a mapping
-from an input noise vector \textbf{z} to its representation of the data and discriminator  maps its
+reproductions of the real data. The generator performs a mapping
+from an input noise vector \textbf{z} to its representation of the data and the discriminator  maps its
 input \textbf{x} to a probability that the input came form either the training
-data or generator.  During training, discriminator  is given a batch of samples that contains one half real data (labelled as 1)
-and one half fake data (labelled as 0) which it then makes predictions on. The
+data or generator.  During training, the discriminator is given a batch of samples that contains one half real data
+and one half fake data which it then makes predictions on. The
 loss for discriminator  is calculated by comparing its predictions to the labelled data through the binary cross-entropy function. The training process
@@
 encourages discriminator  to update its classification abilities. Both networks compete
-in a minimax game that is tied to a value function V (D, G) which generator is trying
-minimise and discriminator  is trying to maximise:
+in a minimax game which generator is trying
+minimise and the discriminator is trying to maximise:
 
@@
 \subsection{Auxiliary conditional GANs}
-In theory, the adversarial process will eventually lead to the local Nash equilibrium [18] where
+In theory, the adversarial process will eventually lead to the local Nash equilibrium \cite{Nash1950} whereby
 both neural networks are trained optimally. In practice, however, GANs are
@@
 gradients when applying gradient descent to a
-non-continuous function. To overcome some of these difficulties [blank]
-proposed adding structure to the latent space by providing G with a class
+non-continuous function. To overcome some of these difficulties, a conditional-GAN (CGANs) \cite{cgan}
+adds structure to the latent space by providing the generator with a class or attribute
 label. This has the effect of making a point in latent space conditional on a
-provided class. [blank] extends this idea further by requiring D to output a
-probability of the data belonging to each class. A pictorial representation on the differences between these approaches is show below.
+provided class. This idea was extended further with auxiliary conditional GANs (ACGANs) \cite{odena2016conditional} that require the discriminator to output a
+probability of data belonging to each class. A pictorial representation on the differences between these approaches is show below.
 
-\begin{figure}[h!]
+\begin{figure}
     \centering
-    %\begin{subfigure}[h]{0.5\textwidth}
-        %\centering
         \input{figures/GAN_diagram_vertical}%     without .tex extension
-    %\end{subfigure}\hfill
-    %\begin{subfigure}[h]{0.5\textwidth}
-       % \centering
         \input{figures/ACGAN_diagram_vertical}%     without .tex extension
-    %\end{subfigure}\hfill
     \caption{Comparison of the original GAN method and the Auxiliary Conditional-GAN method.
@@
 \subsection{Vector Arithmetic}
+\begin{figure}
+    \centering
+    \includegraphics[width=\textwidth]{figures/adding.png}
+    \caption{Vector arithmetic for unmodelled waveforms.
+Keeping the z vectors constant and generating two classes of signals, their class embedding vectors can the be summed to give a new waveform that is comprised of the two classes.}
+    \label{fig:add}
+\end{figure}
 \subsection{Classifier}
@@
 \end{itemize}
+
+\section*{References}
+\bibliography{iopart-num}
 

### 2020-04-06 Paper_draft/main.tex
update

@@
 
-\title{Generative Adversarial Networks and Gravitational Waves}
+\title{Generalised gravitational burst waveform generation with Generative Adversarial Networks}
 
@@
     \centering
-    \includegraphics[width=\textwidth]{figures/train.pdf}
+    \includegraphics[scale=0.7]{figures/training.pdf}
     \caption{Examples of burst training signals. From left to right: sine-gaussian, ringdown, white-noise burst, Gaussian, binary-black hole merger.}
@@
 \subsection{Applying Antenna responses}
-We consider a two detector case where the generator should be trained to output two identical signals with a physical time shift representing the time of flight between detectors and the suppression of amplitudes due to interaction with the detector.
+We consider a two detector case in which the generator is trained to output two identical signals with a physical time shift representing the time of flight between detectors and the suppression of amplitudes due to interaction with the detector.
 To achieve this, the generator is trained to output a single waveform that is then put through a non-trainable ``response" layer as the final layer of the generator.
@@
 \subsection{Architecture details}
-We base the architecture on (cite DCGANS) and adopt the suggestions of (cite wavegan paper) lengthening one-dimensional convolution kernels on both the generator and discriminator.
+We base the architecture on deep convolutional generative adversarial networks \cite{Radford2015} and adopt the suggestions of \cite{DBLP:journals/corr/abs-1809-11096} lengthening one-dimensional convolution kernels on both the generator and discriminator.
 The class label is interpreted as an additional channel early in the generator model.
@@
 \ref{fig:gen_signals}.
+Depending on the orientation of the detector with respect to a hypothetical signal in the sky, the waveforms may appear inverted, shifted in time and their strain attenuated.
 Each plot shows the output of the generator after given randomised $z$, $s$ and one of the five class vectors.
 
-\begin{figure}
+\begin{figure}[h]
     \centering
-    \includegraphics[width=\textwidth]{figures/gen_sigs.png}
+    \includegraphics[width=\textwidth]{figures/generations.pdf}
     \caption{Generated waveforms after training and conditioning on five classes.
+The generator will output 2 identical waveforms shifted in time (shown by light and dark blue lines) and their amplitudes reduced by detector response.
 The generator is able to capture the characteristics of each waveform and structure the class space to give control over which waveform to generate.
-Depending on the orientation of the detector with respect to a hypothetical signal in the sky, the waveforms may appear inverted, shifted in time and their strain attenuated.}
+Each row shows a random assortment of one of the five classes the GAN is trained on.
+}
     \label{fig:gen_signals}
 \end{figure}
+
 \subsection{Latent space interpolation}
@@
 The only exception is BBH waveforms, which is expected as they were trained with more variety of parameters and coinsitently have their peaks in the last quarter of the time series.
-\begin{figure}
+\begin{figure}[h]
     \centering
-    \includegraphics[width=\textwidth]{figures/fixed_class_slerp.png}
+    \includegraphics[width=\textwidth]{figures/fix_c_interp_z.pdf}
     \caption{Interpolations between two random latent points in z.
-Moving right along the columns moves a step in z while holding c fixed.
-Each row changes the class vector while maintaining the same interpolations in z.}
+Each row uniformly interpolates between two points in $\mathbf{z}$ keeping the class fixed.
+Each subplot shows the next interpolated signal (dark line) and the fixed point in $\mathbf{z}$ (light line).
+}
     \label{fig:z_interp}
@@
     \centering
-    \includegraphics[width=\textwidth]{figures/fixed_z_slerp.png}
-    \caption{Class space interpolation with latent space held constant throughout.}
+    \includegraphics[width=\textwidth]{figures/fix_z_interp_c.pdf}
+    \caption{Class space interpolation with latent space held constant throughout. }
     \label{fig:c_interp}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\textwidth]{figures/4_corners.pdf}
+    \caption{We generate the four corners of the grid, then interpolate between both the z and c vectors.
+Although the network was only trained on binary attributes for c, interpolation results show that the computed latent space is smooth between attributes, and not simply discrete to those shown in the training set.}
+    \label{fig:4_c_interp}
 \end{figure}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
+\begin{comment}
 \begin{itemize}
@@
 \end{itemize}
+\end{comment}
 
+\newpage
 \section*{References}

### 2020-04-17 Paper_draft/main.tex
New changes for first draft

@@
 \usepackage{comment}
-%\usepackage{subcaption}
+%\usepackage{subcaptncluon}
 \usepackage{tikz}
@@
 \usepackage{amssymb}
+\usepackage{hyperref}
 \newcommand{\gguide}{{\it Preparing graphics for IOP Publishing journals}}
@@
 
-\title{Generalised gravitational burst waveform generation with Generative Adversarial Networks}
+\title{Generalised gravitational burst generation with Generative Adversarial Networks}
 
-\author{J. McGinn}
+\author{J. McGinn, C. Messenger, I.S. Heng}
 
@@
 \begin{abstract}
-
+The next generation of Gravitational wave detectors will accelerate the number of gravitational wave detection's such that we can gain new in site into the physics behind the sources causing the phenomena.
+Numerical simulations and matched filtering are the standard for detecting gravitational waves for know sources such as binary-black hole mergers.
+Other sources of gravitational waves that remain elusive to standard modelling techniques and are expected to be detectable, however, there must be a way to characterise them in order to build a model template.
+Here we construct a unmodeled burst generation scheme using Generative adversarial networks - a powerful class of machine learning.
 \end{abstract}
@@
 On August 2017 a binary neutron star merger was observed alongside its electron-magnetic counterpart for the first time, giving rise to multimessenger gravitational wave astronomy.
+
 GW bursts are transient signals of typically short duration ($<$ 1s) whose waveforms are not accurately modelled or are complex to re-produce.
-Astrophysical sources for such transients include: Core collapse supernova, Neutron star instabilities, Fallback accretion onto a neutron star, Non axisymetric deformation in magnetars, Pulsar glitches, Neutron star post-mergers.
+Astrophysical sources for such transients include: Core collapse supernova, Neutron star instabilities, Fallback accretion onto a neutron star, Non axisymetric deformation in magnetars, Pulsar glitches and Neutron star post-mergers.
 As GW bursts are un-modelled they are not sensitive to template based detection schemes such as matched-filtering \cite{Owen1998}, instead, detection involves distinguishing the signal from detector noise.
@@
 This makes it a great tool for diagnosing LIGOs sensitivity to frequency.
+
 We aim to explore the use of machine learning in generating and interpreting these mock GW burst signals.
@@
 The generations from GANs are state-of-the-art in fields such as high quality image fidelity \cite{brock2018large,karras2019analyzing}, text-to-image translation \cite{reed2016generative} and video prediction \cite{liang2017dual} as well as time series generations \cite{esteban2017realvalued}.
-GANs train two competing neural networks, consisting of a discriminator that is set up to distinguish
-between real and fake data and a generator that produces synthetic
+
+GANs train two competing neural networks, consisting of a discriminator that is set up to distinguish between real and fake data and a generator that produces synthetic
 reproductions of the real data. The generator performs a mapping
@@
 gradients when applying gradient descent to a
-non-continuous function. To overcome some of these difficulties, a conditional-GAN (CGANs) \cite{cgan}
+non-continuous function.
+
+To overcome some of these difficulties, a conditional varient of GANs named Conditional-GAN (CGANs) \cite{cgan}
 adds structure to the latent space by providing the generator with a class or attribute
-label. This has the effect of making a point in latent space conditional on a
-provided class. This idea was extended further with auxiliary conditional GANs (ACGANs) \cite{odena2016conditional} that require the discriminator to output a
-probability of data belonging to each class. A pictorial representation on the differences between these approaches is show below.
+label.
+The generator learns to segment the latent space by clustering distributions which have similar properties, making a point in latent space conditional on a class.
+This idea was extended further with auxiliary conditional GANs (ACGANs) \cite{odena2016conditional} that require the discriminator to output a
+probability of data belonging to each class. A pictorial representation on the differences between these approaches in Figure \ref{fig:gan_comparison}.
 
@@
 Additionaly, the discrminator learns to classify which class the signal belongs to.}
+    \label{fig:gan_comparison}
 \end{figure}
@@
 	BBH signals are simulated using IMRPhenomD waveform routine from LALSuite which models the inspiral, merger and ringdown of a BBH waveform.
-The component masses lie in the range of [5,70]M$_0$ with zero spins and we fix m$_1$1$>$m$_2$.
+The component masses lie in the range of [5,70]M$_0$ with zero spins and we fix m$_1$ $>$ m$_2$.
 The mass distribution is approximated by a power law with index of 1.6 https://arxiv.org/abs/1811.12940.
@@
     \centering
-    \includegraphics[scale=0.7]{figures/training.pdf}
-    \caption{Examples of burst training signals. From left to right: sine-gaussian, ringdown, white-noise burst, Gaussian, binary-black hole merger.}
+    \includegraphics[width=\textwidth]{figures/train_gen.pdf}
+    \caption{Examples of simulated burst gravitational wave signals.
+Top row shows examples from the training set.
+From left to right: Sine-Gaussian, Ringdown, White-noise burst, Gaussian, Binary black hole merger.
+The bottom row shows the conditional generations from the GAN.
+}
     \label{fig:train}
@@
 
-\subsection{Applying Antenna responses}
-We consider a two detector case in which the generator is trained to output two identical signals with a physical time shift representing the time of flight between detectors and the suppression of amplitudes due to interaction with the detector.
-To achieve this, the generator is trained to output a single waveform that is then put through a non-trainable ``response" layer as the final layer of the generator.
-This layer creates a copy of its input, shifts it along in time and applies antenna responses to both the input and shifted signal.
-The result is a 2x1024 times series waveform representing an overlay data stream from two detector outputs.
-An example of each signal family is shown in Fig.
-\ref{fig:train}.
-
 \subsection{Architecture details}
-We base the architecture on deep convolutional generative adversarial networks \cite{Radford2015} and adopt the suggestions of \cite{DBLP:journals/corr/abs-1809-11096} lengthening one-dimensional convolution kernels on both the generator and discriminator.
-The class label is interpreted as an additional channel early in the generator model.
-This is achieved by projecting the class inputs as a learned embedding layer, into a fully connected layer which can then be concatenated channel-wise to $\textbf{z}$.
-The rest of the model is fully convolutional, upsampled using strided transposed convolutions with batchnormalisation in the first layer and ReLU activations throughout with the exception of Tanh for the output layer.
+Extensions to the original GAN method such as  DCGANs \cite{Radford2015} have been widely praised for building a stable GAN architecture.
+Modern GAN research favours a fully convolution neural network which replace upsampling procedures like maxpooling to strided convolutions.
+Convolutional neural networks (CNNs) are designed to work with grid-like structures that exhibit strong local spatial dependencies.
+Although most work with CNNs involve image based data, they can be applied to other spatially adjacent data types such as time-series and text items.
+Audio synthesis work \cite{DBLP:journals/corr/abs-1809-11096} has showed that GANs can achieve recognisable audio within a few hours.
+We adopt the suggestions of these papers, lengthening one-dimensional convolution kernels on both the generator and discriminator.
+The Generator model is fully convolutional, upsampled using strided transposed convolutions with batchnormalisation in the first layer and ReLU activations throughout with the exception of Tanh for the output layer.
 Each transposed convolutional layer uses a kernel size of 18x1 and stride 2.
 The discriminator network mirrors that of the generator without batch normalization, using LeakyReLU activations, SpatialDropout, and a 2-stride convolution for downsampling.
-The main difference is that the discriminator has two output layers: the first output is a single node activated by a Sigmoid that can be interpreted as the realness of the the signal, the second output is 5 nodes activated using the softmax function predicting the class of the input.
+The discriminator has two output layers: the first output is a single node activated by a Sigmoid that can be interpreted as the realness of the the signal, the second output is 5 nodes activated using the softmax function predicting the class of the input.
 This model is trained with binary cross entropy for the first output and sparse categorical cross-entropy for the second output.
+
 Neural networks and subsequently GANs have multiple parameters a developer can tune when designing the model referred to as hyperparameters.
 The final network design used in this work comes from the use of trial and error and the initial designs influenced by the available literature.
-After tuning the multiple hyperparamters (Table \ref{Tab:hyperparameters}), the GAN is trained for 600000 iterations which in real time is $\Or$(1) day.
+After tuning the multiple hyperparamters (Table \ref{Tab:hyperparameters}), the GAN was trained for 600000 iterations and takes $\Or$(1) day to train.
+
+\subsection{Class labels and embedding}
+A learned embedding is an efficient way of representing categorical or class based data.
+In contrast to traditional "one-hot encoding" where each class is represented by a binary sparse vector, embeddings map each class to its own distinct vector of a given size.
+The elements of these vectors are initialized randomly and tuned during training just like weights.
+This reduces computational cost as the sparse vectors containing mostly zeros are not needed and allows related classes to cluster together.
+Once the networks are trained the learned embedding vectors can be extracted from the model and used as inputs to the generator.
+The benefit here is that the former integer class labels are replaced by higher dimensional vector representations allowing for finer experimenting in other applications.
+The class label is interpreted as an additional channel early in the generator model.
+This is achieved by projecting the class inputs as a learned embedding layer, into a fully connected layer or "dense" layer which can then be concatenated channel-wise to $\textbf{z}$.
+
+\subsection{Applying a time shift and antenna responses}
+We consider a two detector case in which the generator is trained to output two identical signals with a physical time shift representing the time of flight between detectors and the suppression of amplitudes due to interaction with the detector.
+To achieve this, the generator is trained to output a single waveform that is then put through a non-trainable ``response" layer before the output of the generator.
+This layer creates a copy of its input, shifts it along in time and applies antenna responses to both the input and shifted signal.
+The time shift is achieved by converting the waveform to frequency space, multiplying by $e^{2 \pi i f dt}$, where $dt$ is the time shift and converting back to the time domain.
+After which both original and shifted signals are multiplied by the antenna responses.
+Both dt and the antenna responses are calculated using the LALSimulation \cite{lalsuite} package and we choose Hanford and Livingston as detection points.
+The result is a 2x1024 times series waveform representing an overlay data stream from two detector outputs.
+This scheme is also used in generating the training set.
+
 \begin{comment}
@@
 
-Given a 100 dimensional vector drawn from a normal distribution, an integer class label and sky localisation information, the GAN is able to generate burst-like waveforms  generalised from the training set.
+Given a 100 dimensional vector drawn from a normal distribution, a class label and sky localisation information, the GAN is able to generate burst-like waveforms  generalised from the training set.
 We set out by describing the quality of generated waveforms and how they compare to the training set.
@@
 \subsection{Waveform quality}
-The generator network is a function G : $\mathbf{z},\mathbf{c},\mathbb{\textbf{s}}$ $\in$ $\mathbb{R}^{100}$ $\to$ $\mathbb{R}^{1024\times2}$, where $\mathbf{z},\mathbf{c},\mathbb{\textbf{s}}$ are the latent vector, class vector and sky positions respectively.
-Given a latent vector randomly sampled from a normal distribution with zero mean and unit variance, a class label which is represented by a 120 dimensional vector for each class and antenna responses, the results from the generator can be seen in Fig.
-\ref{fig:gen_signals}.
+The generator network is a function G : $\mathbf{z},\mathbf{c},\mathbb{\textbf{s}}$ $\in$ $\mathbb{R}^{100}$ $\to$ $\mathbb{R}^{1024\times2}$, where $\mathbf{z},\mathbf{c},\mathbb{\textbf{s}}$ are the latent vector, class embedding vector and sky positions respectively.
+Given a latent vector randomly sampled from a normal distribution with zero mean and unit variance, a class label which is represented by a 120 dimensional vector for each class and antenna responses, the results from the generator can be seen in Figure \ref{fig:gen_signals}.
 Depending on the orientation of the detector with respect to a hypothetical signal in the sky, the waveforms may appear inverted, shifted in time and their strain attenuated.
-Each plot shows the output of the generator after given randomised $z$, $s$ and one of the five class vectors.
+Each plot shows the output of the generator after given randomised $\mathbf{z}, \mathbb{\textbf{s}}$ and one of the five class vectors $\mathbf{c}$.
 
-\begin{figure}[h]
+\begin{figure}[ht]
     \centering
-    \includegraphics[width=\textwidth]{figures/generations.pdf}
+    \includegraphics[width=\textwidth]{figures/conditional_gens.pdf}
     \caption{Generated waveforms after training and conditioning on five classes.
-The generator will output 2 identical waveforms shifted in time (shown by light and dark blue lines) and their amplitudes reduced by detector response.
+The generator will output two waveforms as seen by detectors in Hanford (red) and Livingston (blue).
 The generator is able to capture the characteristics of each waveform and structure the class space to give control over which waveform to generate.
@@
 
+\subsection{Interpolation}
+Machine learning algorithms are often described as universal function approximators.
+In the generators case it maps samples drawn from a 100 dimensional Gaussian space to its representation of the training set.
+As with any function, there should be a one to one mapping from the domain and co-domain to allow for smooth transitions across the latent space.
+One advantage of using GANs as a waveform generator is that once it is trained, it can perform rapid generations faster than more intricate and computationally expensive algorithms.
+For complicated data sets, the network architecture must be diverse and dense enough to capture distinct variations from the training set.
+Most GANs perform well on relatively low resolution image generations, however, higher resolutions demand larger networks and long training times.
+GANs attempting to replicate complicated structures and do not have the necessary architecture either struggle to produce results at all or fall into the common failure mode know as mode collapse; where the generator produces a small variety of samples or simply memorises the training set.
+To test this, we perform linear interpolations in the latent and class space.
+
 \subsection{Latent space interpolation}
 In this section we explore the latent space formed by the generator by interpolation.
-Keeping the class space fixed and interpolating between to points in z we can see the full effect shown in Fig.
-\ref{fig:z_interp}.
+We take two random points in the latent space and linearly interpolate between them (six times inclusive).
+These new latent space vectors can now be fed into the generator to make predictions on while keeping the class vectors constant.
+The third input, the response values are kept constant for each class.
+The full effect shown in Figure \ref{fig:z_interp}.
 We can see that each plot shows plausible waveforms suggesting that the generator has constructed a smooth space unlike the discrete training case.
 Additionally as each class is given the same latent points to interpolate over, we can see that the waveforms cluster together with respect to their parameters.
-Visually, the sing-gaussian and ring-down waveforms share similar frequencies and the other signals show similar decays and starting epochs.
-The only exception is BBH waveforms, which is expected as they were trained with more variety of parameters and coinsitently have their peaks in the last quarter of the time series.
-\begin{figure}[h]
+Visually, the sine-gaussian and ring-down waveforms share similar frequencies and the other signals show similar decays and starting epochs.
+The only exception is BBH waveforms, which is expected as they were trained with more variety of parameters and consistently have their peaks in the last quarter of the time series.
+
+\begin{figure}[ht]
     \centering
-    \includegraphics[width=\textwidth]{figures/fix_c_interp_z.pdf}
+    \includegraphics[width=\textwidth]{figures/z_interp_fix_c.pdf}
     \caption{Interpolations between two random latent points in z.
 Each row uniformly interpolates between two points in $\mathbf{z}$ keeping the class fixed.
-Each subplot shows the next interpolated signal (dark line) and the fixed point in $\mathbf{z}$ (light line).
-}
+Only a single waveform from the generator is plotted and each signal is re-scaled to [-1,1] effectively removing the antenna responses for clarity.}
     \label{fig:z_interp}
 \end{figure}
+
 \subsection{Class space interpolation}
 In order to explore the class space we keep the latent vector held constant and interpolate through the 5 classes.
-We construct a path between the 5 waveforms and show that the space is populated enough to allow for smooth transitions between classes.
+We construct a path between the 5 waveforms and show that the space is populated enough to allow for transitions between classes.
+Sine-Gaussian to ringdown performs well in interpolation with each signal being a plausible burst GW.
+It is obvious that the embedding layer has clustered these two groups during training as they share many characteristics.
+The other signals have sharper transitions but still retain plausible looking waveforms.
+
 \begin{figure}
     \centering
-    \includegraphics[width=\textwidth]{figures/fix_z_interp_c.pdf}
-    \caption{Class space interpolation with latent space held constant throughout. }
+    \includegraphics[width=\textwidth]{figures/4_c_interp.pdf}
+    \caption{Class space interpolation with latent space held constant throughout.
+The plots show a zoomed in section of the 1s time interval.
+Top row: Sine-Gaussian class to ringdown class, Middle Row: Sine-Gaussian class to whitenoise burst class, Bottom row: Sine-Gaussian class to Gaussian class.}
     \label{fig:c_interp}
@@
 
+\begin{figure}
+    \centering
+    \includegraphics[width=\textwidth]{figures/sg_bbh_interp.pdf}
+    \caption{Class space interpolation with latent space held constant throughout. The full 1s interval is plotted for class based interpolations between a Sine-Gaussian and a BBH in spiral.}
+    \label{fig:sgbbh_interp}
+\end{figure}
+
+\begin{comment}
 \begin{figure}
@@
 \end{figure}
+\end{comment}
 
 \subsection{Vector Arithmetic}
+In DCGANs the authors demonstrated unsupervised vector arithmetic with celebrity face generation.
+They kept points in the latent space and performed simple vector arithmetic to generate new images.
+This allows for intuitive and targeted generation of images.
+However, the authors realised that single images vectors were unstable and there was a need to average three vectors before any arithmetic.
+DCGANs is unconditional, therefore, the vectors used were chosen empirically, generating many faces and choosing the attributes for study.
+Here, we show that this GAN only needs a single vector representation and due to conditioning we can have more control over which vectors to use in the arithmetic.
+In Figure \ref{fig:arithmetic} we generate a whitenoise burst and a BBH insprial using their respective class labels and use a randomised latent point and response.
+Keeping the latent point and response, we average the two class vectors and use this as input to the generator.
+Figure \ref{fig:arithmetic} (c) shows the generation based on the combined class vectors which visually looks similar to a supernova waveform.
+Supernova waveform generations require expensive numerical relativity simulations and various assumptions about the collapse of its parent star.
+Here, we are able to produce similar waves at a fraction of the expense and we are able to further modify the resultant by using different latent space samples.
+\jordan{this is the adding noise thing but i need to work out the correct way to do it with the directional vector}.
+
 \begin{figure}
   \centering
-    \includegraphics[width=\textwidth]{figures/adding.png}
+  \begin{tabular}[b]{c}
+    \includegraphics[width=0.9\textwidth]{figures/wn+bbh.pdf} \\
+    \small ~~~~~~~~~(a)
+  \end{tabular} %\qquad
+
+  \begin{tabular}[b]{c}
+    \includegraphics[width=0.46\textwidth]{figures/ambient_result.pdf} \\
+    \small ~~~~~~~~(b)
+  \end{tabular}
+ \begin{tabular}[b]{c}
+    \includegraphics[width=0.44\textwidth]{figures/arithmetic_result.pdf} \\
+    \small ~~~~~~~~(c)
+  \end{tabular}
+  \caption{Conditional vector arithmetic.
+(a) Generated samples of a whitenoise burst and BBH insprial.
+(c) Effect of naively adding the components from (a) in the time domain.
+\jordan{just adding the two signals post generation} (c) Generation from the combined class vectors.
+}
+  \label{fig:arithmetic}
+\end{figure}
+
+\begin{comment}
+\begin{figure}
+    \centering
+    \includegraphics[width=\textwidth]{figures/arithm.pdf}
     \caption{Vector arithmetic for unmodelled waveforms.
-Keeping the z vectors constant and generating two classes of signals, their class embedding vectors can the be summed to give a new waveform that is comprised of the two classes.}
+Keeping the z vectors constant and generating two classes of signals, their class embedding vectors can then be averaged to produce a new class.
+The generator produces a waveform of this hybrid class (middle of right plot).
+For the surrounding 8 plots we add a small variance of Gaussian noise to the new class.
+}
     \label{fig:add}
 \end{figure}
+\end{comment}
 \subsection{Classifier}
+\jordan{I'm working on this part and how to present the auxiliary part.}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+In this work we present the potential of Generative Adversarial Networks for burst gravitational wave analysis.
+We have shown that GANs have the ability to generate 5 class varieties of modelled burst GW signals that can be generated at whim.
+The latent and class spaces were explored through interpolation and suggest that the space provides smooth translations between classes and overall waveform shape.
+We then showed targeted waveform generation by mixing classes to produce new unmodlled waveform varieties that can be used to test current burst search pipelines.
+\jordan{couple of sentences about classifier}.
+
+In order to extend this work to a viable burst wave generator and classifier a few points require further research.
+In principle it is trivial to add another detector inside the response layer \jordan{response is the wrong thing to say since the time delay isnt really a response, extrinsic layer?
+just non trainable layer?
+The box?}, however, as this now 3 dimensional signal is feed to the discriminator this will no doubt require further tweaking of the network.
+We can add more burst-like wave forms in the training set, like detector glitches which would similarly require further network design.
+The work presented here is noise free.
+To havea complete generation and detection package we would like to train the network on signals hidden in additive Gaussian noise and test the ability of the auxiliary classifier.
+
+The approach shown in this work shows promise in generating unmodelled burst waveforms from exotic sources.
+Having the ability to quickly generate new waveforms is essential to test current detection schemes and their susceptibilty to unmodelled sources.
+We belive that GANs have the ability to generate high fidelity waveforms at a fraction of the computational expense and do not rely on large prior parameter space.
+Having banks of these waveforms at hand can aid in our understand of the physics processes behind these non-standard gravitational wave emitters.
+
+\jordan{I want to include a link to the github etc but also a google collab scrip like the one for BigGANs: \\
+\url{https://colab.research.google.com/github/tensorflow/hub/blob/master/examples/colab/biggan_generation_with_tf_hub.ipynb.} 
+It's fun and gives a better feel for the interpolating that static images.}
+
 \begin{comment}
@@
 
-\newpage
 \section*{References}
@@
 
+\section{Many more generated examples}
+
 \end{document}

### 2020-04-27 Paper_draft/main.tex
Added comments up to 3.1 and added a makefile

@@
 \usepackage{comment}
+\usepackage{acronym}
 %\usepackage{subcaptncluon}
@@
 \newcommand{\michael}[1]{\textbf{\textcolor{orange}{MICHAEL: #1}}}
+\newcommand{\dcc}{LIGO-PXXXXXXX}
+\input{tag.tex}
 \begin{document}
@@
 \begin{indented}
-\item[]March 2020
+\item[]\commitDATE\\\mbox{\small \commitID}\\\mbox{\dcc}
 \end{indented}
@@
 \begin{abstract}
-The next generation of Gravitational wave detectors will accelerate the number of gravitational wave detection's such that we can gain new in site into the physics behind the sources causing the phenomena.
-Numerical simulations and matched filtering are the standard for detecting gravitational waves for know sources such as binary-black hole mergers.
-Other sources of gravitational waves that remain elusive to standard modelling techniques and are expected to be detectable, however, there must be a way to characterise them in order to build a model template.
-Here we construct a unmodeled burst generation scheme using Generative adversarial networks - a powerful class of machine learning.
+The next generation of Gravitational wave detectors will accelerate the number
+of gravitational wave detection's such that we can gain new in site into the
+physics behind the sources causing the phenomena. Numerical simulations and
+matched filtering are the standard for detecting gravitational waves for know
+sources such as binary-black hole mergers. Other sources of gravitational waves
+that remain elusive to standard modelling techniques and are expected to be
+detectable, however, there must be a way to characterise them in order to build
+a model template. Here we construct a unmodeled burst generation scheme using
+Generative adversarial networks - a powerful class of machine learning.
 \end{abstract}
@@
 
+\acrodef{GW}[GW]{gravitational wave}
+\acrodef{GAN}[GAN]{generative adversarial networks}
+\acrodef{CGAN}[CGAN]{conditional generative adversarial networks}
+\acrodef{ACGAN}[ACGAN]{auxilliary conditional generative adversarial networks}
+\acrodef{BBH}[BBH]{binary black hole}
+
 \section{Introduction}
@@
 
-Gravitational-wave (GW) astronomy is now an established field, starting with the first detection of a binary black hole merger \cite{Abbott2016} on September 2015.
-Following this, the first and second observations runs (O1 and O2) of Advanced LIGO and Advanced Virgo reported several more mergers \cite{Abbott2016a, Abbott2017, Abbott2017a, Abbott2017b}.
-On August 2017 a binary neutron star merger was observed alongside its electron-magnetic counterpart for the first time, giving rise to multimessenger gravitational wave astronomy.
+% introduce \ac{GW} astrophsyics
+%
+\ac{GW} astronomy is now an established field, starting with the first
+detection of a binary black hole merger \cite{Abbott2016} in September 2015.
+Following this, the first and second observations runs (O1 and O2) of Advanced
+LIGO and Advanced Virgo~\chris{need refs for the detectors, see here
+https://pnp.ligo.org/ppcomm/standard\_references.html} reported several more
+mergers \cite{Abbott2016a, Abbott2017, Abbott2017a, Abbott2017b}. On August
+2017 a binary neutron star merger was observed alongside its electromagnetic
+counterpart for the first time, giving rise to multimessenger gravitational
+wave astronomy.
 
-GW bursts are transient signals of typically short duration ($<$ 1s) whose waveforms are not accurately modelled or are complex to re-produce.
-Astrophysical sources for such transients include: Core collapse supernova, Neutron star instabilities, Fallback accretion onto a neutron star, Non axisymetric deformation in magnetars, Pulsar glitches and Neutron star post-mergers.
-As GW bursts are un-modelled they are not sensitive to template based detection schemes such as matched-filtering \cite{Owen1998}, instead, detection involves distinguishing the signal from detector noise.
-This is only possible if the detector noise is well characterised and the candidate signal can be differentiated from system or environmental glitches.
-As such, GW burst searches rely on an astrophysical burst signature appearing in multiple detectors.
-Many GW burst algorithms \cite{Klimenko_2008, Aso_2008} are tested and tuned using model waveforms that may or may not have astrophysical significance but have easy to define parameters and share characteristics of real bursts that is enough to simulate coincident non-stationary deviations between detectors.
-Such waveforms may have long-duration, short bandwidth (ringdowns), long-duration, large bandwidth (inspirals) and many algorithms make use of sine-Gaussians: a Gaussian modulated sine wave that is characterised by it's central frequency and narrow bandwidth.
-This makes it a great tool for diagnosing LIGOs sensitivity to frequency.
+% introduce burst searches
+%
+GW bursts are transient signals of typically short duration ($<$ 1s) whose
+waveforms are not accurately modelled or are complex to re-produce.
+Astrophysical sources for such transients include: Core collapse supernova,
+Neutron star instabilities, Fallback accretion onto a neutron star, Non
+axisymetric deformation in magnetars, Pulsar glitches and Neutron star
+post-mergers.  As \ac{GW} bursts are un-modelled they are not sensitive to
+template based detection schemes~\chris{OK, but logically dodgy. You make it
+sound like we could use a template scheme but it would be insensitive. The
+point is that we don't have templates in the first place.} such as
+matched-filtering \cite{Owen1998}, instead, detection involves distinguishing
+the signal from detector noise. This is only possible if the detector noise is
+well characterised and the candidate signal can be differentiated from
+systematic or environmental glitches. As such, \ac{GW} burst searches rely on
+an astrophysical burst signature appearing in multiple detectors~\chris{at
+similar times?}.
 
-We aim to explore the use of machine learning in generating and interpreting these mock GW burst signals.
-Neural networks have shown to replicate the sensitivities of matched filtering in GW detection \cite{Gabbard2017} and rapid parameter estimation \cite{gabbard2019bayesian}, however these methods have primarily been focused on binary black hole signals and have not yet expanded to burst examples.
+% Discuss the family of burst waveforms currently used and why - not in detail, just
+% an introduction 
+%
+Many \ac{GW} burst algorithms \cite{Klimenko_2008, Aso_2008}~\chris{many? needs
+more than 2 refs for many.} are tested and tuned using model waveforms that may
+or may not have astrophysical significance but have easy to define parameters
+and share characteristics of real bursts that is enough to simulate coincident
+non-stationary deviations~\chris{fancy sounding but I'm not sure what
+non-stationary deviations means.} between detectors. Such waveforms may have
+long-duration, short bandwidth (ringdowns), long-duration, large bandwidth
+(inspirals) and many algorithms make use of sine-Gaussians: a Gaussian
+modulated sine wave that is characterised by it's central frequency and narrow
+bandwidth.~\chris{not the time to try to describe the types of burst waveforms.
+Also, be careful with satying things like ringdowns have narrow bandwidth. I
+know we specify a single frequency but becuase of the short duration, the
+signal is broad band. Look at the FFT} This makes it a great tool for
+diagnosing LIGOs sensitivity to frequency.~\chris{strange unfinished sentence.}
+
+% Introduce ML techniques in GWs
+%
+\chris{Introduce ML techniques in GWs}
+
+% What this paper does on GANs in 1 paragraph
+%
+\chris{What this paper does on GANs in 1 paragraph}
+
+% the point of the paper
+%
+\chris{describe the structure of the paper}
+We aim to explore the use of machine learning in generating and interpreting
+these mock \ac{GW} burst signals. Neural networks have shown to replicate the
+sensitivities of matched filtering in \ac{GW} detection \cite{Gabbard2017} and rapid
+parameter estimation \cite{gabbard2019bayesian}, however these methods have
+primarily been focused on binary black hole signals and have not yet expanded
+to burst examples.~\chris{OK, thanks for the referdndes but you should probably
+have more refs to other ML GW papers. I think you should dedicate at least one
+paragrpah to GW ML efforts. The final paragrapgh of the section should
+introduce the paper structure. The penultimate paragraph should expain what the
+point of this paper is - in non technical terms. This is all outlined in the
+bullet points (hidden) at the start of this section.}
 
@@
 
-A subset of deep learning that has seen fruitful development in recent years \cite{Goodfellow2014} is Generative Adversarial Networks (GANs).
-These unsupervised algorithms learn patterns in a given training data set using an adversarial process.
-The generations from GANs are state-of-the-art in fields such as high quality image fidelity \cite{brock2018large,karras2019analyzing}, text-to-image translation \cite{reed2016generative} and video prediction \cite{liang2017dual} as well as time series generations \cite{esteban2017realvalued}.
+% introduce GANs
+%
+A subset of deep learning that has seen fruitful development in recent years
+\cite{Goodfellow2014} is \acp{GAN}. These unsupervised algorithms learn
+patterns in a given training data set using an adversarial process. The
+generations from \acp{GAN} are state-of-the-art in fields such as high quality image
+fidelity \cite{brock2018large,karras2019analyzing}, text-to-image translation
+\cite{reed2016generative} and video prediction \cite{liang2017dual} as well as
+time series generations \cite{esteban2017realvalued}.
 
-GANs train two competing neural networks, consisting of a discriminator that is set up to distinguish between real and fake data and a generator that produces synthetic
-reproductions of the real data. The generator performs a mapping
-from an input noise vector \textbf{z} to its representation of the data and the discriminator  maps its
-input \textbf{x} to a probability that the input came form either the training
-data or generator.  During training, the discriminator is given a batch of samples that contains one half real data
-and one half fake data which it then makes predictions on. The
-loss for discriminator  is calculated by comparing its predictions to the labelled data through the binary cross-entropy function. The training process
-of a GAN alternatively updates the weights of the discriminator  and generator based on information
-on its competitors loss function. This loss of discriminator  is used to update the weights
-of generator to produce more realistic samples of the input distribution, the loss of G
-encourages discriminator  to update its classification abilities. Both networks compete
-in a minimax game which generator is trying
-minimise and the discriminator is trying to maximise:
-
+% How a GAN works
+%
+\acp{GAN} train two competing neural networks, consisting of a discriminator
+that is set up to distinguish between real and fake data and a generator that
+produces synthetic reproductions of the real data. The generator performs a
+mapping from an input noise vector $\mathbf{z}$ to its representation of the
+data and the discriminator maps its input $\mathbf{x}$ to a probability that
+the input came form either the training data or generator.  During training,
+the discriminator is given a batch of samples that contains one half real data
+and one half fake data which it then makes predictions on. The loss for the
+discriminator is calculated by comparing its predictions to the labelled data
+through the binary cross-entropy function. The training process of a \ac{GAN}
+alternatively updates the weights~\chris{too much knowledge assumed - what are
+weights, they haven't been defined} of the discriminator and generator based on
+information on its competitors loss function. This loss of discriminator is
+used to update the weights of the generator to produce more realistic samples
+of the input distribution, the loss of G~\chris{what is G?} encourages the
+discriminator to update its classification abilities. Both networks compete in
+a minimax game~\chris{what is a minimax game? references?} which the generator
+is trying to minimise and the discriminator is trying to
+maximise:~\chris{nicely written, however, it needs an extra 25\% explanation
+for people not familar with ML or GANs in particular. Try to spell things out
+more. Also refer to Fig 1 somewhere in this section.}
+%
 \begin{equation}
@@
 \end{equation}
+%
+~\chris{In line with explanding the explanation a bit more, really take the time
+to state what controls the functions and also deine ALL mathematical variables.
+What are $D, G, V\ldots$ Why are you taking the logs? What situation so you
+start with? What do you end up with? This is a nice start but beef it up.}
+
 \subsection{Auxiliary conditional GANs}
-In theory, the adversarial process will eventually lead to the local Nash equilibrium \cite{Nash1950} whereby
-both neural networks are trained optimally. In practice, however, GANs are
-notoriously difficult to train. Such difficulties include: Non-convergence,
-where the model parameters oscillate and the loss never converges, mode
-collapse where G produces a limited diversity of samples, and diminishing
-gradients when applying gradient descent to a
-non-continuous function.
 
-To overcome some of these difficulties, a conditional varient of GANs named Conditional-GAN (CGANs) \cite{cgan}
-adds structure to the latent space by providing the generator with a class or attribute
-label.
-The generator learns to segment the latent space by clustering distributions which have similar properties, making a point in latent space conditional on a class.
-This idea was extended further with auxiliary conditional GANs (ACGANs) \cite{odena2016conditional} that require the discriminator to output a
-probability of data belonging to each class. A pictorial representation on the differences between these approaches in Figure \ref{fig:gan_comparison}.
+% describing the problems with GANs 
+%
+In theory, the adversarial process will eventually lead to the local Nash
+equilibrium \cite{Nash1950} whereby both neural networks are trained
+optimally~\chris{this statement and this paragraph should be stated in the
+previous section}.  In practice, however, \acp{GAN} are notoriously difficult
+to train. Such difficulties include: Non-convergence, where the model
+parameters~\chris{you haven't stated what the model parameters are yet}
+oscillate and the loss~\chris{the reader soes not know what the loss is and
+what the point of it is} never converges, mode collapse where G produces a
+limited diversity of samples~\chris{samples of what?}, and diminishing
+gradients when applying gradient descent to a non-continuous
+function~\chris{not sure about what non-continuous means here but in general
+you are bringing in too many concepts without explanation e.g., gradient
+descent, why is that relevant? the reader does not know.}.
+
+% introduce CGANs and ACGANs
+%
+To overcome some of these difficulties, a conditional variant of \acp{GAN}
+named \acp{CGAN}~\cite{cgan} adds structure to the latent space~\chris{what is
+the latent space - you called it an input noise vector before} by providing the
+generator with a class or attribute label. The generator learns to segment the
+latent space by clustering distributions which have similar properties, making
+a point in latent space conditional on a class~\chris{are we sure about this?
+all classes share the same latent space and I don't think that the space gets
+segmented into areas corresponding to different classes - I do think that it
+gets broken down into spaces with different intrinsic physical properties e.g.,
+high frequency, long duration, etc...}. This idea was extended further with
+\acp{ACGAN}~\cite{odena2016conditional} that require the discriminator to
+output a probability of data belonging to each class. A pictorial
+representation on the differences between these approaches is shown in
+Fig.~\ref{fig:gan_comparison}.
 
@@
         \input{figures/ACGAN_diagram_vertical}%     without .tex extension
-    \caption{Comparison of the original GAN method and the Auxiliary Conditional-GAN method.
-For ACGANs the training data requires a label denoting its class that is also fed to the generator which then learns to generate waveforms based on the input label.
-Additionaly, the discrminator learns to classify which class the signal belongs to.}
-    \label{fig:gan_comparison}
+    \caption{Comparison of the original GAN method and the Auxiliary
+Conditional-GAN method. For ACGANs the training data requires a label denoting
+its class that is also fed to the generator which then learns to generate
+waveforms based on the input label. Additionaly, the discrminator learns to
+classify which class the signal belongs to.} \label{fig:gan_comparison}
 \end{figure}
+
+\chris{this section is supposed to be on ACGANs but it only mentions them in
+the final sentence. Again, like the previous section, a bit more explanation
+would be good. Does ths maths change? Could you have a new version of Eq 1 for
+CGANs and ACGANs? Also, if would be good to have a statement that you will be
+using one of these methods in this paper.}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-GW burst signals remain an unmodelled phenomenon, as such, current detection algorithms focus on waveform reconstruction reliant on coincident signals within multiple detectors.
-We propose a signal generation scheme utilizing GANs trained on burst-like waveforms.
-The GAN is trained on five signal morphology's spanning a range of prior parameters.
-The families are:
 
@@
 
+% introduce the training data
+%
+\ac{GW} burst signals remain an unmodelled phenomenon, as such, current
+detection algorithms focus on waveform reconstruction reliant on coincident
+signals within multiple detectors~\chris{burst detection algorithms do not need
+waveform reconstruction for searches - it is an add on feature.}. We propose a
+signal generation scheme utilizing~\chris{utilizing certainly is fancier than
+using. Dont go overboard with the language.} \acp{GAN} trained on burst-like
+waveforms. The \ac{GAN}~\chris{is it a GAN or is it a CGAN or an ACGAN? Be
+clearer} is trained on five signal morphology's spanning a range of prior
+parameters. The families are:~\chris{I know they don't all share the same
+parameters but it might be sensible to make a table of the prior ranges rather
+than haviong it all stated in text.}
+%
 \begin{itemize}
-	\item Sine-Gaussian:
+%
+\item Sine-Gaussian:\\
+\chris{don't just start things with an equation}		
+%
 \begin{equation}
@@
 \end{equation}	
+%		
 where $f_0$ is the central frequency that takes values between 30 Hz - 50 Hz.
-$\tau$ is the decay parameter chosen to be between 60s$^{-1}$  and 15s$^{-1}$ and the starting epoch chosen between 0.2s - 0.8s.
-Sine-Gaussian waveforms have a similar form to those produced by the merger of two black holes.
-Although binary mergers tend to be longer in duration.
-	\item Ring-down:
+$\tau$ is the decay parameter chosen to be between 60s$^{-1}$  and 15s$^{-1}$
+and the starting epoch chosen between 0.2s - 0.8s. Sine-Gaussian waveforms have
+a similar form to those produced by the merger of relatively high mass binary
+black holes for which the inspiral phase occurs at frequencies below
+ground-based detector sensitivities.
+%
+\item Ring-down:\\
+\chris{don't just start things with an equation}
+%
 \begin{equation}
@@
 \end{equation}
-		For ring-down signals the parameters for $f_0, \tau, t_0$ are chosen between; 30 Hz-50Hz, 0.02-0.1 and 0.1s-0.8s respectfully.
-These signals aim to replicate the post-merger late stages of binary coalescence.
-	\item White-noise bursts:\hfill \\
-	These signals are produced by inserting samples of random Gaussian noise with zero mean and a variance of 0.1 at a random point between 0.2s - 0.8s.
-The source of this signal type can be attributed to core-collapse supernova.
-	\item Gaussian:\\
-	A simple Gasssian waveform with $t_0$ ranging from 0.2s to 0.8s and $\tau$ between  100$^{-1}$ and 20$^{-1}$
+%		
+For ring-down signals the parameters for $f_0, \tau, t_0$ are chosen between;
+30 Hz-50Hz, 0.02-0.1 and 0.1s-0.8s respectfully. These signals aim to replicate
+the post-merger late stages of binary coalescence.
+%
+\item White-noise bursts:\\
+\chris{where is the waveform equation?}
+These signals are produced by inserting samples of random Gaussian noise with
+zero mean and a variance of 0.1 at a random point between 0.2s - 0.8s. The
+source of this signal type can be attributed to core-collapse
+supernova~\chris{is this correct? these waveofms are approximations so best not
+to say that they correspond directly to physical phenomena}.
+%
+\item Gaussian pulse:\\
+\chris{where is the waveform equation?}
+A simple Gasssian pulse waveform with $t_0$ ranging from 0.2s to 0.8s and
+$\tau$ between  100$^{-1}$ and 20$^{-1}$
+
 \item Binary black holes (BBH): \\
-	BBH signals are simulated using IMRPhenomD waveform routine from LALSuite which models the inspiral, merger and ringdown of a BBH waveform.
-The component masses lie in the range of [5,70]M$_0$ with zero spins and we fix m$_1$ $>$ m$_2$.
-The mass distribution is approximated by a power law with index of 1.6 https://arxiv.org/abs/1811.12940.
-The signals are generated using random right ascensions and declinations uniform over the sky and the inclinations are drawn from the cosine of a uniform distribution in the range [-1,1].
-The peaks of the waveforms are set to be within [0.75,0.95]s of the 1s time interval.
+\ac{BBH} signals are simulated using IMRPhenomD waveform routine from
+LALSuite~\chris{references for both the waveofrm and lalsuite} which models the
+inspiral, merger and ringdown of a \ac{BBH} waveform. The component masses lie
+in the range of [5,70]M$_0$~\chris{not $M_0$ but $M_{\odot}$} with zero spins
+and we fix m$_1$ $>$ m$_2$. The mass distribution is approximated by a power
+law with index of 1.6 https://arxiv.org/abs/1811.12940~\chris{correct;ly
+reference this}. The signals are generated using random right ascensions and
+declinations uniform over the sky and the inclinations are drawn from the
+cosine of a uniform distribution in the range [-1,1]. The peaks of the
+waveforms are set to be within [0.75,0.95]s of the 1s time interval.~\chris{for
+all the signal models please check that the prior ranges and distributions are
+consistent with the presented results.} 
+%
 \end{itemize}
+
+\chris{you seem to be missing a description of the antenna patterns and time
+delay that you apply to each waveform. It should go here. You should also
+include all other technical information like how you normalise the amplitudes
+and how you select random sky positions, how the data is represented to the
+network (as an image or as channels) how many detectors do you use? etc... }
 
@@
     \includegraphics[width=\textwidth]{figures/train_gen.pdf}
-    \caption{Examples of simulated burst gravitational wave signals.
-Top row shows examples from the training set.
-From left to right: Sine-Gaussian, Ringdown, White-noise burst, Gaussian, Binary black hole merger.
-The bottom row shows the conditional generations from the GAN.
-}
-    \label{fig:train}
-\end{figure}
+    \caption{Examples of simulated \ac{GW} burst signals. Top row shows
+examples from the training set. From left to right: Sine-Gaussian, Ringdown,
+White-noise burst, Gaussian pulse, Binary black hole merger. The bottom row
+shows the conditional generations from the GAN.~\chris{slightly more
+explanation. The reader may be concerned that the top and bottom do not look
+the same. Should they? They may wonder why is there only one waveform and not
+one per detector?} } \label{fig:train} \end{figure}
 
@@
 We test vector arithmetic that can be used to generate a new breed of signal by merging two or more families together.
-Finally, we discuss the capacity of the discriminator as a GW burst classifier and the auxiliary component of this work.
+Finally, we discuss the capacity of the discriminator as a \ac{GW} burst classifier and the auxiliary component of this work.
 
@@
 In this work we present the potential of Generative Adversarial Networks for burst gravitational wave analysis.
-We have shown that GANs have the ability to generate 5 class varieties of modelled burst GW signals that can be generated at whim.
+We have shown that GANs have the ability to generate 5 class varieties of modelled burst \ac{GW} signals that can be generated at whim.
 The latent and class spaces were explored through interpolation and suggest that the space provides smooth translations between classes and overall waveform shape.

### 2020-04-27 Paper_draft/git-tag.sh

@@ -1,0 +1,16 @@
+#!/bin/bash
+gitLOG=`git log -1`;
+commitID=`echo "$gitLOG" | grep "^commit " | sed -e"s/commit //g"`;
+commitDate=`echo "$gitLOG" | grep "^Date" | sed -e"s/Date:[ ]*"//g`;
+
+echo "\\def\\commitID{commitID: $commitID}" > __tmp
+echo "\\def\\commitDATE{$commitDate}" >> __tmp
+
+if diff __tmp tag.tex  >/dev/null 2>&1; then
+    ## files are identical, no update required
+    exit 0;
+else
+    ## files diff: update
+    cp __tmp tag.tex;
+fi
+

### 2020-04-27 Paper_draft/main.tex
Added comments up to the results section

@@
 \acrodef{GW}[GW]{gravitational wave}
-\acrodef{GAN}[GAN]{generative adversarial networks}
-\acrodef{CGAN}[CGAN]{conditional generative adversarial networks}
-\acrodef{ACGAN}[ACGAN]{auxilliary conditional generative adversarial networks}
+\acrodef{GAN}[GAN]{generative adversarial network}
+\acrodef{CGAN}[CGAN]{conditional generative adversarial network}
+\acrodef{ACGAN}[ACGAN]{auxilliary conditional generative adversarial network}
+\acrodef{DCGAN}[DCGAN]{deep convolutional generative adversarial network}
+\acrodef{CNN}[CNN]{convolutional neural networks}
 \acrodef{BBH}[BBH]{binary black hole}
@@
 \subsection{Architecture details}
-Extensions to the original GAN method such as  DCGANs \cite{Radford2015} have been widely praised for building a stable GAN architecture.
-Modern GAN research favours a fully convolution neural network which replace upsampling procedures like maxpooling to strided convolutions.
-Convolutional neural networks (CNNs) are designed to work with grid-like structures that exhibit strong local spatial dependencies.
-Although most work with CNNs involve image based data, they can be applied to other spatially adjacent data types such as time-series and text items.
-Audio synthesis work \cite{DBLP:journals/corr/abs-1809-11096} has showed that GANs can achieve recognisable audio within a few hours.
-We adopt the suggestions of these papers, lengthening one-dimensional convolution kernels on both the generator and discriminator.
-The Generator model is fully convolutional, upsampled using strided transposed convolutions with batchnormalisation in the first layer and ReLU activations throughout with the exception of Tanh for the output layer.
-Each transposed convolutional layer uses a kernel size of 18x1 and stride 2.
-The discriminator network mirrors that of the generator without batch normalization, using LeakyReLU activations, SpatialDropout, and a 2-stride convolution for downsampling.
-The discriminator has two output layers: the first output is a single node activated by a Sigmoid that can be interpreted as the realness of the the signal, the second output is 5 nodes activated using the softmax function predicting the class of the input.
-This model is trained with binary cross entropy for the first output and sparse categorical cross-entropy for the second output.
 
-Neural networks and subsequently GANs have multiple parameters a developer can tune when designing the model referred to as hyperparameters.
-The final network design used in this work comes from the use of trial and error and the initial designs influenced by the available literature.
-After tuning the multiple hyperparamters (Table \ref{Tab:hyperparameters}), the GAN was trained for 600000 iterations and takes $\Or$(1) day to train.
+% Introduce some architecture features
+%
+Extensions to the original \ac{GAN} method such as the
+\ac{DCGAN}~\cite{Radford2015} have been widely praised for
+building~\chris{enabling?} a stable \ac{GAN} architecture. Modern \ac{GAN}
+research~\chris{isn't all GAN research modern?} favours a fully convolution
+neural network which replace upsampling procedures like maxpooling to strided
+convolutions~\chris{a couple of things here. Max pooling and striding hasn't
+been introduced, and why do max-pooling and striding upsample? I thought they
+downsampled, don't they? }. \acp{CNN} are designed to work with grid-like
+structures that exhibit strong local spatial dependencies~\chris{great but that
+sounds like a computer science paper. Make it easier for the physicists to
+understand.}. Although most work with \acp{CNN} involve image based data, they
+can be applied to other spatially adjacent data types such as time-series and
+text items. Audio synthesis work~\cite{DBLP:journals/corr/abs-1809-11096} has
+showed that \acp{GAN} can achieve recognisable audio within a few
+hours~\chris{ambiguous. A few hours of training?}.
+
+% specifically define our architecture
+%
+We adopt the suggestions of these papers~\chris{which papers?}, lengthening
+one-dimensional convolution kernels on both the generator and discriminator.
+The Generator model is fully convolutional, upsampled using strided transposed
+convolutions with batch normalisation in the first layer and ReLU activations
+throughout with the exception of Tanh for the output layer. Each transposed
+convolutional layer uses a kernel size of $18\times 1$ and stride of 2. The
+discriminator network mirrors that of the generator without batch
+normalization, using LeakyReLU activations, SpatialDropout, and a 2-stride
+convolution for downsampling. The discriminator has two output layers: the
+first output is a single node activated by a Sigmoid that can be interpreted as
+the realness of the the signal, the second output is 5 nodes activated using
+the softmax function predicting the class of the input.  This model is trained
+with binary cross entropy for the first output and sparse categorical
+cross-entropy for the second output.~\chris{OK, very technically tight but too
+computer sciencey. Try to make it human readbale for a physicist and refer to
+the table of parameters in the appendix.}
+
+% describe the hyperparameter tunings
+%
+Neural networks and subsequently \acp{GAN} have multiple parameters a developer
+can tune when designing the model and these are referred to as hyperparameters.
+The final network design used in this work comes from the use of trial and
+error and the initial designs influenced by the available literature. After
+tuning the multiple hyperparamters (Table~\ref{Tab:hyperparameters}), the GAN
+was trained for $6\times 10^5$ iterations~\chris{what is an iteration here?
+It's not an epoch right?} and takes $\Or$(1) day to train~\chris{trained on
+what? Were there any major decisions made based on the trial and error process?
+Anything that was learned from your mistakes that might be useful to others?}.
 
 \subsection{Class labels and embedding}
-A learned embedding is an efficient way of representing categorical or class based data.
-In contrast to traditional "one-hot encoding" where each class is represented by a binary sparse vector, embeddings map each class to its own distinct vector of a given size.
-The elements of these vectors are initialized randomly and tuned during training just like weights.
-This reduces computational cost as the sparse vectors containing mostly zeros are not needed and allows related classes to cluster together.
-Once the networks are trained the learned embedding vectors can be extracted from the model and used as inputs to the generator.
-The benefit here is that the former integer class labels are replaced by higher dimensional vector representations allowing for finer experimenting in other applications.
-The class label is interpreted as an additional channel early in the generator model.
-This is achieved by projecting the class inputs as a learned embedding layer, into a fully connected layer or "dense" layer which can then be concatenated channel-wise to $\textbf{z}$.
+
+% explain embedding
+%
+A learned embedding is an efficient way of representing categorical or class
+based data. In contrast to traditional "one-hot encoding" where each class is
+represented by a binary sparse vector, embeddings map each class to its own
+distinct vector of a given size. The elements of these vectors are initialized
+randomly and tuned during training just like weights~\chris{I thought that they
+weren't trained. Are they definitely trained? Is this not just a single fully
+connected layer that turns 5 numbers into 120? How is it any different to
+that?}. This reduces computational cost as the sparse vectors containing mostly
+zeros are not needed and allows related classes to cluster together. Once the
+networks are trained the learned embedding vectors can be extracted from the
+model and used as inputs to the generator. The benefit here is that the former
+integer class labels are replaced by higher dimensional vector representations
+allowing for finer experimenting in other applications. The class label is
+interpreted as an additional channel early in the generator model. This is
+achieved by projecting the class inputs as a learned embedding layer, into a
+fully connected layer or "dense" layer which can then be concatenated
+channel-wise to $\textbf{z}$.~\chris{very nice but still a bit too technical
+without consideration for lowly astrophysicists. Can you soften it a bit to
+make it more accessible. Explain more of the concepts when you introduce them.}
+
+\chris{Also, it isn't clear where this comes into your analysis and why it's
+important. I'm not sure that the definition of "signal class" has been made
+anywhere.}
 
 \subsection{Applying a time shift and antenna responses}
-We consider a two detector case in which the generator is trained to output two identical signals with a physical time shift representing the time of flight between detectors and the suppression of amplitudes due to interaction with the detector.
-To achieve this, the generator is trained to output a single waveform that is then put through a non-trainable ``response" layer before the output of the generator.
-This layer creates a copy of its input, shifts it along in time and applies antenna responses to both the input and shifted signal.
-The time shift is achieved by converting the waveform to frequency space, multiplying by $e^{2 \pi i f dt}$, where $dt$ is the time shift and converting back to the time domain.
-After which both original and shifted signals are multiplied by the antenna responses.
-Both dt and the antenna responses are calculated using the LALSimulation \cite{lalsuite} package and we choose Hanford and Livingston as detection points.
-The result is a 2x1024 times series waveform representing an overlay data stream from two detector outputs.
-This scheme is also used in generating the training set.
+
+% Explain the effect of the sky position 
+%
+\chris{Why is this not described in the section defining the signal waveforms?
+There may be a good reason so it may well fit best here. I'm not sure} We
+consider a two detector case~\chris{why 2 detector and not 3?} in which the
+generator is trained to output two identical signals with a physical time shift
+representing the time of flight between detectors and the
+suppression~\chris{not a supression. It's just the antenna response.} of
+amplitudes due to interaction with the detector. To achieve this, the generator
+is trained to output a single waveform that is then put through a non-trainable
+``response" layer before the output of the generator. This layer creates a copy
+of its input, shifts it along in time and applies antenna responses to both the
+input and shifted signal. The time shift is achieved by converting the waveform
+to the frequency domain, multiplying by $e^{2 \pi i f \Delta t}$, where $\Delta
+t$ is the time shift and converting~\chris{converting? what do you mean?} back
+to the time domain. After which, both original and shifted signals are
+multiplied by their respective  antenna responses. Both $\Delta t$ and the
+antenna responses are calculated using the LALSimulation~\cite{lalsuite}
+package and we choose Hanford and Livingston as detection points~\chris{just
+say the detectors}. The result is a $2\times 1024$ times series waveform
+representing an overlay data stream~\chris{what the hell is an overlay data
+stream?} from two detector outputs. This scheme is also used in generating the
+training set.~\chris{OK, first of all you should define some equations here
+rather than just saying everything in words. Why is it here that you reveal the
+data sampling rate? Surely that is an important quantity that shouldn't just be
+stated in this subsection. What about the random sky position that is input to
+the "box"? How is the sky sampled? What about the wrapping from the tim shift?
+Don't you apply a window? The "box" or "response" layer should be visible in
+the network diagram.}
 
@@
 \end{comment}
+
+~\chris{In general I find this section to read like un-connected statements in
+the sense that they are un-connected to each other and un-connected to the main
+GW problem. Try to make it more like a recipe for doing this analysis.}
 

### 2020-05-01 Paper_draft/main.tex
Added more background knowledge

@@
 \usepackage{acronym}
-%\usepackage{subcaptncluon}
+\usepackage{standalone}
+%\usepackage{import}
+\usepackage{subfig}
 \usepackage{tikz}
-\usetikzlibrary{shapes.geometric, arrows, calc}
+\usetikzlibrary{decorations.pathreplacing,angles,quotes,shapes.geometric, arrows,calc}
 \expandafter\let\csname equation*\endcsname\relax 
@@
 \newcommand{\dcc}{LIGO-PXXXXXXX}
-\input{tag.tex}
+%\input{tag.tex}
 \begin{document}
@@
 
-\author{J. McGinn, C. Messenger, I.S. Heng}
+\author{J. McGinn, C. Messenger, I.S. Heng, M. Williams}
 
@@
 \vspace{10pt}
-\begin{indented}
-\item[]\commitDATE\\\mbox{\small \commitID}\\\mbox{\dcc}
-\end{indented}
+%\begin{indented}
+%\item[]\commitDATE\\\mbox{\small \commitID}\\\mbox{\dcc}
+%\end{indented}
 
@@
 Following this, the first and second observations runs (O1 and O2) of Advanced
-LIGO and Advanced Virgo~\chris{need refs for the detectors, see here
-https://pnp.ligo.org/ppcomm/standard\_references.html} reported several more
+LIGO and Advanced Virgo \cite{Prospects-dets, AdvLIGO, AdvLIGO2, AdvVIRGO} ~\chris{need refs for the detectors, see here
+https://pnp.ligo.org/ppcomm/standard\_references.html} ~\jordan{\ding{51}} reported several more
 mergers \cite{Abbott2016a, Abbott2017, Abbott2017a, Abbott2017b}. On August
@@
 axisymetric deformation in magnetars, Pulsar glitches and Neutron star
-post-mergers.  As \ac{GW} bursts are un-modelled they are not sensitive to
-template based detection schemes~\chris{OK, but logically dodgy. You make it
+post-mergers.
+Currently, \ac{GW}s are detected using matched filtering, \cite{Owen1998} a process which requires template banks of possible GW signals.
+As \ac{GW} bursts are un-modelled there are no templates available and so these signals are undetectable through this scheme.
+~\chris{OK, but logically dodgy.
+You make it
 sound like we could use a template scheme but it would be insensitive. The
-point is that we don't have templates in the first place.} such as
-matched-filtering \cite{Owen1998}, instead, detection involves distinguishing
+point is that we don't have templates in the first place.} \jordan{changed this but still reads clunky} Instead, detection involves distinguishing
 the signal from detector noise. This is only possible if the detector noise is
@@
 systematic or environmental glitches. As such, \ac{GW} burst searches rely on
-an astrophysical burst signature appearing in multiple detectors~\chris{at
-similar times?}.
+an astrophysical burst signature appearing in multiple detectors at similar times. ~\chris{at
+similar times?}. \ding{51}
 
@@
 %
-Many \ac{GW} burst algorithms \cite{Klimenko_2008, Aso_2008}~\chris{many? needs
+\ac{GW} burst algorithms \cite{Klimenko_2008, Aso_2008}~\chris{many? needs
 more than 2 refs for many.} are tested and tuned using model waveforms that may
 or may not have astrophysical significance but have easy to define parameters
-and share characteristics of real bursts that is enough to simulate coincident
-non-stationary deviations~\chris{fancy sounding but I'm not sure what
-non-stationary deviations means.} between detectors. Such waveforms may have
+and share characteristics of real bursts that is enough to simulate a \ac{GW} passing ~\chris{fancy sounding but I'm not sure what
+non-stationary deviations means.} between detectors. 
+\begin{comment}Such waveforms may have
 long-duration, short bandwidth (ringdowns), long-duration, large bandwidth
@@
 diagnosing LIGOs sensitivity to frequency.~\chris{strange unfinished sentence.} 
+\end{comment}
 
@@
 
+With the expectation that there will be many more \ac{GW} detections in the future, researches are starting to realise the need for fast and efficient \ac{GW} analysis to compete with the rising number of detections.
+Machine learning has shown great potential for \ac{GW} analysis in areas of detection \cite{george2016deep,Gabbard2017,Gebhard_2019,Krastev_2020}, glitch classification \cite{Bahaadini, George_2018,Razzano_2018} and parameter estimation \cite{gabbard2019bayesian,shen2019deterministic,green2020gravitationalwave}.
+Applying these machine learning algorithms show similar results to matched filtering techniques and have the benefit of being orders of magnitude faster.
+
 % What this paper does on GANs in 1 paragraph
@@
 \chris{What this paper does on GANs in 1 paragraph}
-
+In this work we aim to explore the use of machine learning to generate and interpret
+unmodelled \ac{GW} burst waveforms. \jordan{i haven't mentioned gans yet do i explain it here briefly?}
 % the point of the paper
@@
 \chris{describe the structure of the paper}
+This paper is organised as follows: \jordan{unstructured at the moment}
+
 We aim to explore the use of machine learning in generating and interpreting
@@
 %
-A subset of deep learning that has seen fruitful development in recent years
-\cite{Goodfellow2014} is \acp{GAN}. These unsupervised algorithms learn
+\subsection{Artificial neural networks}
+
+\begin{figure}
+    \begin{minipage}[b]{0.3\linewidth}
+        \subfloat[]{\label{fig:perceptron}\includegraphics[width=\linewidth,height=0.65\linewidth]{figures/neural_network-figure0.pdf}}
+        \par
+        \vspace{\baselineskip}
+        \subfloat[]{\label{fig:tanh_activation}\includegraphics[width=\linewidth,height=0.65\linewidth]{figures/neural_network-figure1.pdf}}
+    \end{minipage}
+        \begin{minipage}[b]{0.7\linewidth}
+        \subfloat[]{\label{fig:neural_network}\includegraphics[width=\linewidth,height=0.65\linewidth]{figures/neural_network-figure2.pdf}}
+    \end{minipage}
+    \caption{Neural Networks (a) A single neuron taking a vector of inputs and returning a singular output based on the weights, bias and activation function of the network.
+(b) The hyperbolic tangent used as an activation function.
+(c) A fully connected neural network containing two hidden layers that performs a mapping of an input vector to a singular output.}
+\end{figure}
+
+Since the birth of programmable computers, people have wondered if machines can develop true intelligence beyond formal mathematical procedures.
+Today, Machine Learning (ML) aims to learn apparent relationships held within the given data or `training data' in order to make accurate predictions without the need for additional programming .
+A common approach in ML relies on the computer learning on past experience to make decisions on future events.
+The hierarchical nature of this approach means that the machine can build complicated concepts from simpler ones.
+This branch of AI is called deep learning.
+Neural networks are the quintessential machine learning algorithm that aims to approximate a function.
+They are built from many single processing units called neurons.
+The simpliest Neural Network is the perceptron layer Figure \ref{fig:perceptron} which holds a single neuron that takes several real inputs $x_{1}, ...
+, x_{i}$ and maps them to an output according to the following linear equation:
+
+\begin{equation}
+\sigma(\sum_i w_i x_i + b)
+\label{eqn:neuron}
+\end{equation}
+where $w$ and $b$ are the weights and bias and $\sigma$ denotes the activation function.
+The weights are numbers which can be thought as the strength between connections.
+The output of a neuron is called its activation.
+Different choices of activation functions allow the user to simulate various models.
+A common example of an activation function is the hyperbolic tangent Figure \ref{fig:tanh_activation} that is used when the outputs of the network must be both positive and negative and re-scaled to $[-1,1]$.
+It is often useful to introduce a bias, $b$, such that the neuron remains inactive above zero but is active when the sum reaches a defined threshold.
+This bias is added before the activation function and it tells us how high the weighted sum needs to be before the neuron becomes active.
+
+The output of a single neuron is defined by \ref{eqn:neuron} and gives a prediction $\hat{y}$ that can be compared to the real value $y$ through a cost or loss function.
+If the loss is non-zero, the network must work to minimise this function by updating the weights in the negative direction of the loss gradient in a process referred to as gradient descent.
+This loss function plays a critical role in how neural networks learn.
+
+A neural network contains many single neurons connected in a layered structure as shown in Figure \ref{fig:neural_network}.
+The activations of the first layer (or input layer) act as the inputs to the second layer and so on until the output layer.
+Multilayered neural networks have intermediate layers between the input and output stages dubbed the hidden layers as the computations performed are not accessible to the user.
+The network can be thought of as a function F: $\mathbb{R}^N\rightarrow \mathbb{R}^M $ reliant on how activations from one layer bring activations in the next.
+The system is analogous to biology, where, some groups of neurons in animal brains cause certain others to fire.
+
+\subsection{GANs}
+
+A subset of deep learning that has seen fruitful development in recent years is \acp{GAN} \cite{Goodfellow2014}. These unsupervised algorithms learn
 patterns in a given training data set using an adversarial process. The
@@
 produces synthetic reproductions of the real data. The generator performs a
-mapping from an input noise vector $\mathbf{z}$ to its representation of the
+mapping from an input noise vector $\mathbf{z}$, that is usually sampled from a n-dimensional Gaussian space known as the latent space, to its representation of the
 data and the discriminator maps its input $\mathbf{x}$ to a probability that
@@
 discriminator is calculated by comparing its predictions to the labelled data
-through the binary cross-entropy function. The training process of a \ac{GAN}
+through the binary cross-entropy function. \jordan{note to myself: This is important since eqn 2 is derived from it (thats where the logs come from)} The training process of a \ac{GAN}
 alternatively updates the weights~\chris{too much knowledge assumed - what are
-weights, they haven't been defined} of the discriminator and generator based on
+weights, they haven't been defined} \jordan{defined above but went on a bit, should i go into back prop and optimizers?} of the discriminator and generator based on
 information on its competitors loss function. This loss of discriminator is
 used to update the weights of the generator to produce more realistic samples
-of the input distribution, the loss of G~\chris{what is G?} encourages the
-discriminator to update its classification abilities. Both networks compete in
+of the input distribution, the loss of the generator encourages the
+discriminator to update its classification abilities. GANs seek to find an equilibrium between the generator and discriminator in the form of a two-player game that can be summarised by the following:
+
+\begin{comment}
+Both networks compete in
 a minimax game~\chris{what is a minimax game? references?} which the generator
@@
 more. Also refer to Fig 1 somewhere in this section.}
+\end{comment}
 %
@@
 \end{equation}
+
+where, V is an objective function that is to be optimized.
+Objective functions are a general term for either a loss function (to be minimized) or a negative loss function (to be maximised).
+D is the discriminator, G is the generator and ${\mathbf{x} \sim p_{\text{r}}(\mathbf{x})}$, ${\mathbf{z} \sim p_{\text{z}}(\mathbf{z})}$ are samples taken from the training data and generated data respectfully.
+In practice this approach was found to be unstable.
+Early on in training the generators weights are initialised randomly meaning that the early generations are noisy and uninformative.
+This means that the discriminator can easily learn to spot the fake generations and so the discriminator wins and the generator cannot continue to improve.
+To overcome this the framing of the generator is often changed.
+Rather than minimizing $\text{log}(1-D(G(\mathbf{z})))$ the objective now is to maximise $\text{log}(D(G(\mathbf{z})))$, that is, to maximise the probability of the generations being predicted as real.
+The idea being that we always want the loosing side to be able to leverage from its competitor.
 %
@@
 
-\subsection{Auxiliary conditional GANs}
-
 % describing the problems with GANs 
@@
 equilibrium \cite{Nash1950} whereby both neural networks are trained
-optimally~\chris{this statement and this paragraph should be stated in the
-previous section}.  In practice, however, \acp{GAN} are notoriously difficult
+optimally. In practice, however, \acp{GAN} are notoriously difficult
 to train. Such difficulties include: Non-convergence, where the model
-parameters~\chris{you haven't stated what the model parameters are yet}
-oscillate and the loss~\chris{the reader soes not know what the loss is and
-what the point of it is} never converges, mode collapse where G produces a
-limited diversity of samples~\chris{samples of what?}, and diminishing
-gradients when applying gradient descent to a non-continuous
-function~\chris{not sure about what non-continuous means here but in general
-you are bringing in too many concepts without explanation e.g., gradient
-descent, why is that relevant? the reader does not know.}.
+parameters oscillate and the loss never converges, mode collapse where the generator produces a
+limited diversity of samples, and diminishing
+gradients when applying gradient descent to a loss function that is discontinuous.
+
+\subsection{Conditional GANs}
 
@@
 %
-To overcome some of these difficulties, a conditional variant of \acp{GAN}
-named \acp{CGAN}~\cite{cgan} adds structure to the latent space~\chris{what is
-the latent space - you called it an input noise vector before} by providing the
+To gain more control over what a GAN is able to generate, a conditional variant of \acp{GAN} named \acp{CGAN}~\cite{cgan} was introduced by feeding in extra information into the generator and discriminator such as a class label or attribute label, c.
+The objective function is then modified:
+\begin{equation}
+\mathop{\text{min}}_{G}  \mathop{\text{max}}_{D} V(D,G) = \mathbb{E}_{\mathbf{x,c} \sim p_{\text{r}}(\mathbf{x,c})} [\text{log} D(\mathbf{x,c})] \\ + \mathbb{E}_{\mathbf{z} \sim p_{\text{z}}(\mathbf{z}),\mathbf{c} \sim p_{\text{r}}(\mathbf{c})} [\text{log}(1-D(G(\mathbf{z,c})))]
+\label{equation:cGANloss}
+\end{equation}
+
+%
+\begin{comment}adds structure to the latent space by providing the
 generator with a class or attribute label. The generator learns to segment the
@@
 gets broken down into spaces with different intrinsic physical properties e.g.,
-high frequency, long duration, etc...}. This idea was extended further with
+high frequency, long duration, etc...}.
+\end{comment}
+%
+This idea was extended further with
 \acp{ACGAN}~\cite{odena2016conditional} that require the discriminator to
@@
 representation on the differences between these approaches is shown in
-Fig.~\ref{fig:gan_comparison}.
+Fig.~\ref{fig:gan_comparison} \jordan{self note: Probably move away from ACGAN part, standalone aux classifiers can be trained later if that's what you want}.
 

### 2020-05-12 Paper_draft/main.tex
modified:   iopart-num.bib 	modified:   main.tex

@@
 
-\acrodef{GW}[GW]{gravitational wave}
+\acrodef{GW}[GW]{Gravitational wave}
 \acrodef{GAN}[GAN]{generative adversarial network}
@@
 %
-\ac{GW} astronomy is now an established field, starting with the first
+Gravitational wave astronomy is now an established field, starting with the first
 detection of a binary black hole merger \cite{Abbott2016} in September 2015.
 Following this, the first and second observations runs (O1 and O2) of Advanced
-LIGO and Advanced Virgo \cite{Prospects-dets, AdvLIGO, AdvLIGO2, AdvVIRGO} ~\chris{need refs for the detectors, see here
-https://pnp.ligo.org/ppcomm/standard\_references.html} ~\jordan{\ding{51}} reported several more
+LIGO and Advanced Virgo \cite{Prospects-dets, AdvLIGO, AdvLIGO2, AdvVIRGO} reported several more Compact Binary Coalescence (CBC)
 mergers \cite{Abbott2016a, Abbott2017, Abbott2017a, Abbott2017b}. On August
@@
 %
+With these successes and continued upgrades to the detectors, further detections of CBCs are expected to be commonplace in a few short years.
+Another group of GW signals that has thus far been undetectable is GW ``bursts".
 GW bursts are transient signals of typically short duration ($<$ 1s) whose
@@
 post-mergers.
-Currently, \ac{GW}s are detected using matched filtering, \cite{Owen1998} a process which requires template banks of possible GW signals.
-As \ac{GW} bursts are un-modelled there are no templates available and so these signals are undetectable through this scheme.
-~\chris{OK, but logically dodgy.
-You make it
-sound like we could use a template scheme but it would be insensitive. The
-point is that we don't have templates in the first place.} \jordan{changed this but still reads clunky} Instead, detection involves distinguishing
-the signal from detector noise. This is only possible if the detector noise is
+
+GW detections so far have used a process called matched filtering, \cite{Owen1998}, where a large template bank of possible GW waveforms are compared to the detector outputs.
+In order to increase the chances of detection these template banks must span a large multi dimensional parameter space and the templates must be accurate, requiring significant computational cost.
+GW bursts are un-modelled; therefore there are no templates available and so these signals are undetectable through this scheme.
+Instead, detection involves distinguishing
+the signal from detector noise.
+Burst searches look for excess power contained in the time-frequency domain and rely on the astrophysical burst waveform appearing in multiple detectors at similar times.
+This is only possible if the detector noise is
 well characterised and the candidate signal can be differentiated from
-systematic or environmental glitches. As such, \ac{GW} burst searches rely on
-an astrophysical burst signature appearing in multiple detectors at similar times. ~\chris{at
-similar times?}. \ding{51}
+systematic or environmental glitches.
 
@@
 %
-\ac{GW} burst algorithms \cite{Klimenko_2008, Aso_2008}~\chris{many? needs
-more than 2 refs for many.} are tested and tuned using model waveforms that may
+\ac{GW} burst algorithms \cite{Klimenko_2008, Aso_2008} are tested and tuned using model waveforms that may
 or may not have astrophysical significance but have easy to define parameters
-and share characteristics of real bursts that is enough to simulate a \ac{GW} passing ~\chris{fancy sounding but I'm not sure what
-non-stationary deviations means.} between detectors. 
+and share characteristics of real bursts that is enough to simulate a \ac{GW} passing between detectors.
+Such waveforms include sine-Gaussians: a Gaussian modulated sine wave that is by it's central frequency and decay parameter.
+Bandlimited white-noise bursts: white noise that is contained within a certain frequency range and ring-downs which mimic the damped oscillations after a CBC merger.
+
 \begin{comment}Such waveforms may have
@@
 %
-\chris{Introduce ML techniques in GWs}
 
 With the expectation that there will be many more \ac{GW} detections in the future, researches are starting to realise the need for fast and efficient \ac{GW} analysis to compete with the rising number of detections.
-Machine learning has shown great potential for \ac{GW} analysis in areas of detection \cite{george2016deep,Gabbard2017,Gebhard_2019,Krastev_2020}, glitch classification \cite{Bahaadini, George_2018,Razzano_2018} and parameter estimation \cite{gabbard2019bayesian,shen2019deterministic,green2020gravitationalwave}.
-Applying these machine learning algorithms show similar results to matched filtering techniques and have the benefit of being orders of magnitude faster.
+While still in its infancy, Machine Learning (ML) with GW has already shown great potential for overcoming data bottlenecks.
+\ac{GW} analysis in areas of detection \cite{george2016deep,Gabbard2017,Gebhard_2019,Krastev_2020}, glitch classification \cite{Bahaadini, George_2018,Razzano_2018} and parameter estimation \cite{gabbard2019bayesian,shen2019deterministic,green2020gravitationalwave} have shown the success of in ML pattern recognition.
+Applying these algorithms show similar results to matched filtering techniques and have the benefit of being orders of magnitude faster.
 
@@
 %
-\chris{What this paper does on GANs in 1 paragraph}
+
 In this work we aim to explore the use of machine learning to generate and interpret
-unmodelled \ac{GW} burst waveforms. \jordan{i haven't mentioned gans yet do i explain it here briefly?}
+unmodelled \ac{GW} burst waveforms.
+Using the generative machine learning model: Generative Adversarial Networks (GANs), we train on five classes of known burst morphologies in the time domain.
+Working on the assumption that GANs construct smooth n-dimension vector spaces between it's input and output, we can then explore the space between the five classes to construct new unmodelled waveforms.
+As all the computationally expensive processes occur during training, the learned model after training is able to produce waveforms much faster than and in fact produce waveforms that are impossible to produce with current techniques.
+These new varieties of waveforms can then be used to diagnose detection algorithms and gain new insight into sources of \ac{GW} bursts.
 % the point of the paper
 %
-\chris{describe the structure of the paper}
+
 This paper is organised as follows: \jordan{unstructured at the moment}
-
-We aim to explore the use of machine learning in generating and interpreting
-these mock \ac{GW} burst signals. Neural networks have shown to replicate the
-sensitivities of matched filtering in \ac{GW} detection \cite{Gabbard2017} and rapid
-parameter estimation \cite{gabbard2019bayesian}, however these methods have
-primarily been focused on binary black hole signals and have not yet expanded
-to burst examples.~\chris{OK, thanks for the referdndes but you should probably
-have more refs to other ML GW papers. I think you should dedicate at least one
-paragrpah to GW ML efforts. The final paragrapgh of the section should
-introduce the paper structure. The penultimate paragraph should expain what the
-point of this paper is - in non technical terms. This is all outlined in the
-bullet points (hidden) at the start of this section.}
 
@@
 Since the birth of programmable computers, people have wondered if machines can develop true intelligence beyond formal mathematical procedures.
-Today, Machine Learning (ML) aims to learn apparent relationships held within the given data or `training data' in order to make accurate predictions without the need for additional programming .
+Today, ML aims to learn apparent relationships held within the given data or `training data' in order to make accurate predictions without the need for additional programming .
 A common approach in ML relies on the computer learning on past experience to make decisions on future events.
@@
 through the binary cross-entropy function. \jordan{note to myself: This is important since eqn 2 is derived from it (thats where the logs come from)} The training process of a \ac{GAN}
-alternatively updates the weights~\chris{too much knowledge assumed - what are
-weights, they haven't been defined} \jordan{defined above but went on a bit, should i go into back prop and optimizers?} of the discriminator and generator based on
+alternatively updates the weights of the discriminator and generator based on
 information on its competitors loss function. This loss of discriminator is
@@
 %
-~\chris{In line with explanding the explanation a bit more, really take the time
-to state what controls the functions and also deine ALL mathematical variables.
-What are $D, G, V\ldots$ Why are you taking the logs? What situation so you
-start with? What do you end up with? This is a nice start but beef it up.}
 
@@
 
+This simple addition has shown to work well in practice, for instance in image-to-image translation \cite{isola2016imagetoimage}. We will be using a conditional GAN for this study.
 %
@@
 %
+\begin{comment}
 This idea was extended further with
@@
 Fig.~\ref{fig:gan_comparison} \jordan{self note: Probably move away from ACGAN part, standalone aux classifiers can be trained later if that's what you want}. 
+\end{comment}
 
@@
 waveforms based on the input label. Additionaly, the discrminator learns to
-classify which class the signal belongs to.} \label{fig:gan_comparison}
+classify which class the signal belongs to. \jordan{change to cGAN}} \label{fig:gan_comparison}
 \end{figure}
-
-\chris{this section is supposed to be on ACGANs but it only mentions them in
-the final sentence. Again, like the previous section, a bit more explanation
-would be good. Does ths maths change? Could you have a new version of Eq 1 for
-CGANs and ACGANs? Also, if would be good to have a statement that you will be
-using one of these methods in this paper.}
 
@@
 %
-\ac{GW} burst signals remain an unmodelled phenomenon, as such, current
-detection algorithms focus on waveform reconstruction reliant on coincident
-signals within multiple detectors~\chris{burst detection algorithms do not need
-waveform reconstruction for searches - it is an add on feature.}. We propose a
-signal generation scheme utilizing~\chris{utilizing certainly is fancier than
-using. Dont go overboard with the language.} \acp{GAN} trained on burst-like
-waveforms. The \ac{GAN}~\chris{is it a GAN or is it a CGAN or an ACGAN? Be
-clearer} is trained on five signal morphology's spanning a range of prior
-parameters. The families are:~\chris{I know they don't all share the same
-parameters but it might be sensible to make a table of the prior ranges rather
-than haviong it all stated in text.}
-%
-\begin{itemize}
-%
-\item Sine-Gaussian:\\
-\chris{don't just start things with an equation}		
-%
-\begin{equation}
-\label{eqn:sg}
-h(t) = A \exp\bigg[ - \frac{(t-t_{0})^2}{\tau^2} \bigg] \sin (2 \pi f_0 (t-t_0))
-\end{equation}	
-%		
-where $f_0$ is the central frequency that takes values between 30 Hz - 50 Hz.
-$\tau$ is the decay parameter chosen to be between 60s$^{-1}$  and 15s$^{-1}$
-and the starting epoch chosen between 0.2s - 0.8s. Sine-Gaussian waveforms have
-a similar form to those produced by the merger of relatively high mass binary
-black holes for which the inspiral phase occurs at frequencies below
-ground-based detector sensitivities.
-%
-\item Ring-down:\\
-\chris{don't just start things with an equation}
-%
-\begin{equation}
-h(t) = A \exp \bigg[-\frac{(t-t_0)}{\tau}\bigg]\sin(2 \pi f_0 (t-t_0))
-\end{equation}
-%		
-For ring-down signals the parameters for $f_0, \tau, t_0$ are chosen between;
-30 Hz-50Hz, 0.02-0.1 and 0.1s-0.8s respectfully. These signals aim to replicate
-the post-merger late stages of binary coalescence.
-%
-\item White-noise bursts:\\
-\chris{where is the waveform equation?}
-These signals are produced by inserting samples of random Gaussian noise with
-zero mean and a variance of 0.1 at a random point between 0.2s - 0.8s. The
-source of this signal type can be attributed to core-collapse
-supernova~\chris{is this correct? these waveofms are approximations so best not
-to say that they correspond directly to physical phenomena}.
-%
-\item Gaussian pulse:\\
-\chris{where is the waveform equation?}
-A simple Gasssian pulse waveform with $t_0$ ranging from 0.2s to 0.8s and
-$\tau$ between  100$^{-1}$ and 20$^{-1}$
 
-\item Binary black holes (BBH): \\
-\ac{BBH} signals are simulated using IMRPhenomD waveform routine from
-LALSuite~\chris{references for both the waveofrm and lalsuite} which models the
+\begin{table}[hb]
+\centering
+\caption{Burst training parameters}
+%\footnotesize
+\begin{tabular}{@{} l l l l l l }
+\br
+\hline
+ Waveform & Central frequency  & Decay & Central time epoch & Mass range \\
+ & (Hz) & (s) & (s) & ($M_{\odot}$) \\
+\mr
+Sine-Gaussian & 70 - 250 & 0.004 - 0.03 & 0.4 - 0.6 & N/A  \\  
+Ringdown & 70 - 250 & 0.004 - 0.03 & 0.4 - 0.6 & N/A \\
+White-noise burst & 70 - 250 & 0.004 - 0.03 & 0.4 - 0.6 & N/A  \\
+Gaussian pulse & N/A & 0.004 - 0.03 & 0.4 - 0.6 & N/A  \\
+BBH & N/A & N/A & N/A & 5 - 70  \\
+ \br
+\end{tabular}\\
+\label{Tab:training_parms}
+\end{table}
+\normalsize
+
+GW burst signals remain an unmodelled phenomenon, as such, current
+detection algorithms focus on waveforms signals appearing within multiple detectors We propose a
+signal generation scheme using \acp{GAN} trained on burst-like
+waveforms. BurstGAN is a conditional GAN that is trained on five signal morphology's spanning a range of prior
+parameters.
+The parameter ranges can be seen in Table \ref{Tab:training_parms} The families are: sine-Gaussian $h(t) = A \exp\bigg[ - \frac{(t-t_{0})^2}{\tau^2} \bigg] \sin (2 \pi f_0 (t-t_0))$, a sinusoidal wave with a Gaussian envelop characterised by a central frequency, $f_0$; Ring-down, $h(t) = A \exp \bigg[-\frac{(t-t_0)}{\tau}\bigg]\sin(2 \pi f_0 (t-t_0))$, with frequency $f_0$ and duration $\tau$, white-noise bursts, with bounded frequency bandwidth $\Delta f$ and duration $\tau$, gaussian pulse $h(t) = \exp(-\frac{t^2}{\tau^2})$ with duration $\tau$ and binary-black hole inspirals which are simulated using IMRPhenomD waveform \cite{Khan_2016} routine from
+LALSuite \cite{lalsuite} which models the
 inspiral, merger and ringdown of a \ac{BBH} waveform. The component masses lie
-in the range of [5,70]M$_0$~\chris{not $M_0$ but $M_{\odot}$} with zero spins
+in the range of [5,70]$M_{\odot}$ with zero spins
 and we fix m$_1$ $>$ m$_2$. The mass distribution is approximated by a power
-law with index of 1.6 https://arxiv.org/abs/1811.12940~\chris{correct;ly
-reference this}. The signals are generated using random right ascensions and
+law with index of 1.6 \cite{Abbott_2019}. The signals are generated using random right ascensions and
 declinations uniform over the sky and the inclinations are drawn from the
 cosine of a uniform distribution in the range [-1,1]. The peaks of the
-waveforms are set to be within [0.75,0.95]s of the 1s time interval.~\chris{for
-all the signal models please check that the prior ranges and distributions are
-consistent with the presented results.} 
+waveforms are set to be within [0.4,0.6]s of the 1s time interval.
+
+All training waveforms are sampled at 1024 Hz.
 %
-\end{itemize}
 
-\chris{you seem to be missing a description of the antenna patterns and time
-delay that you apply to each waveform. It should go here. You should also
-include all other technical information like how you normalise the amplitudes
-and how you select random sky positions, how the data is represented to the
-network (as an image or as channels) how many detectors do you use? etc... }
+\subsection{Applying a time shift and antenna responses}
+
+% Explain the effect of the sky position 
+%
+We consider a two detector case~\chris{why 2 detector and not 3?} in which the
+generator is trained to output two identical signals with a physical time shift
+representing the time of flight between detectors H1 and L1 To achieve this, the generator
+is trained to output a single waveform that is then put through a non-trainable
+``response" layer before the output of the generator.
+This layer takes as input, the generated waveform, time delay and antenna responses.
+The sky location is chosen by drawing from a uniform distribution across the whole sky and the time delay, and antenna responses generated by LALSimulation~\cite{lalsuite}.
+
+This response layer Fourier transforms the waveform
+to the frequency domain, multiplies this by $e^{2 \pi i f \Delta t}$, where $\Delta
+t$ is the time shift and transforming back
+to the time domain. After which, both original and shifted signals are
+multiplied by their respective  antenna responses. The output is two 1024 Hz times series waveform split into two channels.
+This scheme is also used in generating the
+training set.
 
@@
 White-noise burst, Gaussian pulse, Binary black hole merger. The bottom row
-shows the conditional generations from the GAN.~\chris{slightly more
-explanation. The reader may be concerned that the top and bottom do not look
-the same. Should they? They may wonder why is there only one waveform and not
-one per detector?} } \label{fig:train} \end{figure}
+shows the conditional generations from the GAN. Each plots contains only one detector output for ease of viewing.}
+\label{fig:train} \end{figure}
 
@@
 \ac{DCGAN}~\cite{Radford2015} have been widely praised for
-building~\chris{enabling?} a stable \ac{GAN} architecture. Modern \ac{GAN}
-research~\chris{isn't all GAN research modern?} favours a fully convolution
-neural network which replace upsampling procedures like maxpooling to strided
-convolutions~\chris{a couple of things here. Max pooling and striding hasn't
-been introduced, and why do max-pooling and striding upsample? I thought they
-downsampled, don't they? }. \acp{CNN} are designed to work with grid-like
-structures that exhibit strong local spatial dependencies~\chris{great but that
-sounds like a computer science paper. Make it easier for the physicists to
-understand.}. Although most work with \acp{CNN} involve image based data, they
-can be applied to other spatially adjacent data types such as time-series and
-text items. Audio synthesis work~\cite{DBLP:journals/corr/abs-1809-11096} has
-showed that \acp{GAN} can achieve recognisable audio within a few
-hours~\chris{ambiguous. A few hours of training?}.
+enabling a stable \ac{GAN} architecture.
+Most GANs now replace fully connected layers, where each neuron is connect to all the neurons in the previous and next layer, with convolutional layers.
+\ac{CNN} are designed to work with grid-like structures with close local dependencies like image and text based data, however, there are examples of audio synthesis work \cite{DBLP:journals/corr/abs-1809-11096}.
 
@@
 %
-We adopt the suggestions of these papers~\chris{which papers?}, lengthening
+We adopt the suggestions of \cite{Radford2015,DBLP:journals/corr/abs-1809-11096}, lengthening
 one-dimensional convolution kernels on both the generator and discriminator.
@@
 with binary cross entropy for the first output and sparse categorical
-cross-entropy for the second output.~\chris{OK, very technically tight but too
+cross-entropy for the second output. The full architecture description can be seen in Table \ref{Tab:hyperparameters}.~\chris{OK, very technically tight but too
 computer sciencey. Try to make it human readbale for a physicist and refer to
@@
 anywhere.}
-
-\subsection{Applying a time shift and antenna responses}
-
-% Explain the effect of the sky position 
-%
-\chris{Why is this not described in the section defining the signal waveforms?
-There may be a good reason so it may well fit best here. I'm not sure} We
-consider a two detector case~\chris{why 2 detector and not 3?} in which the
-generator is trained to output two identical signals with a physical time shift
-representing the time of flight between detectors and the
-suppression~\chris{not a supression. It's just the antenna response.} of
-amplitudes due to interaction with the detector. To achieve this, the generator
-is trained to output a single waveform that is then put through a non-trainable
-``response" layer before the output of the generator. This layer creates a copy
-of its input, shifts it along in time and applies antenna responses to both the
-input and shifted signal. The time shift is achieved by converting the waveform
-to the frequency domain, multiplying by $e^{2 \pi i f \Delta t}$, where $\Delta
-t$ is the time shift and converting~\chris{converting? what do you mean?} back
-to the time domain. After which, both original and shifted signals are
-multiplied by their respective  antenna responses. Both $\Delta t$ and the
-antenna responses are calculated using the LALSimulation~\cite{lalsuite}
-package and we choose Hanford and Livingston as detection points~\chris{just
-say the detectors}. The result is a $2\times 1024$ times series waveform
-representing an overlay data stream~\chris{what the hell is an overlay data
-stream?} from two detector outputs. This scheme is also used in generating the
-training set.~\chris{OK, first of all you should define some equations here
-rather than just saying everything in words. Why is it here that you reveal the
-data sampling rate? Surely that is an important quantity that shouldn't just be
-stated in this subsection. What about the random sky position that is input to
-the "box"? How is the sky sampled? What about the wrapping from the tim shift?
-Don't you apply a window? The "box" or "response" layer should be visible in
-the network diagram.}
 
@@
 \footnotesize
-\begin{tabular}{@{}lllllll}
+\begin{tabular}{@{}l l l l l l l}
 \br

### 2020-05-29 Paper_draft/main.tex
results from cGAN

@@
 \usepackage{standalone}
+\usepackage{academicons}
+\usepackage{scalerel}
+\usepackage{layouts}
 %\usepackage{import}
@@
 \usetikzlibrary{decorations.pathreplacing,angles,quotes,shapes.geometric, arrows,calc}
+\usetikzlibrary{svg.path}
 \expandafter\let\csname equation*\endcsname\relax 
@@
 \usepackage{hyperref}
+\usepackage[capitalize]{cleveref}
 \newcommand{\gguide}{{\it Preparing graphics for IOP Publishing journals}}
@@
 %\input{tag.tex}
+% Command for ORCID id's
+\definecolor{orcidlogocol}{HTML}{A6CE39}
+\tikzset{
+  orcidlogo/.pic={
+    \fill[orcidlogocol] svg{M256,128c0,70.7-57.3,128-128,128C57.3,256,0,198.7,0,128C0,57.3,57.3,0,128,0C198.7,0,256,57.3,256,128z};
+    \fill[white] svg{M86.3,186.2H70.9V79.1h15.4v48.4V186.2z}
+                 svg{M108.9,79.1h41.6c39.6,0,57,28.3,57,53.6c0,27.5-21.5,53.6-56.8,53.6h-41.8V79.1z M124.3,172.4h24.5c34.9,0,42.9-26.5,42.9-39.7c0-21.5-13.7-39.7-43.7-39.7h-23.7V172.4z}
+                 svg{M88.7,56.8c0,5.5-4.5,10.1-10.1,10.1c-5.6,0-10.1-4.6-10.1-10.1c0-5.6,4.5-10.1,10.1-10.1C84.2,46.7,88.7,51.3,88.7,56.8z};
+  }
+}
+
+\newcommand\orcidicon[1]{\href{https://orcid.org/#1}{\mbox{\scalerel*{
+\begin{tikzpicture}[yscale=-1,transform shape]
+\pic{orcidlogo};
+\end{tikzpicture}
+}{|}}}}
+
+\usepackage{hyperref} %<--- Load after everything else
+
 \begin{document}
@@
 
-\author{J. McGinn, C. Messenger, I.S. Heng, M. Williams}
+\author{
+    J. McGinn \orcidicon{0000-0000-0000-0000},
+    C. Messenger \orcidicon{0000-0001-7488-5022},
+    I.S. Heng \orcidicon{0000-0000-0000-0000},
+    M. J. Williams \orcidicon{0000-0003-2198-2974}
+}
 
@@
 \section{Introduction}
+textwidth in inches: \printinunitsof{in}\prntlen{\textwidth}
 \begin{comment}
@@
 axisymetric deformation in magnetars, Pulsar glitches and Neutron star
-post-mergers.
+post-mergers. \michael{Might be worth citing some sources for this statement}
 
@@
 While still in its infancy, Machine Learning (ML) with GW has already shown great potential for overcoming data bottlenecks.
-\ac{GW} analysis in areas of detection \cite{george2016deep,Gabbard2017,Gebhard_2019,Krastev_2020}, glitch classification \cite{Bahaadini, George_2018,Razzano_2018} and parameter estimation \cite{gabbard2019bayesian,shen2019deterministic,green2020gravitationalwave} have shown the success of in ML pattern recognition.
+\ac{GW} analysis in areas of detection \cite{Gabbard2017,Gebhard_2019,Krastev_2020}, glitch classification \cite{Bahaadini, George_2018,Razzano_2018} and parameter estimation \cite{gabbard2019bayesian,shen2019deterministic,green2020gravitationalwave} have shown the success of in ML pattern recognition.
 Applying these algorithms show similar results to matched filtering techniques and have the benefit of being orders of magnitude faster.
@@
 (b) The hyperbolic tangent used as an activation function.
-(c) A fully connected neural network containing two hidden layers that performs a mapping of an input vector to a singular output.}
+(c) A fully connected neural network containing two hidden layers that performs a mapping of an input vector to a singular output.
+\michael{Equation in the neuron looks very small}}
 \end{figure}
@@
 They are built from many single processing units called neurons.
-The simpliest Neural Network is the perceptron layer Figure \ref{fig:perceptron} which holds a single neuron that takes several real inputs $x_{1}, ...
+The simpliest Neural Network is the perceptron layer \cref{fig:perceptron} which holds a single neuron that takes several real inputs $x_{1}, ...
 , x_{i}$ and maps them to an output according to the following linear equation:
@@
 Different choices of activation functions allow the user to simulate various models.
-A common example of an activation function is the hyperbolic tangent Figure \ref{fig:tanh_activation} that is used when the outputs of the network must be both positive and negative and re-scaled to $[-1,1]$.
+A common example of an activation function is the hyperbolic tangent \cref{fig:tanh_activation} that is used when the outputs of the network must be both positive and negative and re-scaled to $[-1,1]$.
 It is often useful to introduce a bias, $b$, such that the neuron remains inactive above zero but is active when the sum reaches a defined threshold.
@@
 
-The output of a single neuron is defined by \ref{eqn:neuron} and gives a prediction $\hat{y}$ that can be compared to the real value $y$ through a cost or loss function.
+The output of a single neuron is defined by \cref{eqn:neuron} and gives a prediction $\hat{y}$ that can be compared to the real value $y$ through a cost or loss function.
 If the loss is non-zero, the network must work to minimise this function by updating the weights in the negative direction of the loss gradient in a process referred to as gradient descent.
@@
 
-A neural network contains many single neurons connected in a layered structure as shown in Figure \ref{fig:neural_network}.
+A neural network contains many single neurons connected in a layered structure as shown in \cref{fig:neural_network}.
 The activations of the first layer (or input layer) act as the inputs to the second layer and so on until the output layer.
@@
  Waveform & Central frequency  & Decay & Central time epoch & Mass range \\
- & (Hz) & (s) & (s) & ($M_{\odot}$) \\
+ & (Hz) & (s) & (s) & ($\textrm{M}_{\odot}$) \\
 \mr
@@
 parameters.
-The parameter ranges can be seen in Table \ref{Tab:training_parms} The families are: sine-Gaussian $h(t) = A \exp\bigg[ - \frac{(t-t_{0})^2}{\tau^2} \bigg] \sin (2 \pi f_0 (t-t_0))$, a sinusoidal wave with a Gaussian envelop characterised by a central frequency, $f_0$; Ring-down, $h(t) = A \exp \bigg[-\frac{(t-t_0)}{\tau}\bigg]\sin(2 \pi f_0 (t-t_0))$, with frequency $f_0$ and duration $\tau$, white-noise bursts, with bounded frequency bandwidth $\Delta f$ and duration $\tau$, gaussian pulse $h(t) = \exp(-\frac{t^2}{\tau^2})$ with duration $\tau$ and binary-black hole inspirals which are simulated using IMRPhenomD waveform \cite{Khan_2016} routine from
+The parameter ranges can be seen in \cref{Tab:training_parms} The families are: sine-Gaussian $h(t) = A \exp\left[ - (t-t_{0})^2 / \tau^2 \right] \sin (2 \pi f_0 (t-t_0))$, a sinusoidal wave with a Gaussian envelop characterised by a central frequency, $f_0$; Ring-down, $h(t) = A \exp \left[-{(t-t_0)} / {\tau} \right] \sin(2 \pi f_0 (t-t_0))$, with frequency $f_0$ and duration $\tau$, white-noise bursts, with bounded frequency bandwidth $\Delta f$ and duration $\tau$, gaussian pulse $h(t) = \exp(-t^2 / \tau^2)$ with duration $\tau$ and binary-black hole inspirals which are simulated using IMRPhenomD waveform \cite{Khan_2016} routine from
 LALSuite \cite{lalsuite} which models the
 inspiral, merger and ringdown of a \ac{BBH} waveform. The component masses lie
-in the range of [5,70]$M_{\odot}$ with zero spins
-and we fix m$_1$ $>$ m$_2$. The mass distribution is approximated by a power
+in the range of [5,70] $\textrm{M}_{\odot}$ with zero spins
+and we fix m$_1$ $>$ m$_2$ \michael{I think the exponentials look neater without using frac\{\}\{\}}. The mass distribution is approximated by a power
 law with index of 1.6 \cite{Abbott_2019}. The signals are generated using random right ascensions and
@@
 with binary cross entropy for the first output and sparse categorical
-cross-entropy for the second output. The full architecture description can be seen in Table \ref{Tab:hyperparameters}.~\chris{OK, very technically tight but too
+cross-entropy for the second output. The full architecture description can be seen in \cref{Tab:hyperparameters}.~\chris{OK, very technically tight but too
 computer sciencey. Try to make it human readbale for a physicist and refer to
@@
 error and the initial designs influenced by the available literature. After
-tuning the multiple hyperparamters (Table~\ref{Tab:hyperparameters}), the GAN
-was trained for $6\times 10^5$ iterations~\chris{what is an iteration here?
-It's not an epoch right?} and takes $\Or$(1) day to train~\chris{trained on
+tuning the multiple hyperparamters (\cref{Tab:hyperparameters}), the GAN
+was trained for 1000 epochs and takes $\Or$(2) days to train.
+~\jordan{talk about making D and G 'symmetric' increasing batch size, number of filters powers of 2, spatial dropout,no early stopping.} ~\chris{trained on
 what? Were there any major decisions made based on the trial and error process?
@@
 connected layer that turns 5 numbers into 120? How is it any different to
-that?}. This reduces computational cost as the sparse vectors containing mostly
+that?}.
+~\jordan{each class is one number that is turned into 120 numbers, embedding keeps track of the 5x120 numbers and as its training similar classes are grouped together in the class space.
+This explains it better than i can: https://machinelearningmastery.com/what-are-word-embeddings/ } This reduces computational cost as the sparse vectors containing mostly
 zeros are not needed and allows related classes to cluster together. Once the
@@
 The generator network is a function G : $\mathbf{z},\mathbf{c},\mathbb{\textbf{s}}$ $\in$ $\mathbb{R}^{100}$ $\to$ $\mathbb{R}^{1024\times2}$, where $\mathbf{z},\mathbf{c},\mathbb{\textbf{s}}$ are the latent vector, class embedding vector and sky positions respectively.
-Given a latent vector randomly sampled from a normal distribution with zero mean and unit variance, a class label which is represented by a 120 dimensional vector for each class and antenna responses, the results from the generator can be seen in Figure \ref{fig:gen_signals}.
+Given a latent vector randomly sampled from a normal distribution with zero mean and unit variance, a class label which is represented by a 120 dimensional vector for each class and antenna responses, the results from the generator can be seen in \cref{fig:gen_signals}.
 Depending on the orientation of the detector with respect to a hypothetical signal in the sky, the waveforms may appear inverted, shifted in time and their strain attenuated.
@@
     \centering
-    \includegraphics[width=\textwidth]{figures/conditional_gens.pdf}
+    \includegraphics[width=\textwidth]{figures/gens+taining.eps}
     \caption{Generated waveforms after training and conditioning on five classes.
@@
 The third input, the response values are kept constant for each class.
-The full effect shown in Figure \ref{fig:z_interp}.
+The full effect shown in \cref{fig:z_interp}.
 We can see that each plot shows plausible waveforms suggesting that the generator has constructed a smooth space unlike the discrete training case.
@@
     \centering
-    \includegraphics[width=\textwidth]{figures/z_interp_fix_c.pdf}
+    \includegraphics[width=\textwidth]{figures/z_interpolation.eps}
     \caption{Interpolations between two random latent points in z.
@@
     \centering
-    \includegraphics[width=\textwidth]{figures/4_c_interp.pdf}
+    \includegraphics[width=\textwidth]{figures/class_interpolation.eps}
     \caption{Class space interpolation with latent space held constant throughout.
 The plots show a zoomed in section of the 1s time interval.
-Top row: Sine-Gaussian class to ringdown class, Middle Row: Sine-Gaussian class to whitenoise burst class, Bottom row: Sine-Gaussian class to Gaussian class.}
+First row: Sine-Gaussian class to ringdown class, Second Row: Sine-Gaussian class to whitenoise burst class, Third row: Sine-Gaussian class to Gaussian class, Fourth row: Sine-Gaussian to BBH class.}
     \label{fig:c_interp}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics[width=\textwidth]{figures/sg_bbh_interp.pdf}
-    \caption{Class space interpolation with latent space held constant throughout. The full 1s interval is plotted for class based interpolations between a Sine-Gaussian and a BBH in spiral.}
-    \label{fig:sgbbh_interp}
 \end{figure}
@@
 Here, we show that this GAN only needs a single vector representation and due to conditioning we can have more control over which vectors to use in the arithmetic.
-In Figure \ref{fig:arithmetic} we generate a whitenoise burst and a BBH insprial using their respective class labels and use a randomised latent point and response.
+In \cref{fig:arithmetic} we generate a whitenoise burst and a BBH insprial using their respective class labels and use a randomised latent point and response.
 Keeping the latent point and response, we average the two class vectors and use this as input to the generator.
-Figure \ref{fig:arithmetic} (c) shows the generation based on the combined class vectors which visually looks similar to a supernova waveform.
+\Cref{fig:arithmetic} (c) shows the generation based on the combined class vectors which visually looks similar to a supernova waveform.
 Supernova waveform generations require expensive numerical relativity simulations and various assumptions about the collapse of its parent star.
@@
   \end{tabular} %\qquad
-
   \begin{tabular}[b]{c}

### 2020-07-03 Paper_draft/main.tex
changes to cGAN

@@
         \input{figures/ACGAN_diagram_vertical}%     without .tex extension
-    \caption{Comparison of the original GAN method and the Auxiliary
-Conditional-GAN method. For ACGANs the training data requires a label denoting
+    \caption{Comparison of the original GAN method and the
+Conditional-GAN method. For CGANs the training data requires a label denoting
 its class that is also fed to the generator which then learns to generate
-waveforms based on the input label. Additionaly, the discrminator learns to
-classify which class the signal belongs to. \jordan{change to cGAN}} \label{fig:gan_comparison}
+waveforms based on the input label.} \label{fig:gan_comparison}
 \end{figure}
@@
 All training waveforms are sampled at 1024 Hz.
-%
-
-\subsection{Applying a time shift and antenna responses}
-
-% Explain the effect of the sky position 
-%
-We consider a two detector case~\chris{why 2 detector and not 3?} in which the
-generator is trained to output two identical signals with a physical time shift
-representing the time of flight between detectors H1 and L1 To achieve this, the generator
-is trained to output a single waveform that is then put through a non-trainable
-``response" layer before the output of the generator.
-This layer takes as input, the generated waveform, time delay and antenna responses.
-The sky location is chosen by drawing from a uniform distribution across the whole sky and the time delay, and antenna responses generated by LALSimulation~\cite{lalsuite}.
-
-This response layer Fourier transforms the waveform
-to the frequency domain, multiplies this by $e^{2 \pi i f \Delta t}$, where $\Delta
-t$ is the time shift and transforming back
-to the time domain. After which, both original and shifted signals are
-multiplied by their respective  antenna responses. The output is two 1024 Hz times series waveform split into two channels.
-This scheme is also used in generating the
-training set.
 
@@
 normalization, using LeakyReLU activations, SpatialDropout, and a 2-stride
-convolution for downsampling. The discriminator has two output layers: the
-first output is a single node activated by a Sigmoid that can be interpreted as
-the realness of the the signal, the second output is 5 nodes activated using
-the softmax function predicting the class of the input.  This model is trained
+convolution for downsampling. The discriminator output is a single node activated by a Sigmoid that can be interpreted as
+a probability of the the signal being real. This model is trained
 with binary cross entropy for the first output and sparse categorical
@@
 Anything that was learned from your mistakes that might be useful to others?}.
-
-\subsection{Class labels and embedding}
-
-% explain embedding
-%
-A learned embedding is an efficient way of representing categorical or class
-based data. In contrast to traditional "one-hot encoding" where each class is
-represented by a binary sparse vector, embeddings map each class to its own
-distinct vector of a given size. The elements of these vectors are initialized
-randomly and tuned during training just like weights~\chris{I thought that they
-weren't trained. Are they definitely trained? Is this not just a single fully
-connected layer that turns 5 numbers into 120? How is it any different to
-that?}.
-~\jordan{each class is one number that is turned into 120 numbers, embedding keeps track of the 5x120 numbers and as its training similar classes are grouped together in the class space.
-This explains it better than i can: https://machinelearningmastery.com/what-are-word-embeddings/ } This reduces computational cost as the sparse vectors containing mostly
-zeros are not needed and allows related classes to cluster together. Once the
-networks are trained the learned embedding vectors can be extracted from the
-model and used as inputs to the generator. The benefit here is that the former
-integer class labels are replaced by higher dimensional vector representations
-allowing for finer experimenting in other applications. The class label is
-interpreted as an additional channel early in the generator model. This is
-achieved by projecting the class inputs as a learned embedding layer, into a
-fully connected layer or "dense" layer which can then be concatenated
-channel-wise to $\textbf{z}$.~\chris{very nice but still a bit too technical
-without consideration for lowly astrophysicists. Can you soften it a bit to
-make it more accessible. Explain more of the concepts when you introduce them.}
-
-\chris{Also, it isn't clear where this comes into your analysis and why it's
-important. I'm not sure that the definition of "signal class" has been made
-anywhere.}
 
@@
     \label{fig:c_interp}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\textwidth]{figures/sg_bbh_interp.pdf}
+    \caption{Class space interpolation with latent space held constant throughout. The full 1s interval is plotted for class based interpolations between a Sine-Gaussian and a BBH in spiral.}
+    \label{fig:sgbbh_interp}
 \end{figure}

### 2020-07-27 Paper_draft/main.tex
Paper changes to cGAN

@@
 
-\begin{figure}
-    \centering
-    \includegraphics[width=\textwidth]{figures/train_gen.pdf}
-    \caption{Examples of simulated \ac{GW} burst signals. Top row shows
-examples from the training set. From left to right: Sine-Gaussian, Ringdown,
-White-noise burst, Gaussian pulse, Binary black hole merger. The bottom row
-shows the conditional generations from the GAN. Each plots contains only one detector output for ease of viewing.}
-\label{fig:train} \end{figure}
-
 \subsection{Architecture details}
@@
 
+\begin{figure}
+    \centering
+    \includegraphics[width=\textwidth]{figures/generations/sg.png}
+    \includegraphics[width=\textwidth]{figures/generations/rd.png}
+    \includegraphics[width=\textwidth]{figures/generations/wnb.png}
+    \includegraphics[width=\textwidth]{figures/generations/blip.png}
+    \includegraphics[width=\textwidth]{figures/generations/bbh.png}
+    \caption{Examples of \ac{GW} burst signals generated by a conditional generative adversarial network. Top row shows
+examples from the training set. By row: Sine-Gaussian, Ringdown,
+White-noise burst, Gaussian pulse, Binary black hole merger.}
+\label{fig:train} \end{figure}
+
 \subsection{Waveform quality}
@@
 Each plot shows the output of the generator after given randomised $\mathbf{z}, \mathbb{\textbf{s}}$ and one of the five class vectors $\mathbf{c}$.
-
-\begin{figure}[ht]
-    \centering
-    \includegraphics[width=\textwidth]{figures/gens+taining.eps}
-    \caption{Generated waveforms after training and conditioning on five classes.
-The generator will output two waveforms as seen by detectors in Hanford (red) and Livingston (blue).
-The generator is able to capture the characteristics of each waveform and structure the class space to give control over which waveform to generate.
-Each row shows a random assortment of one of the five classes the GAN is trained on.
-}
-    \label{fig:gen_signals}
-\end{figure}
 
@@
 
-\begin{figure}[ht]
-    \centering
-    \includegraphics[width=\textwidth]{figures/z_interpolation.eps}
-    \caption{Interpolations between two random latent points in z.
-Each row uniformly interpolates between two points in $\mathbf{z}$ keeping the class fixed.
-Only a single waveform from the generator is plotted and each signal is re-scaled to [-1,1] effectively removing the antenna responses for clarity.}
-    \label{fig:z_interp}
-\end{figure}
-
 \subsection{Class space interpolation}
@@
     \centering
-    \includegraphics[width=\textwidth]{figures/class_interpolation.eps}
-    \caption{Class space interpolation with latent space held constant throughout.
-The plots show a zoomed in section of the 1s time interval.
-First row: Sine-Gaussian class to ringdown class, Second Row: Sine-Gaussian class to whitenoise burst class, Third row: Sine-Gaussian class to Gaussian class, Fourth row: Sine-Gaussian to BBH class.}
+    \includegraphics[width=\textwidth]{figures/generations/interp_rd-sg.png}
+    \includegraphics[width=\textwidth]{figures/generations/interp_wnb-blip.png}
+    \includegraphics[width=\textwidth]{figures/generations/interp_sg-bbh.png}
+    \caption{Latent space linear interpolation, class space is held constant.}
     \label{fig:c_interp}
@@
 
-\begin{figure}
-    \centering
-    \includegraphics[width=\textwidth]{figures/sg_bbh_interp.pdf}
-    \caption{Class space interpolation with latent space held constant throughout. The full 1s interval is plotted for class based interpolations between a Sine-Gaussian and a BBH in spiral.}
-    \label{fig:sgbbh_interp}
-\end{figure}
-
-\begin{comment}
-\begin{figure}
-    \centering
-    \includegraphics[width=\textwidth]{figures/4_corners.pdf}
-    \caption{We generate the four corners of the grid, then interpolate between both the z and c vectors.
-Although the network was only trained on binary attributes for c, interpolation results show that the computed latent space is smooth between attributes, and not simply discrete to those shown in the training set.}
-    \label{fig:4_c_interp}
-\end{figure}
-\end{comment}
+\subsection{Sampling from simplex section}
 
@@
 \jordan{this is the adding noise thing but i need to work out the correct way to do it with the directional vector}.
-
-\begin{figure}
-  \centering
-  \begin{tabular}[b]{c}
-    \includegraphics[width=0.9\textwidth]{figures/wn+bbh.pdf} \\
-    \small ~~~~~~~~~(a)
-  \end{tabular} %\qquad
-  \begin{tabular}[b]{c}
-    \includegraphics[width=0.46\textwidth]{figures/ambient_result.pdf} \\
-    \small ~~~~~~~~(b)
-  \end{tabular}
- \begin{tabular}[b]{c}
-    \includegraphics[width=0.44\textwidth]{figures/arithmetic_result.pdf} \\
-    \small ~~~~~~~~(c)
-  \end{tabular}
-  \caption{Conditional vector arithmetic.
-(a) Generated samples of a whitenoise burst and BBH insprial.
-(c) Effect of naively adding the components from (a) in the time domain.
-\jordan{just adding the two signals post generation} (c) Generation from the combined class vectors.
-}
-  \label{fig:arithmetic}
-\end{figure}
-
-\begin{comment}
-\begin{figure}
-    \centering
-    \includegraphics[width=\textwidth]{figures/arithm.pdf}
-    \caption{Vector arithmetic for unmodelled waveforms.
-Keeping the z vectors constant and generating two classes of signals, their class embedding vectors can then be averaged to produce a new class.
-The generator produces a waveform of this hybrid class (middle of right plot).
-For the surrounding 8 plots we add a small variance of Gaussian noise to the new class.
-}
-    \label{fig:add}
-\end{figure}
-\end{comment}
-\subsection{Classifier}
-\jordan{I'm working on this part and how to present the auxiliary part.}
 

### 2020-07-27 McGANn.py
Delete McGANn.py

@@ -1,347 +1,0 @@
-import os
-from numpy import zeros
-from numpy import ones
-from numpy import expand_dims
-from numpy.random import randn
-from numpy.random import randint
-from keras.optimizers import Adam
-from keras.models import Model
-from keras.layers import Input
-from keras.layers import Dense
-from keras.layers import Reshape
-from keras.layers import Flatten
-from keras.layers import Conv1D, Conv2D
-from keras.layers import UpSampling1D
-from keras.layers import Conv2DTranspose
-from keras.layers import LeakyReLU
-from keras.layers import BatchNormalization
-from keras.layers import Dropout, SpatialDropout1D
-from keras.layers import Embedding
-from keras.layers import Activation
-from keras.layers import Concatenate
-from keras.initializers import RandomNormal
-from matplotlib import pyplot
-import matplotlib.pyplot as plt
-plt.style.use('seaborn')
-from keras.layers.core import Lambda
-from generate_training_data import *
-
-os.environ["CUDA_VISIBLE_DEVICES"] = '2'
-
-from keras.backend.tensorflow_backend import set_session
-import tensorflow as tf
-tf.compat.v1.disable_eager_execution()
-
-config = tf.ConfigProto()
-config.gpu_options.allow_growth = True  # dynamically grow the memory used on the GPU
-sess = tf.Session(config=config)
-set_session(sess)  # set this TensorFlow session as the default session for Keras
-
-model_size = 2
-n_classes = 5
-T_obs = 1.0
-sample_rate = 1024
-dt = 1.0/sample_rate
-n_signals = 80000
-
-# define the standalone discriminator model
-def define_discriminator(in_shape=(1024,2), n_classes=n_classes):
-    # weight initialization
-    init = RandomNormal(stddev=0.02)
-    # image input
-    in_image = Input(shape=in_shape)
-    # downsample
-    fe = Conv1D(32*model_size, 7, strides=2, padding='same', kernel_initializer=init)(in_image)
-    fe = LeakyReLU(alpha=0.2)(fe)
-    fe = SpatialDropout1D(0.5)(fe)
-    # normal
-    fe = Conv1D(64*model_size, 7, strides=2, padding='same', kernel_initializer=init)(fe)
-    fe = LeakyReLU(alpha=0.2)(fe)
-    fe = SpatialDropout1D(0.5)(fe)
-    # downsample to 7x7
[…]

### 2020-08-24 Paper_draft/main.tex
paper changes

@@
 \section{Introduction}
-textwidth in inches: \printinunitsof{in}\prntlen{\textwidth}
+%textwidth in inches: \printinunitsof{in}\prntlen{\textwidth}
 \begin{comment}
@@
 waveforms are not accurately modelled or are complex to re-produce.
-Astrophysical sources for such transients include: Core collapse supernova,
-Neutron star instabilities, Fallback accretion onto a neutron star, Non
-axisymetric deformation in magnetars, Pulsar glitches and Neutron star
-post-mergers. \michael{Might be worth citing some sources for this statement}
+Astrophysical sources for such transients include: Core collapse supernova \cite{Fryer_2003}, Pulsar glitches \cite{Andersson_2001}, Neutron star
+post-mergers \cite{Baiotti_2007} and other as-yet unexplained physical phenomena.
 
@@
 The system is analogous to biology, where, some groups of neurons in animal brains cause certain others to fire.
+
+\subsection{Convolutional Neural Networks}
+Convolutional Neural Networks (CNNs) are designed to work with grid-like structures that exhibit strong local spatial dependencies.
+An example would be a two-dimensional image as each coloured pixel has similar intensities to their near neighbours.
+The value contained in each pixel can be thought of as adding an additional dimension or channel to the image.
+Although most work with CNNs involve image-based data, they can be applied to other spatially adjacent data types such as time-series and text items.
+CNNs are defined by the use of a convolution operation, a mathematical operation that expresses the amount overlap between functions.
+The convolution is applied by shifting one grid-like structure over the other, drawing out spatially important features between the two.
+A strided convolution reduces the dimensionality of the input while retaining spatial features.
+This can result in a loss of information along the boarders.
+To combat this, the input is padded with zeros at the edges which does not interfere with the convolutional operation.
+The output of the convolutional layer is then passed to an activation function.
 
@@
 in the range of [5,70] $\textrm{M}_{\odot}$ with zero spins
-and we fix m$_1$ $>$ m$_2$ \michael{I think the exponentials look neater without using frac\{\}\{\}}. The mass distribution is approximated by a power
+and we fix m$_1$ $>$ m$_2$. The mass distribution is approximated by a power
 law with index of 1.6 \cite{Abbott_2019}. The signals are generated using random right ascensions and
@@
 a probability of the the signal being real. This model is trained
-with binary cross entropy for the first output and sparse categorical
-cross-entropy for the second output. The full architecture description can be seen in \cref{Tab:hyperparameters}.~\chris{OK, very technically tight but too
-computer sciencey. Try to make it human readbale for a physicist and refer to
-the table of parameters in the appendix.}
+with binary cross entropy.
+The full architecture description can be seen in \cref{Tab:hyperparameters}.
+~\jordan{still too technical im not sure if we need to go into more detail on each thing mentioned.}
+%~\chris{OK, very technically tight but too
+%computer sciencey. Try to make it human readbale for a physicist and refer to
+%the table of parameters in the appendix.}
 
@@
 The final network design used in this work comes from the use of trial and
-error and the initial designs influenced by the available literature. After
+error and the initial designs influenced by the available literature.
+We found that the GAN performed better with both networks having the same number of layers and neurons which should encourage even competition between the generator and discriminator.
+After
 tuning the multiple hyperparamters (\cref{Tab:hyperparameters}), the GAN
-was trained for 1000 epochs and takes $\Or$(2) days to train.
-~\jordan{talk about making D and G 'symmetric' increasing batch size, number of filters powers of 2, spatial dropout,no early stopping.} ~\chris{trained on
-what? Were there any major decisions made based on the trial and error process?
-Anything that was learned from your mistakes that might be useful to others?}.
+was trained on $10^5$ signals which contained an even mixture of sine-gaussian, ringdown, white noise bursts, gaussian blips and BBHs for 1000 epochs and takes $\Or$(2) days to train.
+A larger batch size saw a small increase in performance at the cost of training speed and we decided that 128 was a fair compromise.
 
@@
     \includegraphics[width=\textwidth]{figures/generations/bbh.png}
-    \caption{Examples of \ac{GW} burst signals generated by a conditional generative adversarial network. Top row shows
-examples from the training set. By row: Sine-Gaussian, Ringdown,
+    \caption{Examples of \ac{GW} burst signals generated by a conditional generative adversarial network. By row: Sine-Gaussian, Ringdown,
 White-noise burst, Gaussian pulse, Binary black hole merger.}
-\label{fig:train} \end{figure}
+\label{fig:gen_signals} \end{figure}
 
@@
 The generator network is a function G : $\mathbf{z},\mathbf{c},\mathbb{\textbf{s}}$ $\in$ $\mathbb{R}^{100}$ $\to$ $\mathbb{R}^{1024\times2}$, where $\mathbf{z},\mathbf{c},\mathbb{\textbf{s}}$ are the latent vector, class embedding vector and sky positions respectively.
-Given a latent vector randomly sampled from a normal distribution with zero mean and unit variance, a class label which is represented by a 120 dimensional vector for each class and antenna responses, the results from the generator can be seen in \cref{fig:gen_signals}.
-Depending on the orientation of the detector with respect to a hypothetical signal in the sky, the waveforms may appear inverted, shifted in time and their strain attenuated.
-Each plot shows the output of the generator after given randomised $\mathbf{z}, \mathbb{\textbf{s}}$ and one of the five class vectors $\mathbf{c}$.
+Given a latent vector randomly sampled from a normal distribution with zero mean and unit variance, a class label which is represented by a 5 dimensional one-hot encoded vector for each class, the results from the generator can be seen in \cref{fig:gen_signals}.
+Each plot shows the output of the generator after given randomised $\mathbf{z}$ and one of the five class vectors $\mathbf{c}$.
+ %Depending on the orientation of the detector with respect to a hypothetical signal in the sky, the waveforms may appear inverted, shifted in time and their strain attenuated.
 
@@
 As with any function, there should be a one to one mapping from the domain and co-domain to allow for smooth transitions across the latent space.
-One advantage of using GANs as a waveform generator is that once it is trained, it can perform rapid generations faster than more intricate and computationally expensive algorithms.
+One advantage of using GANs as a waveform generator is that once it is trained, it can perform rapid generations faster than computationally expensive algorithms.
 For complicated data sets, the network architecture must be diverse and dense enough to capture distinct variations from the training set.
@@
 
-\subsection{Latent space interpolation}
+\subsubsection{Latent space interpolation}
 In this section we explore the latent space formed by the generator by interpolation.
-We take two random points in the latent space and linearly interpolate between them (six times inclusive).
+We take two random points in the latent space and linearly interpolate between them.
 These new latent space vectors can now be fed into the generator to make predictions on while keeping the class vectors constant.
-The third input, the response values are kept constant for each class.
 The full effect shown in \cref{fig:z_interp}.
@@
 
-\subsection{Class space interpolation}
+\begin{figure}
+    \centering
+    \includegraphics[width=\textwidth]{figures/generations/z_interp_sg.png}
+    \includegraphics[width=\textwidth]{figures/generations/z_interp_rd.png}
+    \includegraphics[width=\textwidth]{figures/generations/z_interp_wnb.png}
+    \includegraphics[width=\textwidth]{figures/generations/z_interp_blip.png}
+    \includegraphics[width=\textwidth]{figures/generations/z_interp_bbh.png}
+    \caption{Latent space linear interpolation, class space is held constant.}
+    \label{fig:z_interp}
+\end{figure}
+
+\subsubsection{Class space interpolation}
 In order to explore the class space we keep the latent vector held constant and interpolate through the 5 classes.
@@
 Sine-Gaussian to ringdown performs well in interpolation with each signal being a plausible burst GW.
-It is obvious that the embedding layer has clustered these two groups during training as they share many characteristics.
+It is obvious that the GAN has clustered these two groups during training as they share many characteristics.
 The other signals have sharper transitions but still retain plausible looking waveforms.
@@
     \centering
-    \includegraphics[width=\textwidth]{figures/generations/interp_rd-sg.png}
-    \includegraphics[width=\textwidth]{figures/generations/interp_wnb-blip.png}
+    \includegraphics[width=\textwidth]{figures/generations/interp_blip-sg.png}
+    \includegraphics[width=\textwidth]{figures/generations/interp_wnb-rd.png}
     \includegraphics[width=\textwidth]{figures/generations/interp_sg-bbh.png}
-    \caption{Latent space linear interpolation, class space is held constant.}
+    \caption{Class space linear interpolation, class space is held constant. Top row: gaussian blip to sine-gaussian, middle row: white noise burst to ringdown, bottom row: sine-gaussian to BBH.}
     \label{fig:c_interp}
@@
 
-\subsection{Sampling from simplex section}
+\subsection{Using a GAN to generate unmodelled waveforms}
+So far the analysis has focused on interpolating between two classes of signals with the aim to use the interpolated signals as unmodelled waveforms, instead, we may consider random mixtures of classes.
+We defined the classes in one-hot encoding framework, that is, each class resides at the corner points of a 5 dimensional cube.
+In order to generate an even mixture of classes we sample points uniformly in this space.
+\jordan{this would be the box}.
+Alternativly we can sampe points from the plane that intersects the four corners, which for a 5-dimensional case is, sample from a 4-simplex.
+Thks can nbee seen in \ref{fig:unmodelled_samples}.
+\jordan{why?
+this enforces the vector points to sum to one.
+Why is that good?
+Well it keeps the points lying on the simplex.}
 
-\subsection{Vector Arithmetic}
+\begin{figure}
+    \centering
+    \includegraphics[width=\textwidth]{figures/generations/simplex_sample1.png}
+    \includegraphics[width=\textwidth]{figures/generations/simplex_sample2.png}
+    \includegraphics[width=\textwidth]{figures/generations/simplex_sample3.png}
+
+    \includegraphics[width=\textwidth]{figures/generations/uniform_sample3.png}
+    \includegraphics[width=\textwidth]{figures/generations/uniform_sample2.png}
+    \includegraphics[width=\textwidth]{figures/generations/uniform_sample1.png}
+    \caption{GAN generations where the class vectors are sampled from the 4-D plane and sampled uniformly in the class space.}
+    \label{fig:unmodelled_samples}
+\end{figure}
+
+\begin{comment}
+We can now think of ways to properly sample from the space between these points in a uniform way.
+Uniformity enforces the condition that we have a variety of waveforms.
+Thge easiest being to uniformly sample points in this space and use them as the class vectors for the generator.
+Another way would be to keep the magnitude of the class vector as 1.
+For a 5-dimensional space we would sample from the 4-dimensional plane that intersects the corner points.
+\end{comment}
+
+\subsection{CNN analysis}
+In this section of the analysis we will forensically compare generations from the GAN to help determine the success and failures of the model.
+We investigate a simple case of using a CNN to detect whether a signal is contained in noise or if the data is noise only.
+The signals we train the CNN on are generated from the GAN with their latent input randomised from a 100-dimensional Gaussian distribution and are categorised by their method of defining their class vector:
+\begin{itemize}
+	\item Conditional – Definite categorical generations from the GAN. These signals are the closest to the training set.
+	\item Uniform – Generated using a uniform distribution U[0,1] as the input class vector.
+	\item Simplex – Generated using a Dirichlet distribution that samples from the 4-simplex as the input class vector. 
+\end{itemize}
+The CNN is trained to distinguish between two classes: signals in additive Gaussian noise and Gaussian noise, where “signals” are taken from either the Conditional, Uniform or Simplex cases.
+This means in total there are three CNNs to train and all CNNs share the same architectural structure.
+All of the training data used is “whitened” by a power spectral density (PSD) at Advanced LIGO design sensitivity, such that, there is equal power at each frequency and is correctly normalised.
+This procedure is applied to signals whose signal-to-noise ratios (SNRs) are defined prior to be in the range uniformly [1-16].
+For each run the training data consists of 200,000 signals which contain one half noise only and one half signal contained in noise.
+Of that 80\% is used for training and 20\% used for validation.
+A different testing set is also used in analysis that is 200,000 in size.
+
+*table of parameters used for CNN*
+
+In Fig.
+\ref{fig:roc_curves} we compare the CNN results between the three datasets, we train three CNNs on the Conditional, simplex and uniform data sets and use these models to make predictions on the other unseen datasets.
+We make a comparison by fixing the fraction of samples incorrectly identified as signals (false alarm rate) and plotting this versus the optimal SNR of the signals.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.8\textwidth]{figures/conditional_trained.png}
+    \includegraphics[width=0.8\textwidth]{figures/simplex_trained.png}
+    \includegraphics[width=0.8\textwidth]{figures/uniform_trained.png}
+
+    \caption{Efficiency curves comparing the performance of CNNs trained on conditional generations (top), simplex generations (middle), uniform generations (bottom) for a fixed false alarm rate of $10^{-3}$.}
+    \label{fig:roc_curves}
+\end{figure}
+
+These results show for a CNN trained on conditional signals, the uniform data set is distinguishable from the conditional and simplex dataset.
+The CNN is robust enough to capture the differences between the datasets and shows that the GAN can generate a variety of unmodelled waveforms that can be used in future testing.
+
+\begin{comment}
+{\subsection{Vector Arithmetic}
 In DCGANs the authors demonstrated unsupervised vector arithmetic with celebrity face generation.
@@
 \jordan{this is the adding noise thing but i need to work out the correct way to do it with the directional vector}.
+\end{comment}
 

### 2020-08-24 Paper_draft/main.tex
Add punctuation to equations
First set of comments

@@
 \usepackage[capitalize]{cleveref}
+
+\usepackage[mathlines]{lineno}% Enable numbering of text and display math
+\linenumbers\relax % Commence numbering lines
+
 \newcommand{\gguide}{{\it Preparing graphics for IOP Publishing journals}}
@@
 The next generation of Gravitational wave detectors will accelerate the number
-of gravitational wave detection's such that we can gain new in site into the
+of gravitational wave detections such that we can gain new in site into the
 physics behind the sources causing the phenomena. Numerical simulations and
-matched filtering are the standard for detecting gravitational waves for know
+matched filtering are the standard for detecting gravitational waves for known
 sources such as binary-black hole mergers. Other sources of gravitational waves
@@
 detectable, however, there must be a way to characterise them in order to build
-a model template. Here we construct a unmodeled burst generation scheme using
+a model template. \michael{Don't quite follow this sentence.} Here we construct a unmodelled burst generation scheme using
 Generative adversarial networks - a powerful class of machine learning.
@@
 %
-\ac{GW} burst algorithms \cite{Klimenko_2008, Aso_2008} are tested and tuned using model waveforms that may
+\ac{GW} burst detection algorithms \cite{Klimenko_2008, Aso_2008} are tested and tuned using modelled waveforms that may
 or may not have astrophysical significance but have easy to define parameters
-and share characteristics of real bursts that is enough to simulate a \ac{GW} passing between detectors.
-Such waveforms include sine-Gaussians: a Gaussian modulated sine wave that is by it's central frequency and decay parameter.
+and share characteristics of real bursts that are enough to simulate a \ac{GW} passing between detectors.
+Such waveforms include sine-Gaussians: a Gaussian modulated sine wave that is characterised by its central frequency and decay parameter.
 Bandlimited white-noise bursts: white noise that is contained within a certain frequency range and ring-downs which mimic the damped oscillations after a CBC merger.
@@
 
-With the expectation that there will be many more \ac{GW} detections in the future, researches are starting to realise the need for fast and efficient \ac{GW} analysis to compete with the rising number of detections.
+With the expectation that there will be many more \ac{GW} detections in the future, researchers are starting to realise the need for fast and efficient \ac{GW} analysis to compete with the rising number of detections.
 While still in its infancy, Machine Learning (ML) with GW has already shown great potential for overcoming data bottlenecks.
-\ac{GW} analysis in areas of detection \cite{Gabbard2017,Gebhard_2019,Krastev_2020}, glitch classification \cite{Bahaadini, George_2018,Razzano_2018} and parameter estimation \cite{gabbard2019bayesian,shen2019deterministic,green2020gravitationalwave} have shown the success of in ML pattern recognition.
+\ac{GW} analysis in areas of detection \cite{Gabbard2017,Gebhard_2019,Krastev_2020}, glitch classification \cite{Bahaadini, George_2018,Razzano_2018} and
+parameter estimation \cite{gabbard2019bayesian,shen2019deterministic,green2020gravitationalwave} have shown the success of in ML pattern recognition.
 Applying these algorithms show similar results to matched filtering techniques and have the benefit of being orders of magnitude faster.
+\michael{We mention aspects related to detection (pattern matching) but also metion PE in the same sentence and I think this is a bit confusing.}
 
@@
 Using the generative machine learning model: Generative Adversarial Networks (GANs), we train on five classes of known burst morphologies in the time domain.
-Working on the assumption that GANs construct smooth n-dimension vector spaces between it's input and output, we can then explore the space between the five classes to construct new unmodelled waveforms.
-As all the computationally expensive processes occur during training, the learned model after training is able to produce waveforms much faster than and in fact produce waveforms that are impossible to produce with current techniques.
+Working with the assumption that GANs construct smooth n-dimensional vector spaces between its input and output, we can then explore the space between the five classes to construct new unmodelled waveforms.
+As all the computationally expensive processes occur during training, the learned model after
+training is able to produce waveforms much faster than \michael{than what?} and in fact produce waveforms that are impossible to produce with current techniques.
 These new varieties of waveforms can then be used to diagnose detection algorithms and gain new insight into sources of \ac{GW} bursts.
@@
 A common approach in ML relies on the computer learning on past experience to make decisions on future events.
-The hierarchical nature of this approach means that the machine can build complicated concepts from simpler ones.
-This branch of AI is called deep learning.
+\michael{Not sure about the use of computer here, maybe
+\textit{relies on a model}?} The hierarchical nature of this approach means that the machine can build complicated concepts from simpler ones. This branch of AI is called deep learning.
 Neural networks are the quintessential machine learning algorithm that aims to approximate a function.
@@
 \begin{equation}
-\sigma(\sum_i w_i x_i + b)
+\sigma(\sum_i w_i x_i + b),
 \label{eqn:neuron}
@@
 The activations of the first layer (or input layer) act as the inputs to the second layer and so on until the output layer.
-Multilayered neural networks have intermediate layers between the input and output stages dubbed the hidden layers as the computations performed are not accessible to the user.
+Multi-layered neural networks have intermediate layers between the input and output stages dubbed the hidden layers as the computations performed are not accessible to the user.
 The network can be thought of as a function F: $\mathbb{R}^N\rightarrow \mathbb{R}^M $ reliant on how activations from one layer bring activations in the next.
@@
 The value contained in each pixel can be thought of as adding an additional dimension or channel to the image.
-Although most work with CNNs involve image-based data, they can be applied to other spatially adjacent data types such as time-series and text items.
+Although most work with CNNs involve image-based data, they can be applied to other spatially adjacent data types such as time-series and
+text items.
 CNNs are defined by the use of a convolution operation, a mathematical operation that expresses the amount overlap between functions.
 The convolution is applied by shifting one grid-like structure over the other, drawing out spatially important features between the two.
-A strided convolution reduces the dimensionality of the input while retaining spatial features.
+A strided convolution reduces the dimensionality of the input while retaining spatial features \michael{How?
+This is core part of the architecture of the GAN but is quite vague, I don't think it's
+obvious that stride imples moving the filter further.
+Maybe something like: \textit{the distance by which the grid is shifted is known as the stride and increasing it reduces the dimensionality of the output}}.
 This can result in a loss of information along the boarders.
@@
 that is set up to distinguish between real and fake data and a generator that
-produces synthetic reproductions of the real data. The generator performs a
+produces synthetic reproductions of the real data. \michael{Is it clear to the reader that the \textit{fake} data is the same as the synthetic data?} The generator performs a
 mapping from an input noise vector $\mathbf{z}$, that is usually sampled from a n-dimensional Gaussian space known as the latent space, to its representation of the
@@
 \begin{equation}
-\mathop{\text{min}}_{G}  \mathop{\text{max}}_{D} V(D,G) = \mathbb{E}_{\mathbf{x} \sim p_{\text{r}}(\mathbf{x})} [\text{log} D(\mathbf{x})] \\ + \mathbb{E}_{\mathbf{z} \sim p_{\text{z}}(\mathbf{z})} [\text{log}(1-D(G(\mathbf{z})))]
+  \mathop{\text{min}}_{G}  \mathop{\text{max}}_{D} V(D,G) = \mathbb{E}_{\mathbf{x} \sim p_{\text{r}}(\mathbf{x})} [\text{log} D(\mathbf{x})] \\ + \mathbb{E}_{\mathbf{z} \sim p_{\text{z}}(\mathbf{z})} [\text{log}(1-D(G(\mathbf{z})))],
 \label{equation:GANloss}
@@
 
-where, V is an objective function that is to be optimized.
+where V is an objective function that is to be optimized.
 Objective functions are a general term for either a loss function (to be minimized) or a negative loss function (to be maximised).
 D is the discriminator, G is the generator and ${\mathbf{x} \sim p_{\text{r}}(\mathbf{x})}$, ${\mathbf{z} \sim p_{\text{z}}(\mathbf{z})}$ are samples taken from the training data and generated data respectfully.
-In practice this approach was found to be unstable.
-Early on in training the generators weights are initialised randomly meaning that the early generations are noisy and uninformative.
+In practice this approach was found to be unstable \michael{Cite?}.
+Early on in training the
+generators weights are initialised randomly meaning that the early generations are noisy and uninformative.
 This means that the discriminator can easily learn to spot the fake generations and so the discriminator wins and the generator cannot continue to improve.
 To overcome this the framing of the generator is often changed.
-Rather than minimizing $\text{log}(1-D(G(\mathbf{z})))$ the objective now is to maximise $\text{log}(D(G(\mathbf{z})))$, that is, to maximise the probability of the generations being predicted as real.
-The idea being that we always want the loosing side to be able to leverage from its competitor.
+Rather than minimizing $\text{log}(1-D(G(\mathbf{z})))$ the objective now is to maximise $\text{log}(D(G(\mathbf{z})))$, that is, to maximise the probability of the
+generations being predicted as real. The idea being that we always want the loosing side to be able to leverage \michael{information?} from its competitor. 
 %
@@
 To gain more control over what a GAN is able to generate, a conditional variant of \acp{GAN} named \acp{CGAN}~\cite{cgan} was introduced by feeding in extra information into the generator and discriminator such as a class label or attribute label, c.
-The objective function is then modified:
+The objective function \cref{equation:GANloss}  is then modified:
 \begin{equation}
-\mathop{\text{min}}_{G}  \mathop{\text{max}}_{D} V(D,G) = \mathbb{E}_{\mathbf{x,c} \sim p_{\text{r}}(\mathbf{x,c})} [\text{log} D(\mathbf{x,c})] \\ + \mathbb{E}_{\mathbf{z} \sim p_{\text{z}}(\mathbf{z}),\mathbf{c} \sim p_{\text{r}}(\mathbf{c})} [\text{log}(1-D(G(\mathbf{z,c})))]
+  \mathop{\text{min}}_{G}  \mathop{\text{max}}_{D} V(D,G) = \mathbb{E}_{\mathbf{x,c} \sim p_{\text{r}}(\mathbf{x,c})} [\text{log} D(\mathbf{x,c})] \\ + \mathbb{E}_{\mathbf{z} \sim p_{\text{z}}(\mathbf{z}),\mathbf{c} \sim p_{\text{r}}(\mathbf{c})} [\text{log}(1-D(G(\mathbf{z,c})))].
 \label{equation:cGANloss}
@@
 parameters.
-The parameter ranges can be seen in \cref{Tab:training_parms} The families are: sine-Gaussian $h(t) = A \exp\left[ - (t-t_{0})^2 / \tau^2 \right] \sin (2 \pi f_0 (t-t_0))$, a sinusoidal wave with a Gaussian envelop characterised by a central frequency, $f_0$; Ring-down, $h(t) = A \exp \left[-{(t-t_0)} / {\tau} \right] \sin(2 \pi f_0 (t-t_0))$, with frequency $f_0$ and duration $\tau$, white-noise bursts, with bounded frequency bandwidth $\Delta f$ and duration $\tau$, gaussian pulse $h(t) = \exp(-t^2 / \tau^2)$ with duration $\tau$ and binary-black hole inspirals which are simulated using IMRPhenomD waveform \cite{Khan_2016} routine from
+The parameter ranges can be seen in \cref{Tab:training_parms}.
+The families are: sine-Gaussian $h(t) = A \exp\left[ - (t-t_{0})^2 / \tau^2 \right] \sin (2 \pi f_0 (t-t_0))$, a sinusoidal wave with a Gaussian envelop characterised by a central frequency, $f_0$; Ring-down, $h(t) = A \exp \left[-{(t-t_0)} / {\tau} \right] \sin(2 \pi f_0 (t-t_0))$, with frequency $f_0$ and duration $\tau$, white-noise bursts, with bounded frequency bandwidth $\Delta f$ and duration $\tau$, gaussian pulse $h(t) = \exp(-t^2 / \tau^2)$ with duration $\tau$ and binary-black hole inspirals which are simulated using IMRPhenomD waveform \cite{Khan_2016} routine from
 LALSuite \cite{lalsuite} which models the
@@
 cosine of a uniform distribution in the range [-1,1]. The peaks of the
-waveforms are set to be within [0.4,0.6]s of the 1s time interval.
+waveforms are set to be within [0.4, 0.6]s of the 1s time interval.
 
@@
 Most GANs now replace fully connected layers, where each neuron is connect to all the neurons in the previous and next layer, with convolutional layers.
-\ac{CNN} are designed to work with grid-like structures with close local dependencies like image and text based data, however, there are examples of audio synthesis work \cite{DBLP:journals/corr/abs-1809-11096}.
+\ac{CNN} \michael{capitalisation, not sure how it works with the accronyms package} are designed to work with grid-like structures with close local dependencies like image and text based data, however, there are examples of audio synthesis work \cite{DBLP:journals/corr/abs-1809-11096}.
 
@@
 The full architecture description can be seen in \cref{Tab:hyperparameters}.
-~\jordan{still too technical im not sure if we need to go into more detail on each thing mentioned.}
+~\jordan{still too technical im not sure if we need to go into more detail on each thing mentioned.} \michael{This para doesn't seem to technical to me}
 %~\chris{OK, very technically tight but too
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \begin{comment}
@@
 
-Given a 100 dimensional vector drawn from a normal distribution, a class label and sky localisation information, the GAN is able to generate burst-like waveforms  generalised from the training set.
+Given a 100 dimensional vector drawn from a normal distribution, a class label and sky localisation information, the GAN is able to generate burst-like waveforms  generalised from the training set \michael{How is the sky sampled?
+We know it's uniform but we should say explicitly}.
 We set out by describing the quality of generated waveforms and how they compare to the training set.
@@
 The generator network is a function G : $\mathbf{z},\mathbf{c},\mathbb{\textbf{s}}$ $\in$ $\mathbb{R}^{100}$ $\to$ $\mathbb{R}^{1024\times2}$, where $\mathbf{z},\mathbf{c},\mathbb{\textbf{s}}$ are the latent vector, class embedding vector and sky positions respectively.
-Given a latent vector randomly sampled from a normal distribution with zero mean and unit variance, a class label which is represented by a 5 dimensional one-hot encoded vector for each class, the results from the generator can be seen in \cref{fig:gen_signals}.
+\michael{Do we still need to include the class here since the generations do not have the AP applied?
+Either way, I think it's a bit confusing to say the generator takes c as an input.} Given a latent vector randomly sampled from a normal distribution with zero mean and unit variance, a class label which is represented by a 5 dimensional one-hot encoded vector for each class, the results from the generator can be seen in \cref{fig:gen_signals}.
 Each plot shows the output of the generator after given randomised $\mathbf{z}$ and one of the five class vectors $\mathbf{c}$.
@@
 As with any function, there should be a one to one mapping from the domain and co-domain to allow for smooth transitions across the latent space.
-One advantage of using GANs as a waveform generator is that once it is trained, it can perform rapid generations faster than computationally expensive algorithms.
+One advantage of using GANs as a waveform generator is that once it is trained, it can perform rapid generations faster than computationally
+expensive algorithms \michael{e.g.?}.
 For complicated data sets, the network architecture must be diverse and dense enough to capture distinct variations from the training set.
@@
 To test this, we perform linear interpolations in the latent and class space.
+
+\michael{Not going to comment on this section really since I think it will change based on what we discussed.}
 
@@
     \includegraphics[width=\textwidth]{figures/generations/z_interp_bbh.png}
-    \caption{Latent space linear interpolation, class space is held constant.}
+    \caption{Latent space linear interpolation, class space is constant.}
     \label{fig:z_interp}
@@
 \subsubsection{Class space interpolation}
-In order to explore the class space we keep the latent vector held constant and interpolate through the 5 classes.
+In order to explore the class space we keep the latent vector constant and interpolate through the 5 classes.
 We construct a path between the 5 waveforms and show that the space is populated enough to allow for transitions between classes.
@@
 \end{comment}
+
+\michael{We don't show any results with two detectors yet we use two detectors for the CNN, we might want to think when/where it's best to show some generations with both detectors.
+Maybe when we show a signal with noise since it's all part of the post-processing?}
 

### 2020-08-31 Paper_draft/main.tex
modified:   Paper_draft/main.tex

@@
 matched filtering are the standard for detecting gravitational waves for known
-sources such as binary-black hole mergers. Other sources of gravitational waves
+sources such as binary-black hole mergers. There are other sources of gravitational waves
 that remain elusive to standard modelling techniques and are expected to be
-detectable, however, there must be a way to characterise them in order to build
-a model template. \michael{Don't quite follow this sentence.} Here we construct a unmodelled burst generation scheme using
+detectable. Here we construct a unmodelled burst generation scheme using
 Generative adversarial networks - a powerful class of machine learning.
@@
 \ac{GW} analysis in areas of detection \cite{Gabbard2017,Gebhard_2019,Krastev_2020}, glitch classification \cite{Bahaadini, George_2018,Razzano_2018} and
-parameter estimation \cite{gabbard2019bayesian,shen2019deterministic,green2020gravitationalwave} have shown the success of in ML pattern recognition.
+parameter estimation \cite{gabbard2019bayesian,shen2019deterministic,green2020gravitationalwave}.
 Applying these algorithms show similar results to matched filtering techniques and have the benefit of being orders of magnitude faster.
@@
 As all the computationally expensive processes occur during training, the learned model after
-training is able to produce waveforms much faster than \michael{than what?} and in fact produce waveforms that are impossible to produce with current techniques.
+training is able to produce waveforms in fractions of a second and in fact produce waveforms that are impossible to produce with current techniques.
 These new varieties of waveforms can then be used to diagnose detection algorithms and gain new insight into sources of \ac{GW} bursts.
@@
 Rather than minimizing $\text{log}(1-D(G(\mathbf{z})))$ the objective now is to maximise $\text{log}(D(G(\mathbf{z})))$, that is, to maximise the probability of the
-generations being predicted as real. The idea being that we always want the loosing side to be able to leverage \michael{information?} from its competitor. 
+generations being predicted as real. The idea being that we always want the losing side to be able to leverage \michael{information?} from its competitor. 
 %
@@
 waveforms. BurstGAN is a conditional GAN that is trained on five signal morphology's spanning a range of prior
-parameters.
-The parameter ranges can be seen in \cref{Tab:training_parms}.
-The families are: sine-Gaussian $h(t) = A \exp\left[ - (t-t_{0})^2 / \tau^2 \right] \sin (2 \pi f_0 (t-t_0))$, a sinusoidal wave with a Gaussian envelop characterised by a central frequency, $f_0$; Ring-down, $h(t) = A \exp \left[-{(t-t_0)} / {\tau} \right] \sin(2 \pi f_0 (t-t_0))$, with frequency $f_0$ and duration $\tau$, white-noise bursts, with bounded frequency bandwidth $\Delta f$ and duration $\tau$, gaussian pulse $h(t) = \exp(-t^2 / \tau^2)$ with duration $\tau$ and binary-black hole inspirals which are simulated using IMRPhenomD waveform \cite{Khan_2016} routine from
+parameters. The parameter ranges can be seen in \cref{Tab:training_parms}. The families are:
+
+\begin{itemize}
+
+\item Sine-Gaussian $h_{sg}(t) = A \exp\left[ - (t-t_{0})^2 / \tau^2 \right] \sin (2 \pi f_0 (t-t_0))$, a sinusoidal wave with a Gaussian envelop characterised by a central frequency, $f_0$;.
+\item Ring-down, $h(t) = A \exp \left[-{(t-t_0)} / {\tau} \right] \sin(2 \pi f_0 (t-t_0))$, with frequency $f_0$ and duration $\tau$
+\item White-noise bursts, with bounded frequency bandwidth $\Delta f$ and duration $\tau$.
+\item Gaussian pulse $h(t) = \exp(-t^2 / \tau^2)$ with duration. $\tau$.
+\item Binary-black hole inspirals which are simulated using IMRPhenomD waveform \cite{Khan_2016} routine from
 LALSuite \cite{lalsuite} which models the
@@
 declinations uniform over the sky and the inclinations are drawn from the
-cosine of a uniform distribution in the range [-1,1]. The peaks of the
-waveforms are set to be within [0.4, 0.6]s of the 1s time interval.
-
-All training waveforms are sampled at 1024 Hz.
+cosine of a uniform distribution in the range [-1,1]. 
+\end{itemize}
+The peaks of the waveforms are set to be within [0.4, 0.6]s of the 1s time interval and all training waveforms are sampled at 1024 Hz.
 
@@
 
-Given a 100 dimensional vector drawn from a normal distribution, a class label and sky localisation information, the GAN is able to generate burst-like waveforms  generalised from the training set \michael{How is the sky sampled?
-We know it's uniform but we should say explicitly}.
+Given a 100 dimensional vector drawn from a normal distribution and a class label, the GAN is able to generate burst-like waveforms  generalised from the training set.
 We set out by describing the quality of generated waveforms and how they compare to the training set.
 We then explore the structure of the latent and class spaces by interpolating between points in these spaces.
-We test vector arithmetic that can be used to generate a new breed of signal by merging two or more families together.
-Finally, we discuss the capacity of the discriminator as a \ac{GW} burst classifier and the auxiliary component of this work.
+We test  two methods of sampling from the class space that can be used to generate a new breed of signal by merging two or more families together.
 
@@
 
-\subsection{Waveform quality}
-The generator network is a function G : $\mathbf{z},\mathbf{c},\mathbb{\textbf{s}}$ $\in$ $\mathbb{R}^{100}$ $\to$ $\mathbb{R}^{1024\times2}$, where $\mathbf{z},\mathbf{c},\mathbb{\textbf{s}}$ are the latent vector, class embedding vector and sky positions respectively.
-\michael{Do we still need to include the class here since the generations do not have the AP applied?
-Either way, I think it's a bit confusing to say the generator takes c as an input.} Given a latent vector randomly sampled from a normal distribution with zero mean and unit variance, a class label which is represented by a 5 dimensional one-hot encoded vector for each class, the results from the generator can be seen in \cref{fig:gen_signals}.
+\subsection{Signal generation}
+The generator network is a function G : $\mathbf{z},\mathbf{c} $ $\in$ $\mathbb{R}^{100}$ $\to$ $\mathbb{R}^{1024\times2}$, where $\mathbf{z},\mathbf{c}$ are the latent vector and class vector.
+Given a latent vector randomly sampled from a normal distribution with zero mean and unit variance, a class label which is represented by a 5 dimensional one-hot encoded vector for each class, the results from the generator can be seen in \cref{fig:gen_signals}.
 Each plot shows the output of the generator after given randomised $\mathbf{z}$ and one of the five class vectors $\mathbf{c}$.
@@
 
-\michael{Not going to comment on this section really since I think it will change based on what we discussed.}
-
-\subsubsection{Latent space interpolation}
 In this section we explore the latent space formed by the generator by interpolation.
@@
 \begin{table}[hb]
-\caption{ACGAN architecture}
+\caption{CGAN architecture}
 \footnotesize

### 2020-09-03 Paper_draft/main.tex
Added comments to section 1

@@
 The next generation of Gravitational wave detectors will accelerate the number
-of gravitational wave detections such that we can gain new in site into the
+of ac{GW} detections such that we can gain new in site into the
 physics behind the sources causing the phenomena. Numerical simulations and
-matched filtering are the standard for detecting gravitational waves for known
-sources such as binary-black hole mergers. There are other sources of gravitational waves
+matched filtering are the standard for detecting ac{GW}s for known
+sources such as binary-black hole mergers. There are other sources of ac{GW}s
 that remain elusive to standard modelling techniques and are expected to be
@@
 Generative adversarial networks - a powerful class of machine learning.
+\chris{time to add a real abstract}
 \end{abstract}
@@
 \acrodef{GW}[GW]{Gravitational wave}
+\acrodef{CBC}[CBC]{compact binary coalescence} 
+\acrodef{ML}[ML]{machine learning}
 \acrodef{GAN}[GAN]{generative adversarial network}
@@
 %
-Gravitational wave astronomy is now an established field, starting with the first
-detection of a binary black hole merger \cite{Abbott2016} in September 2015.
+\ac{GW} astronomy is now an established field, starting with the first
+detection of a binary black hole merger~\cite{Abbott2016} in September 2015.
 Following this, the first and second observations runs (O1 and O2) of Advanced
-LIGO and Advanced Virgo \cite{Prospects-dets, AdvLIGO, AdvLIGO2, AdvVIRGO} reported several more Compact Binary Coalescence (CBC)
-mergers \cite{Abbott2016a, Abbott2017, Abbott2017a, Abbott2017b}. On August
-2017 a binary neutron star merger was observed alongside its electromagnetic
-counterpart for the first time, giving rise to multimessenger gravitational
-wave astronomy.
+LIGO and Advanced Virgo~\cite{Prospects-dets, AdvLIGO, AdvLIGO2, AdvVIRGO}
+reported several more \ac{CBC} mergers~\cite{Abbott2016a, Abbott2017,
+Abbott2017a, Abbott2017b}. On 17th August 2017 a binary neutron star merger was
+observed alongside its electromagnetic counterpart for the first time, giving
+rise to multi-messenger ac{GW} astronomy.
 
@@
 %
-With these successes and continued upgrades to the detectors, further detections of CBCs are expected to be commonplace in a few short years.
-Another group of GW signals that has thus far been undetectable is GW ``bursts".
-GW bursts are transient signals of typically short duration ($<$ 1s) whose
-waveforms are not accurately modelled or are complex to re-produce.
-Astrophysical sources for such transients include: Core collapse supernova \cite{Fryer_2003}, Pulsar glitches \cite{Andersson_2001}, Neutron star
-post-mergers \cite{Baiotti_2007} and other as-yet unexplained physical phenomena.
+With these successes and continued upgrades to the detectors, further
+detections of \acp{CBC} are expected to be commonplace in future advanced
+detcetor observation runs. Another group of \ac{GW} signals that has thus far
+been undetected is \ac{GW} ``bursts". \ac{GW} bursts are classed as transient
+signals of typically short duration ($<$ 1s) whose waveforms are not accurately
+modelled or are complex to reproduce. Astrophysical sources for such transients
+include: Core collapse supernova~\cite{Fryer_2003}, Pulsar
+glitches~\cite{Andersson_2001}, Neutron star post-mergers~\cite{Baiotti_2007}
+and other as-yet unexplained astrophysical phenomena.
 
-GW detections so far have used a process called matched filtering, \cite{Owen1998}, where a large template bank of possible GW waveforms are compared to the detector outputs.
-In order to increase the chances of detection these template banks must span a large multi dimensional parameter space and the templates must be accurate, requiring significant computational cost.
-GW bursts are un-modelled; therefore there are no templates available and so these signals are undetectable through this scheme.
-Instead, detection involves distinguishing
-the signal from detector noise.
-Burst searches look for excess power contained in the time-frequency domain and rely on the astrophysical burst waveform appearing in multiple detectors at similar times.
-This is only possible if the detector noise is
-well characterised and the candidate signal can be differentiated from
-systematic or environmental glitches.
+% more details on burst searches
+%
+\ac{GW} detections so far have used a process called
+matched-filtering,~\cite{Owen1998}, where a large template bank of possible
+\ac{GW} waveforms are compared to the detector outputs. In order to increase
+the chances of detection these template banks must span a large
+multi-dimensional parameter space and the templates must be accurate, requiring
+significant computational cost~\chris{the accuracy doesn't obviously lead to a
+cost increase}. \ac{GW} bursts are un-modelled~\chris{except for the ones you
+mentione before? SNe, glicthes, post-merger? }; therefore there are no
+templates available and so matched-filtering is unsuitable for the detection of
+these signals.  Instead, detection involves distinguishing the signal from
+detector noise~\chris{but that's also what matched-filtering does}. Burst
+searches look for excess power contained in the time-frequency
+domain~\chris{all of them? In any case you have to provide references here to
+the pipelines (cWB, x-pipeline, etc... Siong can help)} and rely on the
+astrophysical burst waveform appearing in multiple detectors at similar times.
+This is only possible if the detector noise is well characterised and the
+candidate signal can be differentiated from systematic or environmental
+glitches.
 
@@
 %
-\ac{GW} burst detection algorithms \cite{Klimenko_2008, Aso_2008} are tested and tuned using modelled waveforms that may
-or may not have astrophysical significance but have easy to define parameters
-and share characteristics of real bursts that are enough to simulate a \ac{GW} passing between detectors.
-Such waveforms include sine-Gaussians: a Gaussian modulated sine wave that is characterised by its central frequency and decay parameter.
-Bandlimited white-noise bursts: white noise that is contained within a certain frequency range and ring-downs which mimic the damped oscillations after a CBC merger.
+\ac{GW} burst detection algorithms~\cite{Klimenko_2008, Aso_2008} are tested
+and tuned using modelled waveforms that may or may not have astrophysical
+significance but have easy to define parameters and share characteristics of
+real bursts that are enough to simulate a \ac{GW} passing between
+detectors~\chris{long sentence}. Such waveforms include sine-Gaussians: a
+Gaussian modulated sine wave that is characterised by its central frequency and
+decay parameter. Bandlimited white-noise bursts: white noise that is contained
+within a certain frequency range and ring-downs which mimic the damped
+oscillations after a \ac{CBC} merger.~\chris{seems strange to list only 3 of
+the 5 that we will be using later on.}
 
+% cut this text if not going to be used
+%
 \begin{comment}Such waveforms may have
@@
 %
+With the expectation that there will be many more \ac{GW} detections in the
+future, there is a growing need for fast and efficient \ac{GW} analysis methods
+to match the rising number of detections. While still in its infancy, \ac{ML}
+applications to \ac{GW} analyses have already shown great potential for
+overcoming data bottlenecks~\chris{what does that mean?}. \ac{GW} analysis in
+areas of detection~\cite{Gabbard2017,Gebhard_2019,Krastev_2020}, glitch
+classification~\cite{Bahaadini, George_2018,Razzano_2018} and parameter
+estimation~\cite{gabbard2019bayesian, shen2019deterministic,
+green2020gravitationalwave}~\chris{unfinished sentence, plus I wouldn't
+reference the Shen paper}. Applying these algorithms show similar results to
+matched-filtering techniques and have the benefit of being orders of magnitude
+faster. \michael{We mention aspects related to detection (pattern matching) but
+also metion PE in the same sentence and I think this is a bit
+confusing.}~\chris{yes, the matched-filtering comp[arison is only relevent for
+searches. The biggest speed gain is for the Bayesian PE. I also think that you
+need to reference more of the ML-GW literature here. I've added Mervyn's SNe
+paper, Joe's latest paper, our latest Gaussian ?Mixture model paper, 2 CW
+papers and the recent ML review paper to the bibligrapohy file but there are
+quite a few others. Have a look at the review to steal references. In each case
+try to say 1 sentence about what they do if possible.}
 
-With the expectation that there will be many more \ac{GW} detections in the future, researchers are starting to realise the need for fast and efficient \ac{GW} analysis to compete with the rising number of detections.
-While still in its infancy, Machine Learning (ML) with GW has already shown great potential for overcoming data bottlenecks.
-\ac{GW} analysis in areas of detection \cite{Gabbard2017,Gebhard_2019,Krastev_2020}, glitch classification \cite{Bahaadini, George_2018,Razzano_2018} and
-parameter estimation \cite{gabbard2019bayesian,shen2019deterministic,green2020gravitationalwave}.
-Applying these algorithms show similar results to matched filtering techniques and have the benefit of being orders of magnitude faster.
-\michael{We mention aspects related to detection (pattern matching) but also metion PE in the same sentence and I think this is a bit confusing.}
+% What this paper does on GANs in 1 paragraph - the point of the paper
+%
+In this work we aim to explore the use of \ac{ML} to generate and interpret
+unmodelled \ac{GW} burst waveforms. Using the generative machine learning
+model: \acp{GAN}, we train on five classes of known~\chris{are they known? In
+what sense?} burst morphologies~\chris{fancy word - what about waveform class?}
+in the time domain. Working with the assumption that \acp{GAN} construct smooth
+$n$-dimensional vector spaces between their input and output, we can then
+explore the space between the five classes to construct new
+unmodelled~\chris{hybrid?} waveforms. As all the computationally expensive
+processes occur during training, the learned model after training is able to
+produce waveforms in fractions of a second and in fact produce waveforms that
+are impossible~\chris{never say never (or impossible)} to produce with current
+techniques. These new varieties of waveforms can then be used to diagnose
+detection algorithms and gain new insight into sources of \ac{GW}
+bursts~\chris{yes, they can help diagnose or calibrate or assess the sensitivty
+of detection algorithms but also allow us to better train our algorithms to a
+broader range of possible signals and therefore enhance our detection ability}.
 
-% What this paper does on GANs in 1 paragraph
+% the structure of the paper
 %
-
-In this work we aim to explore the use of machine learning to generate and interpret
-unmodelled \ac{GW} burst waveforms.
-Using the generative machine learning model: Generative Adversarial Networks (GANs), we train on five classes of known burst morphologies in the time domain.
-Working with the assumption that GANs construct smooth n-dimensional vector spaces between its input and output, we can then explore the space between the five classes to construct new unmodelled waveforms.
-As all the computationally expensive processes occur during training, the learned model after
-training is able to produce waveforms in fractions of a second and in fact produce waveforms that are impossible to produce with current techniques.
-These new varieties of waveforms can then be used to diagnose detection algorithms and gain new insight into sources of \ac{GW} bursts.
-% the point of the paper
-%
-
-This paper is organised as follows: \jordan{unstructured at the moment}
+This paper is organised as follows: \jordan{unstructured at the
+moment}~\chris{time to add the structure.}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-In this work we present the potential of Generative Adversarial Networks for burst gravitational wave analysis.
+In this work we present the potential of Generative Adversarial Networks for burst ac{GW} analysis.
 We have shown that GANs have the ability to generate 5 class varieties of modelled burst \ac{GW} signals that can be generated at whim.
@@
 We belive that GANs have the ability to generate high fidelity waveforms at a fraction of the computational expense and do not rely on large prior parameter space.
-Having banks of these waveforms at hand can aid in our understand of the physics processes behind these non-standard gravitational wave emitters.
+Having banks of these waveforms at hand can aid in our understand of the physics processes behind these non-standard ac{GW} emitters.
 
@@
 \section*{References}
-\bibliography{iopart-num}
+\bibliography{references}
 

### 2020-09-03 Paper_draft/main.tex
Added comments up to start of section 3

@@
 
-\acrodef{GW}[GW]{Gravitational wave}
+\acrodef{GW}[GW]{gravitational wave}
 \acrodef{CBC}[CBC]{compact binary coalescence} 
 \acrodef{ML}[ML]{machine learning}
+\acrodef{AI}[AI]{artificial intelligence}
+\acrodef{CNN}[CNN]{convolutional neural network}
 \acrodef{GAN}[GAN]{generative adversarial network}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Introduction}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %textwidth in inches: \printinunitsof{in}\prntlen{\textwidth}
@@
 %
-\ac{GW} detections so far have used a process called
+\ac{GW} searches for modelled signals so far have used a process called
 matched-filtering,~\cite{Owen1998}, where a large template bank of possible
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Generative Adversarial Networks}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
     \end{minipage}
-    \caption{Neural Networks (a) A single neuron taking a vector of inputs and returning a singular output based on the weights, bias and activation function of the network.
-(b) The hyperbolic tangent used as an activation function.
-(c) A fully connected neural network containing two hidden layers that performs a mapping of an input vector to a singular output.
-\michael{Equation in the neuron looks very small}}
+    \caption{Neural Networks (a) A single neuron taking a vector of inputs and
+returning a single output based on the weights, bias and activation function
+of the network. (b) The hyperbolic tangent used as an activation
+function.~\chris{is this the actual activation that you use in the GAN?
+otherwise why focus on it alone, you could plot a handful on the same plot} (c)
+A fully connected~\chris{you haven't mentioned what a fully connected network
+actually is in the text} neural network containing two hidden layers that performs a
+mapping of an input vector to a single output. \michael{Equation in the
+neuron looks very small}~\chris{I agree, but the equation in (b) is even
+smaller. I would also recommed that you make the style of the FC network hidden
+and output layer neurons the same as the single perceptron in terms of colours.
+You could put $x_i$s in the input layer.}}
 \end{figure}
 
-Since the birth of programmable computers, people have wondered if machines can develop true intelligence beyond formal mathematical procedures.
-Today, ML aims to learn apparent relationships held within the given data or `training data' in order to make accurate predictions without the need for additional programming .
-A common approach in ML relies on the computer learning on past experience to make decisions on future events.
-\michael{Not sure about the use of computer here, maybe
-\textit{relies on a model}?} The hierarchical nature of this approach means that the machine can build complicated concepts from simpler ones. This branch of AI is called deep learning.
-Neural networks are the quintessential machine learning algorithm that aims to approximate a function.
-They are built from many single processing units called neurons.
-The simpliest Neural Network is the perceptron layer \cref{fig:perceptron} which holds a single neuron that takes several real inputs $x_{1}, ...
-, x_{i}$ and maps them to an output according to the following linear equation:
+% inroduce the concept of ML
+%
+Since the birth of programmable computers, people have wondered if machines can
+develop true intelligence beyond formal mathematical procedures. Today, \ac{ML}
+aims to learn apparent relationships held within the given data or `training
+data' in order to make accurate predictions without the need for additional
+programming. A common approach in \ac{ML} relies on the computer learning on
+past experience to make decisions on future events. \michael{Not sure about the
+use of computer here, maybe \textit{relies on a model}?} The hierarchical
+nature of this approach means that the machine can build complicated concepts
+from simpler ones~\chris{what hierarchical nature? You haven't mentioned
+anything about that.}. This branch of \ac{AI} is called deep
+learning~\chris{OK, but as long as you explain the hierarchy thing and how it
+implies complicated concepts from simpler ones.}.
 
-\begin{equation}
+% Introduce basic neural networks - a perceptron layer
+%
+Neural networks are the quintessential~\chris{really? quintessential?} \ac{ML}
+algorithm that aims to approximate a function. They are built from many single
+processing units called neurons. The simpliest Neural Network is the perceptron
+layer~\cref{fig:perceptron} which holds a single neuron that takes several real
+inputs $x_{1},\ldots, x_{i}$~\chris{and outputs what? also $i$ is the index and not the "final" index}
+and maps them to an output according to the linear equation 
+%
+\begin{align}
 \sigma(\sum_i w_i x_i + b),
 \label{eqn:neuron}
-\end{equation}
-where $w$ and $b$ are the weights and bias and $\sigma$ denotes the activation function.
-The weights are numbers which can be thought as the strength between connections.
-The output of a neuron is called its activation.
-Different choices of activation functions allow the user to simulate various models.
-A common example of an activation function is the hyperbolic tangent \cref{fig:tanh_activation} that is used when the outputs of the network must be both positive and negative and re-scaled to $[-1,1]$.
-It is often useful to introduce a bias, $b$, such that the neuron remains inactive above zero but is active when the sum reaches a defined threshold.
-This bias is added before the activation function and it tells us how high the weighted sum needs to be before the neuron becomes active.
+\end{align}
+%
+\chris{it's not an equation if it's not equal to something. Please make it
+eaqual something.} where $w$ and $b$ are the weights and bias and $\sigma$
+denotes the activation function. The weights are numbers which can be thought
+as the strength between connections~\chris{what connestions? between what
+objects?}. The output of a neuron is called its activation and different
+choices of activation function allow the user~\chris{are we users or developers
+or what?} to simulate various models. A common example of an activation
+function is the hyperbolic tangent~\cref{fig:tanh_activation} that is used when
+the outputs of the network must be both positive and negative~\chris{how can an
+output be both positive and negative. The language is ambiguous and confusing}
+and re-scaled to $[-1,1]$~\chris{at this stage in the explanation the reader
+has no idea what an output would look like or why it would be rescaled}. It is
+often useful to introduce a bias, $b$, such that the neuron remains inactive
+above zero but is active when the sum reaches a defined threshold. This bias is
+added before the activation function and it tells us how high the weighted sum
+needs to be before the neuron becomes active.~\chris{well kind of, but also not
+really. I would advise you to rewrite this (if we keep it) in a minimalist
+style just explaining what each item is and not trying to describe what it
+does.}
 
-The output of a single neuron is defined by \cref{eqn:neuron} and gives a prediction $\hat{y}$ that can be compared to the real value $y$ through a cost or loss function.
-If the loss is non-zero, the network must work to minimise this function by updating the weights in the negative direction of the loss gradient in a process referred to as gradient descent.
-This loss function plays a critical role in how neural networks learn.
+% the cost or loss function
+%
+The output of a single neuron is defined by~\cref{eqn:neuron} and gives a
+prediction $\hat{y}$ that can be compared to the real value $y$~\chris{what the
+hell is $y$, it's not been mentioned before} through a loss (also known as a
+cost) function. If the loss is non-zero~\chris{no, it doesn't matter whether
+the number is above or below or equal to zero, the machine will try to minimise
+the number (if negative, it will try to make it more negative)}, the network
+must work to minimise this function by updating the weights in the negative
+direction of the loss gradient in a process referred to as gradient
+descent~\chris{give reference and also make the distinction between this and
+the actual method used to do it, back progagation}. This loss function plays a
+critical role in how neural networks learn~\chris{OK, but are you going to
+expand on that or just leave it there? As far as I can tell from the text it's
+the *only* way network's learn so that's pretty critical and already evident}.
 
-A neural network contains many single neurons connected in a layered structure as shown in \cref{fig:neural_network}.
-The activations of the first layer (or input layer) act as the inputs to the second layer and so on until the output layer.
-Multi-layered neural networks have intermediate layers between the input and output stages dubbed the hidden layers as the computations performed are not accessible to the user.
-The network can be thought of as a function F: $\mathbb{R}^N\rightarrow \mathbb{R}^M $ reliant on how activations from one layer bring activations in the next.
-The system is analogous to biology, where, some groups of neurons in animal brains cause certain others to fire.
+% basic network structure
+%
+A neural network contains many single neurons connected in a layered structure
+as shown in~\cref{fig:neural_network}. The activations of the first layer (or
+input layer) act as the inputs to the second layer and so on until the output
+layer. Multi-layered neural networks have intermediate layers between the input
+and output stages dubbed the hidden layers as the computations performed are
+not accessible to the user~\chris{well that's not really true. We can access
+everything if we want but it depends on what you define as a user. Best to
+simply state what they're clalled and no need to give a reason.}. The network
+can be thought of as a function F: $\mathbb{R}^N\rightarrow
+\mathbb{R}^M$~\chris{does F not have to be in math-mode too? Is is a
+mathematical symbol?} reliant on how activations from one layer bring
+activations in the next~\chris{yes, kind of, but also reliant on the trained
+weights and biases too, so actually reliant on everything}. The system is
+analogous to biology, where, some groups of neurons in animal brains cause
+certain others to fire~\chris{best to stay away from analogies like these where
+the practical specifics can be picked apart}.
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Convolutional Neural Networks}
-Convolutional Neural Networks (CNNs) are designed to work with grid-like structures that exhibit strong local spatial dependencies.
-An example would be a two-dimensional image as each coloured pixel has similar intensities to their near neighbours.
-The value contained in each pixel can be thought of as adding an additional dimension or channel to the image.
-Although most work with CNNs involve image-based data, they can be applied to other spatially adjacent data types such as time-series and
-text items.
-CNNs are defined by the use of a convolution operation, a mathematical operation that expresses the amount overlap between functions.
-The convolution is applied by shifting one grid-like structure over the other, drawing out spatially important features between the two.
-A strided convolution reduces the dimensionality of the input while retaining spatial features \michael{How?
-This is core part of the architecture of the GAN but is quite vague, I don't think it's
-obvious that stride imples moving the filter further.
-Maybe something like: \textit{the distance by which the grid is shifted is known as the stride and increasing it reduces the dimensionality of the output}}.
-This can result in a loss of information along the boarders.
-To combat this, the input is padded with zeros at the edges which does not interfere with the convolutional operation.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+\acp{CNN} are designed to work with grid-like input structures that exhibit
+strong local spatial dependencies. An example would be a two-dimensional image
+as each coloured pixel has similar intensities to their near
+neighbours~\chris{it's not about that really, it's like you said, it's about
+spatial relationships}. The value contained in each pixel can be thought of as
+adding an additional dimension or channel to the image~\chris{no, the dimension
+and channel are specifically defined. A 2D image has 2 dimensions. An RGB image
+has 3 numbers per pixel and these are typcally stored as channels. Channels are
+dealt with differently to dimensions}. Although most work with \acp{CNN}
+involve image-based data, they can be applied to other spatially adjacent data
+types such as time-series and text items. \acp{CNN} are defined by the use of a
+convolution operation, a mathematical operation that expresses the amount
+overlap between functions. The convolution is applied by shifting one grid-like
+structure over the other, drawing out spatially important features between the
+two~\chris{yes, but what is being dragged over what? Time to define the
+convolutional neuron? Maybe add an equation?}. A strided convolution reduces
+the dimensionality of the input while retaining spatial features \michael{How?
+This is core part of the architecture of the GAN but is quite vague, I don't
+think it's obvious that stride imples moving the filter further. Maybe
+something like: \textit{the distance by which the grid is shifted is known as
+the stride and increasing it reduces the dimensionality of the
+output}}~\chris{why are we talking about strides at this point? Are they
+important for the GAN? You haven't mentioned kernel sizes or dropout. are these
+equally important?}. This can result in a loss of information along the
+borders~\chris{the borders of what?}. To combat this, the input is padded with
+zeros at the edges which does not interfere with the convolutional operation.
 The output of the convolutional layer is then passed to an activation function.
 
+~\chris{I'm getting the sense that these 2 sections of ANNs and CNNs aren't
+really helpful in their current state. They should either be removed OR tidied
+up. I don't think they need to be expanded upon but various statements can be
+removed and other important things can be added. Imagine reading this with no
+knowledge of ML. Do you get informed by this or confused?}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{GANs}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+% basic intro to GANs
+%
+A subset of deep learning that has seen fruitful development in recent years
+are \acp{GAN}~\cite{Goodfellow2014}. These unsupervised~\chris{they have
+training data don't they? Is that unsupervised?} algorithms learn patterns in a
+given training data set using an adversarial process. The generations from
+\acp{GAN} are state-of-the-art~\chris{a phrase that will not stand the test of
+time} in fields such as high quality image
+fidelity~\cite{brock2018large,karras2019analyzing}, text-to-image
+translation~\cite{reed2016generative}, and video
+prediction~\cite{liang2017dual} as well as time series
+generations~\cite{esteban2017realvalued}~\chris{do we still not have any other
+GW GAN applications to reference or are we hoping to still be the first?}.
 
-A subset of deep learning that has seen fruitful development in recent years is \acp{GAN} \cite{Goodfellow2014}. These unsupervised algorithms learn
-patterns in a given training data set using an adversarial process. The
-generations from \acp{GAN} are state-of-the-art in fields such as high quality image
-fidelity \cite{brock2018large,karras2019analyzing}, text-to-image translation
-\cite{reed2016generative} and video prediction \cite{liang2017dual} as well as
-time series generations \cite{esteban2017realvalued}.
-
-% How a GAN works
+% Basic components of a GAN
 %
 \acp{GAN} train two competing neural networks, consisting of a discriminator
-that is set up to distinguish between real and fake data and a generator that
-produces synthetic reproductions of the real data. \michael{Is it clear to the reader that the \textit{fake} data is the same as the synthetic data?} The generator performs a
-mapping from an input noise vector $\mathbf{z}$, that is usually sampled from a n-dimensional Gaussian space known as the latent space, to its representation of the
-data and the discriminator maps its input $\mathbf{x}$ to a probability that
-the input came form either the training data or generator.  During training,
-the discriminator is given a batch of samples that contains one half real data
-and one half fake data which it then makes predictions on. The loss for the
-discriminator is calculated by comparing its predictions to the labelled data
-through the binary cross-entropy function. \jordan{note to myself: This is important since eqn 2 is derived from it (thats where the logs come from)} The training process of a \ac{GAN}
+network that is set up to distinguish between real and fake data and a
+generator network that produces synthetic (fake) versions of the real data.
+\michael{Is it clear to the reader that the \textit{fake} data is the same as
+the synthetic data?} The generator performs a mapping from an input noise
+vector $\mathbf{z}$, that is usually sampled from a $n$-dimensional~\chris{be
+careful with statments about $n$-dimensions since $n$ is a variable and could
+mean the number of latent dimensions or the number of class dimensions or data
+dimensions, etc...} Gaussian space known as the latent space, to its
+representation of the data, and the discriminator maps its input $\mathbf{x}$ to
+a probability that the input came from either the training (real) data or
+generator (fake).
+
+% training a GAN
+%
+During training, the discriminator is given a batch~\chris{you have not
+introduced batches yet. Best to do that in the ANN section} of samples that
+contains one half real data and one half fake data which it then makes
+predictions on.  The loss for the discriminator is calculated by comparing its
+predictions to the labelled data through the binary cross-entropy function.
+\jordan{note to myself: This is important since eqn 2 is derived from it (thats
+where the logs come from)}~\chris{either give a reference to binary cross
+entropy or define it here mathematically}. The training process of a \ac{GAN}
 alternatively updates the weights of the discriminator and generator based on
-information on its competitors loss function. This loss of discriminator is
-used to update the weights of the generator to produce more realistic samples
-of the input distribution, the loss of the generator encourages the
-discriminator to update its classification abilities. GANs seek to find an equilibrium between the generator and discriminator in the form of a two-player game that can be summarised by the following:
-
+information on its competitors loss function~\chris{you haven't fully explained
+how the loss is computed in the 2 phases of each training pass. I recommend
+that you add that here other wise discussion of generator loss and discrimator
+loss makes no sense.}. This loss of the discriminator is used to update the
+weights of the generator to produce more realistic samples of the input
+distribution, the loss of the generator encourages the discriminator to update
+its classification abilities. \acp{GAN} seek to find an equilibrium between the
+generator and discriminator in the form of a two-player game that can be
+summarised by 
+%
+\begin{align}
+  \mathop{\text{min}}_{G}  \mathop{\text{max}}_{D} V(D,G) &= \mathbb{E}_{\mathbf{x} \sim p_{\text{r}}(\mathbf{x})} [\text{log} D(\mathbf{x})] + \mathbb{E}_{\mathbf{z} \sim p_{\text{z}}(\mathbf{z})} [\text{log}(1-D(G(\mathbf{z})))],
+\label{equation:GANloss}
+\end{align}
+%
+% remove these comments 
+%
 \begin{comment}
@@
 %
-\begin{equation}
-  \mathop{\text{min}}_{G}  \mathop{\text{max}}_{D} V(D,G) = \mathbb{E}_{\mathbf{x} \sim p_{\text{r}}(\mathbf{x})} [\text{log} D(\mathbf{x})] \\ + \mathbb{E}_{\mathbf{z} \sim p_{\text{z}}(\mathbf{z})} [\text{log}(1-D(G(\mathbf{z})))],
-\label{equation:GANloss}
-\end{equation}
-
-where V is an objective function that is to be optimized.
-Objective functions are a general term for either a loss function (to be minimized) or a negative loss function (to be maximised).
-D is the discriminator, G is the generator and ${\mathbf{x} \sim p_{\text{r}}(\mathbf{x})}$, ${\mathbf{z} \sim p_{\text{z}}(\mathbf{z})}$ are samples taken from the training data and generated data respectfully.
-In practice this approach was found to be unstable \michael{Cite?}.
-Early on in training the
-generators weights are initialised randomly meaning that the early generations are noisy and uninformative.
-This means that the discriminator can easily learn to spot the fake generations and so the discriminator wins and the generator cannot continue to improve.
-To overcome this the framing of the generator is often changed.
-Rather than minimizing $\text{log}(1-D(G(\mathbf{z})))$ the objective now is to maximise $\text{log}(D(G(\mathbf{z})))$, that is, to maximise the probability of the
-generations being predicted as real. The idea being that we always want the losing side to be able to leverage \michael{information?} from its competitor. 
+where $V$ is an objective function that is to be optimised. Objective functions
+are a general term for either a loss function (to be minimized) or a negative
+loss function (to be maximised). We use $D$ to define the discriminator
+function~\chris{output interpreted as a probability?} , $G$ for the generator
+function and ${\mathbf{x} \sim p_{\text{r}}(\mathbf{x})}$, ${\mathbf{z} \sim
+p_{\text{z}}(\mathbf{z})}$ are samples taken from the training data and
+generated data respectfully~\chris{no, $z$ can't be from the data since it's
+not called $x$. It is from the latent space distribution.}. In practice this
+approach was found to be unstable \michael{Cite?}~\chris{unstable for us or
+unstable in general, also add reference.}. Early on in training the generators
+weights are initialised randomly meaning that the early generations are noisy
+and uninformative. This means that the discriminator can easily learn to spot
+the fake generations and so the discriminator wins and the generator cannot
+continue to improve. To overcome this the framing~\chris{what is framing in
+this context?} of the generator is often changed. Rather than minimizing
+$\text{log}(1-D(G(\mathbf{z})))$ the objective now is to maximise
+$\text{log}(D(G(\mathbf{z})))$, that is, to maximise the probability of the
+generations being predicted as real. The idea being that we always want the
+losing side to be able to leverage \michael{information?} from its
+competitor.~\chris{OK, does this all mean that the previous equation is wrong?
+If so, why quote it. Just use the actual correct equation and explain why it's
+correct rather than explaining why something is wrong. I would also try to link
+up this equation with how we actually train i.e., we compute the first term by
+drawing samples from the training set $x$ and getting the average log-prob of
+the discriminator (not quite true since we actually input a mix of real $x$ and
+fake $G(z)\rightarrow x'$). Then we take a set of fake $x'$ made using $G(z)$
+with $z$ drawn from the latent space, and get the loss (but we switch the
+labels hence the $1-D(G(z))$. See what I mean? You shouls also refer to Fig 2
+here.} 
 %
@@
 In theory, the adversarial process will eventually lead to the local Nash
-equilibrium \cite{Nash1950} whereby both neural networks are trained
-optimally. In practice, however, \acp{GAN} are notoriously difficult
-to train. Such difficulties include: Non-convergence, where the model
-parameters oscillate and the loss never converges, mode collapse where the generator produces a
-limited diversity of samples, and diminishing
-gradients when applying gradient descent to a loss function that is discontinuous.
+equilibrium~\cite{Nash1950} whereby both neural networks are trained
+optimally~\chris{vague and not informative statement. What does optimal mean
+here?}. In practice, however, \acp{GAN} are notoriously difficult to train with
+difficulties that include: Non-convergence, where the model parameters
+oscillate and the loss never converges, mode collapse where the generator
+produces a limited diversity of samples, and diminishing gradients when
+applying gradient descent to a loss function that is discontinuous.~\chris{OK,
+difficult to train. I understand. Why are you telling the reader this? Will we
+be referring back to these issues later?}
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Conditional GANs}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 %
-To gain more control over what a GAN is able to generate, a conditional variant of \acp{GAN} named \acp{CGAN}~\cite{cgan} was introduced by feeding in extra information into the generator and discriminator such as a class label or attribute label, c.
-The objective function \cref{equation:GANloss}  is then modified:
-\begin{equation}
-  \mathop{\text{min}}_{G}  \mathop{\text{max}}_{D} V(D,G) = \mathbb{E}_{\mathbf{x,c} \sim p_{\text{r}}(\mathbf{x,c})} [\text{log} D(\mathbf{x,c})] \\ + \mathbb{E}_{\mathbf{z} \sim p_{\text{z}}(\mathbf{z}),\mathbf{c} \sim p_{\text{r}}(\mathbf{c})} [\text{log}(1-D(G(\mathbf{z,c})))].
+To gain more control over what a GAN is able to generate, a conditional variant
+of \acp{GAN} named \acp{CGAN}~\cite{cgan} was introduced by feeding in extra
+information into the generator and discriminator such as a class label or
+attribute label, $c$. The objective function~\cref{equation:GANloss}~\chris{I
+think it owuld be be best if you just stick to loss function rather than
+switching between loss and objective} is then
+%
+\begin{align}
+  \mathop{\text{min}}_{G}  \mathop{\text{max}}_{D} V(D,G) &= \mathbb{E}_{\mathbf{x,c} \sim p_{\text{r}}(\mathbf{x,c})} [\text{log} D(\mathbf{x,c})] + \mathbb{E}_{\mathbf{z} \sim p_{\text{z}}(\mathbf{z}),\mathbf{c} \sim p_{\text{r}}(\mathbf{c})} [\text{log}(1-D(G(\mathbf{z,c})))].
 \label{equation:cGANloss}
-\end{equation}
+\end{align}
 
-This simple addition has shown to work well in practice, for instance in image-to-image translation \cite{isola2016imagetoimage}. We will be using a conditional GAN for this study.
+This simple addition has shown to work well in practice, for instance in
+image-to-image translation~\cite{isola2016imagetoimage}. We will be using a
+conditional GAN for this study.~\chris{OK, but you have not defined the new
+changes to the loss function in the text. Please indicate that the training
+data and labels are being drawn from a joint distribution $p_r(x,c)$ and when
+making fake data you are drawing from $p_r(c)$ independent of =$p(z)$. However,
+what does the $r$ stand for and why is it important, and what defines $p_r(c)$?}
+
+~\chris{Finally, you need to refer to and discuss Figure 2. It is currently
+neither referenced or discussed.}
+
+% get rid of these comments if they are no longer useful
 %
@@
 its class that is also fed to the generator which then learns to generate
-waveforms based on the input label.} \label{fig:gan_comparison}
+waveforms based on the input label.~\chris{OK, a few things. Try to separate
+these a bit and maybe make them subplots with sublabels indicating GAN and CGAN
+distinction. Replace noise with latent (or otherwise). Noise implies GW data
+noise which it is not. Overall it's a bit basic and doesn't indicate either the
+2 competing training steps or any aspect of the loss or specify that $x$ and
+$z$ (and $c$) are drawn from distributions already defined in the text. Maybe it's OK without
+that. As for the CGAN, I'm troubled by the fact that there is only one $c$ box.
+It implies that the same $c$ value is given to each real and fake $x$ data when
+in fact each $x$ sample has it's own randomly drawn $c$ value.}} \label{fig:gan_comparison}
 \end{figure}

### 2020-09-03 Paper_draft/main.tex
Added comments up start of section 4

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Methodology}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \centering
-\caption{Burst training parameters}
+\caption{Burst training parameters~\chris{Add a bit more caption description
+here. Plus address the issues of the actual distributions used (uniform) and
+how you include the BBH parameters. It's also not obvious that all the classes
+share the same 3 parameters.}}
 %\footnotesize
@@
 
-GW burst signals remain an unmodelled phenomenon, as such, current
-detection algorithms focus on waveforms signals appearing within multiple detectors We propose a
-signal generation scheme using \acp{GAN} trained on burst-like
-waveforms. BurstGAN is a conditional GAN that is trained on five signal morphology's spanning a range of prior
-parameters. The parameter ranges can be seen in \cref{Tab:training_parms}. The families are:
-
+% introduce the signal models
+%
+\ac{GW} burst signals remain an unmodelled phenomenon~\chris{as in the
+introduction I think you need to make the distinction between unmodelled and
+modelled burst analyses}, as such, current detection algorithms exploit the
+fact that astrophysical signals will appear within data from multiple detectors
+in coincidence and share the same waveform morphology.~\chris{I have added to
+this first sentence but it still doesn't naturally lead intpo the next one} We
+propose a signal generation scheme using a \ac{CGAN} trained on burst-like
+waveforms. We call this \texttt{BurstGAN}~\chris{give reference to code repo
+here} and is a \ac{CGAN} trained on five signal classes each spanning a range
+of prior signal parameters. The signal classes are:
+
+% list the 5 waveform classes
+%
 \begin{itemize}
-
-\item Sine-Gaussian $h_{sg}(t) = A \exp\left[ - (t-t_{0})^2 / \tau^2 \right] \sin (2 \pi f_0 (t-t_0))$, a sinusoidal wave with a Gaussian envelop characterised by a central frequency, $f_0$;.
-\item Ring-down, $h(t) = A \exp \left[-{(t-t_0)} / {\tau} \right] \sin(2 \pi f_0 (t-t_0))$, with frequency $f_0$ and duration $\tau$
-\item White-noise bursts, with bounded frequency bandwidth $\Delta f$ and duration $\tau$.
-\item Gaussian pulse $h(t) = \exp(-t^2 / \tau^2)$ with duration. $\tau$.
-\item Binary-black hole inspirals which are simulated using IMRPhenomD waveform \cite{Khan_2016} routine from
-LALSuite \cite{lalsuite} which models the
-inspiral, merger and ringdown of a \ac{BBH} waveform. The component masses lie
-in the range of [5,70] $\textrm{M}_{\odot}$ with zero spins
-and we fix m$_1$ $>$ m$_2$. The mass distribution is approximated by a power
-law with index of 1.6 \cite{Abbott_2019}. The signals are generated using random right ascensions and
-declinations uniform over the sky and the inclinations are drawn from the
-cosine of a uniform distribution in the range [-1,1]. 
+%
+\item {\bf Sine-Gaussian}: $h_{\text{sg}}(t) = A \exp\left[ - (t-t_{0})^2 /
+\tau^2 \right] \sin (2 \pi f_0 (t-t_0))$, a sinusoidal wave with a Gaussian
+envelope characterised by a central frequency, $f_0$.~\chris{what about
+amplitude, time of arrival and initial phase? For all the other classes too.}
+%
+\item {\bf Ring-down}: $h_{\text{rd}}(t) = A \exp \left[-{(t-t_0)} / {\tau}
+\right] \sin(2 \pi f_0 (t-t_0))$, with frequency $f_0$ and duration $\tau$
+%
+\item {\bf White-noise bursts}: $h_{\text{wn}}(t_j) = Ag_j\exp\left[ -
+(t-t_{0})^2 / \tau^2 \right]$ where $g_j$ are drawn from a zero mean unit
+variance Gaussian distribution and ahave a bounded frequency bandwidth $\Delta
+f$ and duration $\tau$~\chris{no, they have a Gaussian envelope with a duration
+parameter $tau$, we don't explicitly define the bandwidth}.
+%
+\item {\bf Gaussian pulse}: $h_{\text{gp}}(t) = \exp(-t^2 / \tau^2)$ with
+duration parameter $\tau$.
+%
+\item {\bf Binary-black hole}: Simulated using the IMRPhenomD
+waveform~\cite{Khan_2016} routine from LALSuite~\cite{lalsuite} which models
+the inspiral, merger and ringdown of a \ac{BBH} waveform. The component masses
+lie in the range of [5,70] $\textrm{M}_{\odot}$ with zero spins and we fix
+$m_1>m_2$. The mass distribution is approximated by a power law with
+index of 1.6~\cite{Abbott_2019}. The signals are generated using random right
+ascensions and declinations uniform over the sky and the inclinations are drawn
+from the cosine of a uniform distribution in the range [-1,1].~\chris{OK, we
+have an issue here. First the prior parameters and ranges are being defined
+here rather than in the table with the other classes. Second, you are
+randomising the sky in order to get random antenna patterns which only act to
+change the relative amplitudes in multiple detectors - whcih we don't use any
+more. So I would say that you shoudl only use the plus polarisation since it is
+the same as the cross but pi/2 out of phase.}  
+%
 \end{itemize}
-The peaks of the waveforms are set to be within [0.4, 0.6]s of the 1s time interval and all training waveforms are sampled at 1024 Hz.
-
+%
+The location of the peak amplitude of the waveforms (corresponding to the
+mid-points of all but the ring-down and \ac{BBH} classes) are randomly drawn to
+be within [0.4, 0.6] sec from the start of the 1 sec time interval and all
+training waveforms are sampled at 1024 Hz.  The parameter prior ranges are
+defined in~\cref{Tab:training_parms}.~\chris{Yes, those are the ranges but what
+are the distributions?}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Architecture details}
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
 % Introduce some architecture features
@@
 Extensions to the original \ac{GAN} method such as the
-\ac{DCGAN}~\cite{Radford2015} have been widely praised for
-enabling a stable \ac{GAN} architecture.
-Most GANs now replace fully connected layers, where each neuron is connect to all the neurons in the previous and next layer, with convolutional layers.
-\ac{CNN} \michael{capitalisation, not sure how it works with the accronyms package} are designed to work with grid-like structures with close local dependencies like image and text based data, however, there are examples of audio synthesis work \cite{DBLP:journals/corr/abs-1809-11096}.
+\ac{DCGAN}~\cite{Radford2015} have been widely praised for enabling a stable
+\ac{GAN} architecture. Most GANs now replace fully connected layers, where each
+neuron is connect to all the neurons in the previous and next layer, with
+convolutional layers. \acp{CNN}~\michael{capitalisation, not sure how it works
+with the accronyms package}~\chris{I will fix this} are designed to work with
+grid-like structures with close local dependencies like image and text based
+data, however, there are examples of audio synthesis
+work~\cite{DBLP:journals/corr/abs-1809-11096}.~\chris{this text sounds very
+similar to the CNN text from earlier. Do you need this here? Can you simply say
+that we are using a DCGAN architecture or say that our networks use
+convolutional layers and then move on?}
 
@@
 %
-We adopt the suggestions of \cite{Radford2015,DBLP:journals/corr/abs-1809-11096}, lengthening
-one-dimensional convolution kernels on both the generator and discriminator.
-The Generator model is fully convolutional, upsampled using strided transposed
-convolutions with batch normalisation in the first layer and ReLU activations
-throughout with the exception of Tanh for the output layer. Each transposed
-convolutional layer uses a kernel size of $18\times 1$ and stride of 2. The
-discriminator network mirrors that of the generator without batch
-normalization, using LeakyReLU activations, SpatialDropout, and a 2-stride
-convolution for downsampling. The discriminator output is a single node activated by a Sigmoid that can be interpreted as
-a probability of the the signal being real. This model is trained
-with binary cross entropy.
-The full architecture description can be seen in \cref{Tab:hyperparameters}.
-~\jordan{still too technical im not sure if we need to go into more detail on each thing mentioned.} \michael{This para doesn't seem to technical to me}
-%~\chris{OK, very technically tight but too
-%computer sciencey. Try to make it human readbale for a physicist and refer to
-%the table of parameters in the appendix.}
+We adopt the suggestions
+of~\cite{Radford2015,DBLP:journals/corr/abs-1809-11096}, lengthening
+one-dimensional convolution kernels on both the generator and
+discriminator~\chris{what does this statment actually mean and why are you
+opening the paragrpah with it?}.  The Generator model is fully convolutional,
+upsampled using strided transposed~\chris{you mentioned strides before but not
+transposing. Can you explain that aspect seomwhere earlier on.} convolutions
+with batch normalisation~\chris{same here, can you mention it earlier} in the
+first layer and ReLU~\chris{you can easily mention ReLU and other activations
+earlier} activations throughout with the exception of the Tanh activation for
+the output layer~\chris{why do you need this for the output? State that it is
+to guarantee the output function is bound between [-1,1]}. Each transposed
+convolutional layer uses a kernel size of $18\times 1$~\chris{by saying 18x1
+you are saying that you are using a 2D kernel with width 1 but why not just say
+you use a 1D kernel of size 18?} and stride of 2. The discriminator network
+mirrors that of the generator without batch normalization~\chris{why?}, using
+LeakyReLU activations, SpatialDropout, and a 2-stride convolution for
+downsampling~\chris{any reason for these choices?}. The discriminator output is
+a single node with Sigmoid activation that can be interpreted as a probability
+of the the signal being real. This model is trained with binary cross
+entropy~\chris{how exactly if the output is 1 number rather than 2 (binary)?}.
+The full architecture description can be seen in~\cref{Tab:hyperparameters}.
+~\jordan{still too technical im not sure if we need to go into more detail on
+each thing mentioned.} \michael{This para doesn't seem to technical to
+me}~\chris{same here, not too technical but lacking detail and motivation for
+choices.}
+%~\chris{OK, very technically tight but too computer sciencey. Try to make it
+%human readbale for a physicist and refer to the table of parameters in the
+%appendix.}
 
@@
 The final network design used in this work comes from the use of trial and
-error and the initial designs influenced by the available literature.
-We found that the GAN performed better with both networks having the same number of layers and neurons which should encourage even competition between the generator and discriminator.
-After
-tuning the multiple hyperparamters (\cref{Tab:hyperparameters}), the GAN
-was trained on $10^5$ signals which contained an even mixture of sine-gaussian, ringdown, white noise bursts, gaussian blips and BBHs for 1000 epochs and takes $\Or$(2) days to train.
-A larger batch size saw a small increase in performance at the cost of training speed and we decided that 128 was a fair compromise.
+error and the initial designs influenced by the available literature. We found
+that the \ac{GAN} performed better with both networks having the same number of
+layers and neurons which should~\chris{should? well does it?} encourage even
+competition between the generator and discriminator.  After tuning the multiple
+hyperparameters (see \cref{Tab:hyperparameters}), the \ac{GAN} was trained on
+$10^5$ signals which contained an even mixture~\chris{be a bit more specific
+about what an even mixture is - technically they are drawn from a categorical
+distribution with equal propabilities for each class} of
+sine-Gaussian~\chris{Gauss was a person so we have to capitalise his stuff},
+ring-down, white noise bursts, Gaussian pulse and \acp{BBH} for 1000 epochs and
+takes $\Or$(2) days to train~\chris{on what? be specific}. A larger batch size
+saw a small increase in performance~\chris{what is performance in this case} at
+the cost of training speed and we decided that 128~\chris{128 what? Also, why
+pick on batch size as the thing to comment on here? What about learning rate,
+kernel size, etc...} was a fair compromise.
 
@@
 
-~\chris{In general I find this section to read like un-connected statements in
-the sense that they are un-connected to each other and un-connected to the main
-GW problem. Try to make it more like a recipe for doing this analysis.}
+~\chris{Please add a loss plot and use a paragrpah to describe what is going
+on.}
 

### 2020-09-03 Paper_draft/main.tex
Finished my comments

@@
 
+~\chris{there needs to be some more discusiion of what the latent space
+and $z$ variables represent in the GAN in general. It maps the intrinsic
+variation of the training space onto the Gaussian latent space distribution.}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \end{figure}
+
+~\chris{After describing the latent space meaning in the GAN section you need
+to bring that together with a discussion of the entirely seperate class space
+and how it is defined with reference to the on-hot encoded corners of a 5-D
+vector space. Here is where you can inroduce the concept of the space and
+mention the issue of probing the regions between the corners}
 
@@
 \begin{comment}
-
 \begin{itemize}
@@
 
-Given a 100 dimensional vector drawn from a normal distribution and a class label, the GAN is able to generate burst-like waveforms  generalised from the training set.
-We set out by describing the quality of generated waveforms and how they compare to the training set.
-We then explore the structure of the latent and class spaces by interpolating between points in these spaces.
-We test  two methods of sampling from the class space that can be used to generate a new breed of signal by merging two or more families together.
+% describe the main idea
+%
+Given a 100-dimensional vector drawn from a normal distribution and a class
+label, the GAN is able to generate burst-like waveforms generalised from the
+training set~\chris{please state this in terms of the latent space and class
+space}. We set out by describing the quality of generated waveforms and
+how they compare to the training set. We then explore the structure of the
+latent and class spaces by interpolating between points in these spaces. We
+test two methods of sampling from the class space that can be used to generate
+a new breed of signal composed of weighted elements of each training class.
 
@@
     \caption{Examples of \ac{GW} burst signals generated by a conditional generative adversarial network. By row: Sine-Gaussian, Ringdown,
-White-noise burst, Gaussian pulse, Binary black hole merger.}
-\label{fig:gen_signals} \end{figure}
-
-\subsection{Signal generation}
-The generator network is a function G : $\mathbf{z},\mathbf{c} $ $\in$ $\mathbb{R}^{100}$ $\to$ $\mathbb{R}^{1024\times2}$, where $\mathbf{z},\mathbf{c}$ are the latent vector and class vector.
-Given a latent vector randomly sampled from a normal distribution with zero mean and unit variance, a class label which is represented by a 5 dimensional one-hot encoded vector for each class, the results from the generator can be seen in \cref{fig:gen_signals}.
-Each plot shows the output of the generator after given randomised $\mathbf{z}$ and one of the five class vectors $\mathbf{c}$.
- %Depending on the orientation of the detector with respect to a hypothetical signal in the sky, the waveforms may appear inverted, shifted in time and their strain attenuated.
-
-\subsection{Interpolation}
-Machine learning algorithms are often described as universal function approximators.
-In the generators case it maps samples drawn from a 100 dimensional Gaussian space to its representation of the training set.
-As with any function, there should be a one to one mapping from the domain and co-domain to allow for smooth transitions across the latent space.
-One advantage of using GANs as a waveform generator is that once it is trained, it can perform rapid generations faster than computationally
-expensive algorithms \michael{e.g.?}.
-For complicated data sets, the network architecture must be diverse and dense enough to capture distinct variations from the training set.
-Most GANs perform well on relatively low resolution image generations, however, higher resolutions demand larger networks and long training times.
-GANs attempting to replicate complicated structures and do not have the necessary architecture either struggle to produce results at all or fall into the common failure mode know as mode collapse; where the generator produces a small variety of samples or simply memorises the training set.
-To test this, we perform linear interpolations in the latent and class space.
-
-In this section we explore the latent space formed by the generator by interpolation.
-We take two random points in the latent space and linearly interpolate between them.
-These new latent space vectors can now be fed into the generator to make predictions on while keeping the class vectors constant.
-The full effect shown in \cref{fig:z_interp}.
-We can see that each plot shows plausible waveforms suggesting that the generator has constructed a smooth space unlike the discrete training case.
-Additionally as each class is given the same latent points to interpolate over, we can see that the waveforms cluster together with respect to their parameters.
-Visually, the sine-gaussian and ring-down waveforms share similar frequencies and the other signals show similar decays and starting epochs.
-The only exception is BBH waveforms, which is expected as they were trained with more variety of parameters and consistently have their peaks in the last quarter of the time series.
+White-noise burst, Gaussian pulse, Binary black hole merger.~\chris{please add
+lots more description to the caption regarding wjhat you are plotting. Mention
+that these are generated waveforms plotted as a function of time, latent space
+values are randomised for each panel (or are they the same for each column?)
+classes on each row. Also mention the zoom in on the time axis. Also fix the
+time axis limits so they are consistent across all waveforms.}}
+\label{fig:gen_signals} 
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Known class signal generation}
+
+The generator network is a function $G$ : $\mathbf{z},\mathbf{c} $ $\in$
+$\mathbb{R}^{100}$ $\to$ $\mathbb{R}^{1024\times2}$,~\chris{why is this
+outputting to 2 timeseries? Is this out of date?} where $\mathbf{z},\mathbf{c}$
+are the latent vector and class vector~\chris{these have already been defined
+}. Given a latent vector randomly sampled from a normal distribution with zero
+mean and unit variance, a class label which is represented by a 5 dimensional
+one-hot encoded vector for each class~\chris{give an example e.g.
+$c=[0,1,0,0,0]$ represents the ring-down signal class}, the results from the
+generator can be seen in \cref{fig:gen_signals}~\chris{please indicate that
+this is all done after training has completed}. Each plot shows the output of
+the generator for random input latent space vectors $\mathbf{z}$ and each row
+corresponds to one of the five class vectors $\mathbf{c}$.~\chris{yes? What
+about the plot? Anything positive to say about what you're showing? Please
+comment on the quality of the generated waveforms and the good varaition within
+each class representative of the variation in the training data. The point is
+to show the general variation and quality.}
+
+\chris{You also need to make it clear somewhere (maybe here) that you are
+generting single polarisation waveforms with normalised amplitude fixed to
+unity.}
+
+\chris{Also, how is the reader going to judge that your waveforms are good if
+we don't show any examples of the training data. I recommend a single plot
+showing 5 waveforms (5 panels horizontally) for reference.}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Interpolation within the latent space}
+
+% expain what we are planning to show here
+%
+\ac{ML} algorithms are often described as universal function approximators. In
+the case of the generator it maps samples drawn from a 100 dimensional Gaussian
+distribution in the latent space to its representation of the training set. As
+with any function, there should be a one to one mapping from the domain and
+co-domain to allow for smooth transitions across the latent space. One
+advantage of using \acp{GAN} as a waveform generator is that once it is
+trained, it can perform rapid generations faster than computationally expensive
+algorithms \michael{e.g.?}~\chris{you can maybe reference Seb Kahn and Green
+here soon. It will be on the arXiv next week I think - they did fast CBC
+waveform generation.  Also Walter Del Pozzo has a paper xoming out soon on
+this. Neither use GANs though, just ML}. For complicated data sets, the network
+architecture must be diverse and dense enough to capture distinct variations
+from the training set.  Most GANs perform well on relatively low resolution
+image generations, however, higher resolutions demand larger networks and long
+training times. GANs attempting to replicate complicated structures and do not
+have the necessary architecture either struggle to produce results at all or
+fall into the common failure mode know as mode collapse; where the generator
+produces a small variety of samples or simply memorises the training set. To
+test this, we perform linear interpolations in the latent and class
+space.~\chris{lots of technical talk before actually saying what you are trying
+to do. Reverse this. Also try to provide references for the technical talk}
+
+\chris{this paragraph should come before the other one since it explains what
+you are doing before going into technical stuff} In this section we explore the
+latent space formed by the generator by interpolation. We take two random
+points in the latent space and linearly interpolate between them~\chris{OK, but
+how do you select the latent points? Are they the same pair of points for each
+class?}. These new latent space vectors can now be fed into the generator to
+make predictions on~\chris{"to make predictions on" - what does that mean?}
+while keeping the class vectors constant at each of the 5 \chris{fiducial?}
+training classes. The full effect shown in~\cref{fig:z_interp}~\chris{not a
+sentence}. We can see that each plot shows plausible waveforms suggesting that
+the generator has constructed a smooth space unlike the discrete training
+case~\chris{don't confuse the issue by saying that the class space is discrtee
+when later we want to show the opposite}. Additionally as each class is given
+the same latent points to interpolate over, we can see that the waveforms
+cluster together with respect to their parameters. Visually, the sine-gaussian
+and ring-down waveforms share similar frequencies and the other signals show
+similar decays and starting epochs for a common latent space input. The only
+exception is for the \ac{BBH} waveforms. This can be explained by the fact that
+they were trained with more variety of parameters~\chris{what is more variety
+of parameters? Does it really mean anything?} and consistently have their peak
+amplitudes in the last quarter of the time series~\chris{do they? In the plot
+the peak amplitude locations seem to range from 0.6 back to 0.5 but that's not
+too different to the ring-downs, the white noise or the pulse. The
+sine-Gaussian is the one that stands out as different. Can you please verify
+the correctness of the plot you are referring to.}.
+
+\chris{I think that it might be sensible to hand-pick the latent space
+locations as the origin and the point $[1,1,\ldots,1]/2$. When you do random
+locations we don't know what we should expect to get.}
 
@@
     \includegraphics[width=\textwidth]{figures/generations/z_interp_bbh.png}
-    \caption{Latent space linear interpolation, class space is constant.}
+    \caption{Latent space linear interpolation, class space is
+constant.~\chris{lots more discription needed. what is being plotted against
+what? What is being held fixed, what is being varied.}}
     \label{fig:z_interp}
@@
 
-\subsubsection{Class space interpolation}
-In order to explore the class space we keep the latent vector constant and interpolate through the 5 classes.
-We construct a path between the 5 waveforms and show that the space is populated enough to allow for transitions between classes.
-Sine-Gaussian to ringdown performs well in interpolation with each signal being a plausible burst GW.
-It is obvious that the GAN has clustered these two groups during training as they share many characteristics.
-The other signals have sharper transitions but still retain plausible looking waveforms.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{Interpolation between pairs of classes}
+
+In order to explore the class space we keep the latent vector constant and
+interpolate through the 5 classes. We construct a path between the 5 waveforms
+and show that the space is populated enough to allow for transitions between
+classes. Sine-Gaussian to ringdown performs well in interpolation with each
+signal being a plausible burst GW. It is obvious that the GAN has clustered
+these two groups during training as they share many characteristics. The other
+signals have sharper transitions but still retain plausible looking waveforms.
+
+~\chris{this is one of  the most important sections of the paper and there
+is barely 1 paragrpah about it. Please beter explain what you are doing in
+general when you fix the latent space location and explore the class space. The
+concept of having arbitrary points in the 5-D class space should have been made
+clear earlier on in the CGAN section (or elsewhere). There also isn't currently a
+reference to the corresponding figure.}
 
@@
     \includegraphics[width=\textwidth]{figures/generations/interp_sg-bbh.png}
-    \caption{Class space linear interpolation, class space is held constant. Top row: gaussian blip to sine-gaussian, middle row: white noise burst to ringdown, bottom row: sine-gaussian to BBH.}
+    \caption{Class space linear interpolation, class space is held
+constant~\chris{no it isn't}.
+Top row: gaussian blip to sine-Gaussian, middle row: white noise burst to
+ringdown, bottom row: sine-Gaussian to BBH.~\chris{Again, more description,
+start from the basics, what is plotted against what. Is the latent space fixed
+the same for each row? Add the class space vectors on each panel. We have 5
+classes and so there are 10 possible pairs but you can't fit 10 rows here so
+why do 3? Why not 5 or 6? }}
     \label{fig:c_interp}
@@
 
-\subsection{Using a GAN to generate unmodelled waveforms}
-So far the analysis has focused on interpolating between two classes of signals with the aim to use the interpolated signals as unmodelled waveforms, instead, we may consider random mixtures of classes.
-We defined the classes in one-hot encoding framework, that is, each class resides at the corner points of a 5 dimensional cube.
-In order to generate an even mixture of classes we sample points uniformly in this space.
-\jordan{this would be the box}.
-Alternativly we can sampe points from the plane that intersects the four corners, which for a 5-dimensional case is, sample from a 4-simplex.
-Thks can nbee seen in \ref{fig:unmodelled_samples}.
-\jordan{why?
-this enforces the vector points to sum to one.
-Why is that good?
-Well it keeps the points lying on the simplex.}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{General interpolsation within the class space}
+
+So far the analysis has focused~\chris{not really focussed, you only dedicated
+1 paragraph to it in the previous subsection} on interpolating between two
+classes of signals with the aim to use the interpolated signals as unmodelled
+waveforms, instead, we may consider random mixtures of classes~\chris{don't
+sell this according to our thought processes as we did the research, sell it as
+"we just explained the pair interpolation since it's a stepping stone to the
+general interpolation"}. We defined the classes in one-hot encoding framework,
+that is, each class resides at the corner points of a 5 dimensional
+cube~\chris{this should have already been stated n earlier sections}. In order
+to generate an even mixture~\chris{by definition, it won't be an even mixture
+if points are randomly sampled} of classes we sample points uniformly in this
+space. \jordan{this would be the box}. Alternativly we can sampe points from
+the plane that intersects the four corners, which for a 5-dimensional case is,
+sample from a 4-simplex.~\chris{please dedicate an entire paragraph to the
+simplex and box explanation. You may even need an equation or 2.} This can be
+seen in~\ref{fig:unmodelled_samples}. \jordan{why? this enforces the vector
+points to sum to one. Why is that good? Well it keeps the points lying on the
+simplex.}~\chris{indeed. The reasons were originally that the plane is the
+simplest structure (a hyper-surface or manifold if you;re being fancy) in the
+class space that intersects all classes and has a symmetry such that no class
+is favoured over any other - however that property is largely due to the
+locations within the one-hot encoding space. Sampling from the simplex can be
+seen as sampling from between the classes - truly interpolating within the
+space. Alternatively, the cube is not the simplest space since it contains
+points up to a distance of unity from the closst class e.g. [0,0,0,0,0] is a
+distance of 1 away from all classes (as is [1,1,1,1,1]). This space contains
+the simplex as a subspace but also allows for some level of extrapolation.
+Hence we would expect the unexpected in the cube and hope for less surprises
+with the simplex. THere is also the possibility of exploring outside the cube.
+}
+
+~\chris{Also, discuss the corresponding figure! There has to be comment on the
+features of simplex vs box generations as well as general comments about how
+the GAN likes to mix signals up. Pick on specific examples and comment on
+interesting or annoying features.}
 
@@
     \includegraphics[width=\textwidth]{figures/generations/simplex_sample3.png}
-
     \includegraphics[width=\textwidth]{figures/generations/uniform_sample3.png}
@@
     \includegraphics[width=\textwidth]{figures/generations/uniform_sample1.png}
-    \caption{GAN generations where the class vectors are sampled from the 4-D plane and sampled uniformly in the class space.}
+    \caption{GAN generations where the class vectors are sampled from the 4-D
+plane and sampled uniformly in the class space.~\chris{As always, far more
+description needed. What are you plotting against what? Do you fix or randomise
+the latent space locations? You absolutely need to specify which are simplex
+and which are box.}}
     \label{fig:unmodelled_samples}
@@
 
+~\chris{I have an idea for the plots. Could we have a colour coding system
+where each class gets a colour and then when you mix them you plot it with the
+mixed colours - you average the RGB values. Maybe everything would look brown?
+Worth a try?}
+
+% remove these comments
+%
 \begin{comment}
-We can now think of ways to properly sample from the space between these points in a uniform way.
-Uniformity enforces the condition that we have a variety of waveforms.
-Thge easiest being to uniformly sample points in this space and use them as the class vectors for the generator.
-Another way would be to keep the magnitude of the class vector as 1.
-For a 5-dimensional space we would sample from the 4-dimensional plane that intersects the corner points.
-\end{comment}
-
-\michael{We don't show any results with two detectors yet we use two detectors for the CNN, we might want to think when/where it's best to show some generations with both detectors.
-Maybe when we show a signal with noise since it's all part of the post-processing?}
-
-\subsection{CNN analysis}
-In this section of the analysis we will forensically compare generations from the GAN to help determine the success and failures of the model.
-We investigate a simple case of using a CNN to detect whether a signal is contained in noise or if the data is noise only.
-The signals we train the CNN on are generated from the GAN with their latent input randomised from a 100-dimensional Gaussian distribution and are categorised by their method of defining their class vector:
+We can now think of ways to properly sample from the space between these points
+in a uniform way. Uniformity enforces the condition that we have a variety of
+waveforms. Thge easiest being to uniformly sample points in this space and use
+them as the class vectors for the generator. Another way would be to keep the
+magnitude of the class vector as 1. For a 5-dimensional space we would sample
+from the 4-dimensional plane that intersects the corner points.  \end{comment}
+
+\michael{We don't show any results with two detectors yet we use two detectors
+for the CNN, we might want to think when/where it's best to show some
+generations with both detectors. Maybe when we show a signal with noise since
+it's all part of the post-processing?}~\chris{I agree, see my comment in the
+CNN section next.}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Searching for generalised burst - a CNN analysis}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+In this section of the analysis we will forensically~\chris{no we won't}
+compare different waveform generations from the \ac{CGAN} to help determine the
+success and failures of the model~\chris{what does this mean? What model?}. We
+investigate a simple case using a \ac{CNN} to detect whether a signal is
+contained in noise or if the data contains noise only. The signals we use to
+train the \ac{CNN} are generated from the \ac{GAN} with their latent input
+randomised from a 100-dimensional Gaussian distribution~\chris{yes, but this
+should be obvious since we never deviate from the 100-D latent vector approach}
+and are categorised by the method used to sample from the class space. These
+methods are divided into the following:
+
 \begin{itemize}
-	\item Conditional – Definite categorical generations from the GAN. These signals are the closest to the training set.
-	\item Uniform – Generated using a uniform distribution U[0,1] as the input class vector.
-	\item Simplex – Generated using a Dirichlet distribution that samples from the 4-simplex as the input class vector. 
+%
+\item {\bf Conditional}: Definite categorical generations~\chris{yes, but what
+does that mean. You've never mentioned that phrase before} from the \ac{GAN}.
+These signals are the closest to the training set.
+%
+\item {\bf Uniform}: Generated using a uniform distribution U[0,1] as the input
+class vector~\chris{yes, but you need to specify the 5-D nature of the space}.
+%
+\item {\bf Simplex}: Generated using a Dirichlet distribution that samples from the
+4-simplex as the input class vector and includes within it the conditional
+locations.~\chris{all fine as long as you have defined the 4-simplex earlier
+on.} 
+%
 \end{itemize}
-The CNN is trained to distinguish between two classes: signals in additive Gaussian noise and Gaussian noise, where “signals” are taken from either the Conditional, Uniform or Simplex cases.
-This means in total there are three CNNs to train and all CNNs share the same architectural structure.
-All of the training data used is “whitened” by a power spectral density (PSD) at Advanced LIGO design sensitivity, such that, there is equal power at each frequency and is correctly normalised.
-This procedure is applied to signals whose signal-to-noise ratios (SNRs) are defined prior to be in the range uniformly [1-16].
-For each run the training data consists of 200,000 signals which contain one half noise only and one half signal contained in noise.
-Of that 80\% is used for training and 20\% used for validation.
-A different testing set is also used in analysis that is 200,000 in size.
-
-*table of parameters used for CNN*
-
-In Fig.
-\ref{fig:roc_curves} we compare the CNN results between the three datasets, we train three CNNs on the Conditional, simplex and uniform data sets and use these models to make predictions on the other unseen datasets.
-We make a comparison by fixing the fraction of samples incorrectly identified as signals (false alarm rate) and plotting this versus the optimal SNR of the signals.
+
+\chris{please add an example plot showing the normalised and whitened input of
+an SNR=8 signal, one panel for each detector, with noisy signal and noise-free
+signal plotted on top. Then remember to reference it in the text.}
+
+The CNN~\chris{whoah, hold on. What CNN? You said you were going to use one but
+can we get a few more details first. what's the input, what's the output,
+what's the loss function, then point us to a table of params in the appendix.}
+is trained to distinguish between two classes: signals in additive Gaussian
+noise and Gaussian noise, where “signals” are taken from either the
+Conditional, Uniform or Simplex cases~\chris{the signals+noise and noise
+statement is repetetive of the previous paragraph.}. This means in total there
+are three \acp{CNN} to train and all \acp{CNN} share the same architectural
+structure. All of the training data used is whitened using the Advanced LIGO
+design sensitivity \ac{PSD}, such that there is equal noise power at each
+frequency and the data is correctly normalised~\chris{but what is correctly
+normalised. Remember trhat we have to be reproducible so you have to make sure
+that someone reading this can repeat your experiment.}. This procedure is
+applied to signals whose \acp{SNR} are sampled uniformly in the range $[1-16]$.
+For each run~\chris{what is a run} the training data consists of $2\times 10^5$
+signals which contain one half noise only and one half signal contained in
+noise. Of that, 80\% is used for training and 20\% used for validation. A
+different testing set is also used in the analysis that is $2\times 10^5$ in
+size.~\chris{This final sentence is worded strangely but also why do we have
+such a large testing set? I can only imagine that we did this so that we could
+go to small $\sim 10^{-5}$ false alarm rates. Is that right?}
+
+\chris{there is no mention of the "old" box, the one that randomised the sky
+location, time shifted the signals and applied the antenna patterns. Also no
+mention of multi-detector data and no mention of use of channels. Please add
+all of this. }
+
+*table of parameters used for CNN*~\chris{put this in the appendix with the
+GAN table}
+
+In~\cref{fig:roc_curves} we compare the \ac{CNN} results between the three
+datasets, we train three \acp{CNN} on the Conditional, simplex and uniform data sets
+and use these models to make predictions on the other unseen datasets. We make
+a comparison by fixing the fraction of samples incorrectly identified as
+signals (false alarm rate) and plotting this versus the optimal SNR of the
+signals.~\chris{this last sentence isn't quite right}
 
@@
     \includegraphics[width=0.8\textwidth]{figures/uniform_trained.png}
-
-    \caption{Efficiency curves comparing the performance of CNNs trained on conditional generations (top), simplex generations (middle), uniform generations (bottom) for a fixed false alarm rate of $10^{-3}$.}
+    \caption{Efficiency curves comparing the performance of \acp{CNN} trained on
+conditional generations (top), simplex generations (middle), uniform
+generations (bottom) for a fixed false alarm rate of $10^{-3}$.~\chris{more
+description. What is plotted against what? The fonts are different to the other
+plots. The y-axis is not a rate but a prbability (a FAP unfortunately)}}
 \label{fig:roc_curves} 
@@
 
-These results show for a CNN trained on conditional signals, the uniform data set is distinguishable from the conditional and simplex dataset.
-The CNN is robust enough to capture the differences between the datasets and shows that the GAN can generate a variety of unmodelled waveforms that can be used in future testing.
-
+These results show for a \ac{CNN} trained on conditional signals, the uniform data
+set is distinguishable from the conditional and simplex dataset. The \ac{CNN} is
+robust enough to capture the differences between the datasets and shows that
+the GAN can generate a variety of unmodelled waveforms that can be used in
+future testing.
+
+~\chris{please write more about the results of the CNN}
+
+% remove this comment if not being used
 \begin{comment}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-In this work we present the potential of Generative Adversarial Networks for burst ac{GW} analysis.
-We have shown that GANs have the ability to generate 5 class varieties of modelled burst \ac{GW} signals that can be generated at whim.
-The latent and class spaces were explored through interpolation and suggest that the space provides smooth translations between classes and overall waveform shape.
-We then showed targeted waveform generation by mixing classes to produce new unmodlled waveform varieties that can be used to test current burst search pipelines.
-\jordan{couple of sentences about classifier}.
-
-In order to extend this work to a viable burst wave generator and classifier a few points require further research.
-In principle it is trivial to add another detector inside the response layer \jordan{response is the wrong thing to say since the time delay isnt really a response, extrinsic layer?
-just non trainable layer?
-The box?}, however, as this now 3 dimensional signal is feed to the discriminator this will no doubt require further tweaking of the network.
-We can add more burst-like wave forms in the training set, like detector glitches which would similarly require further network design.
-The work presented here is noise free.
-To havea complete generation and detection package we would like to train the network on signals hidden in additive Gaussian noise and test the ability of the auxiliary classifier.
-
-The approach shown in this work shows promise in generating unmodelled burst waveforms from exotic sources.
-Having the ability to quickly generate new waveforms is essential to test current detection schemes and their susceptibilty to unmodelled sources.
-We belive that GANs have the ability to generate high fidelity waveforms at a fraction of the computational expense and do not rely on large prior parameter space.
-Having banks of these waveforms at hand can aid in our understand of the physics processes behind these non-standard ac{GW} emitters.
-
-\jordan{I want to include a link to the github etc but also a google collab scrip like the one for BigGANs: \\
+
+% summary of the paper
+%
+In this work we present the potential of \acp{GAN} for
+burst \ac{GW} analysis. We have shown that \acp{GAN} have the ability to generate 5
+class varieties~\chris{yes, but you make it sound like 5 is special and it's
+not} of modelled burst \ac{GW} signals that can be generated at
+whim~\chris{really? whim?}. The latent and class spaces were explored through interpolation and
+suggest that the space provides smooth translations between classes and overall
+waveform shape. We then showed targeted waveform generation by mixing classes
+to produce new unmodelled waveform varieties that can be used to test current
+burst search pipelines. \jordan{couple of sentences about
+classifier}.~\chris{expand this. You have 15-20 pages of material so you can
+get a nioce big paragrpah or 2 out of this. It will be repetitive, yes, but
+that's the point.}
+
+% extra things to think about
+%
+In order to extend this work to a viable burst wave generator and classifier a
+few points require further research. In principle it is trivial to add another
+detector inside the response layer \jordan{response is the wrong thing to say
+since the time delay isnt really a response, extrinsic layer? just non
+trainable layer? The box?}, however, as this now 3 dimensional signal is feed
+to the discriminator this will no doubt require further tweaking of the
+network. We can add more burst-like wave forms in the training set, like
+detector glitches which would similarly require further network design. The
+work presented here is noise free. To havea complete generation and detection
+package we would like to train the network on signals hidden in additive
+Gaussian noise and test the ability of the auxiliary classifier. 
+~\chris{this paragrph is old and out of date. Please unpdate it.}
+
+The approach shown in this work shows promise in generating unmodelled burst
+waveforms from exotic~\chris{no} sources. Having the ability to quickly
+generate new waveforms is essential to test current detection schemes and their
+susceptibilty to unmodelled sources. We believe that \acp{GAN} have the ability
+to generate high fidelity waveforms at a fraction of the computational
+expense~\chris{don't focus on the expense part since burst waveforms are cheap
+anyway} and do not rely on large prior parameter space. Having banks of these
+waveforms at hand can aid in our understand of the physics processes behind
+these non-standard ac{GW} emitters.  
+~\chris{we need to write down paragrph headinsg in the next meeting. I'm tired.}
+
+\jordan{I want to include a link to the github etc but also a google collab
+scrip like the one for BigGANs: \\
 \url{https://colab.research.google.com/github/tensorflow/hub/blob/master/examples/colab/biggan_generation_with_tf_hub.ipynb.}
@@
 \begin{table}[hb]
-\caption{CGAN architecture}
+\caption{CGAN architecture~\chris{More, more, more desctription. Also split the
+generatpr and descriminator parts.}}
 \footnotesize
@@
 \section{Many more generated examples}
+~\chris{do we still need this?}
 

### 2020-09-09 Paper_draft/figures/ACGAN_diagram_vertical.tex
changes to cGAN
addressed comments up to section 3

@@
 \node (r) [X real] {\textbf{X} real};
-\node (f) [X fake, right of = r] {\textbf{X} fake};
+\node (f) [X fake, right of = r, xshift = 0cm] {\textbf{X} fake};
 \node (G) [generator,above of = f, scale = 2] {\textbf{G}};
-\node (z) [zinput] [zinput, above of = G, xshift = 1cm] {\textbf{z} (noise)};
+\node (z) [zinput] [zinput, above of = G, xshift = 1cm] {\textbf{z} (latent)};
 \node (c) [coutput, left of = z] {\textbf{c} (class)};
 \node (D) [discriminator, below of = f, xshift = -1cm, scale = 2] {\textbf{D}};
-\node (rf) [real/fake, below of = D, xshift = 1.2cm] {real/fake};
-\node (co) [coutput, left of = rf, xshift = -0.5cm] {c = 1, 2, ...};
+\node (rf) [real/fake, below of = D] {real/fake};
+%\node (co) [coutput, left of = rf, xshift = -0.5cm] {c = 1, 2, ...};
 
 \draw [arrow] (z) edge[out=270,in=90] (G);
+\draw [arrow] (c) edge[out=270,in=90] (D);
 \draw [arrow] (c) edge[out=270,in=90] (G);
@@
 \draw [arrow] (D) edge[out=270,in=90] (rf);
-\draw [arrow] (D) edge[out=270,in=90] (co);
+%\draw [arrow] (D) edge[out=270,in=90] (co);
 

### 2020-09-09 Paper_draft/figures/NN_basics.tex
addressed comments up to section 3

\documentclass{article}
\usepackage[subpreambles=true]{standalone}
\usepackage{graphicx}
\usepackage{amsmath,amssymb}
\usepackage{tikz}
\usetikzlibrary{decorations.pathreplacing,angles,quotes,shapes.geometric, arrows,calc}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{wrapfig, blindtext}
\usepackage{pgfplots}
\usepackage{tikz}
\usetikzlibrary{decorations.pathreplacing,angles,quotes,shapes.geometric, arrows,calc}
\usepackage{import}
\pgfplotsset{compat=1.16}

\begin{document}
\begin{figure}[h!]
\begin{subfigure}[b]{0.30\linewidth}
   \begin{subfigure}[b]{1\linewidth}
   	\centering
	\resizebox{\linewidth}{!}{
 	\begin{tikzpicture}		
		    \node[scale=0.3] 		   (x1) at (0,0.8) {$x_1$}; 
		    \node[scale=0.3] 		   (x2) at (0,0.5) {$x_2$};  
		    \node[scale=0.3] 		   (x3) at (0,0.2) {$x_3$};       
    		    \node [draw, circle,scale=0.18,fill=blue!25]          (c3) at (0.5,0.5) {\Large $\sigma(\sum_i w_i x_i + b)$};
    \draw[->] (x1)--(c3);
    \draw[->] (x2)--(c3);
    \draw[->] (x3)--(c3);
     \draw[->] (c3)--(1,0.5);
   	\end{tikzpicture}
	}
	\caption{}
	 \label{fig:perceptron}
 \end{subfigure}

   \begin{subfigure}[b]{1\textwidth}
  	\centering
	\resizebox{\linewidth}{!}{
\begin{tikzpicture}
\begin{axis}[
    xmin=-2.5, xmax=2.5,
    ymin=-1.5, ymax=1.5,
    axis lines=center,
    axis on top=true,
    domain=-2.5:2.5,
    ylabel=$\sigma$,
    xlabel=$x$,
    ]

    \addplot [mark=none,draw=red,ultra thick] {tanh(\x)};
    \node [left, red] at (axis cs: 0,0.5) {\Large $\sigma(x) = \tanh x$};

    %% Add the asymptotes
    \draw [blue, dotted, thick] (axis cs:-2.5,-1)-- (axis cs:0,-1);
    \draw [blue, dotted, thick] (axis cs:+2.5,+1)-- (axis cs:0,+1);
\end{axis}
\end{tikzpicture}
	}
	\caption{}
	 \label{fig:tanh}
\end{subfigure}
\end{subfigure}
	 \begin{subfigure}[b]{0.70\textwidth}
\centering
\resizebox{\linewidth}{!}{
\def\layersep{1.5cm}
\begin{tikzpicture}[shorten >=1pt,draw=black, ->,node distance=\layersep]

    \tikzstyle{every pin edge}=[<-,shorten <=1pt]
    \tikzstyle{neuron}=[circle,draw=black, very thick, fill=blue!25, minimum size=22pt,inner sep=0pt]
    \tikzstyle{input neuron}=[circle,draw=black,very thick,fill=black!25, minimum size=22pt,inner sep=0pt];
    \tikzstyle{output neuron}=[neuron];
    \tikzstyle{hidden neuron}=[circle,draw=black,very thick,fill=blue!25,minimum size=22pt,inner sep=0pt];
    \tikzstyle{annot} = [text width=4em, text centered]

    % Draw the input layer nodes
    \foreach \name / \y in {1,...,5}
    % This is the same as writing \foreach \name / \y in {1/1,2/2,3/3,4/4}
        \node[input neuron] (I-\name) at (0,-\y) {$x_{\name}$};

    % Draw the hidden layer nodes
    \foreach \name / \y in {1,...,3}
        \path[yshift=-1cm]
            node[hidden neuron] (H-\name) at (\layersep,-\y cm) {};

  \foreach \namee / \y in {1,...,3}
        \path[yshift=-1 cm]
            node[hidden neuron] (H1-\namee) at (2*\layersep,-\y cm){};

    % Draw the output layer node
  \node[output neuron,pin={[pin edge={->}]right:}, right of=H1-2] (O) {};
    % Connect every node in the input layer with every node in the
    % hidden layer.
    \foreach \source in {1,...,5}
        \foreach \dest in {1,...,3}
            \path (I-\source) edge (H-\dest);

 \foreach \source in {1,...,3}
        \foreach \dest in {1,...,3}
            \path (H-\source) edge (H1-\dest);

    % Connect every node in the hidden layer with the output layer
    \foreach \source in {1,...,3}
        \path (H1-\source) edge (O);

    % Annotate the layers
    %\node[annot,above of=H-1, node distance=1cm] (hl) {Hidden layers};
   % \node[annot,left of=I-4] at (0) {Input layer};
    %\node[annot,right of=hl] {Output layer};

    \draw[decoration={brace,mirror,raise=15pt},decorate,-]
  (I-1.north) -- node[left=0.8cm,scale=0.7] {Input layer} (I-5.south);

    \draw[decoration={brace,raise=15pt},decorate,-]
  (H-1.west) --  node[above=0.8cm,scale=0.7]{Hidden layers}  (H1-1.east);

    \draw[decoration={brace,raise=15pt},decorate,-]
  (O.west) --  node[above=0.8cm,scale=0.7]{Output layers}  (O.east);

\end{tikzpicture}
}
 \caption{}
 \label{fig:network}
 \end{subfigure}

\caption{Neural Networks (a) A single neuron taking a vector of inputs and
returning a single output based on the weights, bias and activation function
of the network. (b) The hyperbolic tangent used as an activation
function.~\chris{is this the actual activation that you use in the GAN?
otherwise why focus on it alone, you could plot a handful on the same plot} (c)
A fully connected~\chris{you haven't mentioned what a fully connected network
actually is in the text} neural network containing two hidden layers that performs a
mapping of an input vector to a single output. \michael{Equation in the
neuron looks very small}~\chris{I agree, but the equation in (b) is even
smaller. I would also recommed that you make the style of the FC network hidden
and output layer neurons the same as the single perceptron in terms of colours.
You could put $x_i$s in the input layer.}}
\end{figure}

\end{document}

### 2020-09-09 Paper_draft/main.tex
addressed comments up to section 3

@@
 \usepackage{layouts}
-%\usepackage{import}
-\usepackage{subfig}
+\usepackage{import}
+%\usepackage{subfig}
+\usepackage{subcaption}
 \usepackage{tikz}
@@
 \usepackage[capitalize]{cleveref}
+
+\usepackage{graphicx}
+\usetikzlibrary{decorations.pathreplacing,angles,quotes,shapes.geometric, arrows,calc}
+\usepackage{wrapfig, blindtext}
+\usepackage{pgfplots}
+\pgfplotsset{compat=1.16}
 
@@
 the chances of detection these template banks must span a large
-multi-dimensional parameter space and the templates must be accurate, requiring
-significant computational cost~\chris{the accuracy doesn't obviously lead to a
-cost increase}. \ac{GW} bursts are un-modelled~\chris{except for the ones you
-mentione before? SNe, glicthes, post-merger? }; therefore there are no
+multi-dimensional parameter space requiring
+significant computational cost. For \ac{GW} bursts that remain un-modelled; there are no
 templates available and so matched-filtering is unsuitable for the detection of
-these signals.  Instead, detection involves distinguishing the signal from
-detector noise~\chris{but that's also what matched-filtering does}. Burst
-searches look for excess power contained in the time-frequency
-domain~\chris{all of them? In any case you have to provide references here to
-the pipelines (cWB, x-pipeline, etc... Siong can help)} and rely on the
+these signals.  Instead, detection algorithms like (cWB, x-pipeline, etc... \jordan{reference}) involve distinguishing the signal from
+detector noise by looking for excess power contained in the time-frequency
+domain and rely on the
 astrophysical burst waveform appearing in multiple detectors at similar times.
@@
 within a certain frequency range and ring-downs which mimic the damped
-oscillations after a \ac{CBC} merger.~\chris{seems strange to list only 3 of
-the 5 that we will be using later on.}
-
+oscillations after a \ac{CBC} merger. A Gaussian blip: a short exponential increase the decrease in amplitude and a Binary black hole in spiral. 
 % cut this text if not going to be used
@@
 future, there is a growing need for fast and efficient \ac{GW} analysis methods
-to match the rising number of detections. While still in its infancy, \ac{ML}
-applications to \ac{GW} analyses have already shown great potential for
-overcoming data bottlenecks~\chris{what does that mean?}. \ac{GW} analysis in
-areas of detection~\cite{Gabbard2017,Gebhard_2019,Krastev_2020}, glitch
-classification~\cite{Bahaadini, George_2018,Razzano_2018} and parameter
-estimation~\cite{gabbard2019bayesian, shen2019deterministic,
-green2020gravitationalwave}~\chris{unfinished sentence, plus I wouldn't
-reference the Shen paper}. Applying these algorithms show similar results to
-matched-filtering techniques and have the benefit of being orders of magnitude
-faster. \michael{We mention aspects related to detection (pattern matching) but
-also metion PE in the same sentence and I think this is a bit
-confusing.}~\chris{yes, the matched-filtering comp[arison is only relevent for
-searches. The biggest speed gain is for the Bayesian PE. I also think that you
-need to reference more of the ML-GW literature here. I've added Mervyn's SNe
-paper, Joe's latest paper, our latest Gaussian ?Mixture model paper, 2 CW
-papers and the recent ML review paper to the bibligrapohy file but there are
-quite a few others. Have a look at the review to steal references. In each case
-try to say 1 sentence about what they do if possible.}
+to match the rising number of detections. While still in its infancy, applying \ac{ML} to \ac{GW} analyses have already shown great potential in
+areas of detection~\cite{Gabbard2017,Gebhard_2019,Krastev_2020}, where these techniques have matched the sensitivity of matched filtering for Advanced LIGO and Advanced Virgo gravitational-wave searches.
+In identifying and classifying detector noise transients or  'glitches"~\cite{Bahaadini, George_2018,Razzano_2018, 2020arXiv200801262G}.
+In Bayesian parameter
+estimation~\cite{gabbard2019bayesian,
+green2020gravitationalwave} where \ac{ML} techniques can recover parameters of a \ac{GW} signal significantly faster than standard methods.
+Long duration signals like continuous \ac{GW} require long observing times and therefore have large amounts of data needing to be processed.
+Current \ac{ML} approaches~\cite{2020PhRvD.102b2005D, 2019PhRvD.100d4009D, 2020arXiv200708207B} are particularly well suited to dealing with this as once trained the searches can be performed quickly.
+\jordan{quicker than than what?}
 
@@
 unmodelled \ac{GW} burst waveforms. Using the generative machine learning
-model: \acp{GAN}, we train on five classes of known~\chris{are they known? In
-what sense?} burst morphologies~\chris{fancy word - what about waveform class?}
-in the time domain. Working with the assumption that \acp{GAN} construct smooth
-$n$-dimensional vector spaces between their input and output, we can then
+model, \acp{GAN}, we train on five classes of waveforms in the time domain. Working on the assumption that \acp{GAN} construct smooth
+ high dimensional vector spaces between their input and output, we can then
 explore the space between the five classes to construct new
-unmodelled~\chris{hybrid?} waveforms. As all the computationally expensive
+hybrid waveforms. As all the computationally expensive
 processes occur during training, the learned model after training is able to
 produce waveforms in fractions of a second and in fact produce waveforms that
-are impossible~\chris{never say never (or impossible)} to produce with current
+are difficult to produce with current
 techniques. These new varieties of waveforms can then be used to diagnose
-detection algorithms and gain new insight into sources of \ac{GW}
-bursts~\chris{yes, they can help diagnose or calibrate or assess the sensitivty
-of detection algorithms but also allow us to better train our algorithms to a
-broader range of possible signals and therefore enhance our detection ability}.
+detection algorithms, gain new insight into sources of \ac{GW}
+bursts and  allow us to better train our algorithms to a
+broader range of possible signals and therefore enhance our detection ability.
 
@@
 
-\begin{figure}
-    \begin{minipage}[b]{0.3\linewidth}
-        \subfloat[]{\label{fig:perceptron}\includegraphics[width=\linewidth,height=0.65\linewidth]{figures/neural_network-figure0.pdf}}
-        \par
-        \vspace{\baselineskip}
-        \subfloat[]{\label{fig:tanh_activation}\includegraphics[width=\linewidth,height=0.65\linewidth]{figures/neural_network-figure1.pdf}}
-    \end{minipage}
-        \begin{minipage}[b]{0.7\linewidth}
-        \subfloat[]{\label{fig:neural_network}\includegraphics[width=\linewidth,height=0.65\linewidth]{figures/neural_network-figure2.pdf}}
-    \end{minipage}
+% inroduce the concept of ML
+%
+
+\begin{figure}[h!]
+\begin{subfigure}[b]{0.30\textwidth}
+   \begin{subfigure}[b]{1\textwidth}
+   	\centering
+	\resizebox{\textwidth}{!}{
+ 	\begin{tikzpicture}		
+		    \node[scale=0.3] 		   (x1) at (0,0.8) {$x_1$}; 
+		    \node[scale=0.3] 		   (x2) at (0,0.5) {$x_2$};  
+		    \node[scale=0.3] 		   (x3) at (0,0.2) {$x_3$};       
+    		    \node [draw, circle,scale=0.18,fill=blue!25]          (c3) at (0.7,0.5) {\Large $\sigma(\sum_i w_i x_i + b)$};
+    \draw[->] (x1)--(c3);
+    \draw[->] (x2)--(c3);
+    \draw[->] (x3)--(c3);
+     \draw[->] (c3)--(1.3,0.5);
+   	\end{tikzpicture}
+	}
+	\caption{}
+	 \label{fig:perceptron}
+ \end{subfigure}
+
+   \begin{subfigure}[b]{1\textwidth}
+  	\centering
+	\resizebox{\textwidth}{!}{
+\begin{tikzpicture}
+\begin{axis}[
+    xmin=-2.5, xmax=2.5,
+    ymin=-1.5, ymax=1.5,
+    axis lines=center,
+    axis on top=true,
+    domain=-2.5:2.5,
+    ylabel=$\sigma$,
+    xlabel=$x$,
+    ]
+
+    \addplot [mark=none,draw=green,ultra thick] {tanh(\x)};
+    \addplot+[mark=none,draw=blue,domain=-2.5:0,ultra thick] {0};
+    \addplot+[mark=none,draw=blue,domain=0:2.5,ultra thick] {x};
+    \addplot+[mark=none,red,dotted,domain=-2:0,ultra thick] {0.2*x};
+    \addplot+[mark=none,red,dotted,domain=0:2.5,ultra thick] {x};
+
+    %% Add the asymptotes
+\end{axis}
+\end{tikzpicture}
+	}
+	\caption{}
+	 \label{fig:activations}
+\end{subfigure}
+\end{subfigure}
+	 \begin{subfigure}[b]{0.70\textwidth}
+\centering
+\resizebox{\textwidth}{!}{
+\def\layersep{1.5cm}
+\begin{tikzpicture}[shorten >=1pt,draw=black, ->,node distance=\layersep]
+
+    \tikzstyle{every pin edge}=[<-,shorten <=1pt]
+    \tikzstyle{neuron}=[circle,draw=black, very thick, fill=blue!25, minimum size=22pt,inner sep=0pt]
+    \tikzstyle{input neuron}=[circle,draw=black,very thick,fill=black!25, minimum size=22pt,inner sep=0pt];
+    \tikzstyle{output neuron}=[neuron];
+    \tikzstyle{hidden neuron}=[circle,draw=black,very thick,fill=blue!25,minimum size=22pt,inner sep=0pt];
+    \tikzstyle{annot} = [text width=4em, text centered]
+
+    % Draw the input layer nodes
+    \foreach \name / \y in {1,...,5}
+    % This is the same as writing \foreach \name / \y in {1/1,2/2,3/3,4/4}
+        \node[input neuron] (I-\name) at (0,-\y) {$x_{\name}$};
+
+    % Draw the hidden layer nodes
+    \foreach \name / \y in {1,...,3}
+        \path[yshift=-1cm]
+            node[hidden neuron] (H-\name) at (\layersep,-\y cm) {};
+
+  \foreach \namee / \y in {1,...,3}
+        \path[yshift=-1 cm]
+            node[hidden neuron] (H1-\namee) at (2*\layersep,-\y cm){};
+
+    % Draw the output layer node
+  \node[output neuron,pin={[pin edge={->}]right:}, right of=H1-2] (O) {};
+    % Connect every node in the input layer with every node in the
+    % hidden layer.
+    \foreach \source in {1,...,5}
+        \foreach \dest in {1,...,3}
+            \path (I-\source) edge (H-\dest);
+
+ \foreach \source in {1,...,3}
+        \foreach \dest in {1,...,3}
+            \path (H-\source) edge (H1-\dest);
+
+    % Connect every node in the hidden layer with the output layer
+    \foreach \source in {1,...,3}
+        \path (H1-\source) edge (O);
+
+    % Annotate the layers
+    %\node[annot,above of=H-1, node distance=1cm] (hl) {Hidden layers};
+   % \node[annot,left of=I-4] at (0) {Input layer};
+    %\node[annot,right of=hl] {Output layer};
+
+    \draw[decoration={brace,mirror,raise=15pt},decorate,-]
+  (I-1.north) -- node[left=0.8cm,scale=0.7] {Input layer} (I-5.south);
+
+    \draw[decoration={brace,raise=15pt},decorate,-]
+  (H-1.west) --  node[above=0.8cm,scale=0.7]{Hidden layers}  (H1-1.east);
+
+    \draw[decoration={brace,raise=15pt},decorate,-]
+  (O.west) --  node[above=0.8cm,scale=0.7]{Output layers}  (O.east);
+
+\end{tikzpicture}
+}
+ \caption{}
+ \label{fig:network}
+ \end{subfigure}
+
 \caption{Neural Networks (a) A single neuron taking a vector of inputs and
 returning a single output based on the weights, bias and activation function
-of the network. (b) The hyperbolic tangent used as an activation
-function.~\chris{is this the actual activation that you use in the GAN?
-otherwise why focus on it alone, you could plot a handful on the same plot} (c)
-A fully connected~\chris{you haven't mentioned what a fully connected network
-actually is in the text} neural network containing two hidden layers that performs a
-mapping of an input vector to a single output. \michael{Equation in the
-neuron looks very small}~\chris{I agree, but the equation in (b) is even
-smaller. I would also recommed that you make the style of the FC network hidden
-and output layer neurons the same as the single perceptron in terms of colours.
-You could put $x_i$s in the input layer.}}
+of the network.
+(b) A selection of activation functions used in this study.
+The hyperbolic tangent (Green), Rectified linear unit \cite{relu} (Blue) and Leaky rectified linear unit \cite{Maas2013RectifierNI} (Red).
+(c)
+A an example of a neural network containing two hidden layers that performs a
+mapping of an input vector to a single output.}
 \end{figure}
 
-% inroduce the concept of ML
-%
-Since the birth of programmable computers, people have wondered if machines can
-develop true intelligence beyond formal mathematical procedures. Today, \ac{ML}
-aims to learn apparent relationships held within the given data or `training
+\ac{ML} aims to learn apparent relationships held within given data or `training
 data' in order to make accurate predictions without the need for additional
-programming. A common approach in \ac{ML} relies on the computer learning on
-past experience to make decisions on future events. \michael{Not sure about the
-use of computer here, maybe \textit{relies on a model}?} The hierarchical
-nature of this approach means that the machine can build complicated concepts
-from simpler ones~\chris{what hierarchical nature? You haven't mentioned
-anything about that.}. This branch of \ac{AI} is called deep
-learning~\chris{OK, but as long as you explain the hierarchy thing and how it
-implies complicated concepts from simpler ones.}.
+programming. A common approach in \ac{ML} relies on the model learning on
+past experience to make decisions on future events. Deep learning is a branch of \ac{ML} that takes inspiration from biological processes in the brain.
 
@@
 %
-Neural networks are the quintessential~\chris{really? quintessential?} \ac{ML}
-algorithm that aims to approximate a function. They are built from many single
-processing units called neurons. The simpliest Neural Network is the perceptron
+\begin{comment}
+Neural networks are the quintessential~\chris{really? quintessential?} \jordan{It's a perfectly cromulent word https://www.imdb.com/title/tt0701155/} \ac{ML}
+algorithm that aims to approximate a function. 
+\end{comment}
+
+Artificial neural networks are universal function approximators that are built from many single
+processing units called neurons. The simplest neural network is the perceptron
 layer~\cref{fig:perceptron} which holds a single neuron that takes several real
-inputs $x_{1},\ldots, x_{i}$~\chris{and outputs what? also $i$ is the index and not the "final" index}
-and maps them to an output according to the linear equation 
+inputs $x_{i},\ldots, x_{n}$
+and maps them to an \jordan{probability?} output according to the linear function, 
 %
 \begin{align}
-\sigma(\sum_i w_i x_i + b),
+f(x) = \sigma(\sum_i w_i x_i + b),
 \label{eqn:neuron}
@@
 %
-\chris{it's not an equation if it's not equal to something. Please make it
-eaqual something.} where $w$ and $b$ are the weights and bias and $\sigma$
+where $w$ and $b$ are the weights and bias and $\sigma$
 denotes the activation function. The weights are numbers which can be thought
-as the strength between connections~\chris{what connestions? between what
-objects?}. The output of a neuron is called its activation and different
-choices of activation function allow the user~\chris{are we users or developers
-or what?} to simulate various models. A common example of an activation
-function is the hyperbolic tangent~\cref{fig:tanh_activation} that is used when
-the outputs of the network must be both positive and negative~\chris{how can an
-output be both positive and negative. The language is ambiguous and confusing}
-and re-scaled to $[-1,1]$~\chris{at this stage in the explanation the reader
-has no idea what an output would look like or why it would be rescaled}. It is
-often useful to introduce a bias, $b$, such that the neuron remains inactive
-above zero but is active when the sum reaches a defined threshold. This bias is
-added before the activation function and it tells us how high the weighted sum
-needs to be before the neuron becomes active.~\chris{well kind of, but also not
-really. I would advise you to rewrite this (if we keep it) in a minimalist
-style just explaining what each item is and not trying to describe what it
-does.}
-
-% the cost or loss function
-%
-The output of a single neuron is defined by~\cref{eqn:neuron} and gives a
-prediction $\hat{y}$ that can be compared to the real value $y$~\chris{what the
-hell is $y$, it's not been mentioned before} through a loss (also known as a
-cost) function. If the loss is non-zero~\chris{no, it doesn't matter whether
-the number is above or below or equal to zero, the machine will try to minimise
-the number (if negative, it will try to make it more negative)}, the network
-must work to minimise this function by updating the weights in the negative
-direction of the loss gradient in a process referred to as gradient
-descent~\chris{give reference and also make the distinction between this and
-the actual method used to do it, back progagation}. This loss function plays a
-critical role in how neural networks learn~\chris{OK, but are you going to
-expand on that or just leave it there? As far as I can tell from the text it's
-the *only* way network's learn so that's pretty critical and already evident}.
+of as the strength between connected neurons.
+The output of a neuron is defined by its activation function which controls how the neuron 'fires" depending on its input.
+Some examples of commonly used activation functions are shown in~\cref{fig:activations}.
+It is often useful to introduce a bias, $b$, such that the neuron remains inactive
+above zero but is active when the sum reaches a defined threshold.
 
@@
 A neural network contains many single neurons connected in a layered structure
-as shown in~\cref{fig:neural_network}. The activations of the first layer (or
+as shown in~\cref{fig:network}. The activation's of the first layer (or
 input layer) act as the inputs to the second layer and so on until the output
 layer. Multi-layered neural networks have intermediate layers between the input
-and output stages dubbed the hidden layers as the computations performed are
-not accessible to the user~\chris{well that's not really true. We can access
-everything if we want but it depends on what you define as a user. Best to
-simply state what they're clalled and no need to give a reason.}. The network
-can be thought of as a function F: $\mathbb{R}^N\rightarrow
-\mathbb{R}^M$~\chris{does F not have to be in math-mode too? Is is a
-mathematical symbol?} reliant on how activations from one layer bring
-activations in the next~\chris{yes, kind of, but also reliant on the trained
-weights and biases too, so actually reliant on everything}. The system is
-analogous to biology, where, some groups of neurons in animal brains cause
-certain others to fire~\chris{best to stay away from analogies like these where
-the practical specifics can be picked apart}.
+and output stages dubbed the hidden layers.
+
+% the cost or loss function
+%
+The output of a single neuron is gives a
+prediction that can be compared to the real value through a loss (also known as a
+cost) function. The network must work to minimise this function by updating the weights in the negative
+direction of the loss gradient in a process referred to as gradient
+descent \cite{ruder2016overview}.
+The training process for a single layered network is easy to compute as the weights relate directly to the gradient of the loss function the network is trying to minimise.
+For deeper architectures, the loss is a complicated function of all the weights in all the layers.
+The backpropagation \cite{Nielsen1992} algorithm acts over the many paths from node to output.
+It does so in two phases:
+
+\begin{itemize}
+\item Forward phase: For one instance of training, the inputs are fed forward through the network using the current weights and the final output is compared to the training labels.
+The derivative of the loss function is then computed.
+\item Backward phase: This phase learns how the gradient of the loss function changes when the weights are varied.
+Starting at the output node, the algorithm goes backwards through the network (hence the name).
+The weights that give the steepest descent to the loss function are saved for the next training instance.
+\end{itemize}
+This process of updating the weights is repeated until the loss function reaches convergence or a global minimum.
+The training data is cycled through in epochs.
+An epoch is defined when the entire data set is fed through the network.
+It is impractical to feed the entire data set into the network at once, so the training is split up into smaller more manageable batches.
+Finally, the number of batches needed to compete one epoch is referred to as the iterations.
 
@@
 \acp{CNN} are designed to work with grid-like input structures that exhibit
-strong local spatial dependencies. An example would be a two-dimensional image
-as each coloured pixel has similar intensities to their near
-neighbours~\chris{it's not about that really, it's like you said, it's about
-spatial relationships}. The value contained in each pixel can be thought of as
-adding an additional dimension or channel to the image~\chris{no, the dimension
-and channel are specifically defined. A 2D image has 2 dimensions. An RGB image
-has 3 numbers per pixel and these are typcally stored as channels. Channels are
-dealt with differently to dimensions}. Although most work with \acp{CNN}
+strong local spatial dependencies. Although most work with \acp{CNN}
 involve image-based data, they can be applied to other spatially adjacent data
@@
 convolution operation, a mathematical operation that expresses the amount
-overlap between functions. The convolution is applied by shifting one grid-like
-structure over the other, drawing out spatially important features between the
-two~\chris{yes, but what is being dragged over what? Time to define the
-convolutional neuron? Maybe add an equation?}. A strided convolution reduces
-the dimensionality of the input while retaining spatial features \michael{How?
-This is core part of the architecture of the GAN but is quite vague, I don't
-think it's obvious that stride imples moving the filter further. Maybe
-something like: \textit{the distance by which the grid is shifted is known as
+overlap between functions.
+Much like traditional neural networks the convolution operation in this context involves multiplying the input by an array of weights, called a filter or a kernel qhich is typically smaller in size than the input.
+The convolution is applied by shifting the kernel over the input, drawing out spatially important features between the
+two. The distance by which the grid is shifted is known as
 the stride and increasing it reduces the dimensionality of the
-output}}~\chris{why are we talking about strides at this point? Are they
-important for the GAN? You haven't mentioned kernel sizes or dropout. are these
-equally important?}. This can result in a loss of information along the
-borders~\chris{the borders of what?}. To combat this, the input is padded with
-zeros at the edges which does not interfere with the convolutional operation.
-The output of the convolutional layer is then passed to an activation function.
-
-~\chris{I'm getting the sense that these 2 sections of ANNs and CNNs aren't
-really helpful in their current state. They should either be removed OR tidied
-up. I don't think they need to be expanded upon but various statements can be
-removed and other important things can be added. Imagine reading this with no
-knowledge of ML. Do you get informed by this or confused?}
+output. The output of the convolutional layer is then passed to an activation function.
 
@@
 A subset of deep learning that has seen fruitful development in recent years
-are \acp{GAN}~\cite{Goodfellow2014}. These unsupervised~\chris{they have
-training data don't they? Is that unsupervised?} algorithms learn patterns in a
+are \acp{GAN}~\cite{Goodfellow2014}. These unsupervised algorithms learn patterns in a
 given training data set using an adversarial process. The generations from
-\acp{GAN} are state-of-the-art~\chris{a phrase that will not stand the test of
-time} in fields such as high quality image
+\acp{GAN} are currently state-of-the-art in fields such as high quality image
 fidelity~\cite{brock2018large,karras2019analyzing}, text-to-image
@@
 generations~\cite{esteban2017realvalued}~\chris{do we still not have any other
-GW GAN applications to reference or are we hoping to still be the first?}.
+GW GAN applications to reference or are we hoping to still be the first?}. \jordan{None that i can find?}
 
@@
 network that is set up to distinguish between real and fake data and a
-generator network that produces synthetic (fake) versions of the real data.
-\michael{Is it clear to the reader that the \textit{fake} data is the same as
-the synthetic data?} The generator performs a mapping from an input noise
-vector $\mathbf{z}$, that is usually sampled from a $n$-dimensional~\chris{be
-careful with statments about $n$-dimensions since $n$ is a variable and could
-mean the number of latent dimensions or the number of class dimensions or data
-dimensions, etc...} Gaussian space known as the latent space, to its
-representation of the data, and the discriminator maps its input $\mathbf{x}$ to
-a probability that the input came from either the training (real) data or
+generator network that produces fake versions of the real data. The generator model performs a mapping from a fixed length vector $\mathbf{z}$ to its
+representation of the data.
+The input vector is drawn randomly from a Gaussian distribution which is referred to as a latent space comprised of latent variables.
+The latent space is a compressed representation of a data distribution which the generator applies meaning to during training.
+Sampling points from this space allows the generator to produce a variety of different generations, with different points corresponding to different features in the generations.
+The discriminator maps its input $\mathbf{x}$ to a probability that the input came from either the training (real) data or
 generator (fake).
 
+\begin{comment}
+Chris' definition of latent space if needed: It maps the intrinsic
+variation of the training space onto the Gaussian latent space distribution.
+\end{comment}
+
 % training a GAN
 %
-During training, the discriminator is given a batch~\chris{you have not
-introduced batches yet. Best to do that in the ANN section} of samples that
-contains one half real data and one half fake data which it then makes
-predictions on.  The loss for the discriminator is calculated by comparing its
-predictions to the labelled data through the binary cross-entropy function.
-\jordan{note to myself: This is important since eqn 2 is derived from it (thats
-where the logs come from)}~\chris{either give a reference to binary cross
-entropy or define it here mathematically}. The training process of a \ac{GAN}
-alternatively updates the weights of the discriminator and generator based on
-information on its competitors loss function~\chris{you haven't fully explained
-how the loss is computed in the 2 phases of each training pass. I recommend
-that you add that here other wise discussion of generator loss and discrimator
-loss makes no sense.}. This loss of the discriminator is used to update the
-weights of the generator to produce more realistic samples of the input
-distribution, the loss of the generator encourages the discriminator to update
-its classification abilities. \acp{GAN} seek to find an equilibrium between the
-generator and discriminator in the form of a two-player game that can be
-summarised by 
-%
-\begin{align}
-  \mathop{\text{min}}_{G}  \mathop{\text{max}}_{D} V(D,G) &= \mathbb{E}_{\mathbf{x} \sim p_{\text{r}}(\mathbf{x})} [\text{log} D(\mathbf{x})] + \mathbb{E}_{\mathbf{z} \sim p_{\text{z}}(\mathbf{z})} [\text{log}(1-D(G(\mathbf{z})))],
-\label{equation:GANloss}
-\end{align}
-%
-% remove these comments 
-%
-\begin{comment}
-Both networks compete in
-a minimax game~\chris{what is a minimax game? references?} which the generator
-is trying to minimise and the discriminator is trying to
-maximise:~\chris{nicely written, however, it needs an extra 25\% explanation
-for people not familar with ML or GANs in particular. Try to spell things out
-more. Also refer to Fig 1 somewhere in this section.}
-\end{comment}
-%
-where $V$ is an objective function that is to be optimised. Objective functions
-are a general term for either a loss function (to be minimized) or a negative
-loss function (to be maximised). We use $D$ to define the discriminator
-function~\chris{output interpreted as a probability?} , $G$ for the generator
-function and ${\mathbf{x} \sim p_{\text{r}}(\mathbf{x})}$, ${\mathbf{z} \sim
-p_{\text{z}}(\mathbf{z})}$ are samples taken from the training data and
-generated data respectfully~\chris{no, $z$ can't be from the data since it's
-not called $x$. It is from the latent space distribution.}. In practice this
-approach was found to be unstable \michael{Cite?}~\chris{unstable for us or
-unstable in general, also add reference.}. Early on in training the generators
-weights are initialised randomly meaning that the early generations are noisy
-and uninformative. This means that the discriminator can easily learn to spot
-the fake generations and so the discriminator wins and the generator cannot
-continue to improve. To overcome this the framing~\chris{what is framing in
-this context?} of the generator is often changed. Rather than minimizing
-$\text{log}(1-D(G(\mathbf{z})))$ the objective now is to maximise
-$\text{log}(D(G(\mathbf{z})))$, that is, to maximise the probability of the
-generations being predicted as real. The idea being that we always want the
-losing side to be able to leverage \michael{information?} from its
-competitor.~\chris{OK, does this all mean that the previous equation is wrong?
-If so, why quote it. Just use the actual correct equation and explain why it's
-correct rather than explaining why something is wrong. I would also try to link
-up this equation with how we actually train i.e., we compute the first term by
-drawing samples from the training set $x$ and getting the average log-prob of
-the discriminator (not quite true since we actually input a mix of real $x$ and
-fake $G(z)\rightarrow x'$). Then we take a set of fake $x'$ made using $G(z)$
-with $z$ drawn from the latent space, and get the loss (but we switch the
-labels hence the $1-D(G(z))$. See what I mean? You shouls also refer to Fig 2
-here.} 
-%
-
-% describing the problems with GANs 
-%
-In theory, the adversarial process will eventually lead to the local Nash
-equilibrium~\cite{Nash1950} whereby both neural networks are trained
-optimally~\chris{vague and not informative statement. What does optimal mean
-here?}. In practice, however, \acp{GAN} are notoriously difficult to train with
-difficulties that include: Non-convergence, where the model parameters
-oscillate and the loss never converges, mode collapse where the generator
-produces a limited diversity of samples, and diminishing gradients when
-applying gradient descent to a loss function that is discontinuous.~\chris{OK,
-difficult to train. I understand. Why are you telling the reader this? Will we
-be referring back to these issues later?}
-
-~\chris{there needs to be some more discusiion of what the latent space
-and $z$ variables represent in the GAN in general. It maps the intrinsic
-variation of the training space onto the Gaussian latent space distribution.}
-
+During training, the discriminator and generator are updated in parallel using batches of data.
+Random latent vectors are given to the generator to produce a batch of fake samples and an equal batch of real samples is taken from the training data.
+The discriminator makes predictions on the real and fake samples and the model is updated through minimising the binary cross-entropy function \cite{Goodfellow-et-al-2016}
+
+\begin{equation}
+    L = -y \log(p) + (1 - y) \log(1-p),
+    \label{eqn:gloss}
+\end{equation}
+where p is the networks output and y is the true output. 
+To update the generator, a new batch of fake samples is generated by drawing new points in the latent space and passing this to the discriminator.
+The generators loss is computed by minimizing the discriminators loss averaged over the batch but with switched labels
+
+\begin{equation}
+    L_{G} = n^{-1} \sum\limits_{i=1}^n \log(1-D(G(\mathbf{z}_{i}))),
+\end{equation}
+where D is the discriminator and G is the generator.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 information into the generator and discriminator such as a class label or
-attribute label, $c$. The objective function~\cref{equation:GANloss}~\chris{I
-think it owuld be be best if you just stick to loss function rather than
-switching between loss and objective} is then
-%
-\begin{align}
-  \mathop{\text{min}}_{G}  \mathop{\text{max}}_{D} V(D,G) &= \mathbb{E}_{\mathbf{x,c} \sim p_{\text{r}}(\mathbf{x,c})} [\text{log} D(\mathbf{x,c})] + \mathbb{E}_{\mathbf{z} \sim p_{\text{z}}(\mathbf{z}),\mathbf{c} \sim p_{\text{r}}(\mathbf{c})} [\text{log}(1-D(G(\mathbf{z,c})))].
-\label{equation:cGANloss}
-\end{align}
-
-This simple addition has shown to work well in practice, for instance in
-image-to-image translation~\cite{isola2016imagetoimage}. We will be using a
-conditional GAN for this study.~\chris{OK, but you have not defined the new
-changes to the loss function in the text. Please indicate that the training
-data and labels are being drawn from a joint distribution $p_r(x,c)$ and when
-making fake data you are drawing from $p_r(c)$ independent of =$p(z)$. However,
-what does the $r$ stand for and why is it important, and what defines $p_r(c)$?}
-
-~\chris{Finally, you need to refer to and discuss Figure 2. It is currently
-neither referenced or discussed.}
-
-% get rid of these comments if they are no longer useful
-%
-\begin{comment}adds structure to the latent space by providing the
-generator with a class or attribute label. The generator learns to segment the
-latent space by clustering distributions which have similar properties, making
-a point in latent space conditional on a class~\chris{are we sure about this?
-all classes share the same latent space and I don't think that the space gets
-segmented into areas corresponding to different classes - I do think that it
-gets broken down into spaces with different intrinsic physical properties e.g.,
-high frequency, long duration, etc...}.
-\end{comment}
-%
-\begin{comment}
-This idea was extended further with
-\acp{ACGAN}~\cite{odena2016conditional} that require the discriminator to
-output a probability of data belonging to each class. A pictorial
-representation on the differences between these approaches is shown in
-Fig.~\ref{fig:gan_comparison} \jordan{self note: Probably move away from ACGAN part, standalone aux classifiers can be trained later if that's what you want}. 
-\end{comment}
-
-\begin{figure}
+attribute label, $c$.
+This simple addition has shown to work well in practice, for instance in image-to-image translation~\cite{isola2016imagetoimage}.
+We defined the classes in one-hot encoding framework, that is, each class resides at the corner points of a 5 dimensional cube.
+For example e.g.
+$c=[0,1,0,0,0]$ represents the ring-down signal class.
+The training data and labels are drawn from a joint distribution $p_{real}(x,c)$, whereas when generating fake data we sample from $p(c)$ and $p(z)$ independently.
+While the generator and disriinmator now have two inputs $D(\mathbf{z},\mathbf{c})$ and $G(\mathbf{z},\mathbf{c})$ the networks are still trained via Eq.
+\eqref{eqn:gloss} as the discriminator only needs to output the realness/fakeness.
+Fig. \ref{fig:gan_comparison} shows the differences in inputs and outputs of a GAN compared with a \ac{CGAN}. We will be using a conditional GAN for this study.
+
+\begin{figure}[h!]
+    \begin{subfigure}{.5\textwidth}
      \centering
-        \input{figures/GAN_diagram_vertical}%     without .tex extension
-        \input{figures/ACGAN_diagram_vertical}%     without .tex extension
+        \input{figures/GAN_diagram_vertical}
+        \caption{GAN}
+    \end{subfigure}
+    \begin{subfigure}{.5\textwidth}
+     \centering
+        \input{figures/ACGAN_diagram_vertical}
+        \caption{CGAN}
+    \end{subfigure}
     \caption{Comparison of the original GAN method and the
@@
 its class that is also fed to the generator which then learns to generate
-waveforms based on the input label.~\chris{OK, a few things. Try to separate
-these a bit and maybe make them subplots with sublabels indicating GAN and CGAN
-distinction. Replace noise with latent (or otherwise). Noise implies GW data
-noise which it is not. Overall it's a bit basic and doesn't indicate either the
+waveforms based on the input label.~\chris{Overall it's a bit basic and doesn't indicate either the
 2 competing training steps or any aspect of the loss or specify that $x$ and

### 2020-09-11 Paper_draft/main.tex
New edits and complete comments to section 4

@@
 and output stages dubbed the hidden layers.
-
 % the cost or loss function
@@
 An epoch is defined when the entire data set is fed through the network.
-It is impractical to feed the entire data set into the network at once, so the training is split up into smaller more manageable batches.
+As it is impractical to feed the entire data set into the network at once, so the training is split up into smaller more manageable batches.
 Finally, the number of batches needed to compete one epoch is referred to as the iterations.
@@
 the stride and increasing it reduces the dimensionality of the
-output. The output of the convolutional layer is then passed to an activation function.
+output, this process is know as down sampling.
+Alternatively, up sampling the inputs can be achieved using a transposed convolution \cite{dumoulin2016guide}.
+The output of the convolutional layer is then passed to an activation function.
+For deep neural networks, techniques like BatchNormalisation \cite{ioffe2015batch} which standardise the inputs to a layer and SpatialDropout \cite{tompson2014efficient} which sever connections between neurons can both help to stabilise learning.
 
@@
 \begin{equation}
-    L = -y \log(p) + (1 - y) \log(1-p),
-    \label{eqn:gloss}
+    L = -y \log(\hat{y}) + (1 - y) \log(1-\hat{y}),
+    \label{eqn:crossentropy}
 \end{equation}
-where p is the networks output and y is the true output. 
-To update the generator, a new batch of fake samples is generated by drawing new points in the latent space and passing this to the discriminator.
-The generators loss is computed by minimizing the discriminators loss averaged over the batch but with switched labels
+where $\hat{y}$ is the network prediction and $y$ is the true output.
+While training the discriminator, D, on real data, we set $y = 1$ and $\hat{y} = D(x)$ which from eqn.
+\ref{eqn:crossentropy} gives $L(D(x),1) = \log(D(x))$.
+While training on fake data produced by the generator, G, $y = 0$ and $\hat{y} = D(G(z))$ and so, $L(D(G(z)),0) = \log(1-(D(G(z))))$.
+\jordan{whole derivation unnecessary?} Since the objective of the discriminator is to correctly classify fake and real data these equations should be maximised, while the goal of the generator should be to minimize these equations.
+This gives the \ac{GAN} loss as
 
 \begin{equation}
-    L_{G} = n^{-1} \sum\limits_{i=1}^n \log(1-D(G(\mathbf{z}_{i}))),
+   \mathop{\text{min}}_{G}  \mathop{\text{max}}_{D} V(D,G) = \mathbb{E}_{\mathbf{x} \sim p_{\text{\text{data}}}(\mathbf{x})} [\text{log} D(\mathbf{x})] + \mathbb{E}_{\mathbf{z} \sim p_{\text{z}}(\mathbf{z})} [\text{log}(1-D(G(\mathbf{z})))],
+ \label{equation:GANloss}
  \end{equation}
-where D is the discriminator and G is the generator.
+where $p_{\text{\text{data}}}(\mathbf{x})$ is the distribution of real data and $p_{\text{z}}(\mathbf{z})$ is the distribution of the latent space.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 $c=[0,1,0,0,0]$ represents the ring-down signal class.
-The training data and labels are drawn from a joint distribution $p_{real}(x,c)$, whereas when generating fake data we sample from $p(c)$ and $p(z)$ independently.
-While the generator and disriinmator now have two inputs $D(\mathbf{z},\mathbf{c})$ and $G(\mathbf{z},\mathbf{c})$ the networks are still trained via Eq.
-\eqref{eqn:gloss} as the discriminator only needs to output the realness/fakeness.
+The training data and labels are drawn from a joint distribution $p_{data}(\mathbf{x},\mathbf{c})$, whereas when generating fake data we sample from $\mathbf{c}$ and $p_{z}(\mathbf{z})$ independently.
+\href{equation:GANloss} is modified to include the class labels
+~
+\begin{equation}
+   \mathop{\text{min}}_{G}  \mathop{\text{max}}_{D} V(D,G) = \mathbb{E}_{\mathbf{x} \sim p_{\text{\text{data}}}(\mathbf{x})} [\text{log} D(\mathbf{x|c})] + \mathbb{E}_{\mathbf{z} \sim p_{\text{z}}(\mathbf{z})} [\text{log}(1-D(G(\mathbf{z|c})))].
+ \label{equation:CGANloss}
+ \end{equation}
 Fig. \ref{fig:gan_comparison} shows the differences in inputs and outputs of a GAN compared with a \ac{CGAN}. We will be using a conditional GAN for this study.
@@
 its class that is also fed to the generator which then learns to generate
-waveforms based on the input label.~\chris{Overall it's a bit basic and doesn't indicate either the
+waveforms based on the input label.}
+\begin{comment}
+~\chris{Overall it's a bit basic and doesn't indicate either the
 2 competing training steps or any aspect of the loss or specify that $x$ and
@@
 It implies that the same $c$ value is given to each real and fake $x$ data when
-in fact each $x$ sample has it's own randomly drawn $c$ value.}} \label{fig:gan_comparison}
+in fact each $x$ sample has it's own randomly drawn $c$ value.}
+\end{comment}
+\label{fig:gan_comparison}
 \end{figure}
-
-~\chris{After describing the latent space meaning in the GAN section you need
-to bring that together with a discussion of the entirely seperate class space
-and how it is defined with reference to the on-hot encoded corners of a 5-D
-vector space. Here is where you can inroduce the concept of the space and
-mention the issue of probing the regions between the corners}
 
@@
 %
-\ac{GW} burst signals remain an unmodelled phenomenon~\chris{as in the
-introduction I think you need to make the distinction between unmodelled and
-modelled burst analyses}, as such, current detection algorithms exploit the
-fact that astrophysical signals will appear within data from multiple detectors
-in coincidence and share the same waveform morphology.~\chris{I have added to
-this first sentence but it still doesn't naturally lead intpo the next one} We
-propose a signal generation scheme using a \ac{CGAN} trained on burst-like
-waveforms. We call this \texttt{BurstGAN}~\chris{give reference to code repo
-here} and is a \ac{CGAN} trained on five signal classes each spanning a range
+We propose a signal generation scheme using a \ac{CGAN} trained on burst-like
+waveforms. We call this \texttt{BurstGAN} \cite{jordan_git} and is a \ac{CGAN} trained on five signal classes each spanning a range
 of prior signal parameters. The signal classes are:
@@
 \tau^2 \right] \sin (2 \pi f_0 (t-t_0))$, a sinusoidal wave with a Gaussian
-envelope characterised by a central frequency, $f_0$.~\chris{what about
-amplitude, time of arrival and initial phase? For all the other classes too.}
+envelope characterised by a central frequency, $f_0$, amplitude, $A$, time of arrival, $t_{0}$. 
 %
 \item {\bf Ring-down}: $h_{\text{rd}}(t) = A \exp \left[-{(t-t_0)} / {\tau}
-\right] \sin(2 \pi f_0 (t-t_0))$, with frequency $f_0$ and duration $\tau$
+\right] \sin(2 \pi f_0 (t-t_0))$, with frequency $f_0$ and duration $\tau$, amplitude, $A$, time of arrival, $t_{0}$. 
 %
@@
 (t-t_{0})^2 / \tau^2 \right]$ where $g_j$ are drawn from a zero mean unit
-variance Gaussian distribution and ahave a bounded frequency bandwidth $\Delta
-f$ and duration $\tau$~\chris{no, they have a Gaussian envelope with a duration
-parameter $tau$, we don't explicitly define the bandwidth}.
+variance Gaussian distribution with a Gaussian envelope of duration $tau$.
 %
@@
 $m_1>m_2$. The mass distribution is approximated by a power law with
-index of 1.6~\cite{Abbott_2019}. The signals are generated using random right
-ascensions and declinations uniform over the sky and the inclinations are drawn
-from the cosine of a uniform distribution in the range [-1,1].~\chris{OK, we
-have an issue here. First the prior parameters and ranges are being defined
-here rather than in the table with the other classes. Second, you are
-randomising the sky in order to get random antenna patterns which only act to
-change the relative amplitudes in multiple detectors - whcih we don't use any
-more. So I would say that you shoudl only use the plus polarisation since it is
-the same as the cross but pi/2 out of phase.}  
+index of 1.6~\cite{Abbott_2019}. The inclinations are drawn
+such that the cosine of the angles lies uniformly in the range [-1,1] and we only use the plus polarisation.
 %
@@
 The location of the peak amplitude of the waveforms (corresponding to the
-mid-points of all but the ring-down and \ac{BBH} classes) are randomly drawn to
+mid-points of all but the ring-down and \ac{BBH} classes) are randomly drawn from a uniform distribution to
 be within [0.4, 0.6] sec from the start of the 1 sec time interval and all
 training waveforms are sampled at 1024 Hz.  The parameter prior ranges are
-defined in~\cref{Tab:training_parms}.~\chris{Yes, those are the ranges but what
-are the distributions?}
+defined in~\cref{Tab:training_parms}. All training data is rescaled such that their amplitudes peak at 1.
 
@@
 %
-Extensions to the original \ac{GAN} method such as the
-\ac{DCGAN}~\cite{Radford2015} have been widely praised for enabling a stable
-\ac{GAN} architecture. Most GANs now replace fully connected layers, where each
-neuron is connect to all the neurons in the previous and next layer, with
-convolutional layers. \acp{CNN}~\michael{capitalisation, not sure how it works
-with the accronyms package}~\chris{I will fix this} are designed to work with
-grid-like structures with close local dependencies like image and text based
-data, however, there are examples of audio synthesis
-work~\cite{DBLP:journals/corr/abs-1809-11096}.~\chris{this text sounds very
-similar to the CNN text from earlier. Do you need this here? Can you simply say
-that we are using a DCGAN architecture or say that our networks use
-convolutional layers and then move on?}
-
-% specifically define our architecture
-%
-We adopt the suggestions
-of~\cite{Radford2015,DBLP:journals/corr/abs-1809-11096}, lengthening
-one-dimensional convolution kernels on both the generator and
-discriminator~\chris{what does this statment actually mean and why are you
-opening the paragrpah with it?}.  The Generator model is fully convolutional,
-upsampled using strided transposed~\chris{you mentioned strides before but not
-transposing. Can you explain that aspect seomwhere earlier on.} convolutions
-with batch normalisation~\chris{same here, can you mention it earlier} in the
-first layer and ReLU~\chris{you can easily mention ReLU and other activations
-earlier} activations throughout with the exception of the Tanh activation for
-the output layer~\chris{why do you need this for the output? State that it is
-to guarantee the output function is bound between [-1,1]}. Each transposed
-convolutional layer uses a kernel size of $18\times 1$~\chris{by saying 18x1
-you are saying that you are using a 2D kernel with width 1 but why not just say
-you use a 1D kernel of size 18?} and stride of 2. The discriminator network
-mirrors that of the generator without batch normalization~\chris{why?}, using
+For this work we use a \ac{DCGAN}~\cite{Radford2015} architecture. The generator model is fully convolutional,
+upsampled using strided transposed convolutions
+with batch normalisation in the
+first layer and ReLU activations throughout with the exception of the Tanh activation for
+the output layer. The use of Tanh guarantees the output function is bound between [-1,1]. Each transposed
+convolutional layer uses a kernel size of 18 and stride of 2. The discriminator network
+mirrors that of the generator without batch normalization, using
 LeakyReLU activations, SpatialDropout, and a 2-stride convolution for
-downsampling~\chris{any reason for these choices?}. The discriminator output is
-a single node with Sigmoid activation that can be interpreted as a probability
-of the the signal being real. This model is trained with binary cross
-entropy~\chris{how exactly if the output is 1 number rather than 2 (binary)?}.
-The full architecture description can be seen in~\cref{Tab:hyperparameters}.
-~\jordan{still too technical im not sure if we need to go into more detail on
-each thing mentioned.} \michael{This para doesn't seem to technical to
-me}~\chris{same here, not too technical but lacking detail and motivation for
-choices.}
-%~\chris{OK, very technically tight but too computer sciencey. Try to make it
-%human readbale for a physicist and refer to the table of parameters in the
-%appendix.}
+downsampling. The discriminator output is a single node with Sigmoid activation that can be interpreted as a probability of the the signal being real and both models are trained with binary cross
+entropy. The full architecture description can be seen in~\cref{Tab:hyperparameters}.
 
@@
 that the \ac{GAN} performed better with both networks having the same number of
-layers and neurons which should~\chris{should? well does it?} encourage even
+layers and neurons which encourages even
 competition between the generator and discriminator.  After tuning the multiple
 hyperparameters (see \cref{Tab:hyperparameters}), the \ac{GAN} was trained on
-$10^5$ signals which contained an even mixture~\chris{be a bit more specific
-about what an even mixture is - technically they are drawn from a categorical
-distribution with equal propabilities for each class} of
-sine-Gaussian~\chris{Gauss was a person so we have to capitalise his stuff},
-ring-down, white noise bursts, Gaussian pulse and \acp{BBH} for 1000 epochs and
-takes $\Or$(2) days to train~\chris{on what? be specific}. A larger batch size
-saw a small increase in performance~\chris{what is performance in this case} at
-the cost of training speed and we decided that 128~\chris{128 what? Also, why
-pick on batch size as the thing to comment on here? What about learning rate,
-kernel size, etc...} was a fair compromise.
-
-\begin{comment}
-include Plot_NN to show generator architecture
-\end{comment}
-
-~\chris{Please add a loss plot and use a paragrpah to describe what is going
-on.}
+$10^5$ signals  drawn from a categorical
+distribution with equal propabilities for each class of
+sine-Gaussian,
+ring-down, white noise bursts, Gaussian pulse and \acp{BBH}. \jordan{add how many epochs trained for, on what hardware and how long}
+
+As \acp{GAN} are trained by updating one model at the expense of the other, they can be hard to train.
+The goal of GAN training is to find an equilibrium between the two models, if this cannot be found then it is said that the \ac{GAN} has failed to converge.
+One way to diagnose \acp{GAN} during the development process is to keep track of the loss over time.
+Loss plots, for example, as seen in fig.
+\ref{fig:lossplot} can help to identify common failure modes or to check if the \ac{GAN} has indeed converged.
+There is currently no notion of early stopping in \acp{GAN}, instead, training is halted after convergence and by visually inspecting the generations.
+
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width=1\textwidth]{Paper_draft/figures/Screenshot 2020-09-11 at 16.52.47.png}
+    \caption{Line plots of the discriminator (blue) and generator (orange) loss v iterations.
+Early in training the losses oscillates as both models attempt to find their equilibrium, after which, both losses vary around 0.7.}
+    \label{fig:lossplot}
+\end{figure}
 

### 2020-09-14 Paper_draft/main.tex
edits to plots

@@
 \centering
-\caption{Burst training parameters~\chris{Add a bit more caption description
+\caption{The parameters used in generating the set of training data. The parameters are drawn uniformly in the below ranges. ~\chris{Add a bit more caption description
 here. Plus address the issues of the actual distributions used (uniform) and
@@
 training waveforms are sampled at 1024 Hz.  The parameter prior ranges are
-defined in~\cref{Tab:training_parms}. All training data is rescaled such that their amplitudes peak at 1.
+defined in~\cref{Tab:training_parms} and a sample of training waveforms are shown in \ref{fig:training_waveforms}. All training data is rescaled such that their amplitudes peak at 1.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\textwidth]{Paper_draft/figures/training-4.png}
+    \caption{Examples of the five different waveforms that were used in training the \ac{GAN} for this study. \jordan{put in the parms here too?}}
+    \label{fig:training_waveforms}
+\end{figure}
 
@@
 %
-Given a 100-dimensional vector drawn from a normal distribution and a class
+Given a 100-dimensional vector drawn from a normal distributed latent space and a one-hot encoded class
 label, the GAN is able to generate burst-like waveforms generalised from the
-training set~\chris{please state this in terms of the latent space and class
-space}. We set out by describing the quality of generated waveforms and
+training set. We set out by describing the quality of generated waveforms and
 how they compare to the training set. We then explore the structure of the
@@
     \includegraphics[width=\textwidth]{figures/generations/bbh.png}
-    \caption{Examples of \ac{GW} burst signals generated by a conditional generative adversarial network. By row: Sine-Gaussian, Ringdown,
-White-noise burst, Gaussian pulse, Binary black hole merger.~\chris{please add
-lots more description to the caption regarding wjhat you are plotting. Mention
-that these are generated waveforms plotted as a function of time, latent space
-values are randomised for each panel (or are they the same for each column?)
-classes on each row. Also mention the zoom in on the time axis. Also fix the
-time axis limits so they are consistent across all waveforms.}}
+    \caption{\ac{GAN} Generated waveforms plotted as a function of time.
+The latent space inputs for each panel is randomised and each row is assigned one of the five class vectors.
+By row: Sine-Gaussian, Ringdown,
+White-noise burst, Gaussian pulse, Binary black hole merger.
+On the first four rows each x axis is zoomed for ease of viewing, while the last row shows the full one second.
+\jordan{re-do with latent space all zeros to all ones (see colab)}}
 \label{fig:gen_signals} 
@@
 
-The generator network is a function $G$ : $\mathbf{z},\mathbf{c} $ $\in$
-$\mathbb{R}^{100}$ $\to$ $\mathbb{R}^{1024\times2}$,~\chris{why is this
-outputting to 2 timeseries? Is this out of date?} where $\mathbf{z},\mathbf{c}$
-are the latent vector and class vector~\chris{these have already been defined
-}. Given a latent vector randomly sampled from a normal distribution with zero
-mean and unit variance, a class label which is represented by a 5 dimensional
-one-hot encoded vector for each class~\chris{give an example e.g.
-$c=[0,1,0,0,0]$ represents the ring-down signal class}, the results from the
-generator can be seen in \cref{fig:gen_signals}~\chris{please indicate that
-this is all done after training has completed}. Each plot shows the output of
+After training the networks, the generator's function is to map $G$ : $\mathbf{z},\mathbf{c} $ $\in$
+$\mathbb{R}^{100}$ $\to$ $\mathbb{R}^{1024}$. The results from the
+generator can be seen in \cref{fig:gen_signals}. Each plot shows the output of
 the generator for random input latent space vectors $\mathbf{z}$ and each row
@@
 %
-\ac{ML} algorithms are often described as universal function approximators. In
-the case of the generator it maps samples drawn from a 100 dimensional Gaussian
-distribution in the latent space to its representation of the training set. As
-with any function, there should be a one to one mapping from the domain and
-co-domain to allow for smooth transitions across the latent space. One
-advantage of using \acp{GAN} as a waveform generator is that once it is
-trained, it can perform rapid generations faster than computationally expensive
-algorithms \michael{e.g.?}~\chris{you can maybe reference Seb Kahn and Green
-here soon. It will be on the arXiv next week I think - they did fast CBC
-waveform generation.  Also Walter Del Pozzo has a paper xoming out soon on
-this. Neither use GANs though, just ML}. For complicated data sets, the network
-architecture must be diverse and dense enough to capture distinct variations
-from the training set.  Most GANs perform well on relatively low resolution
-image generations, however, higher resolutions demand larger networks and long
-training times. GANs attempting to replicate complicated structures and do not
-have the necessary architecture either struggle to produce results at all or
-fall into the common failure mode know as mode collapse; where the generator
-produces a small variety of samples or simply memorises the training set. To
-test this, we perform linear interpolations in the latent and class
-space.~\chris{lots of technical talk before actually saying what you are trying
-to do. Reverse this. Also try to provide references for the technical talk}
-
-\chris{this paragraph should come before the other one since it explains what
-you are doing before going into technical stuff} In this section we explore the
-latent space formed by the generator by interpolation. We take two random
+In this section we explore the latent space formed by the generator by interpolation. We take two random
 points in the latent space and linearly interpolate between them~\chris{OK, but
@@
 locations we don't know what we should expect to get.}
+
+\ac{ML} algorithms are often described as universal function approximators. In
+the case of the generator it maps samples drawn from a 100 dimensional Gaussian
+distribution in the latent space to its representation of the training set. As
+with any function, there should be a one to one mapping from the domain and
+co-domain to allow for smooth transitions across the latent space. One
+advantage of using \acp{GAN} as a waveform generator is that once it is
+trained, it can perform rapid generations faster than computationally expensive
+algorithms \michael{e.g.?}~\chris{you can maybe reference Seb Kahn and Green
+here soon. It will be on the arXiv next week I think - they did fast CBC
+waveform generation.  Also Walter Del Pozzo has a paper xoming out soon on
+this. Neither use GANs though, just ML}. For complicated data sets, the network
+architecture must be diverse and dense enough to capture distinct variations
+from the training set.  Most GANs perform well on relatively low resolution
+image generations, however, higher resolutions demand larger networks and long
+training times. GANs attempting to replicate complicated structures and do not
+have the necessary architecture either struggle to produce results at all or
+fall into the common failure mode know as mode collapse; where the generator
+produces a small variety of samples or simply memorises the training set. To
+test this, we perform linear interpolations in the latent and class
+space.~\chris{lots of technical talk before actually saying what you are trying
+to do. Reverse this. Also try to provide references for the technical talk}
 

### 2020-09-17 Paper_draft/main.tex
more edits

@@
     \centering
-    \includegraphics[width=\textwidth]{Paper_draft/figures/training-4.png}
+    \includegraphics[width=\textwidth]{figures/training-sample.png}
     \caption{Examples of the five different waveforms that were used in training the \ac{GAN} for this study. \jordan{put in the parms here too?}}
@@
 The goal of GAN training is to find an equilibrium between the two models, if this cannot be found then it is said that the \ac{GAN} has failed to converge.
-One way to diagnose \acp{GAN} during the development process is to keep track of the loss over time.
+One way to diagnose \acp{GAN} during the development process is to keep track of the loss and accuracy over time.
 Loss plots, for example, as seen in fig.
-\ref{fig:lossplot} can help to identify common failure modes or to check if the \ac{GAN} has indeed converged.
-There is currently no notion of early stopping in \acp{GAN}, instead, training is halted after convergence and by visually inspecting the generations.
+\cref{fig:lossplot} can help to identify common failure modes or to check if the \ac{GAN} has indeed converged.
+Accuracy is the number of correct predictions made divided by total number of predictions.
+\jordan{mention why accuracy can be misleading?
+\cite{https://en.wikipedia.org/wiki/Accuracy_paradox}} There is currently no notion of early stopping in \acp{GAN}, instead, training is halted after convergence and by visually inspecting the generations.
 
@@
     \centering
-    \includegraphics[width=1\textwidth]{Paper_draft/figures/Screenshot 2020-09-11 at 16.52.47.png}
-    \caption{Line plots of the discriminator (blue) and generator (orange) loss v iterations.
-Early in training the losses oscillates as both models attempt to find their equilibrium, after which, both losses vary around 0.7.}
+    \includegraphics[width=1\textwidth]{figures/losses.png}
+    \caption{Plot of the discriminator and generator loss and accuracy as a function of iterations.
+Early in training the losses oscillates as both models attempt to find their equilibrium, after which, both losses vary around 0.7-1.}
     \label{fig:lossplot}
@@
 the generator for random input latent space vectors $\mathbf{z}$ and each row
-corresponds to one of the five class vectors $\mathbf{c}$.~\chris{yes? What
-about the plot? Anything positive to say about what you're showing? Please
-comment on the quality of the generated waveforms and the good varaition within
-each class representative of the variation in the training data. The point is
-to show the general variation and quality.}
-
-\chris{You also need to make it clear somewhere (maybe here) that you are
-generting single polarisation waveforms with normalised amplitude fixed to
-unity.}
-
-\chris{Also, how is the reader going to judge that your waveforms are good if
-we don't show any examples of the training data. I recommend a single plot
-showing 5 waveforms (5 panels horizontally) for reference.}
+corresponds to one of the five class vectors $\mathbf{c}$.
+The generations show good quality likeliness and good variation within each class representative of the variation of the training data.
+All generations are single plus polarised waveforms and their amplitudes are normalised to unity after generation.
 
@@
 %
-In this section we explore the latent space formed by the generator by interpolation. We take two random
-points in the latent space and linearly interpolate between them~\chris{OK, but
-how do you select the latent points? Are they the same pair of points for each
-class?}. These new latent space vectors can now be fed into the generator to
-make predictions on~\chris{"to make predictions on" - what does that mean?}
-while keeping the class vectors constant at each of the 5 \chris{fiducial?}
-training classes. The full effect shown in~\cref{fig:z_interp}~\chris{not a
-sentence}. We can see that each plot shows plausible waveforms suggesting that
-the generator has constructed a smooth space unlike the discrete training
-case~\chris{don't confuse the issue by saying that the class space is discrtee
-when later we want to show the opposite}. Additionally as each class is given
-the same latent points to interpolate over, we can see that the waveforms
-cluster together with respect to their parameters. Visually, the sine-gaussian
-and ring-down waveforms share similar frequencies and the other signals show
-similar decays and starting epochs for a common latent space input. The only
-exception is for the \ac{BBH} waveforms. This can be explained by the fact that
-they were trained with more variety of parameters~\chris{what is more variety
-of parameters? Does it really mean anything?} and consistently have their peak
-amplitudes in the last quarter of the time series~\chris{do they? In the plot
-the peak amplitude locations seem to range from 0.6 back to 0.5 but that's not
-too different to the ring-downs, the white noise or the pulse. The
-sine-Gaussian is the one that stands out as different. Can you please verify
-the correctness of the plot you are referring to.}.
-
-\chris{I think that it might be sensible to hand-pick the latent space
-locations as the origin and the point $[1,1,\ldots,1]/2$. When you do random
-locations we don't know what we should expect to get.}
-
 \ac{ML} algorithms are often described as universal function approximators. In
@@
 test this, we perform linear interpolations in the latent and class
-space.~\chris{lots of technical talk before actually saying what you are trying
-to do. Reverse this. Also try to provide references for the technical talk}
+space. We take two random
+points in the 100-dimensional latent space and linearly interpolate between them.
+These new interpolated latent space vectors along with class vectors can now be fed into the generator to produce interpolated waveforms.
+\cref{fig:z_interp} shows the generated waveforms, with the class vectors held constant along each row.
+We can see that each plot shows plausible waveforms suggesting that
+the generator has constructed a smooth traversable, space. Additionally, as each class is given
+the same latent points to interpolate over, we can see that the waveforms
+cluster together with respect to their parameters. Visually, the sine-Gaussian
+and ring-down waveforms share similar frequencies and the other signals show
+similar decays and starting epochs for a common latent space input.
+
+\chris{I think that it might be sensible to hand-pick the latent space
+locations as the origin and the point $[1,1,\ldots,1]/2$. When you do random
+locations we don't know what we should expect to get.} \jordan{the origin point for some signals either produce no data or rubbish generations}
 
@@
     \includegraphics[width=\textwidth]{figures/generations/z_interp_bbh.png}
-    \caption{Latent space linear interpolation, class space is
-constant.~\chris{lots more discription needed. what is being plotted against
-what? What is being held fixed, what is being varied.}}
+    \caption{Generated interpolated waveforms plotted as a function of time.
+The latent space inputs for the first and last columns are random vectors drawn from a Gaussian distribution and the between panels are linearly interpolated vectors between these two points.
+Each row keeps on of the class vetors constant thoughout the latent space interpolation.
+On the first four rows each x axis is zoomed for ease of viewing, while the last row shows the full one second time interval.}
     \label{fig:z_interp}
@@
 
+While the \ac{GAN} is trained on distinct one-hot encoded classes, we may test arbitrary points in the 5-dimensional space to produce indistinct or "inbetween" waveforms.
 In order to explore the class space we keep the latent vector constant and
-interpolate through the 5 classes. We construct a path between the 5 waveforms
-and show that the space is populated enough to allow for transitions between
+interpolate through the 5 classes. We construct a path between two waveforms
+and show in \cref{fig:c_in	terp} that the space is populated enough to allow for transitions between
 classes.  Sine-Gaussian to ringdown performs well in interpolation with each
@@
 
-~\chris{this is one of  the most important sections of the paper and there
-is barely 1 paragrpah about it. Please beter explain what you are doing in
-general when you fix the latent space location and explore the class space. The
-concept of having arbitrary points in the 5-D class space should have been made
-clear earlier on in the CGAN section (or elsewhere). There also isn't currently a
-reference to the corresponding figure.}
-
 \begin{figure}
@@
     \includegraphics[width=\textwidth]{figures/generations/interp_sg-bbh.png}
-    \caption{Class space linear interpolation, class space is held
-constant~\chris{no it isn't}.
+    \caption{Generated class interpolated waveforms as a function of time.
+The latent space vectors are held constant for each panel while each row shows generations using linearly interpolated classes as inputs to the generator.
 Top row: gaussian blip to sine-Gaussian, middle row: white noise burst to
-ringdown, bottom row: sine-Gaussian to BBH.~\chris{Again, more description,
-start from the basics, what is plotted against what. Is the latent space fixed
-the same for each row? Add the class space vectors on each panel. We have 5
-classes and so there are 10 possible pairs but you can't fit 10 rows here so
-why do 3? Why not 5 or 6? }}
+ring-down, bottom row: sine-Gaussian to BBH.~\chris{10 possible pairs but you can't fit 10 rows here so
+why do 3? Why not 5 or 6? }/\jordan{add vectors above panels.}}
     \label{fig:c_interp}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{General interpolsation within the class space}
-
-So far the analysis has focused~\chris{not really focussed, you only dedicated
-1 paragraph to it in the previous subsection} on interpolating between two
-classes of signals with the aim to use the interpolated signals as unmodelled
-waveforms, instead, we may consider random mixtures of classes~\chris{don't
-sell this according to our thought processes as we did the research, sell it as
-"we just explained the pair interpolation since it's a stepping stone to the
-general interpolation"}. We defined the classes in one-hot encoding framework,
-that is, each class resides at the corner points of a 5 dimensional
-cube~\chris{this should have already been stated n earlier sections}. In order
+\subsection{General points within the class space}
+We have shown that the \acp{GAN} latent space and class space has structure that can be navigated through with interpolation between paris of signals.
+Taken a step further, we can sample from the class space in novel ways to create new inputs for the generator.
+These new points are categorised by the method used to sample from the class space.
+The methods we use are divided into the following:
+
+\begin{itemize}
+%
+\item {\bf Conditional}: The original one-hot categorical generations from the \ac{GAN}.
+These signals are the closest to the training set.
+%
+\item {\bf Uniform}: Generated using a uniform distribution U[0,1] as the input
+class vector.
+%
+\item {\bf Simplex}: Generated using a Dirichlet distribution that samples from the
+4-simplex as the input class vector and includes within it the conditional
+locations.
+%
+\end{itemize}
+
+ In order
 to generate an even mixture~\chris{by definition, it won't be an even mixture
@@
 
-% remove these comments
-%
-\begin{comment}
-We can now think of ways to properly sample from the space between these points
-in a uniform way. Uniformity enforces the condition that we have a variety of
-waveforms. Thge easiest being to uniformly sample points in this space and use
-them as the class vectors for the generator. Another way would be to keep the
-magnitude of the class vector as 1. For a 5-dimensional space we would sample
-from the 4-dimensional plane that intersects the corner points.  \end{comment}
-
 \michael{We don't show any results with two detectors yet we use two detectors
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Searching for generalised burst - a CNN analysis}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
+\begin{figure}
+    \centering
+    \includegraphics[width=\textwidth]{figures/SNR8.png}
+    \caption{\ac{CNN} training data.
+Whitened noise free sine-Gaussian timeseries as seen by Hanford (red) and Livingston (light blue) detectors.
+These signals with fixed SNR = 8, re-scaled by the two detector network SNR.
+The dark blue time series for each plot shows either the same signal with added detector noise from Hanford (left) or Livingston (right).
+The signals plus added noise is used to train, test and validate the \ac{CNN}.}
+\end{figure}
+
 \chris{please add an example plot showing the normalised and whitened input of
@@
 is trained to distinguish between two classes: signals in additive Gaussian
-noise and Gaussian noise, where “signals” are taken from either the
+noise and Gaussian noise, where â signalsâ are taken from either the
 Conditional, Uniform or Simplex cases~\chris{the signals+noise and noise

### 2020-10-08 Paper_draft/main.tex
Updates from Overleaf
Comments addressed up to the conclusion, waiting on new results from another GAN run

@@
 \begin{abstract}
-The next generation of Gravitational wave detectors will accelerate the number
-of ac{GW} detections such that we can gain new in site into the
-physics behind the sources causing the phenomena. Numerical simulations and
-matched filtering are the standard for detecting ac{GW}s for known
-sources such as binary-black hole mergers. There are other sources of ac{GW}s
-that remain elusive to standard modelling techniques and are expected to be
-detectable. Here we construct a unmodelled burst generation scheme using
-Generative adversarial networks - a powerful class of machine learning.
-\chris{time to add a real abstract}
+We introduce the use of conditional generative adversarial networks for generalised gravitational wave burst generations in the time domain.
+Generative adversarial networks are generative machine learning models that produce new data based on the statistics of the training set.
+We condition the network on five classes of time-series signals: Sine-Gaussian, Ring-down, white noise burst, Gaussian blip and binary black hole merger and show that the model can replicate the features of these classes.
+Additionally, we show the model can produce generalised burst signals through interpolation and class mixing.
+Further, we build a convolution neural network classifier to predict the detectability of these newly produced signals in LIGO detector noise against more traditional burst waveforms.
 \end{abstract}
@@
 \acrodef{BBH}[BBH]{binary black hole}
+\acrodef{SNR}[SNR]{signal to noise ratio}
+\acrodef{PSD}[PSD]{power spectral density}
 
@@
 %
-\ac{GW} searches for modelled signals so far have used a process called
+\ac{GW} searches for modelled signals use a process called
 matched-filtering,~\cite{Owen1998}, where a large template bank of possible
@@
 \ac{GW} burst detection algorithms~\cite{Klimenko_2008, Aso_2008} are tested
-and tuned using modelled waveforms that may or may not have astrophysical
-significance but have easy to define parameters and share characteristics of
-real bursts that are enough to simulate a \ac{GW} passing between
-detectors~\chris{long sentence}. Such waveforms include sine-Gaussians: a
+and tuned using modelled waveforms that have easy to define parameters and share characteristics of real bursts that aim to simulate a \ac{GW} passing between
+detectors. Such waveforms include sine-Gaussians: a
 Gaussian modulated sine wave that is characterised by its central frequency and
@@
 Current \ac{ML} approaches~\cite{2020PhRvD.102b2005D, 2019PhRvD.100d4009D, 2020arXiv200708207B} are particularly well suited to dealing with this as once trained the searches can be performed quickly.
-\jordan{quicker than than what?}
 
@@
 inputs $x_{i},\ldots, x_{n}$
-and maps them to an \jordan{probability?} output according to the linear function, 
+and maps them to an output according to the linear function, 
 %
@@
 This process of updating the weights is repeated until the loss function reaches convergence or a global minimum.
-The training data is cycled through in epochs.
-An epoch is defined when the entire data set is fed through the network.
-As it is impractical to feed the entire data set into the network at once, so the training is split up into smaller more manageable batches.
+The training data is cycled through in epochs, where an epoch is defined when the entire data set is fed through the network.
+As it is impractical to feed the entire data into the network at once, the training is split up into smaller more manageable batches.
 Finally, the number of batches needed to compete one epoch is referred to as the iterations.
@@
 overlap between functions.
-Much like traditional neural networks the convolution operation in this context involves multiplying the input by an array of weights, called a filter or a kernel qhich is typically smaller in size than the input.
+Much like traditional neural networks the convolution operation in this context involves multiplying the input by an array of weights, called a filter or a kernel which is typically smaller in size than the input.
 The convolution is applied by shifting the kernel over the input, drawing out spatially important features between the
@@
 the stride and increasing it reduces the dimensionality of the
-output, this process is know as down sampling.
+output in a process know as down sampling.
 Alternatively, up sampling the inputs can be achieved using a transposed convolution \cite{dumoulin2016guide}.
-The output of the convolutional layer is then passed to an activation function.
+The output of the convolutional layer is then passed to an activation function and through the next layers.
 For deep neural networks, techniques like BatchNormalisation \cite{ioffe2015batch} which standardise the inputs to a layer and SpatialDropout \cite{tompson2014efficient} which sever connections between neurons can both help to stabilise learning.
@@
 prediction~\cite{liang2017dual} as well as time series
-generations~\cite{esteban2017realvalued}~\chris{do we still not have any other
-GW GAN applications to reference or are we hoping to still be the first?}. \jordan{None that i can find?}
+generations~\cite{esteban2017realvalued}.
 
@@
 \begin{equation}
-    L = -y \log(\hat{y}) + (1 - y) \log(1-\hat{y}),
+    L = -y \log(\hat{y}) - (1 - y) \log(1-\hat{y}),
     \label{eqn:crossentropy}
@@
 where $\hat{y}$ is the network prediction and $y$ is the true output.
-While training the discriminator, D, on real data, we set $y = 1$ and $\hat{y} = D(x)$ which from eqn.
-\ref{eqn:crossentropy} gives $L(D(x),1) = \log(D(x))$.
-While training on fake data produced by the generator, G, $y = 0$ and $\hat{y} = D(G(z))$ and so, $L(D(G(z)),0) = \log(1-(D(G(z))))$.
-\jordan{whole derivation unnecessary?} Since the objective of the discriminator is to correctly classify fake and real data these equations should be maximised, while the goal of the generator should be to minimize these equations.
+While training the discriminator, D, on real data, we set $y = 1$ and $\hat{y} = D(\mathbf{x})$ which from \cref{eqn:crossentropy} gives $L(D(\mathbf{x}),1) = \log(D(\mathbf{x}))$.
+While training on fake data produced by the generator, G, $y = 0$ and $\hat{y} = D(G(\mathbf{z}))$ and so, $L(D(G(\mathbf{z})),0) = \log(1-(D(G(\mathbf{z}))))$.
+Since the objective of the discriminator is to correctly classify fake and real data these equations should be maximised, while the goal of the generator should be to minimize these equations.
 This gives the \ac{GAN} loss as
@@
 \begin{equation}
-   \mathop{\text{min}}_{G}  \mathop{\text{max}}_{D} V(D,G) = \mathbb{E}_{\mathbf{x} \sim p_{\text{\text{data}}}(\mathbf{x})} [\text{log} D(\mathbf{x})] + \mathbb{E}_{\mathbf{z} \sim p_{\text{z}}(\mathbf{z})} [\text{log}(1-D(G(\mathbf{z})))],
+   \mathop{\text{min}}_{G}  \mathop{\text{max}}_{D} V(D,G) = \mathbb{E}_{\mathbf{x} \sim p_{\text{\text{data}}}(\mathbf{x})} [\text{log} D(\mathbf{x})] + \mathbb{E}_{\mathbf{z} \sim p_{\mathbf{z}}(\mathbf{z})} [\text{log}(1-D(G(\mathbf{z})))],
  \label{equation:GANloss}
@@
 information into the generator and discriminator such as a class label or
-attribute label, $c$.
+attribute label, $\mathbf{c}$.
 This simple addition has shown to work well in practice, for instance in image-to-image translation~\cite{isola2016imagetoimage}.
 We defined the classes in one-hot encoding framework, that is, each class resides at the corner points of a 5 dimensional cube.
-For example e.g.
-$c=[0,1,0,0,0]$ represents the ring-down signal class.
-The training data and labels are drawn from a joint distribution $p_{data}(\mathbf{x},\mathbf{c})$, whereas when generating fake data we sample from $\mathbf{c}$ and $p_{z}(\mathbf{z})$ independently.
+For example $\mathbf{c}=[0,1,0,0,0]$ represents the ring-down signal class.
+The training data and labels are drawn from a joint distribution $p_{\text{data}}(\mathbf{x},\mathbf{c})$, whereas when generating fake data we sample from $\mathbf{c}$ and $p_{\mathbf{z}}(\mathbf{z})$ independently.
 \href{equation:GANloss} is modified to include the class labels
@@
     \caption{Comparison of the original GAN method and the
-Conditional-GAN method. For CGANs the training data requires a label denoting
+conditional-GAN method.
+$\textbf{G}$ and $\textbf{D}$ denote the generator and discriminator neural networks respectively while $\textbf{X} \text{real}$ and $\textbf{X} \text{fake}$ represent samples drawn from the training set and the generated set.
+For CGANs the training data requires a label denoting
 its class that is also fed to the generator which then learns to generate
@@
 \centering
-\caption{The parameters used in generating the set of training data. The parameters are drawn uniformly in the below ranges. ~\chris{Add a bit more caption description
-here. Plus address the issues of the actual distributions used (uniform) and
-how you include the BBH parameters. It's also not obvious that all the classes
-share the same 3 parameters.}}
+\caption{The parameters used in generating the training data. Each parameter is drawn uniformly in the below ranges.}
 %\footnotesize
@@
 \mr
-Sine-Gaussian & 70 - 250 & 0.004 - 0.03 & 0.4 - 0.6 & N/A  \\  
+Sine-Gaussian & 70 - 250 & 0.004 - 0.03 & 0.4 - 0.6 & -  \\  
 Ringdown & 70 - 250 & 0.004 - 0.03 & 0.4 - 0.6 & N/A \\
 White-noise burst & 70 - 250 & 0.004 - 0.03 & 0.4 - 0.6 & N/A  \\
-Gaussian pulse & N/A & 0.004 - 0.03 & 0.4 - 0.6 & N/A  \\
-BBH & N/A & N/A & N/A & 5 - 70  \\
+Gaussian pulse & - & 0.004 - 0.03 & 0.4 - 0.6 & -  \\
+BBH & - & - & - & 30 - 70  \\
  \br
@@
 mid-points of all but the ring-down and \ac{BBH} classes) are randomly drawn from a uniform distribution to
-be within [0.4, 0.6] sec from the start of the 1 sec time interval and all
+be within [0.4, 0.6] seconds from the start of the 1 sec time interval and all
 training waveforms are sampled at 1024 Hz.  The parameter prior ranges are
-defined in~\cref{Tab:training_parms} and a sample of training waveforms are shown in \ref{fig:training_waveforms}. All training data is rescaled such that their amplitudes peak at 1.
+defined in~\cref{Tab:training_parms} and a sample of training waveforms are shown in \cref{fig:training_waveforms}. All training data is rescaled such that their amplitudes peak at 1.
 
@@
     \includegraphics[width=\textwidth]{figures/training-sample.png}
-    \caption{Examples of the five different waveforms that were used in training the \ac{GAN} for this study. \jordan{put in the parms here too?}}
+    \caption{Examples of the five different waveforms that were used in training the \ac{GAN} for this study.
+Values of the parameters were selected randomly from uniform distributions from \cref{Tab:hyperparameters}.}
     \label{fig:training_waveforms}
@@
 One way to diagnose \acp{GAN} during the development process is to keep track of the loss and accuracy over time.
-Loss plots, for example, as seen in fig.
-\cref{fig:lossplot} can help to identify common failure modes or to check if the \ac{GAN} has indeed converged.
+Loss plots, for example, as seen in \cref{fig:lossplot} can help to identify common failure modes or to check if the \ac{GAN} has indeed converged.
 Accuracy is the number of correct predictions made divided by total number of predictions.
-\jordan{mention why accuracy can be misleading?
-\cite{https://en.wikipedia.org/wiki/Accuracy_paradox}} There is currently no notion of early stopping in \acp{GAN}, instead, training is halted after convergence and by visually inspecting the generations.
+There is currently no notion of early stopping in \acp{GAN}, instead, training is halted after convergence and by visually inspecting the generations.
 
@@
     \caption{Plot of the discriminator and generator loss and accuracy as a function of iterations.
-Early in training the losses oscillates as both models attempt to find their equilibrium, after which, both losses vary around 0.7-1.}
+Early in training the losses oscillates as both models attempt to find their equilibrium, after which, both losses vary around a point which signifies stable training.
+Accuracy's on the real and fake data are similar showing that neither model is stronger than the other.}
     \label{fig:lossplot}
@@
 By row: Sine-Gaussian, Ringdown,
-White-noise burst, Gaussian pulse, Binary black hole merger.
-On the first four rows each x axis is zoomed for ease of viewing, while the last row shows the full one second.
-\jordan{re-do with latent space all zeros to all ones (see colab)}}
+White-noise burst, Gaussian pulse, Binary black hole merger. On the first four rows each x axis is zoomed for ease of viewing, while the last row shows the full one second.}
 \label{fig:gen_signals} 
@@
 %
-\item {\bf Conditional}: The original one-hot categorical generations from the \ac{GAN}.
+\item {\bf Vertex}: Points that lie at the corners of the five dimensional class space.
 These signals are the closest to the training set.
@@
 \item {\bf Simplex}: Generated using a Dirichlet distribution that samples from the
-4-simplex as the input class vector and includes within it the conditional
-locations.
+4-simplex inside the class space.
 %
@@
 
- In order
-to generate an even mixture~\chris{by definition, it won't be an even mixture
-if points are randomly sampled} of classes we sample points uniformly in this
-space. \jordan{this would be the box}. Alternativly we can sampe points from
-the plane that intersects the four corners, which for a 5-dimensional case is,
-sample from a 4-simplex.~\chris{please dedicate an entire paragraph to the
-simplex and box explanation. You may even need an equation or 2.} This can be
-seen in~\ref{fig:unmodelled_samples}. \jordan{why? this enforces the vector
-points to sum to one. Why is that good? Well it keeps the points lying on the
-simplex.}~\chris{indeed. The reasons were originally that the plane is the
-simplest structure (a hyper-surface or manifold if you;re being fancy) in the
-class space that intersects all classes and has a symmetry such that no class
-is favoured over any other - however that property is largely due to the
-locations within the one-hot encoding space. Sampling from the simplex can be
-seen as sampling from between the classes - truly interpolating within the
-space. Alternatively, the cube is not the simplest space since it contains
-points up to a distance of unity from the closst class e.g. [0,0,0,0,0] is a
-distance of 1 away from all classes (as is [1,1,1,1,1]). This space contains
-the simplex as a subspace but also allows for some level of extrapolation.
-Hence we would expect the unexpected in the cube and hope for less surprises
-with the simplex. THere is also the possibility of exploring outside the cube.
-}
+The vertex points are the most straightforward where one entry contains 1 and the other entries are zero and are equivalent to the class vectors that the GAN is trained on e.g.
+$\mathbf{c} = [1,0,0,0,0]$ would correspond to a Sine-Gaussian generation.
+Uniform class vectors sample from a uniform distribution and act like a random draw from the class space.
+Uniformly sampling contains points up to a distance of unit from the closest class e.g.
+[0,0,0,0,0] is of distance 1 away from all classes (as is [1,1,1,1,1]).
+For simplex class vectors, we sample from the simplest hypersurface that intersects all the classes and has a symmetry such that no class is favoured over any other.
+For our 5-dimensional case this would correspond to a 4-simplex manifold.
+Sampling from the simplex can be seen as sampling from between the classes within the space.
+We can expect a priori that the uniformly sampled space (which contains the simplex as a subspace) will allow for some level of extrapolation.
 
@@
 the latent space locations? You absolutely need to specify which are simplex
-and which are box.}}
+and which are box.\jordan{this needs re thinking n how to show the three cases in a nice way, or just describe it in the caption? first three rows are from simplex" etc?}}}
     \label{fig:unmodelled_samples}
@@
 
-\section{Searching for generalised burst - a CNN analysis}
-
-In this section of the analysis we will forensically~\chris{no we won't}
-compare different waveform generations from the \ac{CGAN} to help determine the
-success and failures of the model~\chris{what does this mean? What model?}. We
-investigate a simple case using a \ac{CNN} to detect whether a signal is
-contained in noise or if the data contains noise only. The signals we use to
-train the \ac{CNN} are generated from the \ac{GAN} with their latent input
-randomised from a 100-dimensional Gaussian distribution~\chris{yes, but this
-should be obvious since we never deviate from the 100-D latent vector approach}
-and are categorised by the method used to sample from the class space. These
-methods are divided into the following:
-
-\begin{itemize}
-%
-\item {\bf Conditional}: Definite categorical generations~\chris{yes, but what
-does that mean. You've never mentioned that phrase before} from the \ac{GAN}.
-These signals are the closest to the training set.
-%
-\item {\bf Uniform}: Generated using a uniform distribution U[0,1] as the input
-class vector~\chris{yes, but you need to specify the 5-D nature of the space}.
-%
-\item {\bf Simplex}: Generated using a Dirichlet distribution that samples from the
-4-simplex as the input class vector and includes within it the conditional
-locations.~\chris{all fine as long as you have defined the 4-simplex earlier
-on.} 
-%
-\end{itemize}
-
-\begin{figure}
+\section{Searching for generalised burst using a CNN}
+In this section  we use a convolutional neural network \ac{CNN} 
+to compare different waveform generations from the \ac{CGAN} to help determine the
+success and failures of the model generations. We train a \ac{CNN} to distinguish between two classes: signals in additive Gaussian
+noise and Gaussian noise only. 
+\subsection{Training data} 
+We use three classes of training data: Vertex, Uniform or Simplex cases generated using our \ac{GAN} method and consider two detectors H1 and L1 as joint inputs to the \ac{CNN}.
+For each training set we generated a bank of $2\times 10^5$ signals and apply antenna responses and time delays using routines provided by LALsuite \cite{lalsuite}.
+The polarisation angles are drawn uniformly in the range [0,2$\pi$] and sky positions are generated uniformly on the 2-sphere.
+Time delays between detectors are computed relative to the Earth centre.
+All of the training data used is whitened using the Advanced LIGO
+design sensitivity \ac{PSD}, such that there is equal noise power at each
+frequency and the data is correctly normalised. This procedure is
+applied to signals whose \acp{SNR} are sampled uniformly in the range $[1-16]$.
+Each time series input to the \ac{CNN} is represented by an 1024 x 2 image that is sampled at 1024 hz for each of the two detectors.
+An example time series is shown in \cref{fig:cnn_training}.
+While training the network, the input training data consists of
+signals which contain one half noise only and one half signal contained in
+noise. Of that, 80\% is used for training and 20\% used for validation, while for testing we use $2\times 10^5$ signals in order to use small false alarm rates later.
+
+\begin{figure}[ht!]
     \centering
@@
 The signals plus added noise is used to train, test and validate the \ac{CNN}.}
+     \label{fig:cnn_training}
 \end{figure}
 
-\chris{please add an example plot showing the normalised and whitened input of
-an SNR=8 signal, one panel for each detector, with noisy signal and noise-free
-signal plotted on top. Then remember to reference it in the text.}
-
-The CNN~\chris{whoah, hold on. What CNN? You said you were going to use one but
-can we get a few more details first. what's the input, what's the output,
-what's the loss function, then point us to a table of params in the appendix.}
-is trained to distinguish between two classes: signals in additive Gaussian
-noise and Gaussian noise, where â signalsâ are taken from either the
-Conditional, Uniform or Simplex cases~\chris{the signals+noise and noise
-statement is repetetive of the previous paragraph.}. This means in total there
-are three \acp{CNN} to train and all \acp{CNN} share the same architectural
-structure. All of the training data used is whitened using the Advanced LIGO
-design sensitivity \ac{PSD}, such that there is equal noise power at each
-frequency and the data is correctly normalised~\chris{but what is correctly
-normalised. Remember trhat we have to be reproducible so you have to make sure
-that someone reading this can repeat your experiment.}. This procedure is
-applied to signals whose \acp{SNR} are sampled uniformly in the range $[1-16]$.
-For each run~\chris{what is a run} the training data consists of $2\times 10^5$
-signals which contain one half noise only and one half signal contained in
-noise. Of that, 80\% is used for training and 20\% used for validation. A
-different testing set is also used in the analysis that is $2\times 10^5$ in
-size.~\chris{This final sentence is worded strangely but also why do we have
-such a large testing set? I can only imagine that we did this so that we could
-go to small $\sim 10^{-5}$ false alarm rates. Is that right?}
-
-\chris{there is no mention of the "old" box, the one that randomised the sky
-location, time shifted the signals and applied the antenna patterns. Also no
-mention of multi-detector data and no mention of use of channels. Please add
-all of this. }
-
-*table of parameters used for CNN*~\chris{put this in the appendix with the
-GAN table}
+\subsection{CNN architecture}
+In this approach the input to the \ac{CNN} is a two dimensional vector which is passed through a series of convolutional layers, onto two fully connected or ''Dense" layers and finally to a single output neuron which represents the probability that a signal is present within the noise.
+We used a small amount of dropout and found that the swish activation \cite{ramachandran2017searching} function performed well.
+The output layer is activated by a sigmoid function and we used \cref{eqn:crossentropy} as a loss function and Adam as an optimizer with learning rate set to $10^{-3}$.
+In total we train three separate \acp{CNN} on either the vertex, uniform or simplex data set, however, all \acp{CNN} share the same architectural
+structure and hyperparameters which are shown in \cref{Tab:cnn_training_parms}.
 
@@
 
-% remove this comment if not being used
-\begin{comment}
-{\subsection{Vector Arithmetic}
-In DCGANs the authors demonstrated unsupervised vector arithmetic with celebrity face generation.
-They kept points in the latent space and performed simple vector arithmetic to generate new images.
-This allows for intuitive and targeted generation of images.
-However, the authors realised that single images vectors were unstable and there was a need to average three vectors before any arithmetic.
-DCGANs is unconditional, therefore, the vectors used were chosen empirically, generating many faces and choosing the attributes for study.
-Here, we show that this GAN only needs a single vector representation and due to conditioning we can have more control over which vectors to use in the arithmetic.
-In \cref{fig:arithmetic} we generate a whitenoise burst and a BBH insprial using their respective class labels and use a randomised latent point and response.
-Keeping the latent point and response, we average the two class vectors and use this as input to the generator.
-\Cref{fig:arithmetic} (c) shows the generation based on the combined class vectors which visually looks similar to a supernova waveform.
-Supernova waveform generations require expensive numerical relativity simulations and various assumptions about the collapse of its parent star.
-Here, we are able to produce similar waves at a fraction of the expense and we are able to further modify the resultant by using different latent space samples.
-\jordan{this is the adding noise thing but i need to work out the correct way to do it with the directional vector}.
-\end{comment}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 In this work we present the potential of \acp{GAN} for
-burst \ac{GW} analysis. We have shown that \acp{GAN} have the ability to generate 5
-class varieties~\chris{yes, but you make it sound like 5 is special and it's
-not} of modelled burst \ac{GW} signals that can be generated at
-whim~\chris{really? whim?}. The latent and class spaces were explored through interpolation and
+burst \ac{GW} analysis.
+We have shown that \acp{GAN} have the ability to generate realisitc time series burst data and can be conditioned based on the inherent features of the signals.
+The latent and class spaces were explored through interpolation and
 suggest that the space provides smooth translations between classes and overall
@@
 \begin{table}[hb]
-\caption{CGAN architecture~\chris{More, more, more desctription. Also split the
-generatpr and descriminator parts.}}
-\footnotesize
-\begin{tabular}{@{}l l l l l l l}
+\centering
+\caption{The architecture and hyperparameters describing our CNN consists of four convolutional layers followed by two dense layers.
+The convolutional layers are activated by the swish function, the first dense layer is not activated and dropout is applied, while the final layer uses the sigmoid activation.
+The network is trained by minimising the binary cross entropy and optimised with Adam with learning rate $10^{-3}$.
+We train for 10 epochs with a batch size of 1000.}
+%\footnotesize
+\begin{tabular*}{\textwidth}{c @{\extracolsep{\fill}} c c c c c c}
 \br
- Operation & Kernel & Strides & Output Shape & BN & Dropout & Activation \\
+%\hline
+Operation & Output shape & Kernel size & Stride & Dropout & Activation \\
 \mr
- G(\textbf{z}): Input \textbf{z} $\sim$ Normal(0,0.02) & N/A & N/A & (100,) & \ding{55} & 0 & N/A \\  
- Dense & N/A & N/A & (32768,) & \ding{55} & 0 & ReLU \\  
- Class input c & N/A & N/A & (1,) & \ding{55} & 0 & N/A \\
- Embedding & N/A & N/A & (1, 120) & \ding{55} & 0 & N/A \\
- Dense & N/A & N/A & (1,128) & \ding{55} & 0 & ReLU \\ 
- Reshape \textbf{z} & N/A & N/A & (128, 256) & \ding{55} & 0 & N/A \\
- Reshape c & N/A & N/A & (128, 1) & \ding{55} & 0 & N/A \\
- Concatenate & N/A & N/A & (128, 257) & \ding{55} & 0 & N/A \\
- Reshape & N/A & N/A & (64, 514) & \ding{55} & 0 & N/A \\
- Transposed Convolution & 18x1 & 2 & (256, 256) & \ding{51} & 0 & ReLU\\
- Transposed Convolution & 18x1 & 2 & (512, 128) & \ding{55} & 0 & ReLU\\
- Transposed Convolution & 18x1 & 2 & (1024, 64) & \ding{55} & 0 & ReLU\\
- Convolution & 18x1 & 1 & (1024, 1) & \ding{55} & 0 & Tanh \\
- Sky input & N/A & N/A & (3,) & \ding{55} & 0 & N/A \\
- Concatenate & N/A & N/A & (1027,) &  \ding{55} & 0 & N/A \\
- Lambda & N/A & N/A & (1024, 2) & \ding{55} & 0 & N/A \\
- D(\textbf{x}): Input \textbf{x} & N/A & N/A & (1024, 2) & \ding{55} & 0 & N/A \\
- Convolution & 14x1 & 2 & (512, 64) & \ding{55} & 0.5 & Leaky ReLU \\
- Convolution & 14x1 & 2 & (256, 128) & \ding{55} & 0.5 & Leaky ReLU \\
- Convolution & 14x1 & 2 & (128, 256) & \ding{55} & 0.5 & Leaky ReLU \\
- Convolution & 14x1 & 2 & (64, 512) & \ding{55} & 0.5 & Leaky ReLU \\
- Flatten & N/A & N/A & (32768,) & \ding{55} & 0 & N/A \\
- Dense & N/A & N/A & (1,) & \ding{55} & 0 & Sigmoid \\
- Dense & N/A & N/A & (5,) & \ding{55} & 0 & Softmax \\
+Input & (1024, 2) & N/A  & N/A & N/A & N/A \\
+Convolutional & (512, 8) & 5 & 2 & 0 & Swish  \\
+Convolutional & (256, 8) & 5 & 2 & 0 & Swish  \\
+Convolutional & (128, 8) & 5 & 2 & 0 & Swish  \\
+Convolutional & (64, 8) & 5 & 2 & 0 & Swish  \\
+Dense & (100) & 100 & N/A & 0.2 & Linear  \\
+Dense & (1) & 1 & N/A & 0 & Sigmoid \\
+\end{tabular*}\\
+\begin{tabular*}{\textwidth}{@{}l l l l l l}
+\mr
+Optimizer & Adam($\alpha$ = 0.001, $\beta_{1}$ = 0.5) & & & & \\
+Batch size & 1000 & & & & \\
+Epochs & 100 & & & & \\
+Loss & Binary cross-entropy & & & & \\
  \br
- Optimizer & \multicolumn{6}{l}{Adam($\alpha$ = 0.0002, $\beta_{1}$ = 0.5)} \\
- Batch size & \multicolumn{6}{l}{128}  \\
- Iterations & \multicolumn{6}{l}{60000}  \\
- Leaky ReLU slope & \multicolumn{6}{l}{0.2} \\
- Weight initialization & \multicolumn{6}{l}{Gaussian($\mu$ = 0, $\sigma$ = 0.02)} \\
- Generator loss & \multicolumn{6}{l}{Binary cross-entropy} \\
- Discriminator loss & \multicolumn{6}{l}{Binary cross-entropy \& sparse categorical cross-entropy} \\ 
+\end{tabular*}\\
+\label{Tab:cnn_training_parms}
+\end{table}
+
+\begin{table}[hb]
+\centering
+\caption{The architecture and hyperparameters describing our GAN consisting of discriminator and generator convolution neural networks.
+The discriminator casts the class input through a fully connected layer such that its dimensions match the signals input which it then concatenates channel-wise.
+This is then downsampled through four convolutional layers all activated by Leaky ReLU functions add drops half of the connections at the end of each of these layers.
+The vector is then flattened to one dimension before fully connecting to a single neuron and its output activated by sigmoid to represent the probability the signal came from the training set.
+The generator concatenates the latent and class input vectors which is fed to a fully connected layer.
+This layer is then upsampled by four tranposed convolutions.
+The output of the first layer is batch normalised (BN) and all convolutional layer are activated by ReLU with the exception of the final layer which is Linear.
+Finally, the extra dimension introduced for the convolution is removed.}
+%\footnotesize
+\begin{tabular*}{\textwidth}{c @{\extracolsep{\fill}} c c c c c c}
 \br
-\end{tabular}\\
-\label{Tab:hyperparameters}
+\mr
+%\hline
+&& Discriminator &&& \\
+\mr
+Operation & Output shape & Kernel size & Stride & Dropout & Activation \\
+Class Input & (5) & N/A & N/A & 0  & N/A \\
+Dense & (1024) & N/A & N/A & 0 & N/A \\
+Signal Input & (1024) & N/A & N/A & 0 &  N/A \\
+Concatenate & (1024, 2) & N/A & N/A & 0 &  N/A \\
+Convolutional & (512, 64) & 14 & 2 & 0.5 & Leaky ReLU \\
+Convolutional & (256, 128) & 14 & 2 & 0.5 &  Leaky ReLU \\
+Convolutional & (128, 256) & 14 & 2 & 0.5 & Leaky ReLU \\
+Convolutional & (64, 512) & 14 & 2 & 0.5 &  Leaky ReLU \\
+Flatten & (32768) & N/A & N/A & 0 &  N/A \\
+Dense & (1) & N/A & N/A & 0 & Sigmoid \\
+\mr
+&& Generator &&& \\
+\mr
+Operation & Output shape & Kernel size & Stride & BN & Activation \\
+Class Input & (5) & N/A & N/A & \ding{55}  & N/A \\
+Latent Input  & (100) & N/A & N/A & \ding{55} & N/A \\
+Concatenate & (105) & N/A & N/A & \ding{55} &  N/A \\
+Dense & (32768) & N/A & N/A & \ding{55} &  ReLu \\
+Reshape & (64, 512) & N/A & N/A & N/A \\
+Transposed Conv & (128, 256) & 18 & 2 & \ding{51} & ReLU \\
+Transposed Conv & (256, 128) & 18 & 2 & \ding{55} &  ReLU \\
+Transposed Conv & (512, 264) & 18 & 2 & \ding{55} & ReLU \\
+Transposed Convn & (1024, 1) & 18 & 2 & \ding{55} & Linear \\
+Reshape & (1024) & N/A & N/A & \ding{55} & N/A \\
+\end{tabular*}
+\begin{tabular*}{\textwidth}{@{} l l l l l l}
+\mr
+ Optimizer & Adam($\alpha$ = 0.0002, $\beta_{1}$ = 0.5) \\
+ Batch size & 128  \\
+ Epochs & 100  \\
+ Loss & Binary cross-entropy \\
+ \br
+\end{tabular*}\\
+\label{Tab:gan_training_parms}
 \end{table}
-\normalsize
 

### 2020-10-12 Paper_draft/main.tex
Updates from Overleaf

@@
 
-    \addplot [mark=none,draw=green,ultra thick] {tanh(\x)};
-    \addplot+[mark=none,draw=blue,domain=-2.5:0,ultra thick] {0};
-    \addplot+[mark=none,draw=blue,domain=0:2.5,ultra thick] {x};
-    \addplot+[mark=none,red,dotted,domain=-2:0,ultra thick] {0.2*x};
-    \addplot+[mark=none,red,dotted,domain=0:2.5,ultra thick] {x};
+    \addplot [mark=none,draw=purple,ultra thick] {tanh(\x)};
+    \addplot+[mark=none,draw=green,domain=-2.5:0,ultra thick] {0};
+    \addplot+[mark=none,draw=green,domain=0:2.5,ultra thick] {x};
+    \addplot+[mark=none,orange,domain=-2.5:0,ultra thick] {0.2*x};
+    \addplot+[mark=none,orange,domain=0:2.5,ultra thick] {x};
 
@@
 (b) A selection of activation functions used in this study.
-The hyperbolic tangent (Green), Rectified linear unit \cite{relu} (Blue) and Leaky rectified linear unit \cite{Maas2013RectifierNI} (Red).
+The hyperbolic tangent (purple), Rectified linear unit \cite{relu} (orange) and Leaky rectified linear unit \cite{Maas2013RectifierNI} (green).
 (c)
@@
 the inspiral, merger and ringdown of a \ac{BBH} waveform. The component masses
-lie in the range of [5,70] $\textrm{M}_{\odot}$ with zero spins and we fix
+lie in the range of [30,70] $\textrm{M}_{\odot}$ with zero spins and we fix
 $m_1>m_2$. The mass distribution is approximated by a power law with
@@
 with any function, there should be a one to one mapping from the domain and
-co-domain to allow for smooth transitions across the latent space. One
-advantage of using \acp{GAN} as a waveform generator is that once it is
-trained, it can perform rapid generations faster than computationally expensive
-algorithms \michael{e.g.?}~\chris{you can maybe reference Seb Kahn and Green
-here soon. It will be on the arXiv next week I think - they did fast CBC
-waveform generation.  Also Walter Del Pozzo has a paper xoming out soon on
-this. Neither use GANs though, just ML}. For complicated data sets, the network
-architecture must be diverse and dense enough to capture distinct variations
-from the training set.  Most GANs perform well on relatively low resolution
+co-domain to allow for smooth transitions across the latent space. Most GANs perform well on relatively low resolution
 image generations, however, higher resolutions demand larger networks and long
@@
 
-\chris{I think that it might be sensible to hand-pick the latent space
-locations as the origin and the point $[1,1,\ldots,1]/2$. When you do random
-locations we don't know what we should expect to get.} \jordan{the origin point for some signals either produce no data or rubbish generations}
-
 \begin{figure}
@@
     \caption{Generated interpolated waveforms plotted as a function of time.
-The latent space inputs for the first and last columns are random vectors drawn from a Gaussian distribution and the between panels are linearly interpolated vectors between these two points.
+The latent space inputs for the first  column is a vector of zeros and last columns are vectors of 0.5.
+Between panels are linearly interpolated vectors between these two points.
 Each row keeps on of the class vetors constant thoughout the latent space interpolation.
@@
     \centering
-    \includegraphics[width=\textwidth]{figures/generations/interp_blip-sg.png}
-    \includegraphics[width=\textwidth]{figures/generations/interp_wnb-rd.png}
-    \includegraphics[width=\textwidth]{figures/generations/interp_sg-bbh.png}
+    \includegraphics[width=\textwidth]{figures/generations/sg-rd.png}
+    \includegraphics[width=\textwidth]{figures/generations/rd-wnb.png}
+    \includegraphics[width=\textwidth]{figures/generations/wnb-blip.png}
+    \includegraphics[width=\textwidth]{figures/generations/blip-bbh.png}
+    \includegraphics[width=\textwidth]{figures/generations/bbh-sg.png}
+    \includegraphics[width=\textwidth]{figures/generations/wnb-bbh.png}
     \caption{Generated class interpolated waveforms as a function of time.
-The latent space vectors are held constant for each panel while each row shows generations using linearly interpolated classes as inputs to the generator.
-Top row: gaussian blip to sine-Gaussian, middle row: white noise burst to
-ring-down, bottom row: sine-Gaussian to BBH.~\chris{10 possible pairs but you can't fit 10 rows here so
-why do 3? Why not 5 or 6? }/\jordan{add vectors above panels.}}
+The latent space vectors are fixed at 0.5 for each entry while each row shows generations using linearly interpolated classes as inputs to the generator.
+By row top to bottom: Sine-Gaussian to Ringdown, Ringdown to White-noise burst, Gaussian pulse to BBH, BBH to Sine-Gaussian, White-noise burst to BBH.}
     \label{fig:c_interp}
@@
     \includegraphics[width=\textwidth]{figures/generations/simplex_sample3.png}
+    \caption{GAN generations where the class vectors are sampled from the 4-D
+plane intersecting all classes. Latent space locations for all signals are taken randomly from a Gaussian distribution and the signals are then re-scaled such that they peak at unity.}
+    \label{fig:simplexd_samples}
+\end{figure}
+
+\begin{figure}
+    \centering
     \includegraphics[width=\textwidth]{figures/generations/uniform_sample3.png}
@@
     \includegraphics[width=\textwidth]{figures/generations/uniform_sample1.png}
-    \caption{GAN generations where the class vectors are sampled from the 4-D
-plane and sampled uniformly in the class space.~\chris{As always, far more
-description needed. What are you plotting against what? Do you fix or randomise
-the latent space locations? You absolutely need to specify which are simplex
-and which are box.\jordan{this needs re thinking n how to show the three cases in a nice way, or just describe it in the caption? first three rows are from simplex" etc?}}}
-    \label{fig:unmodelled_samples}
+    \caption{GAN generations where the class vectors are sampled uniformly in the hypercube class space.
+Latent space locations for all signals are taken randomly from a Gaussian distribution and the signals are then re-scaled such that they peak at unity.}
+    \label{fig:uniform_samples}
 \end{figure}
@@
 Worth a try?}
-
-\michael{We don't show any results with two detectors yet we use two detectors
-for the CNN, we might want to think when/where it's best to show some
-generations with both detectors. Maybe when we show a signal with noise since
-it's all part of the post-processing?}~\chris{I agree, see my comment in the
-CNN section next.}
 
@@
 to produce new unmodelled waveform varieties that can be used to test current
-burst search pipelines. \jordan{couple of sentences about
-classifier}.~\chris{expand this. You have 15-20 pages of material so you can
-get a nioce big paragrpah or 2 out of this. It will be repetitive, yes, but
-that's the point.}
+burst search pipelines.
 
@@
 %
-In order to extend this work to a viable burst wave generator and classifier a
-few points require further research. In principle it is trivial to add another
-detector inside the response layer \jordan{response is the wrong thing to say
-since the time delay isnt really a response, extrinsic layer? just non
-trainable layer? The box?}, however, as this now 3 dimensional signal is feed
-to the discriminator this will no doubt require further tweaking of the
-network. We can add more burst-like wave forms in the training set, like
-detector glitches which would similarly require further network design. The
-work presented here is noise free. To havea complete generation and detection
-package we would like to train the network on signals hidden in additive
-Gaussian noise and test the ability of the auxiliary classifier. 
-~\chris{this paragrph is old and out of date. Please unpdate it.}
-
-The approach shown in this work shows promise in generating unmodelled burst
-waveforms from exotic~\chris{no} sources. Having the ability to quickly
+
+Having the ability to quickly
 generate new waveforms is essential to test current detection schemes and their
@@
 ~\chris{we need to write down paragrph headinsg in the next meeting. I'm tired.}
-
-\jordan{I want to include a link to the github etc but also a google collab
-scrip like the one for BigGANs: \\
-\url{https://colab.research.google.com/github/tensorflow/hub/blob/master/examples/colab/biggan_generation_with_tf_hub.ipynb.}
-It's fun and gives a better feel for the interpolating that static images.}
 
@@
 Dense & (32768) & N/A & N/A & \ding{55} &  ReLu \\
-Reshape & (64, 512) & N/A & N/A & N/A \\
+Reshape & (64, 512) & N/A & N/A & \ding{55} & N/A \\
 Transposed Conv & (128, 256) & 18 & 2 & \ding{51} & ReLU \\
@@
 Transposed Conv & (512, 264) & 18 & 2 & \ding{55} & ReLU \\
-Transposed Convn & (1024, 1) & 18 & 2 & \ding{55} & Linear \\
+Transposed Conv & (1024, 1) & 18 & 2 & \ding{55} & Linear \\
 Reshape & (1024) & N/A & N/A & \ding{55} & N/A \\
@@
  Optimizer & Adam($\alpha$ = 0.0002, $\beta_{1}$ = 0.5) \\
- Batch size & 128  \\
+ Batch size & 512  \\
  Epochs & 100  \\

### 2020-10-22 Paper_draft/main.tex
new results

@@
 
+% Commands for references
+\def\prd{\ref@jnl{Phys.~Rev.~D}}
+
 \newcommand{\gguide}{{\it Preparing graphics for IOP Publishing journals}}
@@
 Generative adversarial networks are generative machine learning models that produce new data based on the statistics of the training set.
-We condition the network on five classes of time-series signals: Sine-Gaussian, Ring-down, white noise burst, Gaussian blip and binary black hole merger and show that the model can replicate the features of these classes.
+We condition the network on five classes of time-series signals: sine-Gaussian, ringdown, white noise burst, Gaussian pulse and binary black hole merger and show that the model can replicate the features of these classes.
 Additionally, we show the model can produce generalised burst signals through interpolation and class mixing.
@@
 observed alongside its electromagnetic counterpart for the first time, giving
-rise to multi-messenger ac{GW} astronomy.
+rise to multi-messenger \ac{GW} astronomy.
 
@@
 \ac{GW} searches for modelled signals use a process called
-matched-filtering,~\cite{Owen1998}, where a large template bank of possible
+matched-filtering,~\cite{Owen1998,Usman_2016,sachdev2019gstlal}, where a large template bank of possible
 \ac{GW} waveforms are compared to the detector outputs. In order to increase
@@
 multi-dimensional parameter space requiring
-significant computational cost. For \ac{GW} bursts that remain un-modelled; there are no
+significant computational cost \michael{Do the template banks need to large to increase the chance or to cover the complete range of possible signals we expect?}.
+\jordan{Do they cover the complete range?} \michael{I think they have something like 97\% coverage, I know the number of templates depends on the coverage you want.
+Might we worth asking Chris and Siong}For \ac{GW} bursts that remain unmodeled; there are no
 templates available and so matched-filtering is unsuitable for the detection of
-these signals.  Instead, detection algorithms like (cWB, x-pipeline, etc... \jordan{reference}) involve distinguishing the signal from
+these signals.  Instead, detection algorithms like coherent WaveBurst \cite{drago2020coherent} involve distinguishing the signal from
 detector noise by looking for excess power contained in the time-frequency
@@
 Gaussian modulated sine wave that is characterised by its central frequency and
-decay parameter. Bandlimited white-noise bursts: white noise that is contained
-within a certain frequency range and ring-downs which mimic the damped
-oscillations after a \ac{CBC} merger. A Gaussian blip: a short exponential increase the decrease in amplitude and a Binary black hole in spiral. 
+decay parameter. Bandlimited white noise bursts: white noise that is contained
+within a certain frequency range and ringdowns which mimic the damped
+oscillations after a \ac{CBC} merger. A Gaussian pulse: a short exponential increase then decrease in amplitude and a binary black hole inspiral.
 % cut this text if not going to be used
@@
 future, there is a growing need for fast and efficient \ac{GW} analysis methods
-to match the rising number of detections. While still in its infancy, applying \ac{ML} to \ac{GW} analyses have already shown great potential in
-areas of detection~\cite{Gabbard2017,Gebhard_2019,Krastev_2020}, where these techniques have matched the sensitivity of matched filtering for Advanced LIGO and Advanced Virgo gravitational-wave searches.
-In identifying and classifying detector noise transients or  'glitches"~\cite{Bahaadini, George_2018,Razzano_2018, 2020arXiv200801262G}.
+to match the rising number of detections.
+While still in its infancy, the application of \ac{ML} to \ac{GW} analyses has already shown great potential in areas of detection ~\cite{Gabbard2017,Gebhard_2019,Krastev_2020}, where these techniques have matched the sensitivity of matched filtering for Advanced LIGO and Advanced Virgo gravitational-wave searches.
+In identifying and classifying detector noise transients or  ``glitches''~\cite{Bahaadini, George_2018,Razzano_2018, 2020arXiv200801262G}.
 In Bayesian parameter
-estimation~\cite{gabbard2019bayesian,
-green2020gravitationalwave} where \ac{ML} techniques can recover parameters of a \ac{GW} signal significantly faster than standard methods.
+estimation~\cite{gabbard2019bayesian, green2020gravitationalwave} where \ac{ML} techniques can recover parameters of a \ac{GW} signal significantly faster than standard methods.
 Long duration signals like continuous \ac{GW} require long observing times and therefore have large amounts of data needing to be processed.
@@
 In this work we aim to explore the use of \ac{ML} to generate and interpret
-unmodelled \ac{GW} burst waveforms. Using the generative machine learning
+unmodeled \ac{GW} burst waveforms. Using the generative machine learning
 model, \acp{GAN}, we train on five classes of waveforms in the time domain. Working on the assumption that \acp{GAN} construct smooth
@@
 hybrid waveforms. As all the computationally expensive
-processes occur during training, the learned model after training is able to
-produce waveforms in fractions of a second and in fact produce waveforms that
-are difficult to produce with current
+processes occur during training, once trained, the model is able to
+generate waveforms in fractions of a second and produce waveforms that are difficult to geenrate with current
 techniques. These new varieties of waveforms can then be used to diagnose
 detection algorithms, gain new insight into sources of \ac{GW}
-bursts and  allow us to better train our algorithms to a
+bursts and  allow us to better train our algorithms on a
 broader range of possible signals and therefore enhance our detection ability.
@@
 
-    \addplot [mark=none,draw=purple,ultra thick] {tanh(\x)};
+    \addplot [mark=none,draw=purple,domain=-2.5:2.5,ultra thick] {1/(1+exp(-x))};
     \addplot+[mark=none,draw=green,domain=-2.5:0,ultra thick] {0};
@@
 (b) A selection of activation functions used in this study.
-The hyperbolic tangent (purple), Rectified linear unit \cite{relu} (orange) and Leaky rectified linear unit \cite{Maas2013RectifierNI} (green).
+The sigmoid (purple), rectified linear unit \cite{relu} (orange) and leaky rectified linear unit \cite{Maas2013RectifierNI} (green).
 (c)
@@
 
-\ac{ML} aims to learn apparent relationships held within given data or `training
+\ac{ML} algorithms aim to learn apparent relationships held within given data or `training
 data' in order to make accurate predictions without the need for additional
 programming. A common approach in \ac{ML} relies on the model learning on
-past experience to make decisions on future events. Deep learning is a branch of \ac{ML} that takes inspiration from biological processes in the brain.
+past experience to make decisions on future events. Deep learning is a branch of \ac{ML} that takes inspiration from biological processes in the brain \michael{is it?}.
 
@@
 processing units called neurons. The simplest neural network is the perceptron
-layer~\cref{fig:perceptron} which holds a single neuron that takes several real
+layer~\cref{fig:perceptron} which shows a single neuron that takes a vector of real
 inputs $x_{i},\ldots, x_{n}$
@@
 of as the strength between connected neurons.
-The output of a neuron is defined by its activation function which controls how the neuron 'fires" depending on its input.
+The output of a neuron is defined by its activation function which controls how the neuron `fires' depending on its input.
 Some examples of commonly used activation functions are shown in~\cref{fig:activations}.
@@
 A neural network contains many single neurons connected in a layered structure
-as shown in~\cref{fig:network}. The activation's of the first layer (or
+as shown in~\cref{fig:network}. The activations of the first layer (or
 input layer) act as the inputs to the second layer and so on until the output
@@
 prediction that can be compared to the real value through a loss (also known as a
-cost) function. The network must work to minimise this function by updating the weights in the negative
+cost) function. The network is trained to minimise this function by updating the weights in the negative
 direction of the loss gradient in a process referred to as gradient
@@
 This process of updating the weights is repeated until the loss function reaches convergence or a global minimum.
-The training data is cycled through in epochs, where an epoch is defined when the entire data set is fed through the network.
 As it is impractical to feed the entire data into the network at once, the training is split up into smaller more manageable batches.
-Finally, the number of batches needed to compete one epoch is referred to as the iterations.
+For this work we train on random samples from the training data and define an epoch as the number of training steps.
 
@@
 %
-\acp{CNN} are designed to work with grid-like input structures that exhibit
+\acp{CNN} \michael{This is plural twice, something to do with the acronym package} are designed to work with grid-like input structures that exhibit
 strong local spatial dependencies. Although most work with \acp{CNN}
@@
 convolution operation, a mathematical operation that expresses the amount
-overlap between functions.
+overlap between the data.
 Much like traditional neural networks the convolution operation in this context involves multiplying the input by an array of weights, called a filter or a kernel which is typically smaller in size than the input.
@@
 two. The distance by which the grid is shifted is known as
-the stride and increasing it reduces the dimensionality of the
-output in a process know as down sampling.
-Alternatively, up sampling the inputs can be achieved using a transposed convolution \cite{dumoulin2016guide}.
+the stride and increasing it reduces the dimensionality of the output in a process know as downsampling.
+Alternatively, upsampling the inputs can be achieved using a transposed convolution \cite{dumoulin2016guide}.
 The output of the convolutional layer is then passed to an activation function and through the next layers.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{GANs}
+\subsection{Generative Adversarial Networks}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 This simple addition has shown to work well in practice, for instance in image-to-image translation~\cite{isola2016imagetoimage}.
-We defined the classes in one-hot encoding framework, that is, each class resides at the corner points of a 5 dimensional cube.
-For example $\mathbf{c}=[0,1,0,0,0]$ represents the ring-down signal class.
+We defined the classes by one-hot encoding, that is, each class resides at the corner points of a 5 dimensional cube.
+For example $\mathbf{c}=[0,1,0,0,0]$ represents the ringdown signal class.
 The training data and labels are drawn from a joint distribution $p_{\text{data}}(\mathbf{x},\mathbf{c})$, whereas when generating fake data we sample from $\mathbf{c}$ and $p_{\mathbf{z}}(\mathbf{z})$ independently.
-\href{equation:GANloss} is modified to include the class labels
+\cref{equation:GANloss} is modified to include the class labels
 ~
@@
 conditional-GAN method.
-$\textbf{G}$ and $\textbf{D}$ denote the generator and discriminator neural networks respectively while $\textbf{X} \text{real}$ and $\textbf{X} \text{fake}$ represent samples drawn from the training set and the generated set.
+$\textbf{G}$ and $\textbf{D}$ denote the generator and discriminator neural networks respectively while $\textbf{X}~\text{real}$ and $\textbf{X}~\text{fake}$ represent samples drawn from the training set and the generated set.
 For CGANs the training data requires a label denoting
@@
 Ringdown & 70 - 250 & 0.004 - 0.03 & 0.4 - 0.6 & N/A \\
-White-noise burst & 70 - 250 & 0.004 - 0.03 & 0.4 - 0.6 & N/A  \\
+white noise burst & 70 - 250 & 0.004 - 0.03 & 0.4 - 0.6 & N/A  \\
 Gaussian pulse & - & 0.004 - 0.03 & 0.4 - 0.6 & -  \\
@@
 We propose a signal generation scheme using a \ac{CGAN} trained on burst-like
-waveforms. We call this \texttt{BurstGAN} \cite{jordan_git} and is a \ac{CGAN} trained on five signal classes each spanning a range
+waveforms.
+We call this \texttt{BurstGAN} \cite{jordan_git} \michael{Not sure about citing the repo like this, at first I thought it was a reference to an existing paper} and it is a \ac{CGAN} trained on five signal classes each spanning a range
 of prior signal parameters. The signal classes are:
@@
 %
-\item {\bf Ring-down}: $h_{\text{rd}}(t) = A \exp \left[-{(t-t_0)} / {\tau}
+\item {\bf Ringdown}: $h_{\text{rd}}(t) = A \exp \left[-{(t-t_0)} / {\tau}
 \right] \sin(2 \pi f_0 (t-t_0))$, with frequency $f_0$ and duration $\tau$, amplitude, $A$, time of arrival, $t_{0}$. 
 %
-\item {\bf White-noise bursts}: $h_{\text{wn}}(t_j) = Ag_j\exp\left[ -
+\item {\bf White noise bursts}: $h_{\text{wn}}(t_j) = Ag_j\exp\left[ -
 (t-t_{0})^2 / \tau^2 \right]$ where $g_j$ are drawn from a zero mean unit
@@
 %
-\item {\bf Binary-black hole}: Simulated using the IMRPhenomD
+\item {\bf Binary black hole}: Simulated using the IMRPhenomD
 waveform~\cite{Khan_2016} routine from LALSuite~\cite{lalsuite} which models
@@
 index of 1.6~\cite{Abbott_2019}. The inclinations are drawn
-such that the cosine of the angles lies uniformly in the range [-1,1] and we only use the plus polarisation.
+such that the cosine of the angles lies uniformly in the range [-1,1] and we only use the plus polarisation. \michael{What about the other parameters like distance?}
 %
@@
 The location of the peak amplitude of the waveforms (corresponding to the
-mid-points of all but the ring-down and \ac{BBH} classes) are randomly drawn from a uniform distribution to
+mid-points of all but the ringdown and \ac{BBH} classes) are randomly drawn from a uniform distribution to
 be within [0.4, 0.6] seconds from the start of the 1 sec time interval and all
@@
 %
-For this work we use a \ac{DCGAN}~\cite{Radford2015} architecture. The generator model is fully convolutional,
+The design of the networks is influenced by \cite{Radford2015} in which they use a deep convolution generative adversarial network architecture \ac{DCGAN}. The generator model is fully convolutional,
 upsampled using strided transposed convolutions
 with batch normalisation in the
-first layer and ReLU activations throughout with the exception of the Tanh activation for
-the output layer. The use of Tanh guarantees the output function is bound between [-1,1]. Each transposed
+first layer and ReLU activations throughout with the exception of the a linear activation for
+the output layer. The use of a linear activation guarantees the output can have negative and positive outputs. Each transposed
 convolutional layer uses a kernel size of 18 and stride of 2. The discriminator network
@@
 LeakyReLU activations, SpatialDropout, and a 2-stride convolution for
-downsampling. The discriminator output is a single node with Sigmoid activation that can be interpreted as a probability of the the signal being real and both models are trained with binary cross
-entropy. The full architecture description can be seen in~\cref{Tab:hyperparameters}.
+downsampling. The discriminator output is a single node with sigmoid activation that can be interpreted as a probability of the the signal being real and both models are trained with binary cross
+entropy \cref{eqn:crossentropy}. The full architecture description can be seen in~\cref{Tab:gan_training_parms}.
 
@@
 sine-Gaussian,
-ring-down, white noise bursts, Gaussian pulse and \acp{BBH}. \jordan{add how many epochs trained for, on what hardware and how long}
+ringdown, white noise bursts, Gaussian pulse and \acp{BBH}.
+\jordan{add how many epochs trained for, on what hardware and how long} \michael{Might consider moving some of this paragraph to before the previous one as you explain what hyperparameters are having just discussed them}
 
@@
 Accuracy is the number of correct predictions made divided by total number of predictions.
-There is currently no notion of early stopping in \acp{GAN}, instead, training is halted after convergence and by visually inspecting the generations.
+\michael{This sentence seems rather random} There is currently no notion of early stopping in \acp{GAN}, instead, training is halted after convergence and by visually inspecting the generations.
 
@@
 test two methods of sampling from the class space that can be used to generate
-a new breed of signal composed of weighted elements of each training class.
+a new signals composed of weighted elements of each training class.
 
@@
 The latent space inputs for each panel is randomised and each row is assigned one of the five class vectors.
-By row: Sine-Gaussian, Ringdown,
-White-noise burst, Gaussian pulse, Binary black hole merger. On the first four rows each x axis is zoomed for ease of viewing, while the last row shows the full one second.}
+By row: sine-Gaussian, Ringdown,
+white noise burst, Gaussian pulse, binary black hole merger. On the first four rows each x axis is zoomed for ease of viewing, while the last row shows the full one second.}
 \label{fig:gen_signals} 
@@
 
-After training the networks, the generator's function is to map $G$ : $\mathbf{z},\mathbf{c} $ $\in$
+The generator is trained to map $G$ : $\mathbf{z},\mathbf{c} $ $\in$
 $\mathbb{R}^{100}$ $\to$ $\mathbb{R}^{1024}$. The results from the
@@
 The generations show good quality likeliness and good variation within each class representative of the variation of the training data.
-All generations are single plus polarised waveforms and their amplitudes are normalised to unity after generation.
+All generations are single plus polarised waveforms and their amplitudes are re-scaled such that the maximum amplitude is one.
 
@@
 \ac{ML} algorithms are often described as universal function approximators. In
-the case of the generator it maps samples drawn from a 100 dimensional Gaussian
+the case of the generator it maps samples drawn from a 100-dimensional Gaussian
 distribution in the latent space to its representation of the training set. As
-with any function, there should be a one to one mapping from the domain and
-co-domain to allow for smooth transitions across the latent space. Most GANs perform well on relatively low resolution
+with any function, all elements in the domain should map to one elements in the
+co-domain which allows for smooth transitions across the latent space. Most GANs perform well on relatively low resolution
 image generations, however, higher resolutions demand larger networks and long
-training times. GANs attempting to replicate complicated structures and do not
+training times. GANs attempting to replicate complicated structures that do not
 have the necessary architecture either struggle to produce results at all or
@@
 cluster together with respect to their parameters. Visually, the sine-Gaussian
-and ring-down waveforms share similar frequencies and the other signals show
+and ringdown waveforms share similar frequencies and the other signals show
 similar decays and starting epochs for a common latent space input.
@@
     \caption{Generated interpolated waveforms plotted as a function of time.
-The latent space inputs for the first  column is a vector of zeros and last columns are vectors of 0.5.
+For each interpolation two points were randomly chosen in the latent space on the conditional that they lie at unit distance away from the origin.
 Between panels are linearly interpolated vectors between these two points.
-Each row keeps on of the class vetors constant thoughout the latent space interpolation.
-On the first four rows each x axis is zoomed for ease of viewing, while the last row shows the full one second time interval.}
+Each row keeps on of the class vetors constant throughout the latent space interpolation.}
     \label{fig:z_interp}
@@
 
-While the \ac{GAN} is trained on distinct one-hot encoded classes, we may test arbitrary points in the 5-dimensional space to produce indistinct or "inbetween" waveforms.
+While the \ac{GAN} is trained on distinct one-hot encoded classes, we may test arbitrary points in the 5-dimensional class space to produce indistinct or ``inbetween'' waveforms.
 In order to explore the class space we keep the latent vector constant and
 interpolate through the 5 classes. We construct a path between two waveforms
-and show in \cref{fig:c_in	terp} that the space is populated enough to allow for transitions between
+and show in \cref{fig:c_interp} that the space is populated enough to allow for transitions between
 classes.  Sine-Gaussian to ringdown performs well in interpolation with each
@@
 these two groups during training as they share many characteristics. The other
-signals have sharper transitions but still retain plausible looking waveforms.
+signals have sharper transitions but still retain plausible looking waveforms. \michael{Not sure, but we might want more discussion about the other signals}
 
@@
     \includegraphics[width=\textwidth]{figures/generations/blip-bbh.png}
-    \includegraphics[width=\textwidth]{figures/generations/bbh-sg.png}
-    \includegraphics[width=\textwidth]{figures/generations/wnb-bbh.png}
     \caption{Generated class interpolated waveforms as a function of time.
-The latent space vectors are fixed at 0.5 for each entry while each row shows generations using linearly interpolated classes as inputs to the generator.
-By row top to bottom: Sine-Gaussian to Ringdown, Ringdown to White-noise burst, Gaussian pulse to BBH, BBH to Sine-Gaussian, White-noise burst to BBH.}
+A single latent space vector is used for all generations and is chosen randomly in the latent space.
+Each row shows generations using linearly interpolated classes as inputs to the generator.
+By row top to bottom: Sine-Gaussian to Ringdown, Ringdown to white noise burst, Gaussian pulse to BBH.}
     \label{fig:c_interp}
@@
 We have shown that the \acp{GAN} latent space and class space has structure that can be navigated through with interpolation between paris of signals.
-Taken a step further, we can sample from the class space in novel ways to create new inputs for the generator.
+Taking a step further, we can sample from the class space in novel ways to create new inputs for the generator.
 These new points are categorised by the method used to sample from the class space.
@@
 \item {\bf Uniform}: Generated using a uniform distribution U[0,1] as the input
-class vector.
-%
-\item {\bf Simplex}: Generated using a Dirichlet distribution that samples from the
-4-simplex inside the class space.
+class vector. \michael{I don't think it's quite clear what this means}
+%
+\item {\bf Simplex}: Generated using a Dirichlet distribution to sample from the
+4-simplex inside the class space. \michael{Might have to mentioned the k-value (or whatever it is called) for the Dirichlet since it is only uniform for k=1 I think}
 %
@@
 The vertex points are the most straightforward where one entry contains 1 and the other entries are zero and are equivalent to the class vectors that the GAN is trained on e.g.
-$\mathbf{c} = [1,0,0,0,0]$ would correspond to a Sine-Gaussian generation.
-Uniform class vectors sample from a uniform distribution and act like a random draw from the class space.
+$\mathbf{c} = [1,0,0,0,0]$ would correspond to a sine-Gaussian generation.
+Uniform class vectors sampled from a uniform distribution and act like a random draw from the class space.
 Uniformly sampling contains points up to a distance of unit from the closest class e.g.
@@
 
+\begin{comment}
 ~\chris{Also, discuss the corresponding figure! There has to be comment on the
@@
 
+\michael{You could also point to \cref{fig:gen_signals} since you have figures for Uniform and Simplex}
+\end{comment}
+
 \begin{figure}
@@
     \includegraphics[width=\textwidth]{figures/generations/simplex_sample3.png}
+    \includegraphics[width=\textwidth]{figures/generations/simplex_sample4.png}
+    \includegraphics[width=\textwidth]{figures/generations/simplex_sample5.png}
     \caption{GAN generations where the class vectors are sampled from the 4-D
@@
     \centering
+    \includegraphics[width=\textwidth]{figures/generations/uniform_sample1.png}
+    \includegraphics[width=\textwidth]{figures/generations/uniform_sample2.png}
     \includegraphics[width=\textwidth]{figures/generations/uniform_sample3.png}
-    \includegraphics[width=\textwidth]{figures/generations/uniform_sample2.png}
-    \includegraphics[width=\textwidth]{figures/generations/uniform_sample1.png}
+    \includegraphics[width=\textwidth]{figures/generations/uniform_sample4.png}
+    \includegraphics[width=\textwidth]{figures/generations/uniform_sample5.png}
     \caption{GAN generations where the class vectors are sampled uniformly in the hypercube class space.
@@
 \section{Searching for generalised burst using a CNN}
-In this section  we use a convolutional neural network \ac{CNN} 
+In this section  we use a convolutional neural network \ac{CNN} \michael{accronyms?}
 to compare different waveform generations from the \ac{CGAN} to help determine the
@@
 \subsection{Training data} 
-We use three classes of training data: Vertex, Uniform or Simplex cases generated using our \ac{GAN} method and consider two detectors H1 and L1 as joint inputs to the \ac{CNN}.
+We use three classes of training data: vertex, uniform or simplex cases generated using our \ac{GAN} method and consider two detectors H1 and L1 as joint inputs to the \ac{CNN}.
 For each training set we generated a bank of $2\times 10^5$ signals and apply antenna responses and time delays using routines provided by LALsuite \cite{lalsuite}.
-The polarisation angles are drawn uniformly in the range [0,2$\pi$] and sky positions are generated uniformly on the 2-sphere.
+The polarisation angles are drawn uniformly in the range $[0,2\pi]$ and sky positions are generated uniformly on the 2-sphere \michael{Could instead say they are sampled isotropically}.
 Time delays between detectors are computed relative to the Earth centre.
@@
 \subsection{CNN architecture}
-In this approach the input to the \ac{CNN} is a two dimensional vector which is passed through a series of convolutional layers, onto two fully connected or ''Dense" layers and finally to a single output neuron which represents the probability that a signal is present within the noise.
-We used a small amount of dropout and found that the swish activation \cite{ramachandran2017searching} function performed well.
+In this approach the input to the \ac{CNN} is a 2x1024 time series which is passed through a series of convolutional layers, onto two fully connected or ``Dense'' layers and finally to a single output neuron which represents the probability that a signal is present within the noise.
+We used a small amount \michael{rather in-precise} of dropout and found that the swish activation \cite{ramachandran2017searching} function performed well.
 The output layer is activated by a sigmoid function and we used \cref{eqn:crossentropy} as a loss function and Adam as an optimizer with learning rate set to $10^{-3}$.
-In total we train three separate \acp{CNN} on either the vertex, uniform or simplex data set, however, all \acp{CNN} share the same architectural
-structure and hyperparameters which are shown in \cref{Tab:cnn_training_parms}.
+In total we train three separate \acp{CNN} on either the vertex, uniform or simplex data set share the same architecture and hyperparameters which are shown in \cref{Tab:cnn_training_parms}.
 
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{figures/conditional_trained.png}
-    \includegraphics[width=0.8\textwidth]{figures/simplex_trained.png}
-    \includegraphics[width=0.8\textwidth]{figures/uniform_trained.png}
+    \includegraphics[width=\textwidth]{figures/conditional_trained.png}
+    \includegraphics[width=\textwidth]{figures/simplex_trained.png}
+    \includegraphics[width=\textwidth]{figures/uniform_trained.png}
     \caption{Efficiency curves comparing the performance of \acp{CNN} trained on
 conditional generations (top), simplex generations (middle), uniform
-generations (bottom) for a fixed false alarm rate of $10^{-3}$.~\chris{more
-description. What is plotted against what? The fonts are different to the other
-plots. The y-axis is not a rate but a prbability (a FAP unfortunately)}}
+generations (bottom) for a fixed false alarm rate of $10^{-3}$. The true alarm probability is plotted as a function of the optimal SNR of the signals.}
 \label{fig:roc_curves} 
@@
 robust enough to capture the differences between the datasets and shows that
-the GAN can generate a variety of unmodelled waveforms that can be used in
+the GAN can generate a variety of unmodeled waveforms that can be used in
 future testing.
 
+\begin{comment}
 ~\chris{please write more about the results of the CNN}
+\end{comment}
 
@@
 waveform shape. We then showed targeted waveform generation by mixing classes
-to produce new unmodelled waveform varieties that can be used to test current
+to produce new unmodeled waveform varieties that can be used to test current
 burst search pipelines.
@@
 generate new waveforms is essential to test current detection schemes and their
-susceptibilty to unmodelled sources. We believe that \acp{GAN} have the ability
+susceptibilty to unmodeled sources. We believe \michael{we've shown this!} that \acp{GAN} have the ability
 to generate high fidelity waveforms at a fraction of the computational
@@
 ~\chris{we need to write down paragrph headinsg in the next meeting. I'm tired.}
+
+\michael{We need longer conclusions but I think you're working on this}
 
@@
 \caption{The architecture and hyperparameters describing our CNN consists of four convolutional layers followed by two dense layers.
-The convolutional layers are activated by the swish function, the first dense layer is not activated and dropout is applied, while the final layer uses the sigmoid activation.
+The convolutional layers are activated by the swish function, the first dense layer is not activated \michael{really?
+that doesn't make sense to me} and dropout is applied, while the final layer uses the sigmoid activation.
 The network is trained by minimising the binary cross entropy and optimised with Adam with learning rate $10^{-3}$.
@@
 Dense & (100) & 100 & N/A & 0.2 & Linear  \\
-Dense & (1) & 1 & N/A & 0 & Sigmoid \\
+Dense & (1) & 1 & N/A & 0 & sigmoid \\
 \end{tabular*}\\
@@
 This is then downsampled through four convolutional layers all activated by Leaky ReLU functions add drops half of the connections at the end of each of these layers.
-The vector is then flattened to one dimension before fully connecting to a single neuron and its output activated by sigmoid to represent the probability the signal came from the training set.
+The vector is then flattened to one dimension before fully connecting to a single neuron and its output activated by sigmoid \michael{you some times capitalise this and other time don't} to represent the probability the signal came from the training set.
 The generator concatenates the latent and class input vectors which is fed to a fully connected layer.
 This layer is then upsampled by four tranposed convolutions.
-The output of the first layer is batch normalised (BN) and all convolutional layer are activated by ReLU with the exception of the final layer which is Linear.
-Finally, the extra dimension introduced for the convolution is removed.}
+The output of the first layer is batch normalised (BN) \michael{personally don't like make this into a verb, maybe \textit{batch normalisation is applied to the output of the first layer}}and all convolutional layers are activated by ReLU with the exception of the final layer which is Linear.
+Finally, the extra dimension introduced for the convolution is removed.
+\michael{Is the batchsize right?
+You mentioned 32 the other day.
+I guess this might need updating are the whitening changes.}}
 %\footnotesize
@@
 Flatten & (32768) & N/A & N/A & 0 &  N/A \\
-Dense & (1) & N/A & N/A & 0 & Sigmoid \\
+Dense & (1) & N/A & N/A & 0 & sigmoid \\
 \mr

### 2020-11-05 Paper_draft/main.tex
new gan/cnn results

@@
     \caption{Generated interpolated waveforms plotted as a function of time.
-For each interpolation two points were randomly chosen in the latent space on the conditional that they lie at unit distance away from the origin.
-Between panels are linearly interpolated vectors between these two points.
+For each interpolation two points were randomly chosen in the latent space and the between panels are linearly interpolated vectors between these two points.
 Each row keeps on of the class vetors constant throughout the latent space interpolation.}
@@
 %
-\item {\bf Uniform}: Generated using a uniform distribution U[0,1] as the input
-class vector. \michael{I don't think it's quite clear what this means}
-%
-\item {\bf Simplex}: Generated using a Dirichlet distribution to sample from the
-4-simplex inside the class space. \michael{Might have to mentioned the k-value (or whatever it is called) for the Dirichlet since it is only uniform for k=1 I think}
+\item {\bf Uniform}: Each of the entries in the class vector is sampled from a uniform distribution U[0,1].
+
+%
+\item {\bf Simplex}: This class vector we define as uniformly sampled points on a simplex, which is a generalization of a triangle in k-dimensions.
+We sample uniformly on the k=4 simplex that is embedded in the 5 dimensional class hyper cube.
+In practice we use the equivalent of sampling points from a k=4 Dirichlet distribution and then normalizing.
 %
@@
 In this approach the input to the \ac{CNN} is a 2x1024 time series which is passed through a series of convolutional layers, onto two fully connected or ``Dense'' layers and finally to a single output neuron which represents the probability that a signal is present within the noise.
-We used a small amount \michael{rather in-precise} of dropout and found that the swish activation \cite{ramachandran2017searching} function performed well.
+We used dropout in the final dense layer and found that the swish activation \cite{ramachandran2017searching} function performed well.
 The output layer is activated by a sigmoid function and we used \cref{eqn:crossentropy} as a loss function and Adam as an optimizer with learning rate set to $10^{-3}$.
@@
 
-In~\cref{fig:roc_curves} we compare the \ac{CNN} results between the three
-datasets, we train three \acp{CNN} on the Conditional, simplex and uniform data sets
+\subsection{Results}
+In~\cref{fig:eff_curves} we compare the \ac{CNN} results between the three
+datasets, we train three \acp{CNN} on the vertex, simplex and uniform data sets
 and use these models to make predictions on the other unseen datasets. We make
@@
 
-\begin{figure}
-    \centering
-    \includegraphics[width=\textwidth]{figures/conditional_trained.png}
-    \includegraphics[width=\textwidth]{figures/simplex_trained.png}
-    \includegraphics[width=\textwidth]{figures/uniform_trained.png}
-    \caption{Efficiency curves comparing the performance of \acp{CNN} trained on
-conditional generations (top), simplex generations (middle), uniform
-generations (bottom) for a fixed false alarm rate of $10^{-3}$. The true alarm probability is plotted as a function of the optimal SNR of the signals.}
-\label{fig:roc_curves} 
-\end{figure}
-
-These results show for a \ac{CNN} trained on conditional signals, the uniform data
-set is distinguishable from the conditional and simplex dataset. The \ac{CNN} is
+These results show for a \ac{CNN} trained on vertex signals, the uniform data
+set is distinguishable from the vertex and simplex dataset. The \ac{CNN} is
 robust enough to capture the differences between the datasets and shows that
@@
 
+\begin{itemize}
+    \item vertex trained shows clear delineation from other two classes at snr$>$10. Good to show that they are different. But not all converge to 1.
+    \item simplex trained leads in smaller snrs but eventually all converge to 1
+    \item uniform trained shows much similarity to simplex test set, still different from vertex.
+all converge to 1.
+makes sense if the vertex is a subset of the simplex and uniform classes.
+Also a sign that the GAN likes to keep things as close to vertex as possible?
+\end{itemize}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.7\textwidth]{figures/conditional_trained.png}
+    \includegraphics[width=0.7\textwidth]{figures/simplex_trained.png}
+    \includegraphics[width=0.7\textwidth]{figures/uniform_trained.png}
+    \caption{Efficiency curves comparing the performance of \acp{CNN} trained on
+vertex generations (top), simplex generations (middle), uniform
+generations (bottom) for a fixed false alarm rate of $10^{-3}$. The true alarm probability is plotted as a function of the optimal SNR of the signals.}
+\label{fig:eff_curves} 
+\end{figure}
+
 \begin{comment}
@@
 burst \ac{GW} analysis.
-We have shown that \acp{GAN} have the ability to generate realisitc time series burst data and can be conditioned based on the inherent features of the signals.
+We have shown that \acp{GAN} have the ability to generate realistic time series burst data and can be conditioned based on the inherent features of the signals.
 The latent and class spaces were explored through interpolation and
@@
 
-% extra things to think about
-%
+We then considered three cases of unmodelled generated signals in Gaussian noise and demonstrated that a simple \ac{CNN} could distinguish between them. 
+In contrast to typical approaches in signal generation this is the first time a GAN has been used for generating gravitational wave burst data.
+In the future, as development in GANs and generative machine learning advances it is possible that we can gain greater control over target generation of features.
+Going forward it will also be important to extend our models to treat longer waveforms, higher sampling rates and generations other classes such as detector glitches.
 
@@
 generate new waveforms is essential to test current detection schemes and their
-susceptibilty to unmodeled sources. We believe \michael{we've shown this!} that \acp{GAN} have the ability
-to generate high fidelity waveforms at a fraction of the computational
-expense~\chris{don't focus on the expense part since burst waveforms are cheap
-anyway} and do not rely on large prior parameter space. Having banks of these
+susceptibilty to unmodeled sources. We have shown that \acp{GAN} have the ability
+to generate high fidelity waveforms which do not rely on large prior parameter space. Having banks of these
 waveforms at hand can aid in our understand of the physics processes behind
 these non-standard ac{GW} emitters.
-~\chris{we need to write down paragrph headinsg in the next meeting. I'm tired.}
-
-\michael{We need longer conclusions but I think you're working on this}
 
@@
  Loss & Binary cross-entropy \\
+ \mr
  \br

### 2020-11-11 Paper_draft/main.tex
more words

@@
 \usepackage{hyperref}
+\usepackage{bibentry}
 \usepackage[capitalize]{cleveref}
@@
 %
-\ac{GW} astronomy is now an established field, starting with the first
+Gravitational wave astronomy is now an established field that began with the first
 detection of a binary black hole merger~\cite{Abbott2016} in September 2015.
@@
 matched-filtering,~\cite{Owen1998,Usman_2016,sachdev2019gstlal}, where a large template bank of possible
-\ac{GW} waveforms are compared to the detector outputs. In order to increase
-the chances of detection these template banks must span a large
-multi-dimensional parameter space requiring
-significant computational cost \michael{Do the template banks need to large to increase the chance or to cover the complete range of possible signals we expect?}.
-\jordan{Do they cover the complete range?} \michael{I think they have something like 97\% coverage, I know the number of templates depends on the coverage you want.
-Might we worth asking Chris and Siong}For \ac{GW} bursts that remain unmodeled; there are no
+\ac{GW} waveforms are compared to the detector outputs. For \ac{GW} bursts that remain unmodeled; there are no
 templates available and so matched-filtering is unsuitable for the detection of
@@
 processes occur during training, once trained, the model is able to
-generate waveforms in fractions of a second and produce waveforms that are difficult to geenrate with current
+generate waveforms in fractions of a second and produce waveforms that are difficult to generate with current
 techniques. These new varieties of waveforms can then be used to diagnose
@@
 %
-This paper is organised as follows: \jordan{unstructured at the
-moment}~\chris{time to add the structure.}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Generative Adversarial Networks}
+This paper is organised as follows.
+In \cref{ML overview} we introduce the basic ideas of machine learning and discuss the choice of algorithm we used.
+In \cref{Method} we describe the training data and the details of the model.
+We present the results of the GAN in \cref{results} and show how unmodeled signals can be produced by interpolating and sampling within latent and class spaces.
+In \cref{cnn classifier} we show that a convolutional neural network classifier can be trained to distinguish between sets of our GAN generated waveforms from noise only cases.
+We conclude with a summary of the presented work in \cref{conclusions}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Machine learning} \label{ML overview}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\ac{ML} algorithms aim to learn apparent relationships held within given data or `training
-data' in order to make accurate predictions without the need for additional
-programming. A common approach in \ac{ML} relies on the model learning on
-past experience to make decisions on future events. Deep learning is a branch of \ac{ML} that takes inspiration from biological processes in the brain \michael{is it?}.
-
 % Introduce basic neural networks - a perceptron layer
@@
 
-Artificial neural networks are universal function approximators that are built from many single
+\ac{ML} algorithms aim to learn apparent relationships held within given data or `training
+data' in order to make accurate predictions without the need for additional
+programming. A common approach in \ac{ML} relies on the model learning on
+past experience to make decisions on future events. Artificial neural networks are universal function approximators that are built from many single
 processing units called neurons. The simplest neural network is the perceptron
@@
 %
-\acp{CNN} \michael{This is plural twice, something to do with the acronym package} are designed to work with grid-like input structures that exhibit
+Convolutional neural networks (CNNs) are designed to work with grid-like input structures that exhibit
 strong local spatial dependencies. Although most work with \acp{CNN}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Methodology}
+\section{Training data and architecture} \label{Method}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 We propose a signal generation scheme using a \ac{CGAN} trained on burst-like
-waveforms.
-We call this \texttt{BurstGAN} \cite{jordan_git} \michael{Not sure about citing the repo like this, at first I thought it was a reference to an existing paper} and it is a \ac{CGAN} trained on five signal classes each spanning a range
+waveforms. We call this \texttt{McGANn}\footnote{https://github.com/jmcginn/McGANn} and it is a \ac{CGAN} trained on five signal classes each spanning a range
 of prior signal parameters. The signal classes are:
@@
 \item {\bf Sine-Gaussian}: $h_{\text{sg}}(t) = A \exp\left[ - (t-t_{0})^2 /
-\tau^2 \right] \sin (2 \pi f_0 (t-t_0))$, a sinusoidal wave with a Gaussian
-envelope characterised by a central frequency, $f_0$, amplitude, $A$, time of arrival, $t_{0}$. 
+\tau^2 \right] \sin (2 \pi f_0 (t-t_0) + \phi)$, a sinusoidal wave with a Gaussian
+envelope characterised by a central frequency, $f_0$, amplitude, $A$, time of arrival, $t_{0}$ and phase, $\phi$ which is uniformly sampled between [0,2$\pi$]. 
 %
 \item {\bf Ringdown}: $h_{\text{rd}}(t) = A \exp \left[-{(t-t_0)} / {\tau}
-\right] \sin(2 \pi f_0 (t-t_0))$, with frequency $f_0$ and duration $\tau$, amplitude, $A$, time of arrival, $t_{0}$. 
+\right] \sin(2 \pi f_0 (t-t_0) + \phi)$, with frequency $f_0$ and duration $\tau$, amplitude, $A$, time of arrival, $t_{0}$, $\phi$ which is uniformly sampled between [0,2$\pi$. 
 %
@@
 index of 1.6~\cite{Abbott_2019}. The inclinations are drawn
-such that the cosine of the angles lies uniformly in the range [-1,1] and we only use the plus polarisation. \michael{What about the other parameters like distance?}
+such that the cosine of the angles lies uniformly in the range [-1,1] and we only use the plus polarisation.
 %
@@
 %
-The design of the networks is influenced by \cite{Radford2015} in which they use a deep convolution generative adversarial network architecture \ac{DCGAN}. The generator model is fully convolutional,
-upsampled using strided transposed convolutions
-with batch normalisation in the
-first layer and ReLU activations throughout with the exception of the a linear activation for
-the output layer. The use of a linear activation guarantees the output can have negative and positive outputs. Each transposed
-convolutional layer uses a kernel size of 18 and stride of 2. The discriminator network
-mirrors that of the generator without batch normalization, using
-LeakyReLU activations, SpatialDropout, and a 2-stride convolution for
-downsampling. The discriminator output is a single node with sigmoid activation that can be interpreted as a probability of the the signal being real and both models are trained with binary cross
-entropy \cref{eqn:crossentropy}. The full architecture description can be seen in~\cref{Tab:gan_training_parms}.
-
 % describe the hyperparameter tunings
@@
 ringdown, white noise bursts, Gaussian pulse and \acp{BBH}.
-\jordan{add how many epochs trained for, on what hardware and how long} \michael{Might consider moving some of this paragraph to before the previous one as you explain what hyperparameters are having just discussed them}
-
-As \acp{GAN} are trained by updating one model at the expense of the other, they can be hard to train.
+
+The design of the networks is influenced by \cite{Radford2015} in which they use a deep convolution generative adversarial network architecture \ac{DCGAN}. The generator model is fully convolutional,
+upsampled using strided transposed convolutions
+with batch normalisation in the
+first layer and ReLU activations throughout with the exception of the a linear activation for
+the output layer. The use of a linear activation guarantees the output can have negative and positive outputs. Each transposed
+convolutional layer uses a kernel size of 18 and stride of 2. The discriminator network
+mirrors that of the generator without batch normalization, using
+LeakyReLU activations, SpatialDropout, and a 2-stride convolution for
+downsampling. The discriminator output is a single node with sigmoid activation that can be interpreted as a probability of the the signal being real and both models are trained with binary cross
+entropy \cref{eqn:crossentropy}. The full architecture description can be seen in~\cref{Tab:gan_training_parms}.
+
+As \acp{GAN} are trained by updating one model at the expense of the other, they can be hard to train. GANs attempting to replicate complicated structures that do not
+have the necessary architecture either struggle to produce results at all or
+fall into the common failure mode know as mode collapse; where the generator
+produces a small variety of samples or simply memorises the training set.
 The goal of GAN training is to find an equilibrium between the two models, if this cannot be found then it is said that the \ac{GAN} has failed to converge.
@@
 Accuracy is the number of correct predictions made divided by total number of predictions.
-\michael{This sentence seems rather random} There is currently no notion of early stopping in \acp{GAN}, instead, training is halted after convergence and by visually inspecting the generations.
+There is currently no notion of early stopping in \acp{GAN}, instead, training is halted after convergence and by visually inspecting the generations.
+
+All models were designed with the Python Keras library \cite{} and TensorFlow \cite{} and ran on a GeForce RTX 2080 Ti GPU.
+We train the networks for 500 epochs which takes $\mathcal{O}(10)$ hours and save the model at each epoch.
+We choose an appropriate model by visually inspecting the generations at a point of convergence on the loss plot.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Results}
+\section{Results} \label{results}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Known class signal generation}
+In \cref{fig:gen_signals} we show conditional signal generations using our generator network.
+We can see the generations are of very good quality and appear like they could plausibly have come from the training set.
+We can also see that the model has learned the overall characteristics of the five training classes and is able to disentangle each class and associate them with the conditional input.
+Additionally, as the latent variable changes as do the parameters within each class.
+For instance \cref{fig:gen_signals} shows how signals vary in frequency, central epoch, decays and phase.
+The GANs ability to generate a variety of signals for various latent input indicate stable training and no mode collapse.
+
 \begin{figure}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Known class signal generation}
-
-The generator is trained to map $G$ : $\mathbf{z},\mathbf{c} $ $\in$
-$\mathbb{R}^{100}$ $\to$ $\mathbb{R}^{1024}$. The results from the
-generator can be seen in \cref{fig:gen_signals}. Each plot shows the output of
-the generator for random input latent space vectors $\mathbf{z}$ and each row
-corresponds to one of the five class vectors $\mathbf{c}$.
-The generations show good quality likeliness and good variation within each class representative of the variation of the training data.
-All generations are single plus polarised waveforms and their amplitudes are re-scaled such that the maximum amplitude is one.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Interpolation within the latent space}
@@
 %
-\ac{ML} algorithms are often described as universal function approximators. In
-the case of the generator it maps samples drawn from a 100-dimensional Gaussian
-distribution in the latent space to its representation of the training set. As
-with any function, all elements in the domain should map to one elements in the
-co-domain which allows for smooth transitions across the latent space. Most GANs perform well on relatively low resolution
-image generations, however, higher resolutions demand larger networks and long
-training times. GANs attempting to replicate complicated structures that do not
-have the necessary architecture either struggle to produce results at all or
-fall into the common failure mode know as mode collapse; where the generator
-produces a small variety of samples or simply memorises the training set. To
-test this, we perform linear interpolations in the latent and class
-space. We take two random
-points in the 100-dimensional latent space and linearly interpolate between them.
-These new interpolated latent space vectors along with class vectors can now be fed into the generator to produce interpolated waveforms.
-\cref{fig:z_interp} shows the generated waveforms, with the class vectors held constant along each row.
-We can see that each plot shows plausible waveforms suggesting that
-the generator has constructed a smooth traversable, space. Additionally, as each class is given
-the same latent points to interpolate over, we can see that the waveforms
-cluster together with respect to their parameters. Visually, the sine-Gaussian
-and ringdown waveforms share similar frequencies and the other signals show
-similar decays and starting epochs for a common latent space input.
+ We have shown that the generator produces quality signals and that the model responds well to randomly sampled Gaussian latent vectors.
+We now assume that during training the generator has learned a mapping from a Gaussian latent space to signal space and that this mapping is smooth.
+To test this, we fix the class vector input and linearly interpolate between two randomly chosen point in the latent space.
+In \cref{fig:z_interp} we show the generated waveforms, with the class vectors held constant along each row.
+We can see that each plot shows plausible waveforms suggesting that the generator has constructed a smooth traversable, space.
 
@@
 
-While the \ac{GAN} is trained on distinct one-hot encoded classes, we may test arbitrary points in the 5-dimensional class space to produce indistinct or ``inbetween'' waveforms.
+While the \ac{GAN} is trained on distinct one-hot encoded classes, we may test arbitrary points in the 5-dimensional class space to produce indistinct or hybrid waveforms.
 In order to explore the class space we keep the latent vector constant and
@@
 these two groups during training as they share many characteristics. The other
-signals have sharper transitions but still retain plausible looking waveforms. \michael{Not sure, but we might want more discussion about the other signals}
+signals have sharper transitions but still retain plausible looking waveforms.
 
@@
 $\mathbf{c} = [1,0,0,0,0]$ would correspond to a sine-Gaussian generation.
-Uniform class vectors sampled from a uniform distribution and act like a random draw from the class space.
+Uniform class vectors sampled from a uniform distribution and act like a random draw from the five dimensional hypercube.
 Uniformly sampling contains points up to a distance of unit from the closest class e.g.
@@
 Sampling from the simplex can be seen as sampling from between the classes within the space.
-We can expect a priori that the uniformly sampled space (which contains the simplex as a subspace) will allow for some level of extrapolation.
+
+In \cref{fig:simplexd_samples} we show generations conditioned on class vectors drawn from the 4-simplex.
+There are large variations in the signals with some looking like definitive classes, although this can be partially explained through the random draws from the simplex as there is finite probability that one class entry will dominate over the others.
+For instance the generations that look more like sine-Gaussians than unmodeled generally have a larger value placed in the first entry than others.
+Similarly \cref{fig:uniform_samples} shows generations conditioned on class vectors drawn uniformly in the unit hypercube.
+These types of generations tend to exhibit more noise and some are very low amplitude before being re-scaled.
+Artifacts like the signal not lining up to zero on the y axis is a result of re-scaling a particularly low amplitude signal.
+Both methods of generating unmodeled data, however, do show signals that look unrelated to the training data.
 
@@
 the GAN likes to mix signals up. Pick on specific examples and comment on
-interesting or annoying features.}
+interesting or annoying features.We can expect a priori that the uniformly sampled space (which contains the simplex as a subspace) will allow for some level of extrapolation.}
 
 \michael{You could also point to \cref{fig:gen_signals} since you have figures for Uniform and Simplex}
+
+~\chris{I have an idea for the plots. Could we have a colour coding system
+where each class gets a colour and then when you mix them you plot it with the
+mixed colours - you average the RGB values. Maybe everything would look brown?
+Worth a try?}
 \end{comment}
@@
     \caption{GAN generations where the class vectors are sampled from the 4-D
-plane intersecting all classes. Latent space locations for all signals are taken randomly from a Gaussian distribution and the signals are then re-scaled such that they peak at unity.}
+plane intersecting all classes.
+Latent space locations for all signals are taken randomly from a Gaussian distribution and the signals are then re-scaled such that they peak at unity.
+The class label for each generation is shown above each pannel.}
     \label{fig:simplexd_samples}
@@
 
-~\chris{I have an idea for the plots. Could we have a colour coding system
-where each class gets a colour and then when you mix them you plot it with the
-mixed colours - you average the RGB values. Maybe everything would look brown?
-Worth a try?}
-
-\section{Searching for generalised burst using a CNN}
-In this section  we use a convolutional neural network \ac{CNN} \michael{accronyms?}
+\section{CNN burst classifier} \label{cnn classifier}
+In this section  we use a \ac{CNN}
 to compare different waveform generations from the \ac{CGAN} to help determine the
@@
 For each training set we generated a bank of $2\times 10^5$ signals and apply antenna responses and time delays using routines provided by LALsuite \cite{lalsuite}.
-The polarisation angles are drawn uniformly in the range $[0,2\pi]$ and sky positions are generated uniformly on the 2-sphere \michael{Could instead say they are sampled isotropically}.
+The polarisation angles are drawn uniformly in the range $[0,2\pi]$ and sky positions are sampled isotropically.
 Time delays between detectors are computed relative to the Earth centre.
@@
 
-These results show for a \ac{CNN} trained on vertex signals, the uniform data
-set is distinguishable from the vertex and simplex dataset. The \ac{CNN} is
+These results for a \ac{CNN} trained on vertex signals shows clear delineation from other two classes at snr$>$10.
+For the simplex trained network, the simplex dataset narrowly outperforms the other two sets and, finally, the uniform trained network shows similar performance on all datasets.
+The \ac{CNN} is
 robust enough to capture the differences between the datasets and shows that
@@
 
-\begin{comment}
-~\chris{please write more about the results of the CNN}
-\end{comment}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Conclusions}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Conclusions}\label{conclusions}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \caption{The architecture and hyperparameters describing our CNN consists of four convolutional layers followed by two dense layers.
-The convolutional layers are activated by the swish function, the first dense layer is not activated \michael{really?
-that doesn't make sense to me} and dropout is applied, while the final layer uses the sigmoid activation.
+The convolutional and dense layers are activated by the swish function and dropout is applied, while the final layer uses the sigmoid activation.
 The network is trained by minimising the binary cross entropy and optimised with Adam with learning rate $10^{-3}$.
-We train for 10 epochs with a batch size of 1000.}
+We train for 100 epochs with a batch size of 1000.}
 %\footnotesize
@@
 This is then downsampled through four convolutional layers all activated by Leaky ReLU functions add drops half of the connections at the end of each of these layers.
-The vector is then flattened to one dimension before fully connecting to a single neuron and its output activated by sigmoid \michael{you some times capitalise this and other time don't} to represent the probability the signal came from the training set.
+The vector is then flattened to one dimension before fully connecting to a single neuron and its output activated by sigmoid to represent the probability the signal came from the training set.
 The generator concatenates the latent and class input vectors which is fed to a fully connected layer.
 This layer is then upsampled by four tranposed convolutions.
-The output of the first layer is batch normalised (BN) \michael{personally don't like make this into a verb, maybe \textit{batch normalisation is applied to the output of the first layer}}and all convolutional layers are activated by ReLU with the exception of the final layer which is Linear.
-Finally, the extra dimension introduced for the convolution is removed.
-\michael{Is the batchsize right?
-You mentioned 32 the other day.
-I guess this might need updating are the whitening changes.}}
+Batch normalisation is applied to the output of the first layer and all convolutional layers are activated by ReLU with the exception of the final layer which is Linear.
+Finally, the extra dimension introduced for the convolution is removed.}
 %\footnotesize

### 2020-11-12 Paper_draft/main.tex
Updates from Overleaf

@@
 \end{figure}
-
+%
 % Introduce basic neural networks - a perceptron layer
@@
 A subset of deep learning that has seen fruitful development in recent years
-are \acp{GAN}~\cite{Goodfellow2014}. These unsupervised algorithms learn patterns in a
+are generative adversarial networks \acp{GAN}~\cite{Goodfellow2014}. These unsupervised algorithms learn patterns in a
 given training data set using an adversarial process. The generations from
@@
 generations~\cite{esteban2017realvalued}.
-
+%
 % Basic components of a GAN
@@
 generator (fake).
-
 \begin{comment}
@@
 \end{comment}
-
+%
 % training a GAN
 %
-During training, the discriminator and generator are updated in parallel using batches of data.
+During training, the discriminator and generator are updated using batches of data.
 Random latent vectors are given to the generator to produce a batch of fake samples and an equal batch of real samples is taken from the training data.
 The discriminator makes predictions on the real and fake samples and the model is updated through minimising the binary cross-entropy function \cite{Goodfellow-et-al-2016}
-
+%
 \begin{equation}
@@
 This gives the \ac{GAN} loss as
-
+%
 \begin{equation}
@@
 where $p_{\text{\text{data}}}(\mathbf{x})$ is the distribution of real data and $p_{\text{z}}(\mathbf{z})$ is the distribution of the latent space. 
+\begin{figure}[!h]
+    \centering
+    \includegraphics{figures/BCE-loss.png}
+    \caption{Binary cross-entropy plotted as a function of possible predicted probabilities in the case where the true label $y$ is 1 for a sample size of 512.}
+    \label{fig:BCE_loss}
+\end{figure}
+\subsection{Training stages}
+%
+Training a GAN is involves updating both the discriminator and generator in stages.
+First, the discriminator is updated on real instances from the training set.
+We set the true label $y=1$ and calculate the loss with respect to the predictions $\hat{y}$ via \cref{equation:GANloss}.
+Stochastic gradient descent is used to minimize the loss which has reduced to $L_D(\textrm{real}) = -\log(\hat{y})$.
+The discriminator is then trained on fake instances taken from the generator where we set $y=0$ and minimize $L_D(\textrm{fake}) = -\log(1-\hat{y})$.
+To train the generator, we use a composite model of the generator and discriminator and allow the gradients to flow through this entire model.
+At this step we set the labels for the generator as real $y=1$ and minimize $L_G = -\log(\hat{y})$.
+The act of switching the labels and minimizing this form of loss is identical to the previously mentioned generator loss but is beneficial as in practice this function provides more useful gradients.
+This tweak to the generator loss is called non-saturating generator loss and was reported in the original GAN paper \cite{Goodfellow2014}.
+It was also shown in that paper that if the generator and discriminator can no longer improve, then the discriminator can no longer distinguish between real and fake i.e.
+$D(x) = \frac{1}{2}$.
+In \cref{fig:BCE_loss} we show how the binary-cross entropy varies with probability inputs when the real label is set to 1.
+We can see that for optimal training of the discriminator of 0.5 the binary cross entropy sits around 0.7.
+One could then say that the optimal generator loss during training is 0.7 however in practice the generator loss may be higher due to the continually alternating training method.
+
+As \acp{GAN} are trained by updating one model at the expense of the other, they can be hard to train. GANs attempting to replicate complicated structures that do not
+have the necessary architecture either struggle to produce results at all or
+fall into the common failure mode know as mode collapse; where the generator
+produces a small variety of samples or simply memorises the training set.
+The goal of GAN training is to find an equilibrium between the two models, if this cannot be found then it is said that the \ac{GAN} has failed to converge.
+One way to diagnose \acp{GAN} during the development process is to keep track of the loss and accuracy over time.
+Loss plots, for example, as seen in \cref{fig:lossplot} can help to identify common failure modes or to check if the \ac{GAN} has indeed converged.
+Accuracy is another metric that may be used to monitor convergence and is defined as the number of correct predictions made divided by total number of predictions.
+There is currently no notion of early stopping in \acp{GAN}, instead, training is halted after convergence and by visually inspecting the generations.
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width=0.85\textwidth]{figures/losses.png}
+    \caption{Plot of the discriminator and generator loss and accuracy as a function of epochs.
+Early in training the losses oscillates as both models attempt to find their equilibrium, after which, both losses vary around a point which signifies stable training.
+Accuracy's on the real and fake data are similar showing that neither model is stronger than the other.}
+    \label{fig:lossplot}
+\end{figure}
 
@@
 %
-
-\begin{table}[hb]
+\begin{figure}
+    \centering
+    \includegraphics[width=\textwidth]{figures/training-sample.png}
+    \caption{Examples of the five different waveforms that were used in training the \ac{GAN} for this study.
+Values of the parameters were selected randomly from uniform distributions from \cref{Tab:hyperparameters}.}
+    \label{fig:training_waveforms}
+\end{figure}
+% introduce the signal models
+%
+We propose a signal generation scheme using a \ac{CGAN} trained on burst-like
+waveforms. We call this \texttt{McGANn}\footnote{https://github.com/jmcginn/McGANn} and it is a \ac{CGAN} trained on five signal classes each spanning a range
+of prior signal parameters. The signal classes are:
+
+% list the 5 waveform classes
+%
+\begin{itemize}
+%
+\item {\bf Sine-Gaussian}: $h_{\text{sg}}(t) = A \exp\left[ - (t-t_{0})^2 /
+\tau^2 \right] \sin (2 \pi f_0 (t-t_0) + \phi)$, a sinusoidal wave with a Gaussian
+envelope characterised by a central frequency, $f_0$, amplitude, $A$, time of arrival, $t_{0}$ and phase, $\phi$ which is uniformly sampled between [0,2$\pi$]. 
+%
+\item {\bf Ringdown}: $h_{\text{rd}}(t) = A \exp \left[-{(t-t_0)} / {\tau}
+\right] \sin(2 \pi f_0 (t-t_0) + \phi)$, with frequency $f_0$ and duration $\tau$, amplitude, $A$, time of arrival, $t_{0}$, $\phi$ which is uniformly sampled between [0,2$\pi$. 
+%
+\item {\bf White noise bursts}: $h_{\text{wn}}(t_j) = Ag_j\exp\left[ -
+(t-t_{0})^2 / \tau^2 \right]$ where $g_j$ are drawn from a zero mean unit
+variance Gaussian distribution with a Gaussian envelope of duration $tau$.
+%
+\item {\bf Gaussian pulse}: $h_{\text{gp}}(t) = \exp(-t^2 / \tau^2)$ with
+duration parameter $\tau$.
+%
+\item {\bf Binary black hole}: Simulated using the IMRPhenomD
+waveform~\cite{Khan_2016} routine from LALSuite~\cite{lalsuite} which models
+the inspiral, merger and ringdown of a \ac{BBH} waveform. The component masses
+lie in the range of [30,70] $\textrm{M}_{\odot}$ with zero spins and we fix
+$m_1>m_2$. The mass distribution is approximated by a power law with
+index of 1.6~\cite{Abbott_2019}. The inclinations are drawn
+such that the cosine of the angles lies uniformly in the range [-1,1] and we only use the plus polarisation.
+%
+\end{itemize}
+%
+The location of the peak amplitude of the waveforms (corresponding to the
+mid-points of all but the ringdown and \ac{BBH} classes) are randomly drawn from a uniform distribution to
+be within [0.4, 0.6] seconds from the start of the 1 sec time interval and all
+training waveforms are sampled at 1024 Hz.  The parameter prior ranges are
+defined in~\cref{Tab:training_parms} and a sample of training waveforms are shown in \cref{fig:training_waveforms}. All training data is rescaled such that their amplitudes peak at 1.
+
+\begin{table}[!h]
 \centering
@@
 
-% introduce the signal models
-%
-We propose a signal generation scheme using a \ac{CGAN} trained on burst-like
-waveforms. We call this \texttt{McGANn}\footnote{https://github.com/jmcginn/McGANn} and it is a \ac{CGAN} trained on five signal classes each spanning a range
-of prior signal parameters. The signal classes are:
-
-% list the 5 waveform classes
-%
-\begin{itemize}
-%
-\item {\bf Sine-Gaussian}: $h_{\text{sg}}(t) = A \exp\left[ - (t-t_{0})^2 /
-\tau^2 \right] \sin (2 \pi f_0 (t-t_0) + \phi)$, a sinusoidal wave with a Gaussian
-envelope characterised by a central frequency, $f_0$, amplitude, $A$, time of arrival, $t_{0}$ and phase, $\phi$ which is uniformly sampled between [0,2$\pi$]. 
-%
-\item {\bf Ringdown}: $h_{\text{rd}}(t) = A \exp \left[-{(t-t_0)} / {\tau}
-\right] \sin(2 \pi f_0 (t-t_0) + \phi)$, with frequency $f_0$ and duration $\tau$, amplitude, $A$, time of arrival, $t_{0}$, $\phi$ which is uniformly sampled between [0,2$\pi$. 
-%
-\item {\bf White noise bursts}: $h_{\text{wn}}(t_j) = Ag_j\exp\left[ -
-(t-t_{0})^2 / \tau^2 \right]$ where $g_j$ are drawn from a zero mean unit
-variance Gaussian distribution with a Gaussian envelope of duration $tau$.
-%
-\item {\bf Gaussian pulse}: $h_{\text{gp}}(t) = \exp(-t^2 / \tau^2)$ with
-duration parameter $\tau$.
-%
-\item {\bf Binary black hole}: Simulated using the IMRPhenomD
-waveform~\cite{Khan_2016} routine from LALSuite~\cite{lalsuite} which models
-the inspiral, merger and ringdown of a \ac{BBH} waveform. The component masses
-lie in the range of [30,70] $\textrm{M}_{\odot}$ with zero spins and we fix
-$m_1>m_2$. The mass distribution is approximated by a power law with
-index of 1.6~\cite{Abbott_2019}. The inclinations are drawn
-such that the cosine of the angles lies uniformly in the range [-1,1] and we only use the plus polarisation.
-%
-\end{itemize}
-%
-The location of the peak amplitude of the waveforms (corresponding to the
-mid-points of all but the ringdown and \ac{BBH} classes) are randomly drawn from a uniform distribution to
-be within [0.4, 0.6] seconds from the start of the 1 sec time interval and all
-training waveforms are sampled at 1024 Hz.  The parameter prior ranges are
-defined in~\cref{Tab:training_parms} and a sample of training waveforms are shown in \cref{fig:training_waveforms}. All training data is rescaled such that their amplitudes peak at 1.
-
-\begin{figure}
-    \centering
-    \includegraphics[width=\textwidth]{figures/training-sample.png}
-    \caption{Examples of the five different waveforms that were used in training the \ac{GAN} for this study.
-Values of the parameters were selected randomly from uniform distributions from \cref{Tab:hyperparameters}.}
-    \label{fig:training_waveforms}
-\end{figure}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-As \acp{GAN} are trained by updating one model at the expense of the other, they can be hard to train. GANs attempting to replicate complicated structures that do not
-have the necessary architecture either struggle to produce results at all or
-fall into the common failure mode know as mode collapse; where the generator
-produces a small variety of samples or simply memorises the training set.
-The goal of GAN training is to find an equilibrium between the two models, if this cannot be found then it is said that the \ac{GAN} has failed to converge.
-One way to diagnose \acp{GAN} during the development process is to keep track of the loss and accuracy over time.
-Loss plots, for example, as seen in \cref{fig:lossplot} can help to identify common failure modes or to check if the \ac{GAN} has indeed converged.
-Accuracy is the number of correct predictions made divided by total number of predictions.
-There is currently no notion of early stopping in \acp{GAN}, instead, training is halted after convergence and by visually inspecting the generations.
-
 All models were designed with the Python Keras library \cite{} and TensorFlow \cite{} and ran on a GeForce RTX 2080 Ti GPU.
@@
 We choose an appropriate model by visually inspecting the generations at a point of convergence on the loss plot.
-
-\begin{figure}[h!]
-    \centering
-    \includegraphics[width=1\textwidth]{figures/losses.png}
-    \caption{Plot of the discriminator and generator loss and accuracy as a function of iterations.
-Early in training the losses oscillates as both models attempt to find their equilibrium, after which, both losses vary around a point which signifies stable training.
-Accuracy's on the real and fake data are similar showing that neither model is stronger than the other.}
-    \label{fig:lossplot}
-\end{figure}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 a new signals composed of weighted elements of each training class.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Known class signal generation}
-In \cref{fig:gen_signals} we show conditional signal generations using our generator network.
-We can see the generations are of very good quality and appear like they could plausibly have come from the training set.
-We can also see that the model has learned the overall characteristics of the five training classes and is able to disentangle each class and associate them with the conditional input.
-Additionally, as the latent variable changes as do the parameters within each class.
-For instance \cref{fig:gen_signals} shows how signals vary in frequency, central epoch, decays and phase.
-The GANs ability to generate a variety of signals for various latent input indicate stable training and no mode collapse.
-
-\begin{figure}
+\begin{figure}[!h]
     \centering
@@
 \end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Interpolation within the latent space}
-
-% expain what we are planning to show here
-%
- We have shown that the generator produces quality signals and that the model responds well to randomly sampled Gaussian latent vectors.
-We now assume that during training the generator has learned a mapping from a Gaussian latent space to signal space and that this mapping is smooth.
-To test this, we fix the class vector input and linearly interpolate between two randomly chosen point in the latent space.
-In \cref{fig:z_interp} we show the generated waveforms, with the class vectors held constant along each row.
-We can see that each plot shows plausible waveforms suggesting that the generator has constructed a smooth traversable, space.
-
-\begin{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Known class signal generation}
+In \cref{fig:gen_signals} we show conditional signal generations using our generator network.
+We can see the generations are of very good quality and appear like they could plausibly have come from the training set.
+We can also see that the model has learned the overall characteristics of the five training classes and is able to disentangle each class and associate them with the conditional input.
+Additionally, as the latent variable changes as do the parameters within each class.
+For instance \cref{fig:gen_signals} shows how signals vary in frequency, central epoch, decays and phase.
+The GANs ability to generate a variety of signals for various latent input indicate stable training and no mode collapse.
+\begin{figure}[!h]
     \centering
@@
 \end{figure}
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Interpolation within the latent space}
+%
+% expain what we are planning to show here
+%
+ We have shown that the generator produces quality signals and that the model responds well to randomly sampled Gaussian latent vectors.
+We now assume that during training the generator has learned a mapping from a Gaussian latent space to signal space and that this mapping is smooth.
+To test this, we fix the class vector input and linearly interpolate between two randomly chosen point in the latent space.
+In \cref{fig:z_interp} we show the generated waveforms, with the class vectors held constant along each row.
+We can see that each plot shows plausible waveforms suggesting that the generator has constructed a smooth traversable, space.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 signals have sharper transitions but still retain plausible looking waveforms.
-
-\begin{figure}
+%
+\begin{figure}[!h]
     \centering
@@
 \end{figure}
-
+%
 \subsection{General points within the class space}
@@
 The methods we use are divided into the following:
-
+%
 \begin{itemize}
@@
 \label{fig:eff_curves} 
+\end{figure}
+
+\begin{figure}[t!] % "[t!]" placement specifier just for this example
+\begin{subfigure}{0.48\textwidth}
+\includegraphics[width=\linewidth]{figures/conditional_trained.png}
+\caption{}\label{fig:a}
+\end{subfigure}\hspace*{\fill}
+\begin{subfigure}{0.48\textwidth}
+\includegraphics[width=\linewidth]{figures/efficiency_curve_vtest.png}
+\caption{}\label{fig:b}
+\end{subfigure}
+
+\medskip
+\begin{subfigure}{0.48\textwidth}
+\includegraphics[width=\linewidth]{figures/simplex_trained.png}
+\caption{}\label{fig:c}
+\end{subfigure}\hspace*{\fill}
+\begin{subfigure}{0.48\textwidth}
+\includegraphics[width=\linewidth]{figures/efficiency_curve_stest.png}
+\caption{}\label{fig:d}
+\end{subfigure}
+
+\medskip
+\begin{subfigure}{0.48\textwidth}
+\includegraphics[width=\linewidth]{figures/uniform_trained.png}
+\caption{}\label{fig:e}
+\end{subfigure}\hspace*{\fill}
+\begin{subfigure}{0.48\textwidth}
+\includegraphics[width=\linewidth]{figures/efficiency_curve_utest.png}
+\caption{}\label{fig:f}
+\end{subfigure}
+
+\caption{Efficiency curves comparing the performance of the \acp{CNN}. The true alarm probability is plotted as a function of the optimal SNR of the signals. (a), (c), (e) show a CNN trained on
+vertex generations (top), simplex generations (middle), uniform
+generations (bottom) for a fixed false alarm rate of $10^{-3}$ and tested on all three data sets.
+(b), (d), (f) show fix the testing set vertex (top), simplex (middle), uniform (bottom) and show the performance of three trained CNNs on the different data sets.}   \label{fig:1}
 \end{figure}

### 2020-11-12 Paper_draft/main.tex
Updates from Overleaf

@@
     \caption{Examples of the five different waveforms that were used in training the \ac{GAN} for this study.
-Values of the parameters were selected randomly from uniform distributions from \cref{Tab:hyperparameters}.}
+Values of the parameters were selected randomly from uniform distributions from \cref{Tab:training_parms}}
     \label{fig:training_waveforms}
@@
 competition between the generator and discriminator.  After tuning the multiple
-hyperparameters (see \cref{Tab:hyperparameters}), the \ac{GAN} was trained on
+hyperparameters (see \cref{Tab:gan_training_parms}), the \ac{GAN} was trained on
 $10^5$ signals  drawn from a categorical
@@
 \subsection{General points within the class space}
-We have shown that the \acp{GAN} latent space and class space has structure that can be navigated through with interpolation between paris of signals.
+We have shown that the \acp{GAN} latent space and class space has structure that can be navigated through with interpolation between pairs of signals.
 Taking a step further, we can sample from the class space in novel ways to create new inputs for the generator.
@@
 
-\begin{figure}
-    \centering
-    \includegraphics[width=0.7\textwidth]{figures/conditional_trained.png}
-    \includegraphics[width=0.7\textwidth]{figures/simplex_trained.png}
-    \includegraphics[width=0.7\textwidth]{figures/uniform_trained.png}
-    \caption{Efficiency curves comparing the performance of \acp{CNN} trained on
-vertex generations (top), simplex generations (middle), uniform
-generations (bottom) for a fixed false alarm rate of $10^{-3}$. The true alarm probability is plotted as a function of the optimal SNR of the signals.}
-\label{fig:eff_curves} 
-\end{figure}
-
-\begin{figure}[t!] % "[t!]" placement specifier just for this example
+\begin{figure}[h!] % "[t!]" placement specifier just for this example
 \begin{subfigure}{0.48\textwidth}
 \includegraphics[width=\linewidth]{figures/conditional_trained.png}
-\caption{}\label{fig:a}
+\caption{}
 \end{subfigure}\hspace*{\fill}
@@
 \includegraphics[width=\linewidth]{figures/efficiency_curve_vtest.png}
-\caption{}\label{fig:b}
+\caption{}
 \end{subfigure}
@@
 \includegraphics[width=\linewidth]{figures/simplex_trained.png}
-\caption{}\label{fig:c}
+\caption{}
 \end{subfigure}\hspace*{\fill}
@@
 \includegraphics[width=\linewidth]{figures/efficiency_curve_stest.png}
-\caption{}\label{fig:d}
+\caption{}
 \end{subfigure}
@@
 \includegraphics[width=\linewidth]{figures/uniform_trained.png}
-\caption{}\label{fig:e}
+\caption{}
 \end{subfigure}\hspace*{\fill}
@@
 \includegraphics[width=\linewidth]{figures/efficiency_curve_utest.png}
-\caption{}\label{fig:f}
+\caption{}
 \end{subfigure}
@@
 generations (bottom) for a fixed false alarm rate of $10^{-3}$ and tested on all three data sets.
-(b), (d), (f) show fix the testing set vertex (top), simplex (middle), uniform (bottom) and show the performance of three trained CNNs on the different data sets.}   \label{fig:1}
+(b), (d), (f) show fix the testing set vertex (top), simplex (middle), uniform (bottom) and show the performance of three trained CNNs on the different data sets.}  \jordan{This shows both comparisons of the models v test data and test data v models.} \label{fig:eff_curves}
+\end{figure}
+
+\begin{figure}[h!] % "[t!]" placement specifier just for this example
+\begin{subfigure}{0.48\textwidth}
+\includegraphics[width=\linewidth]{figures/efficiency_curve_vtest.png}
+\caption{}
+\end{subfigure}\hspace*{\fill}
+\begin{subfigure}{0.48\textwidth}
+\includegraphics[width=\linewidth]{figures/efficiency_curve_stest.png}
+\caption{}
+\end{subfigure}
+
+\medskip
+\begin{subfigure}{0.48\textwidth}
+\includegraphics[width=\linewidth]{figures/efficiency_curve_utest.png}
+\caption{}
+\end{subfigure}\hspace*{\fill}
+\begin{subfigure}{0.48\textwidth}
+\includegraphics[width=\linewidth]{figures/efficiency_curve_mix_text.png}
+\caption{}
+\end{subfigure}
+
+\caption{Efficiency curves comparing the performance of the \acp{CNN}.
+The true alarm probability is plotted as a function of the optimal SNR of the signals.
+Plots (a), (b), (c) fix the testing set vertex (top), simplex (middle), uniform (bottom) and show the performance of three trained CNNs on the different data sets for a fixed false alarm rate of $10^{-3}$.
+Plot (d) shows CNNs trained on vertex, an even mixture of vertex and simplex and an even mixture of vertex and uniform and tested against the vertex dataset}  \jordan{This shows just the trained models v a test set with additional "mixture plot"} \label{fig:eff_curves}
 \end{figure}

### 2020-11-19 Paper_draft/main.tex
Updates from Overleaf

@@
 %
+
 In this work we present the potential of \acp{GAN} for
-burst \ac{GW} analysis.
-We have shown that \acp{GAN} have the ability to generate realistic time series burst data and can be conditioned based on the inherent features of the signals.
-The latent and class spaces were explored through interpolation and
-suggest that the space provides smooth translations between classes and overall
-waveform shape. We then showed targeted waveform generation by mixing classes
-to produce new unmodeled waveform varieties that can be used to test current
-burst search pipelines.
-
-We then considered three cases of unmodelled generated signals in Gaussian noise and demonstrated that a simple \ac{CNN} could distinguish between them. 
+burst \ac{GW} generation.
+We have shown that \acp{GAN} have the ability to generate plausible time series burst data and present a novel approach to generating unmodeled waveforms.
+We have shown that CGANs are able distinguish between five distinct classes of burst like signals through conditional training which we can then utilise for targeted generations.
+
+We also show how our GAN constructs smooth latent and class spaces during training and we explore these through interpolation showing smooth translations between classes and overall
+waveform shape.
+Further, we showed targeted waveform generation by mixing classes in the class space through novel ways.
+We are able to produce new unmodeled waveform varieties vastly different from the training set and any known analytical method of generating these signals.
+Such waveforms are in demand in gravitaional wave detection as they allow developers to test their search pipelines and other detection schemes.
+
+We then considered three cases of unmodelled generated signals in Gaussian noise and trained a \ac{CNN} on those data.
+The resulting efficiency curves comparing the detection sensitivities of the CNN as a function of SNR of the waveforms showed that these signals were detectable in noise.
+Although the three datasets were similarly detectable there was some degree of separation between them.
+
 In contrast to typical approaches in signal generation this is the first time a GAN has been used for generating gravitational wave burst data.
-In the future, as development in GANs and generative machine learning advances it is possible that we can gain greater control over target generation of features.
-Going forward it will also be important to extend our models to treat longer waveforms, higher sampling rates and generations other classes such as detector glitches.
+In the future, as development in GANs and generative machine learning advances it is expected that we will gain greater control over target generation of features.
+
+Going forward it will also be important to extend our models to treat longer waveforms, higher sampling rates and conditioning on additional classes.
+One such class of interest wold be "glitch'' data.
+High amplitude short duration, peaks in the output of LIGO detectors that are internal sources of noise rather than of astrophysical origin.
+Using a GAN to model these would aid in the understanding of these glitches and could help to remove them in order to get the cleanest data stream possible.
 

### 2020-11-20 Paper_draft/main.tex
add more text to CNN results section from Thurs meeting

@@
 where $p_{\text{\text{data}}}(\mathbf{x})$ is the distribution of real data and $p_{\text{z}}(\mathbf{z})$ is the distribution of the latent space.
-\begin{figure}[!h]
-    \centering
-    \includegraphics{figures/BCE-loss.png}
-    \caption{Binary cross-entropy plotted as a function of possible predicted probabilities in the case where the true label $y$ is 1 for a sample size of 512.}
-    \label{fig:BCE_loss}
-\end{figure}
+
 \subsection{Training stages}
@@
 $D(x) = \frac{1}{2}$.
-In \cref{fig:BCE_loss} we show how the binary-cross entropy varies with probability inputs when the real label is set to 1.
-We can see that for optimal training of the discriminator of 0.5 the binary cross entropy sits around 0.7.
-One could then say that the optimal generator loss during training is 0.7 however in practice the generator loss may be higher due to the continually alternating training method.
 
@@
 By row: sine-Gaussian, Ringdown,
-white noise burst, Gaussian pulse, binary black hole merger. On the first four rows each x axis is zoomed for ease of viewing, while the last row shows the full one second.}
+white noise burst, Gaussian pulse, binary black hole merger. On the first four rows each x axis is zoomed for ease of viewing.}
 \label{fig:gen_signals} 
@@
 datasets, we train three \acp{CNN} on the vertex, simplex and uniform data sets
-and use these models to make predictions on the other unseen datasets. We make
-a comparison by fixing the fraction of samples incorrectly identified as
-signals (false alarm rate) and plotting this versus the optimal SNR of the
-signals.~\chris{this last sentence isn't quite right}
-
-These results for a \ac{CNN} trained on vertex signals shows clear delineation from other two classes at snr$>$10.
-For the simplex trained network, the simplex dataset narrowly outperforms the other two sets and, finally, the uniform trained network shows similar performance on all datasets.
-The \ac{CNN} is
-robust enough to capture the differences between the datasets and shows that
-the GAN can generate a variety of unmodeled waveforms that can be used in
-future testing.
+and use these models to make predictions on the other unseen testing data.
+The top plot is tested on the vertex data and shows that each model confidently classifies all data at 100\% for SNR$>$13.
+At smaller SNRs the vertex and simplex perform similarly, however, the uniform data performs slightly worse.
+We would expect that when these models are tested on vertex data that everything should be classified at high SNR as the vertex data is a subset of the uniform and vertex.
+The middle plot shows the results of the CNNs trained on simplex data.
+As expected the simplex and vertex models recover 100\% detection at higher SNRs while the vertex trained model fails this test.
+This is explained when we consider that the simplex data is a subset of uniform while the vertex data is not.
+The final plot tests the models on uniform data and show again at high SNRs both simplex and uniform are 100\% detectable as a consequence of our previous subset argument.
+The vertex test is not fully detectable and further supports our premise that the vertex data, which is based on the modelled training data is distinguishable to both unmodelled datasets.
+
+The three tests shown previously show that the vertex model only manages full detection when tested on itself.
+The uniform model performs best in all cases and that it contains signals from the vertex and simplex samples, suggesting that this way of sampling the class space as input to the generator creates a good variety of unmodelled generations.
 
@@
 \begin{figure}[h!] % "[t!]" placement specifier just for this example
-\begin{subfigure}{0.48\textwidth}
-\includegraphics[width=\linewidth]{figures/conditional_trained.png}
-\caption{}
-\end{subfigure}\hspace*{\fill}
-\begin{subfigure}{0.48\textwidth}
+\centering
+\begin{subfigure}{0.7\textwidth}
 \includegraphics[width=\linewidth]{figures/efficiency_curve_vtest.png}
-\caption{}
 \end{subfigure}
 
-\medskip
-\begin{subfigure}{0.48\textwidth}
-\includegraphics[width=\linewidth]{figures/simplex_trained.png}
-\caption{}
-\end{subfigure}\hspace*{\fill}
-\begin{subfigure}{0.48\textwidth}
+\begin{subfigure}{0.7\textwidth}
+\centering
 \includegraphics[width=\linewidth]{figures/efficiency_curve_stest.png}
-\caption{}
 \end{subfigure}
 
-\medskip
-\begin{subfigure}{0.48\textwidth}
-\includegraphics[width=\linewidth]{figures/uniform_trained.png}
-\caption{}
-\end{subfigure}\hspace*{\fill}
-\begin{subfigure}{0.48\textwidth}
+\begin{subfigure}{0.7\textwidth}
+\centering
 \includegraphics[width=\linewidth]{figures/efficiency_curve_utest.png}
-\caption{}
-\end{subfigure}
-
-\caption{Efficiency curves comparing the performance of the \acp{CNN}. The true alarm probability is plotted as a function of the optimal SNR of the signals. (a), (c), (e) show a CNN trained on
-vertex generations (top), simplex generations (middle), uniform
-generations (bottom) for a fixed false alarm rate of $10^{-3}$ and tested on all three data sets.
-(b), (d), (f) show fix the testing set vertex (top), simplex (middle), uniform (bottom) and show the performance of three trained CNNs on the different data sets.}  \jordan{This shows both comparisons of the models v test data and test data v models.} \label{fig:eff_curves}
-\end{figure}
-
-\begin{figure}[h!] % "[t!]" placement specifier just for this example
-\begin{subfigure}{0.48\textwidth}
-\includegraphics[width=\linewidth]{figures/efficiency_curve_vtest.png}
-\caption{}
-\end{subfigure}\hspace*{\fill}
-\begin{subfigure}{0.48\textwidth}
-\includegraphics[width=\linewidth]{figures/efficiency_curve_stest.png}
-\caption{}
-\end{subfigure}
-
-\medskip
-\begin{subfigure}{0.48\textwidth}
-\includegraphics[width=\linewidth]{figures/efficiency_curve_utest.png}
-\caption{}
-\end{subfigure}\hspace*{\fill}
-\begin{subfigure}{0.48\textwidth}
-\includegraphics[width=\linewidth]{figures/efficiency_curve_mix_text.png}
-\caption{}
 \end{subfigure}
@@
 The true alarm probability is plotted as a function of the optimal SNR of the signals.
-Plots (a), (b), (c) fix the testing set vertex (top), simplex (middle), uniform (bottom) and show the performance of three trained CNNs on the different data sets for a fixed false alarm rate of $10^{-3}$.
-Plot (d) shows CNNs trained on vertex, an even mixture of vertex and simplex and an even mixture of vertex and uniform and tested against the vertex dataset}  \jordan{This shows just the trained models v a test set with additional "mixture plot"} \label{fig:eff_curves}
+Each plot shows the performance of a CNN trained on vertex, simplex and uniform datasets tested on vertex (top), simplex (middle), uniform (bottom).}
+\label{fig:eff_curves}
 \end{figure}

### 2020-12-03 Paper_draft/main.tex
First minor edits in the results section

@@
     \caption{\ac{GAN} Generated waveforms plotted as a function of time.
-The latent space inputs for each panel is randomised and each row is assigned one of the five class vectors.
+The latent space inputs for each panel are randomised and each row is assigned one of the five class vectors.
 By row: sine-Gaussian, Ringdown,
-white noise burst, Gaussian pulse, binary black hole merger. On the first four rows each x axis is zoomed for ease of viewing.}
+white noise burst, Gaussian pulse, binary black hole merger. For ease of viewing, the $x$-axis for all panels spans the mid 50\% of the output range.}
 \label{fig:gen_signals} 
@@
 In \cref{fig:gen_signals} we show conditional signal generations using our generator network.
-We can see the generations are of very good quality and appear like they could plausibly have come from the training set.
+We can see the generations are of very good quality and appear as though they could have plausibly come from the training set.
 We can also see that the model has learned the overall characteristics of the five training classes and is able to disentangle each class and associate them with the conditional input.
-Additionally, as the latent variable changes as do the parameters within each class.
-For instance \cref{fig:gen_signals} shows how signals vary in frequency, central epoch, decays and phase.
-The GANs ability to generate a variety of signals for various latent input indicate stable training and no mode collapse.
+Additionally, as the latent variable changes we see indirect evidence of variation within the parameter space for a given class.
+For instance \cref{fig:gen_signals} shows how signals vary in frequency, central epoch, decay timescale, and phase.
+The \acp{GAN} ability to generate a variety of signals for various latent space input indicates stable training and no mode collapse.
 \begin{figure}[!h]
@@
     \includegraphics[width=\textwidth]{figures/generations/z_interp_bbh.png}
-    \caption{Generated interpolated waveforms plotted as a function of time.
-For each interpolation two points were randomly chosen in the latent space and the between panels are linearly interpolated vectors between these two points.
-Each row keeps on of the class vetors constant throughout the latent space interpolation.}
+    \caption{\ac{GAN} generated interpolated waveforms plotted as a function of time showing latent-space interpolations.
+For each interpolation two different points were randomly chosen in the latent space and represent the first last panels in each row.
+The panels between represent signals generated using linearly interpolated vectors between these two points.
+Each row keeps its class vector constant throughout the latent space interpolation.
+By row: sine-Gaussian, Ringdown, white noise burst, Gaussian pulse, binary black hole merger.
+For ease of viewing, the $x$-axis for all panels spans the mid 50\% of the output range.}
     \label{fig:z_interp}
@@
 %
-% expain what we are planning to show here
+% explain what we are planning to show here
 %
  We have shown that the generator produces quality signals and that the model responds well to randomly sampled Gaussian latent vectors.
-We now assume that during training the generator has learned a mapping from a Gaussian latent space to signal space and that this mapping is smooth.
-To test this, we fix the class vector input and linearly interpolate between two randomly chosen point in the latent space.
+We now assume that during training the generator has learned a mapping from a Gaussian latent space to signal space and that this mapping is a smooth function of the underlying latent space.
+To verify this, we fix the class vector input and linearly interpolate between two randomly chosen points in the latent space (different for each class).
 In \cref{fig:z_interp} we show the generated waveforms, with the class vectors held constant along each row.
 We can see that each plot shows plausible waveforms suggesting that the generator has constructed a smooth traversable, space.
+We note that the relationship between the latent space location and the physical signal parameters are hidden from us, and hence the initial and final latent space locations (moving left to right in \cref{fig:z_interp}) simply represent random possible signals learned from the training set prior.
+During training the network should have learned how to smoothly represent the underlying features of a signal as a function of latent space location.
+For example, the linearly interpolated transition through the latent space for the Gaussian pulse signal shows a shift to earlier epoch and larger decay timescale.
+In contrast, the transition for the Ringdown signal appears to pass through a localised region of latent-space consistent with higher central frequency.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 While the \ac{GAN} is trained on distinct one-hot encoded classes, we may test arbitrary points in the 5-dimensional class space to produce indistinct or hybrid waveforms.
-In order to explore the class space we keep the latent vector constant and
-interpolate through the 5 classes. We construct a path between two waveforms
-and show in \cref{fig:c_interp} that the space is populated enough to allow for transitions between
-classes.  Sine-Gaussian to ringdown performs well in interpolation with each
-signal being a plausible burst GW. It is obvious that the GAN has clustered
-these two groups during training as they share many characteristics. The other
-signals have sharper transitions but still retain plausible looking waveforms.
+In order to explore the class-space, in \cref{fig:c_interp} we show results where the latent vector is held constant but we instead linearly
+interpolate within the one-hot encoded class-space between pairs of the well-defined training class locations.
+In this scenario we highlight that the \ac{GAN} has not yet probed this intermediate class-space during its training and therefore we are reliant on the generator having learned any underlying class space relationships between the 5 training classes.
+The results show that for each case that the generated signals show distinct characteristics of the respective class pairs at most stages of the transition.
+We note that transitions in some cases appear to be rather abrupt, e.g., between the Gaussian pulse and the \ac{BBH}, \chris{but we point out that this feature, whilst not uncommon, is a strong function of the random latent-space location.}
 %
@@
     \includegraphics[width=\textwidth]{figures/generations/blip-bbh.png}
-    \caption{Generated class interpolated waveforms as a function of time.
+    \caption{\ac{GAN} generated class interpolated waveforms as a function of time showing class-space interpolations.
 A single latent space vector is used for all generations and is chosen randomly in the latent space.
 Each row shows generations using linearly interpolated classes as inputs to the generator.
-By row top to bottom: Sine-Gaussian to Ringdown, Ringdown to white noise burst, Gaussian pulse to BBH.}
+By row top to bottom: Sine-Gaussian to Ringdown, Ringdown to white noise burst, Gaussian pulse to BBH.\chris{add class vectors on each panel}}
     \label{fig:c_interp}
@@
 \subsection{General points within the class space}
-We have shown that the \acp{GAN} latent space and class space has structure that can be navigated through with interpolation between pairs of signals.
-Taking a step further, we can sample from the class space in novel ways to create new inputs for the generator.
-These new points are categorised by the method used to sample from the class space.
+We have shown that the \acp{GAN} latent-space and class-space have structure that can be navigated via interpolation between pairs of locations within each respective space.
+Taking a step further, we can sample from the class-space in novel ways to create new inputs for the generator.
+These new points are categorised by the method used to sample from the class-space.
 The methods we use are divided into the following:
@@
 \item {\bf Vertex}: Points that lie at the corners of the five dimensional class space.
-These signals are the closest to the training set.
+These class-space locations are equivalent to the training set locations and are our closest generated representation of the training set.
 %
 \item {\bf Uniform}: Each of the entries in the class vector is sampled from a uniform distribution U[0,1].
-
-%
-\item {\bf Simplex}: This class vector we define as uniformly sampled points on a simplex, which is a generalization of a triangle in k-dimensions.
-We sample uniformly on the k=4 simplex that is embedded in the 5 dimensional class hyper cube.
-In practice we use the equivalent of sampling points from a k=4 Dirichlet distribution and then normalizing.
+This is equivalent to sampling uniformly within the 5-dimensional one-hit encoding hyper-cube.
+%
+\item {\bf Simplex}: This class vector we define as uniformly sampled points on a simplex, which is a generalization of a triangle in $k$-dimensions.
+We sample uniformly on the $k=4$ simplex that is embedded in the 5-dimensional class hyper cube.
+In practice we use the equivalent of sampling points from a $k=4$ Dirichlet distribution.
 %

### 2020-12-04 Paper_draft/main.tex
Add a few comments and fix some typos

@@
 generate waveforms in fractions of a second and produce waveforms that are difficult to generate with current
-techniques. These new varieties of waveforms can then be used to diagnose
+techniques. These new varieties of waveforms can then be used to diagnose \michael{not sure about diagnose, maybe test or evaluate?}
 detection algorithms, gain new insight into sources of \ac{GW}
@@
 We present the results of the GAN in \cref{results} and show how unmodeled signals can be produced by interpolating and sampling within latent and class spaces.
-In \cref{cnn classifier} we show that a convolutional neural network classifier can be trained to distinguish between sets of our GAN generated waveforms from noise only cases.
+In \cref{cnn classifier} we show that a convolutional neural network \michael{should this have the accronym?
+Tried to fix it but it only puts the plural for me} classifier can be trained to distinguish between sets of our GAN generated waveforms from noise only cases.
 We conclude with a summary of the presented work in \cref{conclusions}.
@@
 data' in order to make accurate predictions without the need for additional
-programming. A common approach in \ac{ML} relies on the model learning on
+programming. A common approach in \ac{ML} relies on the model learning from
 past experience to make decisions on future events. Artificial neural networks are universal function approximators that are built from many single
@@
  \end{equation}
-where $p_{\text{\text{data}}}(\mathbf{x})$ is the distribution of real data and $p_{\text{z}}(\mathbf{z})$ is the distribution of the latent space.
+where $p_{\text{\text{data}}}(\mathbf{x})$ is the distribution of real data and $p_{\text{z}}(\mathbf{z})$ is the latent distribution.
 
@@
 The act of switching the labels and minimizing this form of loss is identical to the previously mentioned generator loss but is beneficial as in practice this function provides more useful gradients.
-This tweak to the generator loss is called non-saturating generator loss and was reported in the original GAN paper \cite{Goodfellow2014}.
+This tweak to the generator loss is called non-saturating generator loss and was reported in the original \ac{GAN} paper \cite{Goodfellow2014}.
 It was also shown in that paper that if the generator and discriminator can no longer improve, then the discriminator can no longer distinguish between real and fake i.e.
@@
 produces a small variety of samples or simply memorises the training set.
-The goal of GAN training is to find an equilibrium between the two models, if this cannot be found then it is said that the \ac{GAN} has failed to converge.
+The goal of \ac{GAN} training is to find an equilibrium between the two models, if this cannot be found then it is said that the \ac{GAN} has failed to converge.
 One way to diagnose \acp{GAN} during the development process is to keep track of the loss and accuracy over time.
@@
     \caption{Plot of the discriminator and generator loss and accuracy as a function of epochs.
-Early in training the losses oscillates as both models attempt to find their equilibrium, after which, both losses vary around a point which signifies stable training.
-Accuracy's on the real and fake data are similar showing that neither model is stronger than the other.}
+Early in training the losses oscillate as both models attempt to find their equilibrium, after which, both losses vary around a point which signifies stable training.
+Accuracies on the real and fake data are similar showing that neither model is stronger than the other.}
     \label{fig:lossplot}
@@
 %
-To gain more control over what a GAN is able to generate, a conditional variant
+To gain more control over what a \ac{GAN} is able to generate, a conditional variant
 of \acp{GAN} named \acp{CGAN}~\cite{cgan} was introduced by feeding in extra
@@
     \caption{Examples of the five different waveforms that were used in training the \ac{GAN} for this study.
-Values of the parameters were selected randomly from uniform distributions from \cref{Tab:training_parms}}
+Values of the parameters were selected randomly from uniform distributions from \cref{Tab:training_parms}.}
     \label{fig:training_waveforms}
@@
 
-The design of the networks is influenced by \cite{Radford2015} in which they use a deep convolution generative adversarial network architecture \ac{DCGAN}. The generator model is fully convolutional,
+The design of the networks is influenced by \cite{Radford2015} in which they use a \ac{DCGAN} architecture. The generator model is fully convolutional,
 upsampled using strided transposed convolutions
 with batch normalisation in the
-first layer and ReLU activations throughout with the exception of the a linear activation for
+first layer and ReLU activations throughout with the exception of a linear activation for
 the output layer. The use of a linear activation guarantees the output can have negative and positive outputs. Each transposed
@@
 
-All models were designed with the Python Keras library \cite{} and TensorFlow \cite{} and ran on a GeForce RTX 2080 Ti GPU.
+All models were designed with the Python Keras library \cite{} and TensorFlow \cite{} and trained on a GeForce RTX 2080 Ti GPU.
 We train the networks for 500 epochs which takes $\mathcal{O}(10)$ hours and save the model at each epoch.
@@
 %
-\item {\bf Uniform}: Each of the entries in the class vector is sampled from a uniform distribution U[0,1].
-This is equivalent to sampling uniformly within the 5-dimensional one-hit encoding hyper-cube.
-%
 \item {\bf Simplex}: This class vector we define as uniformly sampled points on a simplex, which is a generalization of a triangle in $k$-dimensions.
-We sample uniformly on the $k=4$ simplex that is embedded in the 5-dimensional class hyper cube.
+We sample uniformly on the $k=4$ simplex that is embedded in the 5-dimensional class hyper-cube.
 In practice we use the equivalent of sampling points from a $k=4$ Dirichlet distribution.
+It is useful to think of the simplex as the hyper-plane that intersects all 5 training classes.
+It is a subspace of the Uniform method.
+%
+\item {\bf Uniform}: Each of the entries in the class vector is sampled from a uniform distribution $\text{U}[0,1]$.
+This is equivalent to sampling uniformly within the 5-dimensional one-hot encoding hyper-cube.
 %
@@
 
-The vertex points are the most straightforward where one entry contains 1 and the other entries are zero and are equivalent to the class vectors that the GAN is trained on e.g.
-$\mathbf{c} = [1,0,0,0,0]$ would correspond to a sine-Gaussian generation.
-Uniform class vectors sampled from a uniform distribution and act like a random draw from the five dimensional hypercube.
-Uniformly sampling contains points up to a distance of unit from the closest class e.g.
+The vertex points are the most straightforward where one element of the class vector contains 1 and the other elements are zero.
+these points are equivalent to the class vectors that the \ac{GAN} is trained on e.g., $\mathbf{c} = [1,0,0,0,0]$ would correspond to a sine-Gaussian generation.
+Uniform class vectors with each element sampled from a uniform distribution are equivalent to a random draw from a 5-dimensional hyper-cube.
+Uniformly sampling generates class-space locations up to a maximum distance of unity from the closest class e.g.
 [0,0,0,0,0] is of distance 1 away from all classes (as is [1,1,1,1,1]).
-For simplex class vectors, we sample from the simplest hypersurface that intersects all the classes and has a symmetry such that no class is favoured over any other.
-For our 5-dimensional case this would correspond to a 4-simplex manifold.
-Sampling from the simplex can be seen as sampling from between the classes within the space.
-
-In \cref{fig:simplexd_samples} we show generations conditioned on class vectors drawn from the 4-simplex.
-There are large variations in the signals with some looking like definitive classes, although this can be partially explained through the random draws from the simplex as there is finite probability that one class entry will dominate over the others.
-For instance the generations that look more like sine-Gaussians than unmodeled generally have a larger value placed in the first entry than others.
-Similarly \cref{fig:uniform_samples} shows generations conditioned on class vectors drawn uniformly in the unit hypercube.
-These types of generations tend to exhibit more noise and some are very low amplitude before being re-scaled.
-Artifacts like the signal not lining up to zero on the y axis is a result of re-scaling a particularly low amplitude signal.
-Both methods of generating unmodeled data, however, do show signals that look unrelated to the training data.
+For simplex class vectors, we sample from the simplest hyper-surface that intersects all the classes and has a symmetry such that no training class location (any vertex) is favoured over any other.
+For our 5-dimensional case this corresponds to a 4-simplex manifold.
+Sampling from the simplex can be seen as sampling from the simplest space that spans between the training classes.
+
+In \cref{fig:simplexd_samples} we show generations conditioned on class vectors drawn randomly from the 4-simplex.
+There are large variations in the signals with some having characteristics strongly resembling the training classes, although this can be partially explained through the random draws from the simplex as there is finite probability that one class entry will dominate over the others (i.e., the class-space location is close to a vertex).
+For instance the generations that look more like sine-Gaussians than hybrid waveforms generally have a larger value placed in the first class-space element than others.
+Similarly \cref{fig:uniform_samples} shows generations conditioned on class vectors drawn uniformly in the unit hyper-cube.
+These types of generations tend to exhibit more noise and some tend to be generated with very low amplitude prior to being re-scaled to have maximum amplitude of unity.
+Both methods of generating hybrid waveforms, however, do produce signals that appear to share characteristics from the training set but still be distinct in signal morphology.
+Upon inspection of a larger collection of waveform generations from both methods we do see a tendency for the uniform hyper-cube approach to generate more wider variety of hybrid waveforms that are more visually distinct from the training set.
+This is to be expected given that the simplex class-space is a subset of the hyper-cube and does not explore regions of the class-space as far from the training set vertices.
 
@@
     \includegraphics[width=\textwidth]{figures/generations/simplex_sample5.png}
-    \caption{GAN generations where the class vectors are sampled from the 4-D
-plane intersecting all classes.
-Latent space locations for all signals are taken randomly from a Gaussian distribution and the signals are then re-scaled such that they peak at unity.
-The class label for each generation is shown above each pannel.}
+    \caption{GAN generations where the class vectors are sampled from the 4-dimensional plane (simplex) intersecting all training classes.
+Latent space locations for all signals are taken randomly from a 100-dimensional Gaussian distribution and the signals are then re-scaled such that they have maximum absolute amplitude at unity.
+The class label for each generation is shown above each panel.}
     \label{fig:simplexd_samples}
@@
     \includegraphics[width=\textwidth]{figures/generations/uniform_sample5.png}
-    \caption{GAN generations where the class vectors are sampled uniformly in the hypercube class space.
-Latent space locations for all signals are taken randomly from a Gaussian distribution and the signals are then re-scaled such that they peak at unity.}
+    \caption{GAN generations where the class vectors are sampled uniformly in the hyper-cube class space.
+Latent space locations for all signals are taken randomly from a 100-dimensional Gaussian distribution and the signals are then re-scaled such that they have maximum absolute amplitude at unity.}
     \label{fig:uniform_samples}
@@
 \section{CNN burst classifier} \label{cnn classifier}
-In this section  we use a \ac{CNN}
-to compare different waveform generations from the \ac{CGAN} to help determine the
-success and failures of the model generations. We train a \ac{CNN} to distinguish between two classes: signals in additive Gaussian
-noise and Gaussian noise only. 
-\subsection{Training data} 
-We use three classes of training data: vertex, uniform or simplex cases generated using our \ac{GAN} method and consider two detectors H1 and L1 as joint inputs to the \ac{CNN}.
-For each training set we generated a bank of $2\times 10^5$ signals and apply antenna responses and time delays using routines provided by LALsuite \cite{lalsuite}.
-The polarisation angles are drawn uniformly in the range $[0,2\pi]$ and sky positions are sampled isotropically.
+In this section we develop a basic search analysis using a \ac{CNN} in order to compare the sensitivity of such a search to different \ac{GAN} generated waveforms in additive noise.
+We train a \ac{CNN} to perform simple classification and to distinguish between two classes: signals in additive Gaussian noise and Gaussian noise only.
+We are primarily interested in the relative sensitivity as a function of the types of waveforms used for training the network.
+We are also interested in how these differently trained networks perform when applied to data from waveform generations not used in the training process.
+
+\subsection{Noisy data-sets} 
+We use three classes of waveforms: vertex, uniform, and simplex cases generated using our \ac{GAN} method.
+We then construct noisy time-series data from each waveform representing measurements from the 2 LIGO detector sites, Hanford (H1) and Livingston (L1).
+For each training set we generate $2\times 10^5$ signals and apply antenna responses and sky location dependent relative time delays using routines provided within LALsuite \cite{lalsuite}.
+The generated waveforms are used to represent the plus-polarisation component of signal only and the polarisation angles are drawn uniformly in the range $[0,2\pi]$ and sky positions are sampled isotropically.
 Time delays between detectors are computed relative to the Earth centre.
-All of the training data used is whitened using the Advanced LIGO
-design sensitivity \ac{PSD}, such that there is equal noise power at each
-frequency and the data is correctly normalised. This procedure is
-applied to signals whose \acp{SNR} are sampled uniformly in the range $[1-16]$.
-Each time series input to the \ac{CNN} is represented by an 1024 x 2 image that is sampled at 1024 hz for each of the two detectors.
-An example time series is shown in \cref{fig:cnn_training}.
-While training the network, the input training data consists of
-signals which contain one half noise only and one half signal contained in
-noise. Of that, 80\% is used for training and 20\% used for validation, while for testing we use $2\times 10^5$ signals in order to use small false alarm rates later.
+All of the training data used is whitened using the Advanced LIGO design sensitivity \ac{PSD}\chris{add reference}, such that there is equal noise power at each frequency.
+Signal network \acp{SNR} is drawn uniformly in the range $[1,16]$ and is controlled by an amplitude scaling applied to the waveform.
+Each 1 second duration time-series input to the \ac{CNN} is represented by a 1-dimensional 1024 sample vector with 2 channels representing each detector.
+Example time-series from each detector for a single signal is shown in \cref{fig:cnn_training}.
+The network is trained to be able to identify whether or not a measurement contains a signal and therefore 50\% of the training data have time-series containing signals and 50\% have only noise.
+We randomly divide the data into the 3 standard sets (training, validation, and test data) where 40\% is used for training, 10\% used for validation, and 50\% is used for testing in order to achieve suitably low false-alarm rates.
+For the Uniform and Simplex data-sets samples are drawn uniformly from their respective spaces.
+For the vertex data-set the 5 different vertex locations in class-space are sampled with equal probability.
 
@@
     \includegraphics[width=\textwidth]{figures/SNR8.png}
-    \caption{\ac{CNN} training data.
-Whitened noise free sine-Gaussian timeseries as seen by Hanford (red) and Livingston (light blue) detectors.
-These signals with fixed SNR = 8, re-scaled by the two detector network SNR.
-The dark blue time series for each plot shows either the same signal with added detector noise from Hanford (left) or Livingston (right).
-The signals plus added noise is used to train, test and validate the \ac{CNN}.}
+    \caption{Example of \ac{CNN} training data showing a whitened noisy (dark blue) and noise-free (red, light blue) sine-Gaussian time-series as seen by Hanford (left) and Livingston (right) detectors.
+This signal has network $\text{SNR}=8$.}
      \label{fig:cnn_training}
@@
 \subsection{CNN architecture}
-In this approach the input to the \ac{CNN} is a 2x1024 time series which is passed through a series of convolutional layers, onto two fully connected or ``Dense'' layers and finally to a single output neuron which represents the probability that a signal is present within the noise.
-We used dropout in the final dense layer and found that the swish activation \cite{ramachandran2017searching} function performed well.
-The output layer is activated by a sigmoid function and we used \cref{eqn:crossentropy} as a loss function and Adam as an optimizer with learning rate set to $10^{-3}$.
-In total we train three separate \acp{CNN} on either the vertex, uniform or simplex data set share the same architecture and hyperparameters which are shown in \cref{Tab:cnn_training_parms}.
-
-\subsection{Results}
-In~\cref{fig:eff_curves} we compare the \ac{CNN} results between the three
-datasets, we train three \acp{CNN} on the vertex, simplex and uniform data sets
-and use these models to make predictions on the other unseen testing data.
-The top plot is tested on the vertex data and shows that each model confidently classifies all data at 100\% for SNR$>$13.
-At smaller SNRs the vertex and simplex perform similarly, however, the uniform data performs slightly worse.
-We would expect that when these models are tested on vertex data that everything should be classified at high SNR as the vertex data is a subset of the uniform and vertex.
-The middle plot shows the results of the CNNs trained on simplex data.
-As expected the simplex and vertex models recover 100\% detection at higher SNRs while the vertex trained model fails this test.
+In this approach the input to the \ac{CNN} are 1024 sample time-series (with 2 channels representing each detector output) which are passed through a series of 4 convolutional layers, onto two fully connected or ``Dense'' layers and finally to a single output neuron which represents the probability that a signal is present within the noise.
+We used dropout in the final dense layer and used a selection of different activation functions including the swish activation \cite{ramachandran2017searching} which improved overall performance and a sigmoid activation for the output layer.
+We used binary cross-entropy \cref{eqn:crossentropy} as the loss function and Adam as an optimizer with learning rate set to $10^{-3}$.
+In total we train three separate \acp{CNN} on the vertex, uniform and simplex data set respectively.
+In each case the networks share the same architecture and hyper-parameters which are defined in \cref{Tab:cnn_training_parms}.
+
+\subsection{CNN results}
+We now compare the \ac{CNN} results between the data-sets by first training three \acp{CNN} on the vertex, simplex, and uniform data-sets and then using these models to make predictions on the other testing data unseen during the network training process.
+In~\cref{fig:eff_curves} the top plot represents results from each trained network tested on the vertex data and shows that each model confidently classifies all data at 100\% for \ac{SNR}$>$13.
+At smaller \acp{SNR} the vertex and simplex perform similarly, however, the uniform data performs slightly worse.
+We would expect that when these models are tested on vertex data that everything should be classified at high \ac{SNR} as the vertex data is a subset of the uniform and vertex.
+The middle plot shows the results of the \acp{CNN} trained on simplex data.
+As expected the simplex and vertex models recover 100\% detection at higher \acp{SNR} while the vertex trained model fails this test.
 This is explained when we consider that the simplex data is a subset of uniform while the vertex data is not.
-The final plot tests the models on uniform data and show again at high SNRs both simplex and uniform are 100\% detectable as a consequence of our previous subset argument.
+The final plot tests the models on uniform data and show again at high \acp{SNR} both simplex and uniform are 100\% detectable as a consequence of our previous subset argument.
 The vertex test is not fully detectable and further supports our premise that the vertex data, which is based on the modelled training data is distinguishable to both unmodelled datasets.
@@
 \begin{itemize}
-    \item vertex trained shows clear delineation from other two classes at snr$>$10. Good to show that they are different. But not all converge to 1.
-    \item simplex trained leads in smaller snrs but eventually all converge to 1
+    \item vertex trained shows clear delineation from other two classes at \ac{SNR}$>$10. Good to show that they are different. But not all converge to 1.
+    \item simplex trained leads in smaller \acp{SNR} but eventually all converge to 1
     \item uniform trained shows much similarity to simplex test set, still different from vertex.
@@
 makes sense if the vertex is a subset of the simplex and uniform classes.
-Also a sign that the GAN likes to keep things as close to vertex as possible?
+Also a sign that the \ac{GAN} likes to keep things as close to vertex as possible?
 \end{itemize}
@@
 \caption{Efficiency curves comparing the performance of the \acp{CNN}.
-The true alarm probability is plotted as a function of the optimal SNR of the signals.
-Each plot shows the performance of a CNN trained on vertex, simplex and uniform datasets tested on vertex (top), simplex (middle), uniform (bottom).}
+The true alarm probability is plotted as a function of the optimal \ac{SNR} of the signals.
+Each plot shows the performance of a \ac{CNN} trained on vertex, simplex and uniform datasets tested on vertex (top), simplex (middle), uniform (bottom).}
 \label{fig:eff_curves}
@@
 burst \ac{GW} generation.
-We have shown that \acp{GAN} have the ability to generate plausible time series burst data and present a novel approach to generating unmodeled waveforms.
+We have shown that \acp{GAN} have the ability to generate plausible time series burst data and present a novel approach to generating unmodelled waveforms.
 We have shown that CGANs are able distinguish between five distinct classes of burst like signals through conditional training which we can then utilise for targeted generations.
 
-We also show how our GAN constructs smooth latent and class spaces during training and we explore these through interpolation showing smooth translations between classes and overall
+We also show how our \ac{GAN} constructs smooth latent and class spaces during training and we explore these through interpolation showing smooth translations between classes and overall
 waveform shape.
 Further, we showed targeted waveform generation by mixing classes in the class space through novel ways.
-We are able to produce new unmodeled waveform varieties vastly different from the training set and any known analytical method of generating these signals.
-Such waveforms are in demand in gravitaional wave detection as they allow developers to test their search pipelines and other detection schemes.
+We are able to produce new unmodelled waveform varieties vastly different from the training set and any known analytical method of generating these signals.
+Such waveforms are in demand in gravitational wave detection as they allow developers to test their search pipelines and other detection schemes.
 
 We then considered three cases of unmodelled generated signals in Gaussian noise and trained a \ac{CNN} on those data.
-The resulting efficiency curves comparing the detection sensitivities of the CNN as a function of SNR of the waveforms showed that these signals were detectable in noise.
+The resulting efficiency curves comparing the detection sensitivities of the \ac{CNN} as a function of \ac{SNR} of the waveforms showed that these signals were detectable in noise.
 Although the three datasets were similarly detectable there was some degree of separation between them.
 
-In contrast to typical approaches in signal generation this is the first time a GAN has been used for generating gravitational wave burst data.
-In the future, as development in GANs and generative machine learning advances it is expected that we will gain greater control over target generation of features.
+In contrast to typical approaches in signal generation this is the first time a \ac{GAN} has been used for generating gravitational wave burst data.
+In the future, as development in \acp{GAN} and generative machine learning advances it is expected that we will gain greater control over target generation of features.
 
 Going forward it will also be important to extend our models to treat longer waveforms, higher sampling rates and conditioning on additional classes.
-One such class of interest wold be "glitch'' data.
+One such class of interest would be ``glitch'' data.
 High amplitude short duration, peaks in the output of LIGO detectors that are internal sources of noise rather than of astrophysical origin.
-Using a GAN to model these would aid in the understanding of these glitches and could help to remove them in order to get the cleanest data stream possible.
+Using a \ac{GAN} to model these would aid in the understanding of these glitches and could help to remove them in order to get the cleanest data stream possible.
 
@@
 waveforms at hand can aid in our understand of the physics processes behind
-these non-standard ac{GW} emitters.
+these non-standard \ac{GW} emitters.
 
@@
 \section{List of hyperparameters}
+
 \begin{table}[hb]
 \centering
-\caption{The architecture and hyperparameters describing our CNN consists of four convolutional layers followed by two dense layers.
-The convolutional and dense layers are activated by the swish function and dropout is applied, while the final layer uses the sigmoid activation.
-The network is trained by minimising the binary cross entropy and optimised with Adam with learning rate $10^{-3}$.
-We train for 100 epochs with a batch size of 1000.}
-%\footnotesize
-\begin{tabular*}{\textwidth}{c @{\extracolsep{\fill}} c c c c c c}
-\br
-%\hline
-Operation & Output shape & Kernel size & Stride & Dropout & Activation \\
-\mr
-Input & (1024, 2) & N/A  & N/A & N/A & N/A \\
-Convolutional & (512, 8) & 5 & 2 & 0 & Swish  \\
-Convolutional & (256, 8) & 5 & 2 & 0 & Swish  \\
-Convolutional & (128, 8) & 5 & 2 & 0 & Swish  \\
-Convolutional & (64, 8) & 5 & 2 & 0 & Swish  \\
-Dense & (100) & 100 & N/A & 0.2 & Linear  \\
-Dense & (1) & 1 & N/A & 0 & sigmoid \\
-\end{tabular*}\\
-\begin{tabular*}{\textwidth}{@{}l l l l l l}
-\mr
-Optimizer & Adam($\alpha$ = 0.001, $\beta_{1}$ = 0.5) & & & & \\
-Batch size & 1000 & & & & \\
-Epochs & 100 & & & & \\
-Loss & Binary cross-entropy & & & & \\
- \br
-\end{tabular*}\\
-\label{Tab:cnn_training_parms}
-\end{table}
-
-\begin{table}[hb]
-\centering
-\caption{The architecture and hyperparameters describing our GAN consisting of discriminator and generator convolution neural networks.
+\caption{The architecture and hyperparameters describing our \ac{GAN} consisting of discriminator and generator convolution neural networks.
 The discriminator casts the class input through a fully connected layer such that its dimensions match the signals input which it then concatenates channel-wise.
@@
 
+\begin{table}[hb]
+\centering
+\caption{The architecture and hyperparameters describing our CNN consists of four convolutional layers followed by two dense layers.
+The convolutional and dense layers are activated by the swish function \cite{ramachandran2017searching} and dropout is applied, while the final layer uses the sigmoid activation.
+The network is trained by minimising the binary cross entropy and optimised with Adam with learning rate $10^{-3}$.
+We train for 100 epochs with a batch size of 1000.}
+%\footnotesize
+\begin{tabular*}{\textwidth}{c @{\extracolsep{\fill}} c c c c c c}
+\br
+%\hline
+Operation & Output shape & Kernel size & Stride & Dropout & Activation \\
+\mr
+Input & (1024, 2) & N/A  & N/A & N/A & N/A \\
+Convolutional & (512, 8) & 5 & 2 & 0 & Swish  \\
+Convolutional & (256, 8) & 5 & 2 & 0 & Swish  \\
+Convolutional & (128, 8) & 5 & 2 & 0 & Swish  \\
+Convolutional & (64, 8) & 5 & 2 & 0 & Swish  \\
+Dense & (100) & 100 & N/A & 0.2 & Linear  \\
+Dense & (1) & 1 & N/A & 0 & sigmoid \\
+\end{tabular*}\\
+\begin{tabular*}{\textwidth}{@{}l l l l l l}
+\mr
+Optimizer & Adam($\alpha$ = 0.001, $\beta_{1}$ = 0.5) & & & & \\
+Batch size & 1000 & & & & \\
+Epochs & 100 & & & & \\
+Loss & Binary cross-entropy & & & & \\
+ \br
+\end{tabular*}\\
+\label{Tab:cnn_training_parms}
+\end{table}
+
 \section{Many more generated examples}

### 2020-12-09 Paper_draft/main.tex
Further comments from Michael

@@
 \newcommand{\dcc}{LIGO-PXXXXXXX}
+
+\newcommand{\ndimensional}[1]{$#1$\nobreakdash\discretionary{-}{-}{-}dimensional}
+
 %\input{tag.tex}
@@
 \acrodef{BBH}[BBH]{binary black hole}
-\acrodef{SNR}[SNR]{signal to noise ratio}
+\acrodef{SNR}[SNR]{signal-to-noise ratio}
 \acrodef{PSD}[PSD]{power spectral density}
@@
 (b) A selection of activation functions used in this study.
-The sigmoid (purple), rectified linear unit \cite{relu} (orange) and leaky rectified linear unit \cite{Maas2013RectifierNI} (green).
+The sigmoid (purple), rectified linear unit (ReLU) \cite{relu} (orange) and leaky rectified linear unit \cite{Maas2013RectifierNI} (green).
 (c)
 A an example of a neural network containing two hidden layers that performs a
-mapping of an input vector to a single output.}
+mapping of an input vector to a single output. \michael{Minor comment, it's hard to see what the ReLU is doing above 0, maybe use different line styles for each?}}
 \end{figure}
@@
 The goal of \ac{GAN} training is to find an equilibrium between the two models, if this cannot be found then it is said that the \ac{GAN} has failed to converge.
-One way to diagnose \acp{GAN} during the development process is to keep track of the loss and accuracy over time.
+One way to diagnose \acp{GAN} during the development process is to keep track of the loss and accuracy over time \michael{what is being diagnosed?
+Is development the same as training?
+I get what this sentence is saying but I think it could be re-written}.
 Loss plots, for example, as seen in \cref{fig:lossplot} can help to identify common failure modes or to check if the \ac{GAN} has indeed converged.
@@
 Early in training the losses oscillate as both models attempt to find their equilibrium, after which, both losses vary around a point which signifies stable training.
-Accuracies on the real and fake data are similar showing that neither model is stronger than the other.}
+Accuracies on the real and fake data are similar, showing that neither model is stronger than the other.}
     \label{fig:lossplot}
@@
 attribute label, $\mathbf{c}$.
-This simple addition has shown to work well in practice, for instance in image-to-image translation~\cite{isola2016imagetoimage}.
-We defined the classes by one-hot encoding, that is, each class resides at the corner points of a 5 dimensional cube.
+This simple addition has been shown to work well in practice, for instance in image-to-image translation~\cite{isola2016imagetoimage}.
+We use one-hot encoding to define the classes, that is, each class resides at the corner points of a \ndimensional{5} cube.
 For example $\mathbf{c}=[0,1,0,0,0]$ represents the ringdown signal class.
@@
     \caption{Examples of the five different waveforms that were used in training the \ac{GAN} for this study.
-Values of the parameters were selected randomly from uniform distributions from \cref{Tab:training_parms}.}
+Values of the parameters were selected randomly from uniform distributions from \cref{Tab:training_parms}.
+\michael{Ringdown is hyphenated here, this is the only place}}
     \label{fig:training_waveforms}
@@
 %
-We propose a signal generation scheme using a \ac{CGAN} trained on burst-like
-waveforms. We call this \texttt{McGANn}\footnote{https://github.com/jmcginn/McGANn} and it is a \ac{CGAN} trained on five signal classes each spanning a range
-of prior signal parameters. The signal classes are:
+We propose a signal generation scheme using a \ac{CGAN} trained on burst-like waveforms.
+We call this \texttt{McGANn}\footnote{https://github.com/jmcginn/McGANn} and it is a \ac{CGAN} trained on five signal classes each spanning a range of prior signal parameters.
+The signal classes are:
 
@@
 \item {\bf Sine-Gaussian}: $h_{\text{sg}}(t) = A \exp\left[ - (t-t_{0})^2 /
-\tau^2 \right] \sin (2 \pi f_0 (t-t_0) + \phi)$, a sinusoidal wave with a Gaussian
-envelope characterised by a central frequency, $f_0$, amplitude, $A$, time of arrival, $t_{0}$ and phase, $\phi$ which is uniformly sampled between [0,2$\pi$]. 
+\tau^2 \right] \sin (2 \pi f_0 (t-t_0) + \phi)$, \michael{Could capitalise SG here?} a sinusoidal wave with a Gaussian
+envelope characterised by a central frequency, $f_0$, amplitude, $A$, time of arrival, $t_{0}$ and phase, $\phi$ which is uniformly sampled between $[0, 2\pi]$ \michael{The commas here are a bit of mess, I find it hard to read I think either remove the comma before each symbol or use brackets?
+The same applies to this whole list.
+I've removed them in the next point, see what you think.}.
 %
 \item {\bf Ringdown}: $h_{\text{rd}}(t) = A \exp \left[-{(t-t_0)} / {\tau}
-\right] \sin(2 \pi f_0 (t-t_0) + \phi)$, with frequency $f_0$ and duration $\tau$, amplitude, $A$, time of arrival, $t_{0}$, $\phi$ which is uniformly sampled between [0,2$\pi$. 
+\right] \sin(2 \pi f_0 (t-t_0) + \phi)$, with frequency $f_0$ and duration $\tau$, amplitude $A$, time of arrival $t_{0}$ and phase $\phi$ which is uniformly sampled between $[0, 2\pi]$. 
 %
@@
 mid-points of all but the ringdown and \ac{BBH} classes) are randomly drawn from a uniform distribution to
-be within [0.4, 0.6] seconds from the start of the 1 sec time interval and all
+be within $[0.4, 0.6]$ seconds from the start of the 1 sec time interval and all
 training waveforms are sampled at 1024 Hz.  The parameter prior ranges are
@@
 \centering
-\caption{The parameters used in generating the training data. Each parameter is drawn uniformly in the below ranges.}
+\caption{The parameters used in generating the training data.
+Each parameter is drawn uniformly in the below ranges.
+\michael{You've used a mix of - and N/A, are they the same thing or do they indicate something different?}}
 %\footnotesize
@@
 can tune when designing the model and these are referred to as hyperparameters.
-The final network design used in this work comes from the use of trial and
+The final network design used in this work comes was developed through trial and
 error and the initial designs influenced by the available literature. We found
@@
 
-The design of the networks is influenced by \cite{Radford2015} in which they use a \ac{DCGAN} architecture. The generator model is fully convolutional,
-upsampled using strided transposed convolutions
-with batch normalisation in the
-first layer and ReLU activations throughout with the exception of a linear activation for
-the output layer. The use of a linear activation guarantees the output can have negative and positive outputs. Each transposed
-convolutional layer uses a kernel size of 18 and stride of 2. The discriminator network
-mirrors that of the generator without batch normalization, using
-LeakyReLU activations, SpatialDropout, and a 2-stride convolution for
-downsampling. The discriminator output is a single node with sigmoid activation that can be interpreted as a probability of the the signal being real and both models are trained with binary cross
-entropy \cref{eqn:crossentropy}. The full architecture description can be seen in~\cref{Tab:gan_training_parms}.
-
-All models were designed with the Python Keras library \cite{} and TensorFlow \cite{} and trained on a GeForce RTX 2080 Ti GPU.
+The design of the networks is influenced by \cite{Radford2015} in which they use a \ac{DCGAN} architecture.
+The generator model is fully convolutional, upsampled using strided transposed convolutions with batch normalisation in the first layer and ReLU activations throughout with the exception of a linear activation for the output layer.
+The use of a linear activation guarantees the output can have negative and positive outputs.
+Each transposed convolutional layer uses a kernel size of 18 and stride of 2.
+The discriminator network mirrors that of the generator without batch normalization, using LeakyReLU activations, SpatialDropout, and a 2-stride convolution for downsampling.
+The discriminator output is a single node with sigmoid activation that can be interpreted as a probability of the the signal being real and both models are trained with binary cross entropy \cref{eqn:crossentropy}.
+The full architecture description can be seen in~\cref{Tab:gan_training_parms}.
+
+All models were designed with the Python Keras library \cite{} and TensorFlow \cite{} \michael{Just a reminder these are missing} and trained on a GeForce RTX 2080 Ti GPU.
 We train the networks for 500 epochs which takes $\mathcal{O}(10)$ hours and save the model at each epoch.
@@
 %
-Given a 100-dimensional vector drawn from a normal distributed latent space and a one-hot encoded class
+Given a \ndimensional{100} vector drawn from a normal distributed latent space and a one-hot encoded class
 label, the GAN is able to generate burst-like waveforms generalised from the
@@
 latent and class spaces by interpolating between points in these spaces. We
-test two methods of sampling from the class space that can be used to generate
-a new signals composed of weighted elements of each training class.
+test two methods of sampling \michael{Might be confused, but don't we use three methods: vertex, simplex and uniform?}  from the class space that can be used to generate new signals composed of weighted elements of each training class.
+
 \begin{figure}[!h]
@@
 By row: sine-Gaussian, Ringdown,
-white noise burst, Gaussian pulse, binary black hole merger. For ease of viewing, the $x$-axis for all panels spans the mid 50\% of the output range.}
+white noise burst, Gaussian pulse, binary black hole merger.
+For ease of viewing, the $x$-axis for all panels spans the mid 50\% of the output range.
+\michael{I think we mentioned increasing the y-axis limits a little so it's clearer the signals end at $\pm 1$}}
 \label{fig:gen_signals} 
@@
 In \cref{fig:gen_signals} we show conditional signal generations using our generator network.
-We can see the generations are of very good quality and appear as though they could have plausibly come from the training set.
+We can see the generations are of very good quality \michael{Personally don't like using good quality without a metric to quantify things.} and appear as though they could have plausibly come from the training set.
 We can also see that the model has learned the overall characteristics of the five training classes and is able to disentangle each class and associate them with the conditional input.
@@
 We can see that each plot shows plausible waveforms suggesting that the generator has constructed a smooth traversable, space.
-We note that the relationship between the latent space location and the physical signal parameters are hidden from us, and hence the initial and final latent space locations (moving left to right in \cref{fig:z_interp}) simply represent random possible signals learned from the training set prior.
+We note that the relationship between the latent space location and the physical signal parameters is intractable, and hence the initial and final latent space locations (moving left to right in \cref{fig:z_interp}) simply represent random possible signals learned from the training set prior.
 During training the network should have learned how to smoothly represent the underlying features of a signal as a function of latent space location.
 For example, the linearly interpolated transition through the latent space for the Gaussian pulse signal shows a shift to earlier epoch and larger decay timescale.
-In contrast, the transition for the Ringdown signal appears to pass through a localised region of latent-space consistent with higher central frequency.
+In contrast, the transition for the Ringdown \michael{Ringdown is sometimes capatilised and sometimes not, not sure what convention we're using} signal appears to pass through a localised region of latent-space consistent with higher central frequency.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-While the \ac{GAN} is trained on distinct one-hot encoded classes, we may test arbitrary points in the 5-dimensional class space to produce indistinct or hybrid waveforms.
+While the \ac{GAN} is trained on distinct one-hot encoded classes, we may test arbitrary points in the \ndimensional{5} class space to produce indistinct or hybrid waveforms.
 In order to explore the class-space, in \cref{fig:c_interp} we show results where the latent vector is held constant but we instead linearly
@@
 The results show that for each case that the generated signals show distinct characteristics of the respective class pairs at most stages of the transition.
-We note that transitions in some cases appear to be rather abrupt, e.g., between the Gaussian pulse and the \ac{BBH}, \chris{but we point out that this feature, whilst not uncommon, is a strong function of the random latent-space location.}
+We note that transitions in some cases appear to be rather abrupt, e.g., between the Gaussian pulse and the \ac{BBH}, \chris{but we point out that this feature, whilst not uncommon, is a strong function of the random latent-space location.} \michael{We sometimes hyphenate class space and sometimes don't}
 %
@@
 \subsection{General points within the class space}
-We have shown that the \acp{GAN} latent-space and class-space have structure that can be navigated via interpolation between pairs of locations within each respective space.
+We have shown that the \acp{GAN} latent-space and class-space \michael{Same comment about hyphenation for latent space.} have structure that can be navigated via interpolation between pairs of locations within each respective space.
 Taking a step further, we can sample from the class-space in novel ways to create new inputs for the generator.
@@
 %
-\item {\bf Vertex}: Points that lie at the corners of the five dimensional class space.
+\item {\bf Vertex}: Points that lie at the corners of the \ndimensional{5} class space.
 These class-space locations are equivalent to the training set locations and are our closest generated representation of the training set.
@@
 \item {\bf Simplex}: This class vector we define as uniformly sampled points on a simplex, which is a generalization of a triangle in $k$-dimensions.
-We sample uniformly on the $k=4$ simplex that is embedded in the 5-dimensional class hyper-cube.
+We sample uniformly on the $k=4$ simplex that is embedded in the \ndimensional{5} class hyper-cube.
 In practice we use the equivalent of sampling points from a $k=4$ Dirichlet distribution.
@@
 \item {\bf Uniform}: Each of the entries in the class vector is sampled from a uniform distribution $\text{U}[0,1]$.
-This is equivalent to sampling uniformly within the 5-dimensional one-hot encoding hyper-cube.
+This is equivalent to sampling uniformly within the \ndimensional{5} one-hot encoding hyper-cube.
 %
@@
 
-The vertex points are the most straightforward where one element of the class vector contains 1 and the other elements are zero.
+The vertex points are the most straightforward where one element of the class vector contains one and the other elements are zero.
 these points are equivalent to the class vectors that the \ac{GAN} is trained on e.g., $\mathbf{c} = [1,0,0,0,0]$ would correspond to a sine-Gaussian generation.
-Uniform class vectors with each element sampled from a uniform distribution are equivalent to a random draw from a 5-dimensional hyper-cube.
+Uniform class vectors with each element sampled from a uniform distribution are equivalent to a random draw from a \ndimensional{5} hyper-cube.
 Uniformly sampling generates class-space locations up to a maximum distance of unity from the closest class e.g.
-[0,0,0,0,0] is of distance 1 away from all classes (as is [1,1,1,1,1]).
+$[0,0,0,0,0]$ is of distance 1 away from all classes (as is $[1,1,1,1,1]$ \michael{Isn't this point further?
+$\sqrt{(1-1)^2 + 1^2 + 1^2 + 1^2 + 1^2} = \sqrt{4} = 2$?}).
 For simplex class vectors, we sample from the simplest hyper-surface that intersects all the classes and has a symmetry such that no training class location (any vertex) is favoured over any other.
-For our 5-dimensional case this corresponds to a 4-simplex manifold.
+For our \ndimensional{5} case this corresponds to a 4-simplex manifold.
 Sampling from the simplex can be seen as sampling from the simplest space that spans between the training classes.
@@
 Both methods of generating hybrid waveforms, however, do produce signals that appear to share characteristics from the training set but still be distinct in signal morphology.
-Upon inspection of a larger collection of waveform generations from both methods we do see a tendency for the uniform hyper-cube approach to generate more wider variety of hybrid waveforms that are more visually distinct from the training set.
+Upon inspection of a larger collection of waveform generations from both methods we do see a tendency for the uniform hyper-cube approach to generate a wider variety of hybrid waveforms that are more visually distinct from the training set.
 This is to be expected given that the simplex class-space is a subset of the hyper-cube and does not explore regions of the class-space as far from the training set vertices.
@@
     \includegraphics[width=\textwidth]{figures/generations/simplex_sample5.png}
-    \caption{GAN generations where the class vectors are sampled from the 4-dimensional plane (simplex) intersecting all training classes.
-Latent space locations for all signals are taken randomly from a 100-dimensional Gaussian distribution and the signals are then re-scaled such that they have maximum absolute amplitude at unity.
+    \caption{GAN generations where the class vectors are sampled from the \ndimensional{4} plane (simplex) intersecting all training classes.
+Latent space locations for all signals are taken randomly from a \ndimensional{100} Gaussian distribution and the signals are then re-scaled such that they have maximum absolute amplitude at unity.
 The class label for each generation is shown above each panel.}
@@
     \caption{GAN generations where the class vectors are sampled uniformly in the hyper-cube class space.
-Latent space locations for all signals are taken randomly from a 100-dimensional Gaussian distribution and the signals are then re-scaled such that they have maximum absolute amplitude at unity.}
+Latent space locations for all signals are taken randomly from a \ndimensional{100} Gaussian distribution and the signals are then re-scaled such that they have maximum absolute amplitude at unity.
+\michael{Same comment about y-axis labels}}
     \label{fig:uniform_samples}
@@
 
-\subsection{Noisy data-sets} 
+\subsection{Noisy datasets} 
 We use three classes of waveforms: vertex, uniform, and simplex cases generated using our \ac{GAN} method.
@@
 Signal network \acp{SNR} is drawn uniformly in the range $[1,16]$ and is controlled by an amplitude scaling applied to the waveform.
-Each 1 second duration time-series input to the \ac{CNN} is represented by a 1-dimensional 1024 sample vector with 2 channels representing each detector.
+Each 1 second duration time-series input to the \ac{CNN} is represented by a \ndimensional{1} 1024 sample vector with 2 channels representing each detector.
 Example time-series from each detector for a single signal is shown in \cref{fig:cnn_training}.
@@
 We randomly divide the data into the 3 standard sets (training, validation, and test data) where 40\% is used for training, 10\% used for validation, and 50\% is used for testing in order to achieve suitably low false-alarm rates.
-For the Uniform and Simplex data-sets samples are drawn uniformly from their respective spaces.
+For the Uniform and Simplex datasets samples are drawn uniformly from their respective spaces.
 For the vertex data-set the 5 different vertex locations in class-space are sampled with equal probability.
@@
 We used binary cross-entropy \cref{eqn:crossentropy} as the loss function and Adam as an optimizer with learning rate set to $10^{-3}$.
-In total we train three separate \acp{CNN} on the vertex, uniform and simplex data set respectively.
-In each case the networks share the same architecture and hyper-parameters which are defined in \cref{Tab:cnn_training_parms}.
+In total we train three separate \acp{CNN} on the vertex, uniform and simplex datasets respectively.
+In each case the networks share the same architecture and hyperparameters which are defined in \cref{Tab:cnn_training_parms}.
 
@@
 We now compare the \ac{CNN} results between the data-sets by first training three \acp{CNN} on the vertex, simplex, and uniform data-sets and then using these models to make predictions on the other testing data unseen during the network training process.
-In~\cref{fig:eff_curves} the top plot represents results from each trained network tested on the vertex data and shows that each model confidently classifies all data at 100\% for \ac{SNR}$>$13.
+In~\cref{fig:eff_curves} the top plot represents results from each trained network tested on the vertex data and shows that each model confidently classifies all data at 100\% for $\text{\ac{SNR}} >13$.
 At smaller \acp{SNR} the vertex and simplex perform similarly, however, the uniform data performs slightly worse.
@@
 The true alarm probability is plotted as a function of the optimal \ac{SNR} of the signals.
-Each plot shows the performance of a \ac{CNN} trained on vertex, simplex and uniform datasets tested on vertex (top), simplex (middle), uniform (bottom).}
+Each plot shows the performance of a \ac{CNN} trained on vertex, simplex and uniform datasets tested on vertex (top), simplex (middle), uniform (bottom).
+\michael{Maybe add a subcaption under each saying which dataset the models are tested on}}
 \label{fig:eff_curves}
@@
 Batch normalisation is applied to the output of the first layer and all convolutional layers are activated by ReLU with the exception of the final layer which is Linear.
-Finally, the extra dimension introduced for the convolution is removed.}
+Finally, the extra dimension introduced for the convolution is removed.
+\michael{You say 500 epochs in the test but 100 here, not sure which is right.
+Also could include learning rate with tyhe optimiser}}
 %\footnotesize

### 2020-12-09 Paper_draft/main.tex
addressed some of Michaels comments regarding hyphens and grammatical consistency

@@
 Each parameter is drawn uniformly in the below ranges.
-\michael{You've used a mix of - and N/A, are they the same thing or do they indicate something different?}}
+\michael{You've used a mix of - and N/A, are they the same thing or do they indicate something different?} \jordan{I changed N/A to "-" as they do really mean the same thing.}}
 %\footnotesize
@@
 Sine-Gaussian & 70 - 250 & 0.004 - 0.03 & 0.4 - 0.6 & -  \\  
-Ringdown & 70 - 250 & 0.004 - 0.03 & 0.4 - 0.6 & N/A \\
-white noise burst & 70 - 250 & 0.004 - 0.03 & 0.4 - 0.6 & N/A  \\
+Ringdown & 70 - 250 & 0.004 - 0.03 & 0.4 - 0.6 & - \\
+white noise burst & 70 - 250 & 0.004 - 0.03 & 0.4 - 0.6 & -  \\
 Gaussian pulse & - & 0.004 - 0.03 & 0.4 - 0.6 & -  \\
@@
 latent and class spaces by interpolating between points in these spaces. We
-test two methods of sampling \michael{Might be confused, but don't we use three methods: vertex, simplex and uniform?}  from the class space that can be used to generate new signals composed of weighted elements of each training class.
+test three methods of sampling from the class space that can be used to generate new signals composed of weighted elements of each training class.
 
@@
 The latent space inputs for each panel are randomised and each row is assigned one of the five class vectors.
-By row: sine-Gaussian, Ringdown,
+By row: sine-Gaussian, ringdown,
 white noise burst, Gaussian pulse, binary black hole merger.
@@
     \includegraphics[width=\textwidth]{figures/generations/z_interp_bbh.png}
-    \caption{\ac{GAN} generated interpolated waveforms plotted as a function of time showing latent-space interpolations.
+    \caption{\ac{GAN} generated interpolated waveforms plotted as a function of time showing latent space interpolations.
 For each interpolation two different points were randomly chosen in the latent space and represent the first last panels in each row.
@@
 Each row keeps its class vector constant throughout the latent space interpolation.
-By row: sine-Gaussian, Ringdown, white noise burst, Gaussian pulse, binary black hole merger.
+By row: sine-Gaussian, ringdown, white noise burst, Gaussian pulse, binary black hole merger.
 For ease of viewing, the $x$-axis for all panels spans the mid 50\% of the output range.}
@@
 For example, the linearly interpolated transition through the latent space for the Gaussian pulse signal shows a shift to earlier epoch and larger decay timescale.
-In contrast, the transition for the Ringdown \michael{Ringdown is sometimes capatilised and sometimes not, not sure what convention we're using} signal appears to pass through a localised region of latent-space consistent with higher central frequency.
+In contrast, the transition for the ringdown signal appears to pass through a localised region of latent space consistent with higher central frequency.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 While the \ac{GAN} is trained on distinct one-hot encoded classes, we may test arbitrary points in the \ndimensional{5} class space to produce indistinct or hybrid waveforms.
-In order to explore the class-space, in \cref{fig:c_interp} we show results where the latent vector is held constant but we instead linearly
-interpolate within the one-hot encoded class-space between pairs of the well-defined training class locations.
-In this scenario we highlight that the \ac{GAN} has not yet probed this intermediate class-space during its training and therefore we are reliant on the generator having learned any underlying class space relationships between the 5 training classes.
+In order to explore the class space, in \cref{fig:c_interp} we show results where the latent vector is held constant but we instead linearly
+interpolate within the one-hot encoded class space between pairs of the well-defined training class locations.
+In this scenario we highlight that the \ac{GAN} has not yet probed this intermediate class space during its training and therefore we are reliant on the generator having learned any underlying class space relationships between the 5 training classes.
 The results show that for each case that the generated signals show distinct characteristics of the respective class pairs at most stages of the transition.
-We note that transitions in some cases appear to be rather abrupt, e.g., between the Gaussian pulse and the \ac{BBH}, \chris{but we point out that this feature, whilst not uncommon, is a strong function of the random latent-space location.} \michael{We sometimes hyphenate class space and sometimes don't}
+We note that transitions in some cases appear to be rather abrupt, e.g., between the Gaussian pulse and the \ac{BBH}, \chris{but we point out that this feature, whilst not uncommon, is a strong function of the random latent space location.} \michael{We sometimes hyphenate class space and sometimes don't}
 %
@@
     \includegraphics[width=\textwidth]{figures/generations/blip-bbh.png}
-    \caption{\ac{GAN} generated class interpolated waveforms as a function of time showing class-space interpolations.
+    \caption{\ac{GAN} generated class interpolated waveforms as a function of time showing class space interpolations.
 A single latent space vector is used for all generations and is chosen randomly in the latent space.
 Each row shows generations using linearly interpolated classes as inputs to the generator.
-By row top to bottom: Sine-Gaussian to Ringdown, Ringdown to white noise burst, Gaussian pulse to BBH.\chris{add class vectors on each panel}}
+By row top to bottom: Sine-Gaussian to ringdown, ringdown to white noise burst, Gaussian pulse to BBH.\chris{add class vectors on each panel}}
     \label{fig:c_interp}
@@
 \subsection{General points within the class space}
-We have shown that the \acp{GAN} latent-space and class-space \michael{Same comment about hyphenation for latent space.} have structure that can be navigated via interpolation between pairs of locations within each respective space.
-Taking a step further, we can sample from the class-space in novel ways to create new inputs for the generator.
-These new points are categorised by the method used to sample from the class-space.
+We have shown that the \acp{GAN} latent space and class space \michael{Same comment about hyphenation for latent space.} have structure that can be navigated via interpolation between pairs of locations within each respective space.
+Taking a step further, we can sample from the class space in novel ways to create new inputs for the generator.
+These new points are categorised by the method used to sample from the class space.
 The methods we use are divided into the following:
@@
 \item {\bf Vertex}: Points that lie at the corners of the \ndimensional{5} class space.
-These class-space locations are equivalent to the training set locations and are our closest generated representation of the training set.
+These class space locations are equivalent to the training set locations and are our closest generated representation of the training set.
 %
@@
 Uniform class vectors with each element sampled from a uniform distribution are equivalent to a random draw from a \ndimensional{5} hyper-cube.
-Uniformly sampling generates class-space locations up to a maximum distance of unity from the closest class e.g.
+Uniformly sampling generates class space locations up to a maximum distance of unity from the closest class e.g.
 $[0,0,0,0,0]$ is of distance 1 away from all classes (as is $[1,1,1,1,1]$ \michael{Isn't this point further?
@@
 In \cref{fig:simplexd_samples} we show generations conditioned on class vectors drawn randomly from the 4-simplex.
-There are large variations in the signals with some having characteristics strongly resembling the training classes, although this can be partially explained through the random draws from the simplex as there is finite probability that one class entry will dominate over the others (i.e., the class-space location is close to a vertex).
-For instance the generations that look more like sine-Gaussians than hybrid waveforms generally have a larger value placed in the first class-space element than others.
+There are large variations in the signals with some having characteristics strongly resembling the training classes, although this can be partially explained through the random draws from the simplex as there is finite probability that one class entry will dominate over the others (i.e., the class space location is close to a vertex).
+For instance the generations that look more like sine-Gaussians than hybrid waveforms generally have a larger value placed in the first class space element than others.
 Similarly \cref{fig:uniform_samples} shows generations conditioned on class vectors drawn uniformly in the unit hyper-cube.
@@
 Upon inspection of a larger collection of waveform generations from both methods we do see a tendency for the uniform hyper-cube approach to generate a wider variety of hybrid waveforms that are more visually distinct from the training set.
-This is to be expected given that the simplex class-space is a subset of the hyper-cube and does not explore regions of the class-space as far from the training set vertices.
+This is to be expected given that the simplex class space is a subset of the hyper-cube and does not explore regions of the class space as far from the training set vertices.
 
@@
 For the Uniform and Simplex datasets samples are drawn uniformly from their respective spaces.
-For the vertex data-set the 5 different vertex locations in class-space are sampled with equal probability.
+For the vertex data-set the 5 different vertex locations in class space are sampled with equal probability.
 
@@
 Operation & Output shape & Kernel size & Stride & Dropout & Activation \\
-Class Input & (5) & N/A & N/A & 0  & N/A \\
-Dense & (1024) & N/A & N/A & 0 & N/A \\
-Signal Input & (1024) & N/A & N/A & 0 &  N/A \\
-Concatenate & (1024, 2) & N/A & N/A & 0 &  N/A \\
+Class Input & (5) & - & - & 0  & - \\
+Dense & (1024) & - & - & 0 & - \\
+Signal Input & (1024) & - & - & 0 &  - \\
+Concatenate & (1024, 2) & - & - & 0 &  - \\
 Convolutional & (512, 64) & 14 & 2 & 0.5 & Leaky ReLU \\
@@
 Convolutional & (64, 512) & 14 & 2 & 0.5 &  Leaky ReLU \\
-Flatten & (32768) & N/A & N/A & 0 &  N/A \\
-Dense & (1) & N/A & N/A & 0 & sigmoid \\
+Flatten & (32768) & - & - & 0 &  - \\
+Dense & (1) & - & - & 0 & sigmoid \\
 \mr
@@
 Operation & Output shape & Kernel size & Stride & BN & Activation \\
-Class Input & (5) & N/A & N/A & \ding{55}  & N/A \\
-Latent Input  & (100) & N/A & N/A & \ding{55} & N/A \\
-Concatenate & (105) & N/A & N/A & \ding{55} &  N/A \\
-Dense & (32768) & N/A & N/A & \ding{55} &  ReLu \\
-Reshape & (64, 512) & N/A & N/A & \ding{55} & N/A \\
+Class Input & (5) & - & - & \ding{55}  & - \\
+Latent Input  & (100) & - & - & \ding{55} & - \\
+Concatenate & (105) & - & - & \ding{55} &  - \\
+Dense & (32768) & - & - & \ding{55} &  ReLu \\
+Reshape & (64, 512) & - & - & \ding{55} & - \\
 Transposed Conv & (128, 256) & 18 & 2 & \ding{51} & ReLU \\
@@
 Transposed Conv & (1024, 1) & 18 & 2 & \ding{55} & Linear \\
-Reshape & (1024) & N/A & N/A & \ding{55} & N/A \\
+Reshape & (1024) & - & - & \ding{55} & - \\
 \end{tabular*}
@@
 \mr
-Input & (1024, 2) & N/A  & N/A & N/A & N/A \\
+Input & (1024, 2) & -  & - & - & - \\
 Convolutional & (512, 8) & 5 & 2 & 0 & Swish  \\
@@
 Convolutional & (64, 8) & 5 & 2 & 0 & Swish  \\
-Dense & (100) & 100 & N/A & 0.2 & Linear  \\
-Dense & (1) & 1 & N/A & 0 & sigmoid \\
+Dense & (100) & 100 & - & 0.2 & Swish  \\
+Dense & (1) & 1 & - & 0 & sigmoid \\
 \end{tabular*}\\

### 2020-12-17 Paper_draft/main.tex
recent changes 16/11

@@
 \acrodef{DCGAN}[DCGAN]{deep convolutional generative adversarial network}
-\acrodef{CNN}[CNN]{convolutional neural networks}
 \acrodef{BBH}[BBH]{binary black hole}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%textwidth in inches: \printinunitsof{in}\prntlen{\textwidth}
+textwidth in inches: \printinunitsof{in}\prntlen{\textwidth}
 \begin{comment}
@@
 %
-Gravitational wave astronomy is now an established field that began with the first
+\Ac{GW} astronomy is now an established field that began with the first
 detection of a binary black hole merger~\cite{Abbott2016} in September 2015.
@@
 generate waveforms in fractions of a second and produce waveforms that are difficult to generate with current
-techniques. These new varieties of waveforms can then be used to diagnose \michael{not sure about diagnose, maybe test or evaluate?}
+techniques. These new varieties of waveforms can then be used to evaluate
 detection algorithms, gain new insight into sources of \ac{GW}
@@
 We present the results of the GAN in \cref{results} and show how unmodeled signals can be produced by interpolating and sampling within latent and class spaces.
-In \cref{cnn classifier} we show that a convolutional neural network \michael{should this have the accronym?
-Tried to fix it but it only puts the plural for me} classifier can be trained to distinguish between sets of our GAN generated waveforms from noise only cases.
+In \cref{cnn classifier} we show that a \ac{CNN} classifier can be trained to distinguish between sets of our \ac{GAN} generated waveforms from noise only cases.
 We conclude with a summary of the presented work in \cref{conclusions}.
@@
 	\resizebox{\textwidth}{!}{
- 	\begin{tikzpicture}		
-		    \node[scale=0.3] 		   (x1) at (0,0.8) {$x_1$}; 
-		    \node[scale=0.3] 		   (x2) at (0,0.5) {$x_2$};  
-		    \node[scale=0.3] 		   (x3) at (0,0.2) {$x_3$};       
-    		    \node [draw, circle,scale=0.18,fill=blue!25]          (c3) at (0.7,0.5) {\Large $\sigma(\sum_i w_i x_i + b)$};
-    \draw[->] (x1)--(c3);
-    \draw[->] (x2)--(c3);
-    \draw[->] (x3)--(c3);
-     \draw[->] (c3)--(1.3,0.5);
-   	\end{tikzpicture}
+ 	\includegraphics{figures/neuron.pdf}
 	}
@@
 	\resizebox{\textwidth}{!}{
-\begin{tikzpicture}
-\begin{axis}[
-    xmin=-2.5, xmax=2.5,
-    ymin=-1.5, ymax=1.5,
-    axis lines=center,
-    axis on top=true,
-    domain=-2.5:2.5,
-    ylabel=$\sigma$,
-    xlabel=$x$,
-    ]
-
-    \addplot [mark=none,draw=purple,domain=-2.5:2.5,ultra thick] {1/(1+exp(-x))};
-    \addplot+[mark=none,draw=green,domain=-2.5:0,ultra thick] {0};
-    \addplot+[mark=none,draw=green,domain=0:2.5,ultra thick] {x};
-    \addplot+[mark=none,orange,domain=-2.5:0,ultra thick] {0.2*x};
-    \addplot+[mark=none,orange,domain=0:2.5,ultra thick] {x};
-
-    %% Add the asymptotes
-\end{axis}
-\end{tikzpicture}
-	}
+\includegraphics{figures/activation.pdf}}
 \caption{}
-	 \label{fig:activations}
+\label{fig:activation}
 \end{subfigure}
@@
 \resizebox{\textwidth}{!}{
-\def\layersep{1.5cm}
-\begin{tikzpicture}[shorten >=1pt,draw=black, ->,node distance=\layersep]
-
-    \tikzstyle{every pin edge}=[<-,shorten <=1pt]
-    \tikzstyle{neuron}=[circle,draw=black, very thick, fill=blue!25, minimum size=22pt,inner sep=0pt]
-    \tikzstyle{input neuron}=[circle,draw=black,very thick,fill=black!25, minimum size=22pt,inner sep=0pt];
-    \tikzstyle{output neuron}=[neuron];
-    \tikzstyle{hidden neuron}=[circle,draw=black,very thick,fill=blue!25,minimum size=22pt,inner sep=0pt];
-    \tikzstyle{annot} = [text width=4em, text centered]
-
-    % Draw the input layer nodes
-    \foreach \name / \y in {1,...,5}
-    % This is the same as writing \foreach \name / \y in {1/1,2/2,3/3,4/4}
-        \node[input neuron] (I-\name) at (0,-\y) {$x_{\name}$};
-
-    % Draw the hidden layer nodes
-    \foreach \name / \y in {1,...,3}
-        \path[yshift=-1cm]
-            node[hidden neuron] (H-\name) at (\layersep,-\y cm) {};
-
-  \foreach \namee / \y in {1,...,3}
-        \path[yshift=-1 cm]
-            node[hidden neuron] (H1-\namee) at (2*\layersep,-\y cm){};
-
-    % Draw the output layer node
-  \node[output neuron,pin={[pin edge={->}]right:}, right of=H1-2] (O) {};
-    % Connect every node in the input layer with every node in the
-    % hidden layer.
-    \foreach \source in {1,...,5}
-        \foreach \dest in {1,...,3}
-            \path (I-\source) edge (H-\dest);
-
- \foreach \source in {1,...,3}
-        \foreach \dest in {1,...,3}
-            \path (H-\source) edge (H1-\dest);
-
-    % Connect every node in the hidden layer with the output layer
-    \foreach \source in {1,...,3}
-        \path (H1-\source) edge (O);
-
-    % Annotate the layers
-    %\node[annot,above of=H-1, node distance=1cm] (hl) {Hidden layers};
-   % \node[annot,left of=I-4] at (0) {Input layer};
-    %\node[annot,right of=hl] {Output layer};
-
-    \draw[decoration={brace,mirror,raise=15pt},decorate,-]
-  (I-1.north) -- node[left=0.8cm,scale=0.7] {Input layer} (I-5.south);
-
-    \draw[decoration={brace,raise=15pt},decorate,-]
-  (H-1.west) --  node[above=0.8cm,scale=0.7]{Hidden layers}  (H1-1.east);
-
-    \draw[decoration={brace,raise=15pt},decorate,-]
-  (O.west) --  node[above=0.8cm,scale=0.7]{Output layers}  (O.east);
-
-\end{tikzpicture}
+
+\includegraphics{figures/network.pdf}
 }
@@
 (b) A selection of activation functions used in this study.
-The sigmoid (purple), rectified linear unit (ReLU) \cite{relu} (orange) and leaky rectified linear unit \cite{Maas2013RectifierNI} (green).
+The sigmoid (solid purple), rectified linear unit (ReLU) \cite{relu} (dashed wild strawberry red) and leaky rectified linear unit \cite{Maas2013RectifierNI} (dotted blue).
 (c)
 A an example of a neural network containing two hidden layers that performs a
-mapping of an input vector to a single output. \michael{Minor comment, it's hard to see what the ReLU is doing above 0, maybe use different line styles for each?}}
+mapping of an input vector to a single output.}
 \end{figure}
@@
 %
-where $w$ and $b$ are the weights and bias and $\sigma$
-denotes the activation function. The weights are numbers which can be thought
-of as the strength between connected neurons.
+where $w$ and $b$ are the weights and bias and $\sigma$ denotes the activation function.
+The weights are numbers which can be thought of as the strength between connected neurons.
 The output of a neuron is defined by its activation function which controls how the neuron `fires' depending on its input.
-Some examples of commonly used activation functions are shown in~\cref{fig:activations}.
-It is often useful to introduce a bias, $b$, such that the neuron remains inactive
-above zero but is active when the sum reaches a defined threshold.
+Some examples of commonly used activation functions are shown in~\cref{fig:activation}.
+It is often useful to introduce a bias, $b$, such that the neuron remains inactive above zero but is active when the sum reaches a defined threshold.
 
@@
 The goal of \ac{GAN} training is to find an equilibrium between the two models, if this cannot be found then it is said that the \ac{GAN} has failed to converge.
-One way to diagnose \acp{GAN} during the development process is to keep track of the loss and accuracy over time \michael{what is being diagnosed?
-Is development the same as training?
-I get what this sentence is saying but I think it could be re-written}.
+One way to diagnose problems, such as mode collapse, when training \acp{GAN} is to keep track of the loss and accuracy over time.
 Loss plots, for example, as seen in \cref{fig:lossplot} can help to identify common failure modes or to check if the \ac{GAN} has indeed converged.
@@
 %
-\item {\bf Sine-Gaussian}: $h_{\text{sg}}(t) = A \exp\left[ - (t-t_{0})^2 /
+\item {\bf Sine-Gaussian}: $h_{\text{SG}}(t) = A \exp\left[ - (t-t_{0})^2 /
 \tau^2 \right] \sin (2 \pi f_0 (t-t_0) + \phi)$, \michael{Could capitalise SG here?} a sinusoidal wave with a Gaussian
-envelope characterised by a central frequency, $f_0$, amplitude, $A$, time of arrival, $t_{0}$ and phase, $\phi$ which is uniformly sampled between $[0, 2\pi]$ \michael{The commas here are a bit of mess, I find it hard to read I think either remove the comma before each symbol or use brackets?
-The same applies to this whole list.
-I've removed them in the next point, see what you think.}.
-%
-\item {\bf Ringdown}: $h_{\text{rd}}(t) = A \exp \left[-{(t-t_0)} / {\tau}
+envelope characterised by a central frequency $f_0$, amplitude $A$, time of arrival $t_{0}$ and phase $\phi$ which is uniformly sampled between $[0, 2\pi]$.
+%
+\item {\bf Ringdown}: $h_{\text{RD}}(t) = A \exp \left[-{(t-t_0)} / {\tau}
 \right] \sin(2 \pi f_0 (t-t_0) + \phi)$, with frequency $f_0$ and duration $\tau$, amplitude $A$, time of arrival $t_{0}$ and phase $\phi$ which is uniformly sampled between $[0, 2\pi]$. 
 %
-\item {\bf White noise bursts}: $h_{\text{wn}}(t_j) = Ag_j\exp\left[ -
+\item {\bf White noise bursts}: $h_{\text{WN}}(t_j) = Ag_j\exp\left[ -
 (t-t_{0})^2 / \tau^2 \right]$ where $g_j$ are drawn from a zero mean unit
@@
 %
-\item {\bf Gaussian pulse}: $h_{\text{gp}}(t) = \exp(-t^2 / \tau^2)$ with
+\item {\bf Gaussian pulse}: $h_{\text{GP}}(t) = \exp(-t^2 / \tau^2)$ with
 duration parameter $\tau$.
@@
 \centering
-\caption{The parameters used in generating the training data.
-Each parameter is drawn uniformly in the below ranges.
-\michael{You've used a mix of - and N/A, are they the same thing or do they indicate something different?} \jordan{I changed N/A to "-" as they do really mean the same thing.}}
+\caption{The parameters used in generating the training data. Each parameter is drawn uniformly in the below ranges.}
 %\footnotesize
@@
 
-All models were designed with the Python Keras library \cite{} and TensorFlow \cite{} \michael{Just a reminder these are missing} and trained on a GeForce RTX 2080 Ti GPU.
+All models were designed with the Python Keras library \cite{chollet2015keras} and TensorFlow \cite{tensorflow2015-whitepaper} and trained on a GeForce RTX 2080 Ti GPU.
 We train the networks for 500 epochs which takes $\mathcal{O}(10)$ hours and save the model at each epoch.
@@
 The results show that for each case that the generated signals show distinct characteristics of the respective class pairs at most stages of the transition.
-We note that transitions in some cases appear to be rather abrupt, e.g., between the Gaussian pulse and the \ac{BBH}, \chris{but we point out that this feature, whilst not uncommon, is a strong function of the random latent space location.} \michael{We sometimes hyphenate class space and sometimes don't}
+We note that transitions in some cases appear to be rather abrupt, e.g., between the Gaussian pulse and the \ac{BBH}, \chris{but we point out that this feature, whilst not uncommon, is a strong function of the random latent space location.}
 %
@@
 \subsection{General points within the class space}
-We have shown that the \acp{GAN} latent space and class space \michael{Same comment about hyphenation for latent space.} have structure that can be navigated via interpolation between pairs of locations within each respective space.
+We have shown that the \acp{GAN} latent space and class space have structure that can be navigated via interpolation between pairs of locations within each respective space.
 Taking a step further, we can sample from the class space in novel ways to create new inputs for the generator.
@@
 In this approach the input to the \ac{CNN} are 1024 sample time-series (with 2 channels representing each detector output) which are passed through a series of 4 convolutional layers, onto two fully connected or ``Dense'' layers and finally to a single output neuron which represents the probability that a signal is present within the noise.
-We used dropout in the final dense layer and used a selection of different activation functions including the swish activation \cite{ramachandran2017searching} which improved overall performance and a sigmoid activation for the output layer.
+We used dropout in the final dense layer and used a selection of different activation functions including the swish activation \cite{ramachandran2017searching} which improved overall performance, and a sigmoid activation for the output layer.
 We used binary cross-entropy \cref{eqn:crossentropy} as the loss function and Adam as an optimizer with learning rate set to $10^{-3}$.
@@
 
+\begin{figure}[h!] % "[t!]" placement specifier just for this example
+\centering
+\begin{subfigure}{1\textwidth}
+\centering
+\includegraphics[width=0.7\linewidth]{figures/efficiency_curve_vtest.png}
+%\includegraphics[]{Paper_draft/figures/test.pdf}
+\caption{Tested on vertex}
+\end{subfigure}
+
+\begin{subfigure}{1\textwidth}
+\centering
+\includegraphics[width=0.7\linewidth]{figures/efficiency_curve_stest.png}
+%\includegraphics[]{Paper_draft/figures/test.pdf}
+\caption{Tested on simplex}
+\end{subfigure}
+
+\begin{subfigure}{1\textwidth}
+\centering
+\includegraphics[width=0.7\linewidth]{figures/efficiency_curve_utest.png}
+%\includegraphics[]{Paper_draft/figures/test.pdf}
+\caption{Tested on uniform}
+\end{subfigure}
+
+\caption{Efficiency curves comparing the performance of the \acp{CNN}.
+The true alarm probability is plotted as a function of the optimal \ac{SNR} of the signals.
+Each plot shows the performance of a \ac{CNN} trained on vertex, simplex and uniform datasets tested on vertex (a), simplex (b), uniform (c).}
+\label{fig:eff_curves}
+\end{figure}
+
 \subsection{CNN results}
-We now compare the \ac{CNN} results between the data-sets by first training three \acp{CNN} on the vertex, simplex, and uniform data-sets and then using these models to make predictions on the other testing data unseen during the network training process.
-In~\cref{fig:eff_curves} the top plot represents results from each trained network tested on the vertex data and shows that each model confidently classifies all data at 100\% for $\text{\ac{SNR}} >13$.
-At smaller \acp{SNR} the vertex and simplex perform similarly, however, the uniform data performs slightly worse.
-We would expect that when these models are tested on vertex data that everything should be classified at high \ac{SNR} as the vertex data is a subset of the uniform and vertex.
-The middle plot shows the results of the \acp{CNN} trained on simplex data.
-As expected the simplex and vertex models recover 100\% detection at higher \acp{SNR} while the vertex trained model fails this test.
+
+We now compare the \ac{CNN} results between the datasets by first training three \acp{CNN} on the vertex, simplex, and uniform datasets and then using these models to make predictions on the other testing data that is unseen during the network training process.
+We compare results for the different permutations in n \cref{fig:eff_curves}.
+In this figure the top panel presents results for the three different networks tested on the vertex data and shows that each model confidently detects all the signals with $\text{\acp{SNR}} >13$.
+At lower \acp{SNR} the vertex and uniform datasets perform similarly, however, the simplex trained model performs slightly worse.
+
+We would expect that when the vertex trained model is tested on vertex data that it performs best since the vertex data is a subset of each of the other 2 datasets and the network is not required to classify any samples unlike those it has trained on.
+
+everything should be classified at high \ac{SNR} as the vertex data is a subset of the uniform and vertex.
+The middle plot shows the results of the \acp{CNN} test on simplex data.
+As expected the simplex and uniform models detect 100\% of the signals at higher \acp{SNR} while the vertex trained model fails to detect all the signals event at \ac{SNR} 16.
 This is explained when we consider that the simplex data is a subset of uniform while the vertex data is not.
@@
 
-The three tests shown previously show that the vertex model only manages full detection when tested on itself.
-The uniform model performs best in all cases and that it contains signals from the vertex and simplex samples, suggesting that this way of sampling the class space as input to the generator creates a good variety of unmodelled generations.
+The three tests shown previously show that the vertex model only manages full detection when tested on vertex data.
+The uniform model performs best in all cases and and it contains signals from the vertex and simplex samples, suggesting that this way of sampling the class space as input to the generator creates a good variety of unmodelled generations.
+Furthermore, since it performs equally well as the vertex model on vertex data, we can conclude that the inclusion of the unmodelled signals does not negatively affect the model's performance on modelled signals.
 
@@
 
-\begin{figure}[h!] % "[t!]" placement specifier just for this example
-\centering
-\begin{subfigure}{0.7\textwidth}
-\includegraphics[width=\linewidth]{figures/efficiency_curve_vtest.png}
-\end{subfigure}
-
-\begin{subfigure}{0.7\textwidth}
-\centering
-\includegraphics[width=\linewidth]{figures/efficiency_curve_stest.png}
-\end{subfigure}
-
-\begin{subfigure}{0.7\textwidth}
-\centering
-\includegraphics[width=\linewidth]{figures/efficiency_curve_utest.png}
-\end{subfigure}
-
-\caption{Efficiency curves comparing the performance of the \acp{CNN}.
-The true alarm probability is plotted as a function of the optimal \ac{SNR} of the signals.
-Each plot shows the performance of a \ac{CNN} trained on vertex, simplex and uniform datasets tested on vertex (top), simplex (middle), uniform (bottom).
-\michael{Maybe add a subcaption under each saying which dataset the models are tested on}}
-\label{fig:eff_curves}
-\end{figure}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+\clearpage
+
 \section*{References}
@@
 Batch normalisation is applied to the output of the first layer and all convolutional layers are activated by ReLU with the exception of the final layer which is Linear.
-Finally, the extra dimension introduced for the convolution is removed.
-\michael{You say 500 epochs in the test but 100 here, not sure which is right.
-Also could include learning rate with tyhe optimiser}}
+Finally, the extra dimension introduced for the convolution is removed.}
 %\footnotesize
@@
  Batch size & 512  \\
- Epochs & 100  \\
+ Epochs & 500  \\
  Loss & Binary cross-entropy \\
@@
 \end{table}
+
+\clearpage
 

### 2021-01-05 Paper_draft/main.tex
Add Michael's comments

@@
 \def\prd{\ref@jnl{Phys.~Rev.~D}}
+\def\prl{\ref@jnl{Phys.~Rev.~Letters}}
 
@@
 \begin{abstract}
-We introduce the use of conditional generative adversarial networks for generalised gravitational wave burst generations in the time domain.
+We introduce the use of conditional generative adversarial networks for generalised gravitational wave burst generation in the time domain.
 Generative adversarial networks are generative machine learning models that produce new data based on the statistics of the training set.
@@
 Additionally, we show the model can produce generalised burst signals through interpolation and class mixing.
-Further, we build a convolution neural network classifier to predict the detectability of these newly produced signals in LIGO detector noise against more traditional burst waveforms.
+Further \michael{Futhermore?}, we build a convolutional neural network classifier to predict the detectability of these newly produced signals in LIGO detector noise against more traditional burst waveforms.
 \end{abstract}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-textwidth in inches: \printinunitsof{in}\prntlen{\textwidth}
+%textwidth in inches: \printinunitsof{in}\prntlen{\textwidth}
 \begin{comment}
@@
 
+\michael{Quite a few of the figures are still PNGs, I think we'll need to make PDFs for when we summit.}
+
 % introduce \ac{GW} astrophsyics
@@
 reported several more \ac{CBC} mergers~\cite{Abbott2016a, Abbott2017,
-Abbott2017a, Abbott2017b}. On 17th August 2017 a binary neutron star merger was
+Abbott2017a, Abbott2017b} \michael{O3a paper is on arxiv, shall we cite it?}. On 17th August 2017 a binary neutron star merger was
 observed alongside its electromagnetic counterpart for the first time, giving
@@
 %
-With these successes and continued upgrades to the detectors, further
+With these successes and continued upgrades to the detectors \michael{Cite upgrades?}, further
 detections of \acp{CBC} are expected to be commonplace in future advanced
@@
 matched-filtering,~\cite{Owen1998,Usman_2016,sachdev2019gstlal}, where a large template bank of possible
-\ac{GW} waveforms are compared to the detector outputs. For \ac{GW} bursts that remain unmodeled; there are no
+\ac{GW} waveforms are compared to the detector outputs. For \ac{GW} bursts that remain unmodelled; there are no
 templates available and so matched-filtering is unsuitable for the detection of
-these signals.  Instead, detection algorithms like coherent WaveBurst \cite{drago2020coherent} involve distinguishing the signal from
+these signals.  Instead, detection algorithms like coherent WaveBurst \cite{drago2020coherent} distinguish the signal from
 detector noise by looking for excess power contained in the time-frequency
@@
 %
-\ac{GW} burst detection algorithms~\cite{Klimenko_2008, Aso_2008} are tested
+\ac{GW} burst detection algorithms~\cite{drago2020coherent,Klimenko_2008, Aso_2008} are tested
 and tuned using modelled waveforms that have easy to define parameters and share characteristics of real bursts that aim to simulate a \ac{GW} passing between
@@
 decay parameter. Bandlimited white noise bursts: white noise that is contained
-within a certain frequency range and ringdowns which mimic the damped
+within a certain frequency range. Ringdowns: which mimic the damped
 oscillations after a \ac{CBC} merger. A Gaussian pulse: a short exponential increase then decrease in amplitude and a binary black hole inspiral.
@@
 In Bayesian parameter
-estimation~\cite{gabbard2019bayesian, green2020gravitationalwave} where \ac{ML} techniques can recover parameters of a \ac{GW} signal significantly faster than standard methods.
+estimation~\cite{gabbard2019bayesian,Chua:2019,green2020gravitationalwave} where \ac{ML} techniques can recover parameters of a \ac{GW} signal significantly faster than standard methods.
 Long duration signals like continuous \ac{GW} require long observing times and therefore have large amounts of data needing to be processed.
@@
 In this work we aim to explore the use of \ac{ML} to generate and interpret
-unmodeled \ac{GW} burst waveforms. Using the generative machine learning
+unmodelled \ac{GW} burst waveforms. Using the generative machine learning
 model, \acp{GAN}, we train on five classes of waveforms in the time domain. Working on the assumption that \acp{GAN} construct smooth
@@
 strong local spatial dependencies. Although most work with \acp{CNN}
-involve image-based data, they can be applied to other spatially adjacent data
-types such as time-series and text items. \acp{CNN} are defined by the use of a
+involves image-based data, they can be applied to other spatially adjacent data
+types such as time-series and text items \michael{Could add some references here?}. \acp{CNN} are defined by the use of a
 convolution operation, a mathematical operation that expresses the amount
@@
 two. The distance by which the grid is shifted is known as
-the stride and increasing it reduces the dimensionality of the output in a process know as downsampling.
+the stride and increasing it reduces the dimension of the output in a process know as downsampling.
 Alternatively, upsampling the inputs can be achieved using a transposed convolution \cite{dumoulin2016guide}.
@@
 are generative adversarial networks \acp{GAN}~\cite{Goodfellow2014}. These unsupervised algorithms learn patterns in a
-given training data set using an adversarial process. The generations from
+given training dataset using an adversarial process. The generations from
 \acp{GAN} are currently state-of-the-art in fields such as high quality image
@@
 translation~\cite{reed2016generative}, and video
-prediction~\cite{liang2017dual} as well as time series
+prediction~\cite{liang2017dual} as well as time-series
 generations~\cite{esteban2017realvalued}.
@@
 where $\hat{y}$ is the network prediction and $y$ is the true output.
-While training the discriminator, D, on real data, we set $y = 1$ and $\hat{y} = D(\mathbf{x})$ which from \cref{eqn:crossentropy} gives $L(D(\mathbf{x}),1) = \log(D(\mathbf{x}))$.
-While training on fake data produced by the generator, G, $y = 0$ and $\hat{y} = D(G(\mathbf{z}))$ and so, $L(D(G(\mathbf{z})),0) = \log(1-(D(G(\mathbf{z}))))$.
+While training the discriminator, $D$, on real data, we set $y = 1$ and $\hat{y} = D(\mathbf{x})$ which from \cref{eqn:crossentropy} gives $L(D(\mathbf{x}),1) = \log(D(\mathbf{x}))$.
+While training on fake data produced by the generator, $G$, $y = 0$ and $\hat{y} = D(G(\mathbf{z}))$ and so, $L(D(G(\mathbf{z})),0) = \log(1-(D(G(\mathbf{z}))))$.
 Since the objective of the discriminator is to correctly classify fake and real data these equations should be maximised, while the goal of the generator should be to minimize these equations.
@@
 Training a GAN is involves updating both the discriminator and generator in stages.
-First, the discriminator is updated on real instances from the training set.
+First, the discriminator is updated using real instances from the training set.
 We set the true label $y=1$ and calculate the loss with respect to the predictions $\hat{y}$ via \cref{equation:GANloss}.
@@
 This simple addition has been shown to work well in practice, for instance in image-to-image translation~\cite{isola2016imagetoimage}.
-We use one-hot encoding to define the classes, that is, each class resides at the corner points of a \ndimensional{5} cube.
+We use one-hot encoding to define the classes, that is, each class resides at the corner points of a \ndimensional{5} hyper-cube.
 For example $\mathbf{c}=[0,1,0,0,0]$ represents the ringdown signal class.
@@
 its class that is also fed to the generator which then learns to generate
-waveforms based on the input label.}
+waveforms based on the input label. \michael{We use $\textbf{G}$ here but then use $G$ in the rest of the text.}}
 \begin{comment}
@@
 \item {\bf Sine-Gaussian}: $h_{\text{SG}}(t) = A \exp\left[ - (t-t_{0})^2 /
-\tau^2 \right] \sin (2 \pi f_0 (t-t_0) + \phi)$, \michael{Could capitalise SG here?} a sinusoidal wave with a Gaussian
-envelope characterised by a central frequency $f_0$, amplitude $A$, time of arrival $t_{0}$ and phase $\phi$ which is uniformly sampled between $[0, 2\pi]$.
+\tau^2 \right] \sin (2 \pi f_0 (t-t_0) + \phi)$, a sinusoidal wave \michael{Just sinusoid?
+or sine wave?} with a Gaussian envelope characterised by a central frequency $f_0$, amplitude $A$, time of arrival $t_{0}$ and phase $\phi$ which is uniformly sampled between $[0, 2\pi]$.
 %
@@
 (t-t_{0})^2 / \tau^2 \right]$ where $g_j$ are drawn from a zero mean unit
-variance Gaussian distribution with a Gaussian envelope of duration $tau$.
+variance Gaussian distribution with a Gaussian envelope of duration $\tau$.
 %
@@
 mid-points of all but the ringdown and \ac{BBH} classes) are randomly drawn from a uniform distribution to
-be within $[0.4, 0.6]$ seconds from the start of the 1 sec time interval and all
+be within $[0.4, 0.6]$ seconds from the start of the 1 second time interval and all
 training waveforms are sampled at 1024 Hz.  The parameter prior ranges are
@@
 can tune when designing the model and these are referred to as hyperparameters.
-The final network design used in this work comes was developed through trial and
-error and the initial designs influenced by the available literature. We found
+The final network design used in this work was developed through trial and
+error and the initial designs were influenced by the available literature. We found
 that the \ac{GAN} performed better with both networks having the same number of
@@
 The design of the networks is influenced by \cite{Radford2015} in which they use a \ac{DCGAN} architecture.
-The generator model is fully convolutional, upsampled using strided transposed convolutions with batch normalisation in the first layer and ReLU activations throughout with the exception of a linear activation for the output layer.
+The generator model is fully convolutional, upsampled using strided transposed convolutions with BatchNormalisation in the first layer and ReLU activations throughout with the exception of a linear activation for the output layer.
 The use of a linear activation guarantees the output can have negative and positive outputs.
@@
 %
-Given a \ndimensional{100} vector drawn from a normal distributed latent space and a one-hot encoded class
+Given a \ndimensional{100} vector drawn from a normally distributed latent space and a one-hot encoded class
 label, the GAN is able to generate burst-like waveforms generalised from the
@@
     \caption{\ac{GAN} generated interpolated waveforms plotted as a function of time showing latent space interpolations.
-For each interpolation two different points were randomly chosen in the latent space and represent the first last panels in each row.
+For each interpolation two different points were randomly chosen in the latent space and represent the first and last panels in each row.
 The panels between represent signals generated using linearly interpolated vectors between these two points.
@@
  We have shown that the generator produces quality signals and that the model responds well to randomly sampled Gaussian latent vectors.
-We now assume that during training the generator has learned a mapping from a Gaussian latent space to signal space and that this mapping is a smooth function of the underlying latent space.
+We now assume that during training the generator has learned a mapping from a Gaussian latent space to the signal space and that this mapping is a smooth function of the underlying latent space.
 To verify this, we fix the class vector input and linearly interpolate between two randomly chosen points in the latent space (different for each class).
@@
 Each row shows generations using linearly interpolated classes as inputs to the generator.
-By row top to bottom: Sine-Gaussian to ringdown, ringdown to white noise burst, Gaussian pulse to BBH.\chris{add class vectors on each panel}}
+By row top to bottom: Sine-Gaussian to ringdown, ringdown to white noise burst, white noise burst to Gaussian pulse, Gaussian pulse to BBH.\chris{add class vectors on each panel}}
     \label{fig:c_interp}
@@
 The vertex points are the most straightforward where one element of the class vector contains one and the other elements are zero.
-these points are equivalent to the class vectors that the \ac{GAN} is trained on e.g., $\mathbf{c} = [1,0,0,0,0]$ would correspond to a sine-Gaussian generation.
+These points are equivalent to the class vectors that the \ac{GAN} is trained on e.g., $\mathbf{c} = [1,0,0,0,0]$ would correspond to a sine-Gaussian generation.
 Uniform class vectors with each element sampled from a uniform distribution are equivalent to a random draw from a \ndimensional{5} hyper-cube.
@@
     \caption{GAN generations where the class vectors are sampled from the \ndimensional{4} plane (simplex) intersecting all training classes.
-Latent space locations for all signals are taken randomly from a \ndimensional{100} Gaussian distribution and the signals are then re-scaled such that they have maximum absolute amplitude at unity.
+Latent space locations for all signals are drawn randomly from a \ndimensional{100} Gaussian distribution and the signals are then re-scaled such that they have maximum absolute amplitude at unity.
 The class label for each generation is shown above each panel.}
@@
     \caption{GAN generations where the class vectors are sampled uniformly in the hyper-cube class space.
-Latent space locations for all signals are taken randomly from a \ndimensional{100} Gaussian distribution and the signals are then re-scaled such that they have maximum absolute amplitude at unity.
+Latent space locations for all signals are drawn randomly from a \ndimensional{100} Gaussian distribution and the signals are then re-scaled such that they have maximum absolute amplitude at unity.
 \michael{Same comment about y-axis labels}}
@@
 \section{CNN burst classifier} \label{cnn classifier}
-In this section we develop a basic search analysis using a \ac{CNN} in order to compare the sensitivity of such a search to different \ac{GAN} generated waveforms in additive noise.
+In this section we develop a basic search analysis using a \ac{CNN} in order to compare the sensitivity of such a search using different \ac{GAN} generated waveforms in additive noise.
 We train a \ac{CNN} to perform simple classification and to distinguish between two classes: signals in additive Gaussian noise and Gaussian noise only.
@@
 The generated waveforms are used to represent the plus-polarisation component of signal only and the polarisation angles are drawn uniformly in the range $[0,2\pi]$ and sky positions are sampled isotropically.
-Time delays between detectors are computed relative to the Earth centre.
+Time delays between detectors are computed relative to the Earth's centre.
 All of the training data used is whitened using the Advanced LIGO design sensitivity \ac{PSD}\chris{add reference}, such that there is equal noise power at each frequency.
@@
 Each 1 second duration time-series input to the \ac{CNN} is represented by a \ndimensional{1} 1024 sample vector with 2 channels representing each detector.
-Example time-series from each detector for a single signal is shown in \cref{fig:cnn_training}.
+Example time-series from each detector for a single signal are shown in \cref{fig:cnn_training}.
 The network is trained to be able to identify whether or not a measurement contains a signal and therefore 50\% of the training data have time-series containing signals and 50\% have only noise.
@@
 For the Uniform and Simplex datasets samples are drawn uniformly from their respective spaces.
-For the vertex data-set the 5 different vertex locations in class space are sampled with equal probability.
+For the vertex dataset the 5 different vertex locations in class space are sampled with equal probability.
 
@@
 \subsection{CNN architecture}
-In this approach the input to the \ac{CNN} are 1024 sample time-series (with 2 channels representing each detector output) which are passed through a series of 4 convolutional layers, onto two fully connected or ``Dense'' layers and finally to a single output neuron which represents the probability that a signal is present within the noise.
+In this approach the inputs to the \ac{CNN} are 1024 sample time-series (with two channels representing each detector output) which are passed through a series of four convolutional layers, onto two fully connected or ``Dense'' layers and finally to a single output neuron which represents the probability that a signal is present within the noise.
 We used dropout in the final dense layer and used a selection of different activation functions including the swish activation \cite{ramachandran2017searching} which improved overall performance, and a sigmoid activation for the output layer.
@@
 The true alarm probability is plotted as a function of the optimal \ac{SNR} of the signals.
-Each plot shows the performance of a \ac{CNN} trained on vertex, simplex and uniform datasets tested on vertex (a), simplex (b), uniform (c).}
+Each plot shows the performance of a \ac{CNN} trained on vertex, simplex and uniform datasets tested on vertex (a), simplex (b), uniform (c).
+\michael{Think these were going to be regenerated to fit with captions}}
 \label{fig:eff_curves}
@@
 We now compare the \ac{CNN} results between the datasets by first training three \acp{CNN} on the vertex, simplex, and uniform datasets and then using these models to make predictions on the other testing data that is unseen during the network training process.
-We compare results for the different permutations in n \cref{fig:eff_curves}.
+We compare results for the different permutations in \cref{fig:eff_curves}.
 In this figure the top panel presents results for the three different networks tested on the vertex data and shows that each model confidently detects all the signals with $\text{\acp{SNR}} >13$.
@@
 everything should be classified at high \ac{SNR} as the vertex data is a subset of the uniform and vertex.
-The middle plot shows the results of the \acp{CNN} test on simplex data.
+The middle plot shows the results of the \acp{CNN} tested on simplex data.
 As expected the simplex and uniform models detect 100\% of the signals at higher \acp{SNR} while the vertex trained model fails to detect all the signals event at \ac{SNR} 16.
@@
 The final plot tests the models on uniform data and show again at high \acp{SNR} both simplex and uniform are 100\% detectable as a consequence of our previous subset argument.
-The vertex test is not fully detectable and further supports our premise that the vertex data, which is based on the modelled training data is distinguishable to both unmodelled datasets.
+\michael{Wouldn't we expect the simplex to NOT be 100\% detectable?} The vertex test is not fully detectable and further supports our premise that the vertex data, which is based on the modelled training data is distinguishable to both unmodelled datasets.
 
@@
 burst \ac{GW} generation.
-We have shown that \acp{GAN} have the ability to generate plausible time series burst data and present a novel approach to generating unmodelled waveforms.
+We have shown that \acp{GAN} have the ability to generate plausible time-series burst data and present a novel approach to generating unmodelled waveforms.
 We have shown that CGANs are able distinguish between five distinct classes of burst like signals through conditional training which we can then utilise for targeted generations.
@@
 Although the three datasets were similarly detectable there was some degree of separation between them.
+\michael{Add some detail about uniform being the best}
 
@@
 Using a \ac{GAN} to model these would aid in the understanding of these glitches and could help to remove them in order to get the cleanest data stream possible.
+
+\michael{We only generate one polarisation, might be worth adding something saying that this could be extented to two polarisations in future work?}
 
@@
 these non-standard \ac{GW} emitters.
+
+\michael{Do we need to include acknowledgements? I.e. for grants etc.}
 
@@
 The discriminator casts the class input through a fully connected layer such that its dimensions match the signals input which it then concatenates channel-wise.
-This is then downsampled through four convolutional layers all activated by Leaky ReLU functions add drops half of the connections at the end of each of these layers.
+This is then downsampled through four convolutional layers all activated by Leaky ReLU functions and drops half of the connections at the end of each of these layers.
 The vector is then flattened to one dimension before fully connecting to a single neuron and its output activated by sigmoid to represent the probability the signal came from the training set.
 The generator concatenates the latent and class input vectors which is fed to a fully connected layer.
-This layer is then upsampled by four tranposed convolutions.
+This layer is then upsampled by four transposed convolutions.
 Batch normalisation is applied to the output of the first layer and all convolutional layers are activated by ReLU with the exception of the final layer which is Linear.
@@
 %\footnotesize
+\resizebox{0.8\textwidth}{!}{%
 \begin{tabular*}{\textwidth}{c @{\extracolsep{\fill}} c c c c c c}
@@
 Reshape & (1024) & - & - & \ding{55} & - \\
-\end{tabular*}
+
+\end{tabular*}}
+\resizebox{0.8\textwidth}{!}{%
 \begin{tabular*}{\textwidth}{@{} l l l l l l}
@@
  \br
-\end{tabular*}\\
+\end{tabular*}}\\
 \label{Tab:gan_training_parms}
@@
 Dense & (100) & 100 & - & 0.2 & Swish  \\
-Dense & (1) & 1 & - & 0 & sigmoid \\
-\end{tabular*}\\
+Dense & (1) & 1 & - & 0 & Sigmoid \\
+\end{tabular*}}\\
+\resizebox{0.8\textwidth}{!}{%
 \begin{tabular*}{\textwidth}{@{}l l l l l l}
@@
  \br
-\end{tabular*}\\
+\end{tabular*}}\\
 \label{Tab:cnn_training_parms}

### 2021-01-26 Paper_draft/main.tex
re-gen of plots

@@
 Additionally, we show the model can produce generalised burst signals through interpolation and class mixing.
-Further \michael{Futhermore?}, we build a convolutional neural network classifier to predict the detectability of these newly produced signals in LIGO detector noise against more traditional burst waveforms.
+Furthermore, we build a convolutional neural network classifier to predict the detectability of these newly produced signals in LIGO detector noise against more traditional burst waveforms.
 \end{abstract}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%textwidth in inches: \printinunitsof{in}\prntlen{\textwidth}
+
 \begin{comment}
@@
 
-\michael{Quite a few of the figures are still PNGs, I think we'll need to make PDFs for when we summit.}
-
 % introduce \ac{GW} astrophsyics
 %
-\Ac{GW} astronomy is now an established field that began with the first
+\ac{GW} astronomy is now an established field that began with the first
 detection of a binary black hole merger~\cite{Abbott2016} in September 2015.
@@
 reported several more \ac{CBC} mergers~\cite{Abbott2016a, Abbott2017,
-Abbott2017a, Abbott2017b} \michael{O3a paper is on arxiv, shall we cite it?}. On 17th August 2017 a binary neutron star merger was
+Abbott2017a, Abbott2017b}. On 17th August 2017 a binary neutron star merger was
 observed alongside its electromagnetic counterpart for the first time, giving
 rise to multi-messenger \ac{GW} astronomy.
+The most recent search for compact binary coalescence, 03a, took place between 1 April 2019 and 1 October 2019 with 39 candidate events reported \cite{GWTC2:2020}.
 
@@
 %
-With these successes and continued upgrades to the detectors \michael{Cite upgrades?}, further
+With these successes and continued upgrades to the detectors \cite{2018LRR....21....3A}, further
 detections of \acp{CBC} are expected to be commonplace in future advanced
@@
 involves image-based data, they can be applied to other spatially adjacent data
-types such as time-series and text items \michael{Could add some references here?}. \acp{CNN} are defined by the use of a
+types such as time-series \cite{2018arXiv180904356I} and text items \cite{2020arXiv200403705M}. \acp{CNN} are defined by the use of a
 convolution operation, a mathematical operation that expresses the amount
@@
 its class that is also fed to the generator which then learns to generate
-waveforms based on the input label. \michael{We use $\textbf{G}$ here but then use $G$ in the rest of the text.}}
+waveforms based on the input label.}
 \begin{comment}
@@
     \centering
-    \includegraphics[width=\textwidth]{figures/training-sample.png}
+    \showthe\textwidth
+    \includegraphics[width=\textwidth]{figures/training-sample.pdf}
     \caption{Examples of the five different waveforms that were used in training the \ac{GAN} for this study.
-Values of the parameters were selected randomly from uniform distributions from \cref{Tab:training_parms}.
-\michael{Ringdown is hyphenated here, this is the only place}}
+Values of the parameters were selected randomly from uniform distributions from \cref{Tab:training_parms}.}
     \label{fig:training_waveforms}
@@
 \item {\bf Sine-Gaussian}: $h_{\text{SG}}(t) = A \exp\left[ - (t-t_{0})^2 /
-\tau^2 \right] \sin (2 \pi f_0 (t-t_0) + \phi)$, a sinusoidal wave \michael{Just sinusoid?
-or sine wave?} with a Gaussian envelope characterised by a central frequency $f_0$, amplitude $A$, time of arrival $t_{0}$ and phase $\phi$ which is uniformly sampled between $[0, 2\pi]$.
+\tau^2 \right] \sin (2 \pi f_0 (t-t_0) + \phi)$, a sine wave with a Gaussian envelope characterised by a central frequency $f_0$, amplitude $A$, time of arrival $t_{0}$ and phase $\phi$ which is uniformly sampled between $[0, 2\pi]$.
 %
@@
 By row: sine-Gaussian, ringdown,
-white noise burst, Gaussian pulse, binary black hole merger.
-For ease of viewing, the $x$-axis for all panels spans the mid 50\% of the output range.
-\michael{I think we mentioned increasing the y-axis limits a little so it's clearer the signals end at $\pm 1$}}
+white noise burst, Gaussian pulse, binary black hole merger. For ease of viewing, the $x$-axis for all panels spans the mid 50\% of the output range.}
 \label{fig:gen_signals} 
@@
 In \cref{fig:gen_signals} we show conditional signal generations using our generator network.
-We can see the generations are of very good quality \michael{Personally don't like using good quality without a metric to quantify things.} and appear as though they could have plausibly come from the training set.
+We can see the generations capture the main aspects of each signal class and appear as though they could have plausibly come from the training set.
 We can also see that the model has learned the overall characteristics of the five training classes and is able to disentangle each class and associate them with the conditional input.
@@
 Each row shows generations using linearly interpolated classes as inputs to the generator.
-By row top to bottom: Sine-Gaussian to ringdown, ringdown to white noise burst, white noise burst to Gaussian pulse, Gaussian pulse to BBH.\chris{add class vectors on each panel}}
+By row top to bottom: Sine-Gaussian to ringdown, ringdown to white noise burst, white noise burst to Gaussian pulse, Gaussian pulse to BBH.}
     \label{fig:c_interp}
@@
     \caption{GAN generations where the class vectors are sampled uniformly in the hyper-cube class space.
-Latent space locations for all signals are drawn randomly from a \ndimensional{100} Gaussian distribution and the signals are then re-scaled such that they have maximum absolute amplitude at unity.
-\michael{Same comment about y-axis labels}}
+Latent space locations for all signals are drawn randomly from a \ndimensional{100} Gaussian distribution and the signals are then re-scaled such that they have maximum absolute amplitude at unity.}
     \label{fig:uniform_samples}
@@
 
-\begin{figure}[h!] % "[t!]" placement specifier just for this example
-\centering
-\begin{subfigure}{1\textwidth}
-\centering
-\includegraphics[width=0.7\linewidth]{figures/efficiency_curve_vtest.png}
-%\includegraphics[]{Paper_draft/figures/test.pdf}
-\caption{Tested on vertex}
-\end{subfigure}
-
-\begin{subfigure}{1\textwidth}
-\centering
-\includegraphics[width=0.7\linewidth]{figures/efficiency_curve_stest.png}
-%\includegraphics[]{Paper_draft/figures/test.pdf}
-\caption{Tested on simplex}
-\end{subfigure}
-
-\begin{subfigure}{1\textwidth}
-\centering
-\includegraphics[width=0.7\linewidth]{figures/efficiency_curve_utest.png}
-%\includegraphics[]{Paper_draft/figures/test.pdf}
-\caption{Tested on uniform}
-\end{subfigure}
-
-\caption{Efficiency curves comparing the performance of the \acp{CNN}.
-The true alarm probability is plotted as a function of the optimal \ac{SNR} of the signals.
-Each plot shows the performance of a \ac{CNN} trained on vertex, simplex and uniform datasets tested on vertex (a), simplex (b), uniform (c).
-\michael{Think these were going to be regenerated to fit with captions}}
-\label{fig:eff_curves}
-\end{figure}
-
 \subsection{CNN results}
 
+% vertex tested data
+%
 We now compare the \ac{CNN} results between the datasets by first training three \acp{CNN} on the vertex, simplex, and uniform datasets and then using these models to make predictions on the other testing data that is unseen during the network training process.
@@
 In this figure the top panel presents results for the three different networks tested on the vertex data and shows that each model confidently detects all the signals with $\text{\acp{SNR}} >13$.
-At lower \acp{SNR} the vertex and uniform datasets perform similarly, however, the simplex trained model performs slightly worse.
-
-We would expect that when the vertex trained model is tested on vertex data that it performs best since the vertex data is a subset of each of the other 2 datasets and the network is not required to classify any samples unlike those it has trained on.
-
-everything should be classified at high \ac{SNR} as the vertex data is a subset of the uniform and vertex.
-The middle plot shows the results of the \acp{CNN} tested on simplex data.
-As expected the simplex and uniform models detect 100\% of the signals at higher \acp{SNR} while the vertex trained model fails to detect all the signals event at \ac{SNR} 16.
-This is explained when we consider that the simplex data is a subset of uniform while the vertex data is not.
-The final plot tests the models on uniform data and show again at high \acp{SNR} both simplex and uniform are 100\% detectable as a consequence of our previous subset argument.
-\michael{Wouldn't we expect the simplex to NOT be 100\% detectable?} The vertex test is not fully detectable and further supports our premise that the vertex data, which is based on the modelled training data is distinguishable to both unmodelled datasets.
-
-The three tests shown previously show that the vertex model only manages full detection when tested on vertex data.
-The uniform model performs best in all cases and and it contains signals from the vertex and simplex samples, suggesting that this way of sampling the class space as input to the generator creates a good variety of unmodelled generations.
-Furthermore, since it performs equally well as the vertex model on vertex data, we can conclude that the inclusion of the unmodelled signals does not negatively affect the model's performance on modelled signals.
+At lower \acp{SNR} the vertex and uniform datasets perform similarly, however, at $\rho_{\text{opt}}\sim 10$ the simplex trained model has slightly worse performance, dropping in true alarm probability by a few percent.
+
+We would expect that when the vertex trained model is tested on vertex data that it outperforms the alternatively trained networks.
+This is because the vertex data is a subset of each of the other 2 datasets and the network is not required to classify any samples unlike those it has trained on.
+We also expect that all vertex testing signals should be correctly classified at high \ac{SNR} since the vertex data is a subset of the uniform and simplex training tests.
+The weaker performance of the simplex trained model could be attributed to the lower density of training signal locations in close proximity to the vertices.
+
+% simplex tested data
+%
+The second panel of \cref{fig:eff_curves} shows the results of the differently trained \acp{CNN} tested on simplex data.
+As expected the simplex and uniform models detect 100\% of the signals at higher \acp{SNR}.
+However, the vertex trained model fails to detect all the simplex signals, achieving only $96\%$ true alarm probability at the highest simulated \ac{SNR} $\rho_{\text{opt}}=16$.
+This is explained when we consider that the simplex data is a subset of uniform data while the vertex data is not.
+It is interesting to note that the simplex and uniform trained models perform identically (within statistical uncertainty).
+The uniform model has a larger signal parameter space volume and we might expect it to be more more susceptible to misidentifying instances of the Gaussian noise model as signals from the uniform dataset.
+\begin{figure} % "[t!]" placement specifier just for this example
+\centering
+\begin{subfigure}{1\textwidth}
+\centering
+\includegraphics[scale=0.85]{figures/efficiency_curve_vtest.pdf}
+\caption{Tested on vertex}
+\end{subfigure}
+
+\begin{subfigure}{1\textwidth}
+\centering
+\includegraphics[scale=0.85]{figures/efficiency_curve_stest.pdf}
+\caption{Tested on simplex}
+\end{subfigure}
+
+\begin{subfigure}{1\textwidth}
+\centering
+\includegraphics[scale=0.85]{figures/efficiency_curve_utest.pdf}
+\caption{Tested on uniform}
+\end{subfigure}
+
+\caption{Efficiency curves comparing the performance of the \acp{CNN}.
+The true alarm probability is plotted as a function of the optimal \ac{SNR} of the signals.
+Each plot shows the performance of a \ac{CNN} trained on vertex, simplex and uniform datasets tested on vertex (a), simplex (b), uniform (c).}
+\label{fig:eff_curves}
+\end{figure}
+
+% uniform tested data
+%
+The final panel of~\cref{fig:eff_curves} tests the models on uniform data and again shows that at high \acp{SNR} both simplex and uniform trained models are result in 100\% true alarm probability.
+One might not expect this since the simplex training data is only a subset of the uniform testing data parameter space.
+The simplex trained \ac{CNN} in the high \ac{SNR} limit is able to confidently generalise to be able to identify signals from the uniform testing dataset.
+This is not the case for the vertex trained model which achieves only a 95\% true alarm probability in the high \ac{SNR} limit.
+The vertex trained \ac{CNN} is not able to fully generalise and identify signal from noise for signals within the class space hyper-cube, nor from within the class space simplex hyper-surface.
+We also note that specifically in the $\rho_{\text{opt}}\sim 10$ region we see marginally more sensitive results for the uniform trained model when applied to the uniform testing data in comparison to the simplex trained model.
+This is expected since again the simplex data space is a subset of the uniform data space and the uniform trained model will have explicitly learned how to identify signals in regions distant from the simplex hyper-surface.
+The simplex trained model performs well despite having to extrapolate away from its training space.
+
+% summary of results
+%
+The tests discussed above show that the \ac{CNN} trained on the vertex model only manages full detection when tested on vertex model data.
+The uniform model performs best in all cases and since it contains signals from the vertex and simplex samples and does not appear to suffer from an increased false alarm probability due to its larger parameter space volume.
+This suggests that the uniform method of sampling the class space for training or characterising a search algorithm is the most robust and sensitive approach given the intrinsically unknown nature of \ac{GW} burst signals.
+Furthermore, since the uniform trained model performs equally as well as the vertex trained model when applied to  vertex test data, we can conclude that the inclusion of the unmodelled signals does not negatively affect the model's performance on modelled signals.
 
@@
 %
-
+% basic CGAN
+%
 In this work we present the potential of \acp{GAN} for
@@
 We have shown that \acp{GAN} have the ability to generate plausible time-series burst data and present a novel approach to generating unmodelled waveforms.
-We have shown that CGANs are able distinguish between five distinct classes of burst like signals through conditional training which we can then utilise for targeted generations.
-
-We also show how our \ac{GAN} constructs smooth latent and class spaces during training and we explore these through interpolation showing smooth translations between classes and overall
-waveform shape.
-Further, we showed targeted waveform generation by mixing classes in the class space through novel ways.
-We are able to produce new unmodelled waveform varieties vastly different from the training set and any known analytical method of generating these signals.
-Such waveforms are in demand in gravitational wave detection as they allow developers to test their search pipelines and other detection schemes.
-
-We then considered three cases of unmodelled generated signals in Gaussian noise and trained a \ac{CNN} on those data.
-The resulting efficiency curves comparing the detection sensitivities of the \ac{CNN} as a function of \ac{SNR} of the waveforms showed that these signals were detectable in noise.
-Although the three datasets were similarly detectable there was some degree of separation between them.
-\michael{Add some detail about uniform being the best}
+We have shown that our implementation of a \ac{CGAN} is able to generate five distinct classes of burst like signals through conditional training which can then be utilised for specified signal generations.
+The \acp{CGAN} allows us to map the parameter space of each signal class into a common abstract latent space in which common signal characteristics are grouped into smoothly connected regions.
+We are then able to sample from this space as input to the generator network and produce high fidelity random examples of any of our trained signal classes.
+
+% Class space interpolation
+%
+Whilst we have trained our \ac{CGAN} on 5 discrete signal classes, each having its own signal parameter space, we have shown that we can subsequently sample from the continuous class space to generate hybrid burst waveforms.
+This novel aspect of our analysis takes advantage of the learned mapping between individual discrete signal classes.
+When coupled with the latent space, we are then able to generate hybrid waveforms that span the variation between signal classes and the variation within each class.
+The resultant hybrid waveforms then represent a generalised set of potential \ac{GW} burst waveforms that are vastly different from the limited training set.
+Such waveforms are in demand in \ac{GW} astronomy as they allow burst search pipeline developers to test and enhance their detection schemes.
+
+% the CNN analysis
+%
+To provide a practical example of the usage of these waveforms we have concluded our analysis with a simple search for signals in additive Gaussian noise.
+We have suggested 3 variations of how to sample from the \ac{CGAN} signal class space and have trained a basic \ac{CNN} separately on those data in order to classify whether a signal was present in the noisy data versus only Gaussian noise.
+The resulting trained networks were then tested on independent datasets from each of the three signal hybrid classes.
+The resulting efficiency curves compare the detection sensitivities of the \ac{CNN} as a function of \ac{SNR} and allow us to conclude that in this simple analysis, training the search using the most general set of hybrid waveforms (our "uniform" set) provides the most sensitive overall result.
 
 In contrast to typical approaches in signal generation this is the first time a \ac{GAN} has been used for generating gravitational wave burst data.
-In the future, as development in \acp{GAN} and generative machine learning advances it is expected that we will gain greater control over target generation of features.
-
-Going forward it will also be important to extend our models to treat longer waveforms, higher sampling rates and conditioning on additional classes.
-One such class of interest would be ``glitch'' data.
-High amplitude short duration, peaks in the output of LIGO detectors that are internal sources of noise rather than of astrophysical origin.
-Using a \ac{GAN} to model these would aid in the understanding of these glitches and could help to remove them in order to get the cleanest data stream possible.
+Our approach allows us to explicitly control the mixing of different signal training classes but the variation within the space of signal properties is determined randomly through sampling of the abstract latent space.
+In the future, as development in \acp{GAN} and generative machine learning advances it is expected that we will gain greater control over targeted generation of signal features.
+It will also be important to extend our models to train on, and generate, longer duration waveforms, higher sampling rates, and to be conditioned on additional classes.
+One such set of additional classes of interest would be the population of detector ``glitches''.
+These are typically high-amplitude short-duration events in the output of \ac{GW} detectors that represent sources of terrestrial detector noise rather than that of astrophysical origin.
+Using a \ac{GAN} to model these would provide us with a tool to simulate an unlimited set of glitches which could be used for use in the understanding of these glitches and could help to remove them in order to get the cleanest data stream possible.
 
 \michael{We only generate one polarisation, might be worth adding something saying that this could be extented to two polarisations in future work?}
+
+Test on cWB
+
+mention SNe but don't talk about real noise
 
@@
 these non-standard \ac{GW} emitters.
-
-\michael{Do we need to include acknowledgements? I.e. for grants etc.}
 
@@
 \end{comment}
+
+\ack
+
+The authors also gratefully acknowledge the Science and Technology Facilities Council of the United Kingdom.
+JM is supported by the Science and Technology Facilities Council Newton-Bhabha ST/R001928/1 and the Gravitational-wave Excellence through Alliance Training (GrEAT) Network with China ST/R002770/1 funds.
+CM and ISH are supported by the Science and Technology Research Council (grant No.
+ST/ L000946/1) and acknowledge the European Cooperation in Science and Technology (COST) action CA17137.
+MJW is supported by the Science and Technology Facilities Council [2285031].
 
@@
 
-\section{Many more generated examples}
-~\chris{do we still need this?}
-
 \end{document}

### 2021-01-28 Paper_draft/main.tex
modified:   Paper_draft/main.tex
Detector and detection references updated, PSD reference included, added false alarm prob in text and fig caption,

@@
 \begin{abstract}
-We introduce the use of conditional generative adversarial networks for generalised gravitational wave burst generation in the time domain.
+We introduce the use of conditional generative adversarial networks for generalised GW burst generation in the time domain.
 Generative adversarial networks are generative machine learning models that produce new data based on the statistics of the training set.
@@
 
-\acrodef{GW}[GW]{gravitational wave}
+%\acrodef{GW}[GW]{GW}
 \acrodef{CBC}[CBC]{compact binary coalescence} 
@@
 
-% introduce \ac{GW} astrophsyics
-%
-\ac{GW} astronomy is now an established field that began with the first
-detection of a binary black hole merger~\cite{Abbott2016} in September 2015.
-Following this, the first and second observations runs (O1 and O2) of Advanced
-LIGO and Advanced Virgo~\cite{Prospects-dets, AdvLIGO, AdvLIGO2, AdvVIRGO}
-reported several more \ac{CBC} mergers~\cite{Abbott2016a, Abbott2017,
-Abbott2017a, Abbott2017b}. On 17th August 2017 a binary neutron star merger was
-observed alongside its electromagnetic counterpart for the first time, giving
-rise to multi-messenger \ac{GW} astronomy.
+% introduce GW astrophsyics
+%
+Gravitational wave (GW) astronomy is now an established field that began with the first detection of a binary black hole merger~\cite{Abbott2016} in September 2015.
+Following this, the first and second observations runs (O1 and O2) of Advanced LIGO and Advanced Virgo~\cite{Prospects-dets, AdvLIGO, AdvLIGO2, AdvVIRGO} reported several more \ac{CBC} mergers~\cite{Abbott2016a, Abbott2017, Abbott2017a}.
+On 17th August 2017 a binary neutron star merger was observed alongside its electromagnetic counterpart for the first time, giving rise to multi-messenger GW astronomy \cite{Abbott2017b}.
 The most recent search for compact binary coalescence, 03a, took place between 1 April 2019 and 1 October 2019 with 39 candidate events reported \cite{GWTC2:2020}.
@@
 %
-With these successes and continued upgrades to the detectors \cite{2018LRR....21....3A}, further
+With these successes and continued upgrades to the detectors \cite{det-upgrades1,det-upgrades2}, further
 detections of \acp{CBC} are expected to be commonplace in future advanced
-detcetor observation runs. Another group of \ac{GW} signals that has thus far
-been undetected is \ac{GW} ``bursts". \ac{GW} bursts are classed as transient
+detcetor observation runs. Another group of GW signals that has thus far
+been undetected is GW ``bursts". GW bursts are classed as transient
 signals of typically short duration ($<$ 1s) whose waveforms are not accurately
@@
 %
-\ac{GW} searches for modelled signals use a process called
+GW searches for modelled signals use a process called
 matched-filtering,~\cite{Owen1998,Usman_2016,sachdev2019gstlal}, where a large template bank of possible
-\ac{GW} waveforms are compared to the detector outputs. For \ac{GW} bursts that remain unmodelled; there are no
+GW waveforms are compared to the detector outputs. For GW bursts that remain unmodelled; there are no
 templates available and so matched-filtering is unsuitable for the detection of
@@
 %
-\ac{GW} burst detection algorithms~\cite{drago2020coherent,Klimenko_2008, Aso_2008} are tested
-and tuned using modelled waveforms that have easy to define parameters and share characteristics of real bursts that aim to simulate a \ac{GW} passing between
+GW burst detection algorithms~\cite{drago2020coherent,Klimenko_2008, Aso_2008} are tested
+and tuned using modelled waveforms that have easy to define parameters and share characteristics of real bursts that aim to simulate a GW passing between
 detectors. Such waveforms include sine-Gaussians: a
@@
 %
-With the expectation that there will be many more \ac{GW} detections in the
-future, there is a growing need for fast and efficient \ac{GW} analysis methods
+With the expectation that there will be many more GW detections in the
+future, there is a growing need for fast and efficient GW analysis methods
 to match the rising number of detections.
-While still in its infancy, the application of \ac{ML} to \ac{GW} analyses has already shown great potential in areas of detection ~\cite{Gabbard2017,Gebhard_2019,Krastev_2020}, where these techniques have matched the sensitivity of matched filtering for Advanced LIGO and Advanced Virgo gravitational-wave searches.
-In identifying and classifying detector noise transients or  ``glitches''~\cite{Bahaadini, George_2018,Razzano_2018, 2020arXiv200801262G}.
-In Bayesian parameter
-estimation~\cite{gabbard2019bayesian,Chua:2019,green2020gravitationalwave} where \ac{ML} techniques can recover parameters of a \ac{GW} signal significantly faster than standard methods.
-Long duration signals like continuous \ac{GW} require long observing times and therefore have large amounts of data needing to be processed.
+While still in its infancy, the application of \ac{ML} to GW analyses has already shown great potential in areas of detection~\cite{Gabbard2017,Gebhard_2019,Krastev_2020}, where these techniques have matched the sensitivity of matched filtering for Advanced LIGO and Advanced Virgo GW searches.
+Similarly, for unmodelled burst search the flexibility of \ac{ML} algorithms has been shown to be a natural and sensitive approach to detection~\cite{2020arXiv200914611S}.
+Progress has also been made in identifying and classifying detector noise transients or  ``glitches''~\cite{Bahaadini, George_2018,Razzano_2018, 2020arXiv200801262G} and in Bayesian parameter estimation~\cite{gabbard2019bayesian,Chua:2019,green2020gravitationalwave} where \ac{ML} techniques can recover parameters of a GW signal significantly faster than standard methods.
+Long duration signals like continuous GW require long observing times and therefore have large amounts of data needing to be processed.
 Current \ac{ML} approaches~\cite{2020PhRvD.102b2005D, 2019PhRvD.100d4009D, 2020arXiv200708207B} are particularly well suited to dealing with this as once trained the searches can be performed quickly.
@@
 In this work we aim to explore the use of \ac{ML} to generate and interpret
-unmodelled \ac{GW} burst waveforms. Using the generative machine learning
+unmodelled GW burst waveforms. Using the generative machine learning
 model, \acp{GAN}, we train on five classes of waveforms in the time domain. Working on the assumption that \acp{GAN} construct smooth
@@
 techniques. These new varieties of waveforms can then be used to evaluate
-detection algorithms, gain new insight into sources of \ac{GW}
+detection algorithms, gain new insight into sources of GW
 bursts and  allow us to better train our algorithms on a
@@
 \caption{Neural Networks (a) A single neuron taking a vector of inputs and
-returning a single output based on the weights, bias and activation function
+returning a single output based on the weights, bias, and activation function
 of the network.
 (b) A selection of activation functions used in this study.
-The sigmoid (solid purple), rectified linear unit (ReLU) \cite{relu} (dashed wild strawberry red) and leaky rectified linear unit \cite{Maas2013RectifierNI} (dotted blue).
-(c)
-A an example of a neural network containing two hidden layers that performs a
-mapping of an input vector to a single output.}
+The sigmoid (solid purple), rectified linear unit (ReLU)~\cite{relu} (dashed red) and leaky rectified linear unit~\cite{Maas2013RectifierNI} (dotted blue).
+(c) A an example of a neural network containing two hidden layers that performs a mapping of an input vector to a single output.}
 \end{figure}
@@
 \begin{align}
-f(x) = \sigma(\sum_i w_i x_i + b),
+f(x) = \sigma\left(\sum_i w_i x_i + b\right),
 \label{eqn:neuron}
@@
 The results show that for each case that the generated signals show distinct characteristics of the respective class pairs at most stages of the transition.
-We note that transitions in some cases appear to be rather abrupt, e.g., between the Gaussian pulse and the \ac{BBH}, \chris{but we point out that this feature, whilst not uncommon, is a strong function of the random latent space location.}
+We note that transitions in some cases appear to be rather abrupt, e.g., between the Gaussian pulse and the \ac{BBH}, and that this feature, whilst not uncommon, is a strong function of the random latent space location.
 %
@@
 Uniformly sampling generates class space locations up to a maximum distance of unity from the closest class e.g.
-$[0,0,0,0,0]$ is of distance 1 away from all classes (as is $[1,1,1,1,1]$ \michael{Isn't this point further?
-$\sqrt{(1-1)^2 + 1^2 + 1^2 + 1^2 + 1^2} = \sqrt{4} = 2$?}).
+$[0,0,0,0,0]$ is of distance 1 away from all classes.
 For simplex class vectors, we sample from the simplest hyper-surface that intersects all the classes and has a symmetry such that no training class location (any vertex) is favoured over any other.
@@
 Time delays between detectors are computed relative to the Earth's centre.
-All of the training data used is whitened using the Advanced LIGO design sensitivity \ac{PSD}\chris{add reference}, such that there is equal noise power at each frequency.
+All of the training data used is whitened using the Advanced LIGO design sensitivity \ac{PSD} \cite{designcurve,observing-prospects}, such that there is equal noise power at each frequency.
 Signal network \acp{SNR} is drawn uniformly in the range $[1,16]$ and is controlled by an amplitude scaling applied to the waveform.
@@
 The network is trained to be able to identify whether or not a measurement contains a signal and therefore 50\% of the training data have time-series containing signals and 50\% have only noise.
-We randomly divide the data into the 3 standard sets (training, validation, and test data) where 40\% is used for training, 10\% used for validation, and 50\% is used for testing in order to achieve suitably low false-alarm rates.
+We randomly divide the data into the 3 standard sets (training, validation, and test data) where 40\% is used for training, 10\% used for validation, and 50\% is used for testing in order to achieve suitably low false-alarm probability of $10^{-3}$ .
 For the Uniform and Simplex datasets samples are drawn uniformly from their respective spaces.
@@
 \caption{Efficiency curves comparing the performance of the \acp{CNN}.
-The true alarm probability is plotted as a function of the optimal \ac{SNR} of the signals.
+The true alarm probability is plotted as a function of the optimal \ac{SNR} of the signals for a false alarm probability of $10^{-3}$.
 Each plot shows the performance of a \ac{CNN} trained on vertex, simplex and uniform datasets tested on vertex (a), simplex (b), uniform (c).}
@@
 The uniform model performs best in all cases and since it contains signals from the vertex and simplex samples and does not appear to suffer from an increased false alarm probability due to its larger parameter space volume.
-This suggests that the uniform method of sampling the class space for training or characterising a search algorithm is the most robust and sensitive approach given the intrinsically unknown nature of \ac{GW} burst signals.
+This suggests that the uniform method of sampling the class space for training or characterising a search algorithm is the most robust and sensitive approach given the intrinsically unknown nature of GW burst signals.
 Furthermore, since the uniform trained model performs equally as well as the vertex trained model when applied to  vertex test data, we can conclude that the inclusion of the unmodelled signals does not negatively affect the model's performance on modelled signals.
@@
 In this work we present the potential of \acp{GAN} for
-burst \ac{GW} generation.
+burst GW generation.
 We have shown that \acp{GAN} have the ability to generate plausible time-series burst data and present a novel approach to generating unmodelled waveforms.
@@
 When coupled with the latent space, we are then able to generate hybrid waveforms that span the variation between signal classes and the variation within each class.
-The resultant hybrid waveforms then represent a generalised set of potential \ac{GW} burst waveforms that are vastly different from the limited training set.
-Such waveforms are in demand in \ac{GW} astronomy as they allow burst search pipeline developers to test and enhance their detection schemes.
+The resultant hybrid waveforms then represent a generalised set of potential GW burst waveforms that are vastly different from the limited training set.
+Such waveforms are in demand in GW astronomy as they allow burst search pipeline developers to test and enhance their detection schemes.
 
@@
 
-In contrast to typical approaches in signal generation this is the first time a \ac{GAN} has been used for generating gravitational wave burst data.
+% Glitches
+%
+In contrast to typical approaches in signal generation this is the first time a \ac{GAN} has been used for generating GW burst data.
 Our approach allows us to explicitly control the mixing of different signal training classes but the variation within the space of signal properties is determined randomly through sampling of the abstract latent space.
@@
 One such set of additional classes of interest would be the population of detector ``glitches''.
-These are typically high-amplitude short-duration events in the output of \ac{GW} detectors that represent sources of terrestrial detector noise rather than that of astrophysical origin.
-Using a \ac{GAN} to model these would provide us with a tool to simulate an unlimited set of glitches which could be used for use in the understanding of these glitches and could help to remove them in order to get the cleanest data stream possible.
-
-\michael{We only generate one polarisation, might be worth adding something saying that this could be extented to two polarisations in future work?}
-
-Test on cWB
-
-mention SNe but don't talk about real noise
-
-Having the ability to quickly
-generate new waveforms is essential to test current detection schemes and their
-susceptibilty to unmodeled sources. We have shown that \acp{GAN} have the ability
-to generate high fidelity waveforms which do not rely on large prior parameter space. Having banks of these
-waveforms at hand can aid in our understand of the physics processes behind
-these non-standard \ac{GW} emitters.
+These are typically high-amplitude short-duration events in the output of GW detectors that represent sources of terrestrial detector noise rather than that of astrophysical origin.
+Using a \ac{GAN} to model these would provide us with a tool to simulate an unlimited set of glitches which could be used to better understand their origin and guide us towards more effective methods of mitigation and removal from the data stream.
+
+% Supernova waveforms
+% 
+Another waveform class of interest are those of Supernovae, for which some of our hybrid \ac{GAN} generated waveforms share common features (see Figs.~\ref{fig:simplexd_samples} and~\ref{fig:uniform_samples}).
+Since Supernovae simulations are extremely computationally costly their are relatively few $\mathcal{O}(100s)$ waveforms available for training.
+This makes \acp{GAN} an attractive prospect for generating entirely new pseudo-realistic waveform realisations consistent with the prior distribution defined by the training set.
+The conditional aspect of our \ac{GAN} implementation could also allow the user to specify particular desired physical properties of the generated waveforms.
+For this Supernovae application specifically, we mention the benefit of extending our current method beyond modelling only a single polarisation.
+
+% Final statement
+%
+Having the ability to quickly generate new waveforms is essential to test current GW burst detection schemes~\cite{drago2020coherent,Klimenko_2008, Aso_2008}.
+They can be used to truly assess their sensitivity to unmodeled sources and identify signal features to which they are susceptible.
 

### 2021-01-28 Paper_draft/main.tex
Updated abstract

@@
 \begin{abstract}
-We introduce the use of conditional generative adversarial networks for generalised GW burst generation in the time domain.
-Generative adversarial networks are generative machine learning models that produce new data based on the statistics of the training set.
-We condition the network on five classes of time-series signals: sine-Gaussian, ringdown, white noise burst, Gaussian pulse and binary black hole merger and show that the model can replicate the features of these classes.
-Additionally, we show the model can produce generalised burst signals through interpolation and class mixing.
-Furthermore, we build a convolutional neural network classifier to predict the detectability of these newly produced signals in LIGO detector noise against more traditional burst waveforms.
+We introduce the use of conditional generative adversarial networks for generalised gravitational wave burst generation in the time domain.
+Generative adversarial networks are generative machine learning models that produce new data based on the features of the training data set.
+We condition the network on five classes of time-series signals that are often used to characterise gravitational wave burst searches: sine-Gaussian, ringdown, white noise burst, Gaussian pulse and binary black hole merger.
+We show that the model can replicate the features of these standard signal classes and, in addition, produce generalised burst signals through interpolation and class mixing.
+We also present an example application where a convolutional neural network classifier is trained on burst signals generated by our conditional generative adversarial network.
+We show that a convolutional neural network classifier trained only on the standard five signal classes has a poorer detection efficiency than a convolutional neural network classifier trained on a population of generalised burst signals drawn from the entire signal class space.
 \end{abstract}
@@
     \centering
-    \showthe\textwidth
     \includegraphics[width=\textwidth]{figures/training-sample.pdf}

### 2021-02-18 Paper_draft/main.tex
addressing p&p reviewer comments

@@
 \usepackage[mathlines]{lineno}% Enable numbering of text and display math
-\linenumbers\relax % Commence numbering lines
+%\linenumbers\relax % Commence numbering lines
 
@@
 \begin{document}
-
 \title{Generalised gravitational burst generation with Generative Adversarial Networks}
@@
 
-\address{University of Glasgow, Physics \& Astronomy Department, Glasgow G12 8QQ, UK}
+\address{SUPA, School of Physics and Astronomy, University of Glasgow, Glasgow G12 8QQ, United Kingdom}
 %\ead{jordan.mcginn@glasgow.ac.uk}
@@
 %\end{indented}
-
 \begin{abstract}
@@
 We also present an example application where a convolutional neural network classifier is trained on burst signals generated by our conditional generative adversarial network.
-We show that a convolutional neural network classifier trained only on the standard five signal classes has a poorer detection efficiency than a convolutional neural network classifier trained on a population of generalised burst signals drawn from the entire signal class space.
+We show that a convolutional neural network classifier trained only on the standard five signal classes has a poorer detection efficiency than a convolutional neural network classifier trained on a population of generalised burst signals drawn from the combined signal class space.
 \end{abstract}
@@
 
-\begin{comment}
-\begin{itemize}
-\item Need to introduce GWs - the current state of the field e.g. detections
-and LVC papers \ding{51}
-\item Introduce burst searches - what's the point of burst searches \ding{51} - lots of references 
-\item Discuss the family of burst waveforms currently used and why - not in detail, just
-an introduction \ding{51}
-\item Introduce ML techniques in GWs \ding{51} - lots of references
-\item What this paper does on GANs in 1 paragraph \ding{51}
-\item Describe the structure of the paper 
-\end{itemize}
-\end{comment}
-
 % introduce GW astrophsyics
@@
 %
-\begin{comment}Such waveforms may have
-long-duration, short bandwidth (ringdowns), long-duration, large bandwidth
-(inspirals) and many algorithms make use of sine-Gaussians: a Gaussian
-modulated sine wave that is characterised by it's central frequency and narrow
-bandwidth.~\chris{not the time to try to describe the types of burst waveforms.
-Also, be careful with satying things like ringdowns have narrow bandwidth. I
-know we specify a single frequency but becuase of the short duration, the
-signal is broad band. Look at the FFT} This makes it a great tool for
-diagnosing LIGOs sensitivity to frequency.~\chris{strange unfinished sentence.} 
-\end{comment}
-
 % Introduce ML techniques in GWs
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{comment}
-\begin{itemize}
-\item Describe GANs in detail but really focus on the fact that the reader is a
-GW data analyst - not a computer scientist \ding{51}
-\item A diagram would be very useful \ding{51}
-\item Do not discuss our specific case here - just stay general \ding{51}
-\item A subsection on the specific advanced flavour of GAN that you are using
-here - motivate this choice. \ding{51}
-\end{itemize}
-\end{comment}
-
 % introduce GANs
@@
 %
-\begin{comment}
-Neural networks are the quintessential~\chris{really? quintessential?} \jordan{It's a perfectly cromulent word https://www.imdb.com/title/tt0701155/} \ac{ML}
-algorithm that aims to approximate a function. 
-\end{comment}
-
 \ac{ML} algorithms aim to learn apparent relationships held within given data or `training
@@
 generator (fake).
-\begin{comment}
-Chris' definition of latent space if needed: It maps the intrinsic
-variation of the training space onto the Gaussian latent space distribution.
-\end{comment}
 %
@@
 \begin{equation}
-    L = -y \log(\hat{y}) - (1 - y) \log(1-\hat{y}),
+    L = y \log(\hat{y}) - (1 - y) \log(1-\hat{y}),
     \label{eqn:crossentropy}
@@
 Since the objective of the discriminator is to correctly classify fake and real data these equations should be maximised, while the goal of the generator should be to minimize these equations.
-This gives the \ac{GAN} loss as
+This gives what is know as the \ac{GAN} value function as
 %
@@
 %
-Training a GAN is involves updating both the discriminator and generator in stages.
+Training a GAN involves updating both the discriminator and generator in stages.
 First, the discriminator is updated using real instances from the training set.
-We set the true label $y=1$ and calculate the loss with respect to the predictions $\hat{y}$ via \cref{equation:GANloss}.
-Stochastic gradient descent is used to minimize the loss which has reduced to $L_D(\textrm{real}) = -\log(\hat{y})$.
-The discriminator is then trained on fake instances taken from the generator where we set $y=0$ and minimize $L_D(\textrm{fake}) = -\log(1-\hat{y})$.
+We set the true label $y=1$ and calculate the loss with respect to the predictions $\hat{y}$ via \cref{eqn:crossentropy}.
+Stochastic gradient descent is used to maximise the loss which has reduced to $L_D(\textrm{real}) = \log(\hat{y})$.
+The discriminator is then trained on fake instances taken from the generator where we set $y=0$ and maximise $L_D(\textrm{fake}) = \log(1-\hat{y})$.
 To train the generator, we use a composite model of the generator and discriminator and allow the gradients to flow through this entire model.
-At this step we set the labels for the generator as real $y=1$ and minimize $L_G = -\log(\hat{y})$.
-The act of switching the labels and minimizing this form of loss is identical to the previously mentioned generator loss but is beneficial as in practice this function provides more useful gradients.
+Following on from what was described before, to train the generator we set y = 0 and minimise $L_{G}$(fake) = $\log(1-\hat{y})$.
+During early stages of training the generator produces poor generations and so D can easily determine them as fake i.e.
+$\hat{y})$~0.
+This leads $L_{G}$ to tend to 0 and we encounter the \textit{vanishing gradient problem}, where the gradients become so small that the weights can no longer be updated.
+A solution to this problem involves changing the generator loss to maximise $L_{G}$(fake) = $\log(\hat{y})$ or equivalently continue to minimise $L_{G}$(fake) = $\log(1-\hat{y})$ and simply switch the $y$ label to 1.
 This tweak to the generator loss is called non-saturating generator loss and was reported in the original \ac{GAN} paper \cite{Goodfellow2014}.
@@
 waveforms based on the input label.}
-\begin{comment}
-~\chris{Overall it's a bit basic and doesn't indicate either the
-2 competing training steps or any aspect of the loss or specify that $x$ and
-$z$ (and $c$) are drawn from distributions already defined in the text. Maybe it's OK without
-that. As for the CGAN, I'm troubled by the fact that there is only one $c$ box.
-It implies that the same $c$ value is given to each real and fake $x$ data when
-in fact each $x$ sample has it's own randomly drawn $c$ value.}
-\end{comment}
 \label{fig:gan_comparison}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{comment}
-\begin{itemize}
-\item Need to introduce the scheme you propose to use
-\item A paragraph or subsection on the data generation being very clear on all
-5 waveform models and the prior parameter space for each \ding{51}
-\item A subsection on the design of the network architecture \ding{51}
-\item A subsection on the "box" and why we implement it \ding{51}
-\item A subsection on the training of the network - give rough timings and rule
-of thumb decisions made
-\item Do not discuss the results here 
-\end{itemize}
-\end{comment}
-
 % introduce the training data
@@
 %
-We propose a signal generation scheme using a \ac{CGAN} trained on burst-like waveforms.
-We call this \texttt{McGANn}\footnote{https://github.com/jmcginn/McGANn} and it is a \ac{CGAN} trained on five signal classes each spanning a range of prior signal parameters.
-The signal classes are:
+We propose a signal generation scheme using a CGAN trained on burst-like waveforms which we call \texttt{McGANn}\footnote{https://github.com/jmcginn/McGANn}.
+\texttt{McGANn} is trained on five signal classes which are used to characterise the sensitivity of gravitational wave burst searches (see for example \cite{PhysRevD.100.024017}).
 
@@
 defined in~\cref{Tab:training_parms} and a sample of training waveforms are shown in \cref{fig:training_waveforms}. All training data is rescaled such that their amplitudes peak at 1.
-
 \begin{table}[!h]
@@
 
+With the exception of the binary black hole waveforms, the signal classes described above are analytic proxy waveforms to gravitational wave signals expected from various burst gravitational wave sources.
+For example, numerical relativity simulations show that rapidly rotating stellar core collapse emit gravitational waves that look like sine gaussians with small time constants (low Q).
+Additionally, gravitational waves from hyperbolic black hole encounters look very similar to sine gaussians and gaussian pulses.
+Ringdown signals can be emitted by excited isolated neutron stars, for example, after a pulsar glitch and white noise burst signals mimic the stochastic nature of gravitational wave signals emitted by neutrino driven stellar core collapse.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{comment}
-\begin{itemize}
-\item Begin by outlining the type of results you will be presenting
-\item A subsection on the general quality of generated waveforms - we may need
-to have overlaps between generated wavefoms and training data (maybe)
-\item A subsection on the descriminator - maybe a confusion matrix?
-\item a subsection on the latent space varaition within each class - fixed
-class, sliding in latent space.
-\item A subsection on the class space variation - fixed latent space and
-sliding in the class space.
-\item A final subsection on the general waveform model based on random latent
-and class space locations.
-\item Make no conclusions.
-\end{itemize}
-\end{comment}
-
 % describe the main idea
@@
 This is to be expected given that the simplex class space is a subset of the hyper-cube and does not explore regions of the class space as far from the training set vertices.
-
-\begin{comment}
-~\chris{Also, discuss the corresponding figure! There has to be comment on the
-features of simplex vs box generations as well as general comments about how
-the GAN likes to mix signals up. Pick on specific examples and comment on
-interesting or annoying features.We can expect a priori that the uniformly sampled space (which contains the simplex as a subspace) will allow for some level of extrapolation.}
-
-\michael{You could also point to \cref{fig:gen_signals} since you have figures for Uniform and Simplex}
-
-~\chris{I have an idea for the plots. Could we have a colour coding system
-where each class gets a colour and then when you mix them you plot it with the
-mixed colours - you average the RGB values. Maybe everything would look brown?
-Worth a try?}
-\end{comment}
 
@@
 
-\begin{comment}
-\begin{itemize}
-    \item vertex trained shows clear delineation from other two classes at \ac{SNR}$>$10. Good to show that they are different. But not all converge to 1.
-    \item simplex trained leads in smaller \acp{SNR} but eventually all converge to 1
-    \item uniform trained shows much similarity to simplex test set, still different from vertex.
-all converge to 1.
-makes sense if the vertex is a subset of the simplex and uniform classes.
-Also a sign that the \ac{GAN} likes to keep things as close to vertex as possible?
-\end{itemize}
-\end{comment}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 The resulting trained networks were then tested on independent datasets from each of the three signal hybrid classes.
-The resulting efficiency curves compare the detection sensitivities of the \ac{CNN} as a function of \ac{SNR} and allow us to conclude that in this simple analysis, training the search using the most general set of hybrid waveforms (our "uniform" set) provides the most sensitive overall result.
+The resulting efficiency curves compare the detection sensitivities of the \ac{CNN} as a function of \ac{SNR} and allow us to conclude that in this simple analysis, training the search using the most general set of hybrid waveforms (our ``uniform" set) provides the most sensitive overall result.
 
@@
 They can be used to truly assess their sensitivity to unmodeled sources and identify signal features to which they are susceptible.
-
-\begin{comment}
-\begin{itemize}
-\item Summarise the paper
-\item Dedicate a paragraph to each of the key results discussed in the previous
-section
-\item Have at least one paragraph on the future directions of this work
-\item Conclude with a positive paragrpah about the potential uses and impact of
-the approach.
-\end{itemize}
-\end{comment}
 
@@
 Concatenate & (105) & - & - & \ding{55} &  - \\
-Dense & (32768) & - & - & \ding{55} &  ReLu \\
+Dense & (32768) & - & - & \ding{55} &  ReLU \\
 Reshape & (64, 512) & - & - & \ding{55} & - \\

### 2021-05-05 Paper_draft/main.tex
first response to comments

@@
 \begin{document}
-\title{Generalised gravitational burst generation with Generative Adversarial Networks}
+\title{Generalised gravitational \jordan{wave} burst generation with Generative Adversarial Networks}
 
 \author{
-    J. McGinn \orcidicon{0000-0000-0000-0000},
+    J. McGinn \orcidicon{0000-0001-8910-0881},
     C. Messenger \orcidicon{0000-0001-7488-5022},
-    I.S. Heng \orcidicon{0000-0000-0000-0000},
-    M. J. Williams \orcidicon{0000-0003-2198-2974}
+    M. J. Williams \orcidicon{0000-0003-2198-2974},
+    I. S. Heng \orcidicon{0000-0002-1977-0019}
 }
@@
 glitches.
+\jordan{The presence of environmental glitches can often be associated with transient signals detected by various sensors within the LIGO detectors.
+The detectors record data from many auxiliary channels that are used to monitor instrument and environmental backgrounds.
+This allows some of the glitches to be catalogued and de-coupled from the gravitational wave data thereby improving data quality.
+See \cite{Abbott_2016_noise2,Abbott_2020_noise1} for a more detailed explanation of transient noise and detector characterisation.}
 
@@
 While still in its infancy, the application of \ac{ML} to GW analyses has already shown great potential in areas of detection~\cite{Gabbard2017,Gebhard_2019,Krastev_2020}, where these techniques have matched the sensitivity of matched filtering for Advanced LIGO and Advanced Virgo GW searches.
-Similarly, for unmodelled burst search the flexibility of \ac{ML} algorithms has been shown to be a natural and sensitive approach to detection~\cite{2020arXiv200914611S}.
-Progress has also been made in identifying and classifying detector noise transients or  ``glitches''~\cite{Bahaadini, George_2018,Razzano_2018, 2020arXiv200801262G} and in Bayesian parameter estimation~\cite{gabbard2019bayesian,Chua:2019,green2020gravitationalwave} where \ac{ML} techniques can recover parameters of a GW signal significantly faster than standard methods.
+Similarly, for unmodelled burst search the flexibility of \ac{ML} algorithms has been shown to be a natural and sensitive approach to detection~\cite{2020arXiv200914611S, PhysRevD.103.063011}.
+Progress has also been made in identifying and classifying detector noise transients or  ``glitches''~\cite{Bahaadini, George_2018,Razzano_2018, 2020arXiv200801262G} as well as glitch classification through Gravity Spy \cite{gravityspy_2017}, a combination of machine learning and crowdsourcing.
+In Bayesian parameter estimation~\cite{gabbard2019bayesian,Chua:2019,green2020gravitationalwave} where \ac{ML} techniques can recover parameters of a GW signal significantly faster than standard methods.
 Long duration signals like continuous GW require long observing times and therefore have large amounts of data needing to be processed.
@@
 \begin{equation}
-    L = y \log(\hat{y}) - (1 - y) \log(1-\hat{y}),
+    L = y \log(\hat{y}) + (1 - y) \log(1-\hat{y}),
     \label{eqn:crossentropy}
@@
 One way to diagnose problems, such as mode collapse, when training \acp{GAN} is to keep track of the loss and accuracy over time.
-Loss plots, for example, as seen in \cref{fig:lossplot} can help to identify common failure modes or to check if the \ac{GAN} has indeed converged.
+\jordan{A Loss plots, for example, like the one used for this work} \cref{fig:lossplot} can help to identify common failure modes or to check if the \ac{GAN} has indeed converged.
 Accuracy is another metric that may be used to monitor convergence and is defined as the number of correct predictions made divided by total number of predictions.
@@
 be within $[0.4, 0.6]$ seconds from the start of the 1 second time interval and all
-training waveforms are sampled at 1024 Hz.  The parameter prior ranges are
-defined in~\cref{Tab:training_parms} and a sample of training waveforms are shown in \cref{fig:training_waveforms}. All training data is rescaled such that their amplitudes peak at 1.
+training waveforms are sampled at 1024 Hz.
+\jordan{While in principle GANs are able to generate high fidelity images of the order 1024x1024x3, we choose 1024 Hz due to memory constraints, however, the information content in the burst generations will be broadly similar to a more typical 4000Hz sampling rate and we found that at higher sampling rates the GAN became unstable.
+Mention other GANs as proof that they become unstable and need fancy things like PGAN?}.
+The parameter prior ranges are
+defined in~\cref{Tab:training_parms} and a sample of training waveforms are shown in \cref{fig:training_waveforms}.
+\jordan{These priors are based on LIGO burst group injections with Q's calculated from choosing frequency as the limiting factor.
+The other paramters can then be evaluated based on the Q relation.
+For the BBH waveforms we restrict the mass to be above 30 as lower mass systems would produce longer duration waveforms than typical bursts.} All training data is rescaled such that their amplitudes peak at 1.
 \begin{table}[!h]
@@
 Ringdown signals can be emitted by excited isolated neutron stars, for example, after a pulsar glitch and white noise burst signals mimic the stochastic nature of gravitational wave signals emitted by neutrino driven stellar core collapse.
+\jordan{The classes of signals (and their suitability?) considered in this work are also described in \cite{PhysRevD.100.024017}}.
 
@@
 % 
-Another waveform class of interest are those of Supernovae, for which some of our hybrid \ac{GAN} generated waveforms share common features (see Figs.~\ref{fig:simplexd_samples} and~\ref{fig:uniform_samples}).
+%Another waveform class of interest are those of Supernovae, for which some of our hybrid \ac{GAN} generated waveforms share common features (see Figs.~\ref{fig:simplexd_samples} and~\ref{fig:uniform_samples}).
 Since Supernovae simulations are extremely computationally costly their are relatively few $\mathcal{O}(100s)$ waveforms available for training.

### 2021-05-21 Paper_draft/main.tex
Newest responses

@@
 \begin{document}
-\title{Generalised gravitational \jordan{wave} burst generation with Generative Adversarial Networks}
+\title{Generalised gravitational wave burst generation with Generative Adversarial Networks}
 
@@
 Gravitational wave (GW) astronomy is now an established field that began with the first detection of a binary black hole merger~\cite{Abbott2016} in September 2015.
-Following this, the first and second observations runs (O1 and O2) of Advanced LIGO and Advanced Virgo~\cite{Prospects-dets, AdvLIGO, AdvLIGO2, AdvVIRGO} reported several more \ac{CBC} mergers~\cite{Abbott2016a, Abbott2017, Abbott2017a}.
+Following this, the first and second observation runs (O1 and O2) of Advanced LIGO and Advanced Virgo~\cite{Prospects-dets, AdvLIGO, AdvLIGO2, AdvVIRGO} reported several more \ac{CBC} mergers~\cite{Abbott2016a, Abbott2017, Abbott2017a}.
 On 17th August 2017 a binary neutron star merger was observed alongside its electromagnetic counterpart for the first time, giving rise to multi-messenger GW astronomy \cite{Abbott2017b}.
@@
 glitches.
-\jordan{The presence of environmental glitches can often be associated with transient signals detected by various sensors within the LIGO detectors.
+\jordan{The presence of environmental glitches is often associated with transient signals detected by various sensors within the LIGO and Virgo detectors.
 The detectors record data from many auxiliary channels that are used to monitor instrument and environmental backgrounds.
-This allows some of the glitches to be catalogued and de-coupled from the gravitational wave data thereby improving data quality.
+This allows some of the glitches to be catalogued and removed from the gravitational wave data, thereby improving data quality.
 See \cite{Abbott_2016_noise2,Abbott_2020_noise1} for a more detailed explanation of transient noise and detector characterisation.}
@@
 While still in its infancy, the application of \ac{ML} to GW analyses has already shown great potential in areas of detection~\cite{Gabbard2017,Gebhard_2019,Krastev_2020}, where these techniques have matched the sensitivity of matched filtering for Advanced LIGO and Advanced Virgo GW searches.
-Similarly, for unmodelled burst search the flexibility of \ac{ML} algorithms has been shown to be a natural and sensitive approach to detection~\cite{2020arXiv200914611S, PhysRevD.103.063011}.
-Progress has also been made in identifying and classifying detector noise transients or  ``glitches''~\cite{Bahaadini, George_2018,Razzano_2018, 2020arXiv200801262G} as well as glitch classification through Gravity Spy \cite{gravityspy_2017}, a combination of machine learning and crowdsourcing.
+Similarly, for unmodelled burst searches the flexibility of \ac{ML} algorithms has been shown to be a natural and sensitive approach to detection~\cite{2020arXiv200914611S, PhysRevD.103.063011}.
+\jordan{Progress has also been made in identifying and classifying detector noise transients or  ``glitches''~\cite{Bahaadini, George_2018,Razzano_2018, 2020arXiv200801262G} as well as glitch classification using a combination of \ac{ML} and citizen science \cite{gravityspy_2017}}.
 In Bayesian parameter estimation~\cite{gabbard2019bayesian,Chua:2019,green2020gravitationalwave} where \ac{ML} techniques can recover parameters of a GW signal significantly faster than standard methods.
 Long duration signals like continuous GW require long observing times and therefore have large amounts of data needing to be processed.
-Current \ac{ML} approaches~\cite{2020PhRvD.102b2005D, 2019PhRvD.100d4009D, 2020arXiv200708207B} are particularly well suited to dealing with this as once trained the searches can be performed quickly.
+Current \ac{ML} approaches~\cite{2020PhRvD.102b2005D, 2019PhRvD.100d4009D, 2020arXiv200708207B} are particularly well suited to dealing with this as once trained, searches can be performed quickly.
 
@@
 %
-In this work we aim to explore the use of \ac{ML} to generate and interpret
-unmodelled GW burst waveforms. Using the generative machine learning
+In this work, we aim to explore the use of \ac{ML} to generate and interpret
+unmodelled GW burst waveforms. Using the generative \ac{ML}
 model, \acp{GAN}, we train on five classes of waveforms in the time domain. Working on the assumption that \acp{GAN} construct smooth
@@
 This paper is organised as follows.
-In \cref{ML overview} we introduce the basic ideas of machine learning and discuss the choice of algorithm we used.
+In \cref{ML overview} we introduce the basic ideas of \ac{ML} and discuss the choice of algorithm we used.
 In \cref{Method} we describe the training data and the details of the model.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Machine learning} \label{ML overview}
+\section{Generative adversarial networks} \label{ML overview}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 % introduce GANs
-%
-\subsection{Artificial neural networks}
-
-% inroduce the concept of ML
-%
-
-\begin{figure}[h!]
-\begin{subfigure}[b]{0.30\textwidth}
-   \begin{subfigure}[b]{1\textwidth}
-   	\centering
-	\resizebox{\textwidth}{!}{
- 	\includegraphics{figures/neuron.pdf}
-	}
-	\caption{}
-	 \label{fig:perceptron}
- \end{subfigure}
-
-   \begin{subfigure}[b]{1\textwidth}
-  	\centering
-	\resizebox{\textwidth}{!}{
-\includegraphics{figures/activation.pdf}}
-\caption{}
-\label{fig:activation}
-\end{subfigure}
-\end{subfigure}
-	 \begin{subfigure}[b]{0.70\textwidth}
-\centering
-\resizebox{\textwidth}{!}{
-
-\includegraphics{figures/network.pdf}
-}
- \caption{}
- \label{fig:network}
- \end{subfigure}
-
-\caption{Neural Networks (a) A single neuron taking a vector of inputs and
-returning a single output based on the weights, bias, and activation function
-of the network.
-(b) A selection of activation functions used in this study.
-The sigmoid (solid purple), rectified linear unit (ReLU)~\cite{relu} (dashed red) and leaky rectified linear unit~\cite{Maas2013RectifierNI} (dotted blue).
-(c) A an example of a neural network containing two hidden layers that performs a mapping of an input vector to a single output.}
-\end{figure}
-%
-% Introduce basic neural networks - a perceptron layer
-%
-\ac{ML} algorithms aim to learn apparent relationships held within given data or `training
-data' in order to make accurate predictions without the need for additional
-programming. A common approach in \ac{ML} relies on the model learning from
-past experience to make decisions on future events. Artificial neural networks are universal function approximators that are built from many single
-processing units called neurons. The simplest neural network is the perceptron
-layer~\cref{fig:perceptron} which shows a single neuron that takes a vector of real
-inputs $x_{i},\ldots, x_{n}$
-and maps them to an output according to the linear function, 
-%
-\begin{align}
-f(x) = \sigma\left(\sum_i w_i x_i + b\right),
-\label{eqn:neuron}
-\end{align}
-%
-where $w$ and $b$ are the weights and bias and $\sigma$ denotes the activation function.
-The weights are numbers which can be thought of as the strength between connected neurons.
-The output of a neuron is defined by its activation function which controls how the neuron `fires' depending on its input.
-Some examples of commonly used activation functions are shown in~\cref{fig:activation}.
-It is often useful to introduce a bias, $b$, such that the neuron remains inactive above zero but is active when the sum reaches a defined threshold.
-
-% basic network structure
-%
-A neural network contains many single neurons connected in a layered structure
-as shown in~\cref{fig:network}. The activations of the first layer (or
-input layer) act as the inputs to the second layer and so on until the output
-layer. Multi-layered neural networks have intermediate layers between the input
-and output stages dubbed the hidden layers.
-% the cost or loss function
-%
-The output of a single neuron is gives a
-prediction that can be compared to the real value through a loss (also known as a
-cost) function. The network is trained to minimise this function by updating the weights in the negative
-direction of the loss gradient in a process referred to as gradient
-descent \cite{ruder2016overview}.
-The training process for a single layered network is easy to compute as the weights relate directly to the gradient of the loss function the network is trying to minimise.
-For deeper architectures, the loss is a complicated function of all the weights in all the layers.
-The backpropagation \cite{Nielsen1992} algorithm acts over the many paths from node to output.
-It does so in two phases:
-
-\begin{itemize}
-\item Forward phase: For one instance of training, the inputs are fed forward through the network using the current weights and the final output is compared to the training labels.
-The derivative of the loss function is then computed.
-\item Backward phase: This phase learns how the gradient of the loss function changes when the weights are varied.
-Starting at the output node, the algorithm goes backwards through the network (hence the name).
-The weights that give the steepest descent to the loss function are saved for the next training instance.
-\end{itemize}
-This process of updating the weights is repeated until the loss function reaches convergence or a global minimum.
-As it is impractical to feed the entire data into the network at once, the training is split up into smaller more manageable batches.
-For this work we train on random samples from the training data and define an epoch as the number of training steps.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Convolutional Neural Networks}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-Convolutional neural networks (CNNs) are designed to work with grid-like input structures that exhibit
-strong local spatial dependencies. Although most work with \acp{CNN}
-involves image-based data, they can be applied to other spatially adjacent data
-types such as time-series \cite{2018arXiv180904356I} and text items \cite{2020arXiv200403705M}. \acp{CNN} are defined by the use of a
-convolution operation, a mathematical operation that expresses the amount
-overlap between the data.
-Much like traditional neural networks the convolution operation in this context involves multiplying the input by an array of weights, called a filter or a kernel which is typically smaller in size than the input.
-The convolution is applied by shifting the kernel over the input, drawing out spatially important features between the
-two. The distance by which the grid is shifted is known as
-the stride and increasing it reduces the dimension of the output in a process know as downsampling.
-Alternatively, upsampling the inputs can be achieved using a transposed convolution \cite{dumoulin2016guide}.
-The output of the convolutional layer is then passed to an activation function and through the next layers.
-For deep neural networks, techniques like BatchNormalisation \cite{ioffe2015batch} which standardise the inputs to a layer and SpatialDropout \cite{tompson2014efficient} which sever connections between neurons can both help to stabilise learning.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Generative Adversarial Networks}
+%\subsection{Generative Adversarial Networks}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %
-A subset of deep learning that has seen fruitful development in recent years
+\ac{ML} algorithms aim to learn apparent relationships held within given data or `training
+data' in order to make accurate predictions without the need for additional
+programming. For a general introduction to \ac{ML} see \cite{Goodfellow-et-al-2016}. A subset of deep learning that has seen fruitful development in recent years
 are generative adversarial networks \acp{GAN}~\cite{Goodfellow2014}. These unsupervised algorithms learn patterns in a
@@
 %
-\acp{GAN} train two competing neural networks, consisting of a discriminator
-network that is set up to distinguish between real and fake data and a
-generator network that produces fake versions of the real data. The generator model performs a mapping from a fixed length vector $\mathbf{z}$ to its
+\jordan{\acp{GAN} train two competing neural networks, consisting of a discriminator
+network that is set up to distinguish between real data (those which come from the training set) and fake data which are synthetically generated from the generator network.} The generator model performs a mapping from a fixed length vector $\mathbf{z}$ to its
 representation of the data.
-The input vector is drawn randomly from a Gaussian distribution which is referred to as a latent space comprised of latent variables.
+The input vector is drawn randomly from a Gaussian distribution, which is referred to as a latent space comprised of latent variables.
 The latent space is a compressed representation of a data distribution which the generator applies meaning to during training.
-Sampling points from this space allows the generator to produce a variety of different generations, with different points corresponding to different features in the generations.
-The discriminator maps its input $\mathbf{x}$ to a probability that the input came from either the training (real) data or
+Sampling points in this space allows the generator to produce a variety of different generations, with different points corresponding to different features in the generations.
+The discriminator maps its input $\mathbf{x}$ to a probability that the input comes from either the training (real) data or
 generator (fake).
@@
 %
-Training a GAN involves updating both the discriminator and generator in stages.
+\jordan{Training a GAN involves updating both the discriminator and generator in stages.
 First, the discriminator is updated using real instances from the training set.
-We set the true label $y=1$ and calculate the loss with respect to the predictions $\hat{y}$ via \cref{eqn:crossentropy}.
-Stochastic gradient descent is used to maximise the loss which has reduced to $L_D(\textrm{real}) = \log(\hat{y})$.
-The discriminator is then trained on fake instances taken from the generator where we set $y=0$ and maximise $L_D(\textrm{fake}) = \log(1-\hat{y})$.
+We set the true label $y$ equal to 1 and calculate the loss with respect to the predictions $\hat{y}$ via \cref{eqn:crossentropy}.
+Stochastic gradient descent is used to maximise the discriminators loss on real data, $L_D(\textrm{real}) = \log(\hat{y})$.
+The discriminator is then trained on fake instances taken from the generator where we set $y=0$ and maximise $L_D(\textrm{fake}) = \log(1-\hat{y})$.}
+
 To train the generator, we use a composite model of the generator and discriminator and allow the gradients to flow through this entire model.
 Following on from what was described before, to train the generator we set y = 0 and minimise $L_{G}$(fake) = $\log(1-\hat{y})$.
-During early stages of training the generator produces poor generations and so D can easily determine them as fake i.e.
-$\hat{y})$~0.
+During early stages of training the generator produces poor generations and so D can easily determine them as fake.
 This leads $L_{G}$ to tend to 0 and we encounter the \textit{vanishing gradient problem}, where the gradients become so small that the weights can no longer be updated.
@@
 This tweak to the generator loss is called non-saturating generator loss and was reported in the original \ac{GAN} paper \cite{Goodfellow2014}.
-It was also shown in that paper that if the generator and discriminator can no longer improve, then the discriminator can no longer distinguish between real and fake i.e.
-$D(x) = \frac{1}{2}$.
-
-As \acp{GAN} are trained by updating one model at the expense of the other, they can be hard to train. GANs attempting to replicate complicated structures that do not
-have the necessary architecture either struggle to produce results at all or
-fall into the common failure mode know as mode collapse; where the generator
-produces a small variety of samples or simply memorises the training set.
-The goal of \ac{GAN} training is to find an equilibrium between the two models, if this cannot be found then it is said that the \ac{GAN} has failed to converge.
-One way to diagnose problems, such as mode collapse, when training \acp{GAN} is to keep track of the loss and accuracy over time.
-\jordan{A Loss plots, for example, like the one used for this work} \cref{fig:lossplot} can help to identify common failure modes or to check if the \ac{GAN} has indeed converged.
-Accuracy is another metric that may be used to monitor convergence and is defined as the number of correct predictions made divided by total number of predictions.
-There is currently no notion of early stopping in \acp{GAN}, instead, training is halted after convergence and by visually inspecting the generations.
-\begin{figure}[h!]
-    \centering
-    \includegraphics[width=0.85\textwidth]{figures/losses.png}
-    \caption{Plot of the discriminator and generator loss and accuracy as a function of epochs.
-Early in training the losses oscillate as both models attempt to find their equilibrium, after which, both losses vary around a point which signifies stable training.
-Accuracies on the real and fake data are similar, showing that neither model is stronger than the other.}
-    \label{fig:lossplot}
-\end{figure}
+It was also shown in that paper that if the generator and discriminator can no longer improve, then the discriminator can no longer distinguish between real and fake samples and will continue to output $D(x) = \frac{1}{2}$ in this optimal training scenario.
 
@@
  \end{equation}
-Fig. \ref{fig:gan_comparison} shows the differences in inputs and outputs of a GAN compared with a \ac{CGAN}. We will be using a conditional GAN for this study.
+Fig. \ref{fig:gan_comparison} shows the differences in inputs and output of a GAN compared with a \ac{CGAN}. We will be using a conditional GAN for this study.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Convolutional Neural Networks}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+Convolutional neural networks (CNNs) are designed to work with grid-like input structures that exhibit
+strong local spatial dependencies. Although most work with \acp{CNN}
+involves image-based data, they can be applied to other spatially adjacent data
+types such as time-series \cite{2018arXiv180904356I} and text items \cite{2020arXiv200403705M}. \acp{CNN} are defined by the use of a
+convolution operation, a mathematical operation that expresses the amount
+overlap between the data.
+Much like traditional neural networks, the convolution operation in this context involves multiplying the input by an array of weights, called a filter or a kernel, which is typically smaller in size than the input.
+The convolution is applied by shifting the kernel over the input, drawing out spatially important features between the
+two. The distance by which the grid is shifted is known as
+the stride and increasing it reduces the dimension of the output in a process know as downsampling.
+Alternatively, upsampling the inputs can be achieved using a transposed convolution \cite{dumoulin2016guide}.
+The output of the convolutional layer is then passed to an activation function and through the next layer.
+For deep neural networks, techniques like BatchNormalisation \cite{ioffe2015batch} which standardise the inputs to a layer and SpatialDropout \cite{tompson2014efficient} which sever connections between neurons can both help to stabilise learning.
+
+% inroduce the concept of ML
+%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 % introduce the training data
+%
+% introduce the signal models
 %
@@
 \end{figure}
-% introduce the signal models
-%
 We propose a signal generation scheme using a CGAN trained on burst-like waveforms which we call \texttt{McGANn}\footnote{https://github.com/jmcginn/McGANn}.
@@
 waveform~\cite{Khan_2016} routine from LALSuite~\cite{lalsuite} which models
-the inspiral, merger and ringdown of a \ac{BBH} waveform. The component masses
+the inspiral, merger, and ringdown of a \ac{BBH} waveform. The component masses
 lie in the range of [30,70] $\textrm{M}_{\odot}$ with zero spins and we fix
@@
 training waveforms are sampled at 1024 Hz.
-\jordan{While in principle GANs are able to generate high fidelity images of the order 1024x1024x3, we choose 1024 Hz due to memory constraints, however, the information content in the burst generations will be broadly similar to a more typical 4000Hz sampling rate and we found that at higher sampling rates the GAN became unstable.
-Mention other GANs as proof that they become unstable and need fancy things like PGAN?}.
+\jordan{While in principle GANs are able to generate higher dimensional spaces, we choose 1 second segments sampled at 1024 Hz to reduce development/training time.
+The advantages of going to a higher sampling rate would be to model higher-frequency/broader-band signals and/or longer duration signals.
+The disadvantages would be increased training time, possible encroachment on the memory limitations of the GPU, and the potential requirement for further development of the GAN architecture}.
 The parameter prior ranges are
-defined in~\cref{Tab:training_parms} and a sample of training waveforms are shown in \cref{fig:training_waveforms}.
-\jordan{These priors are based on LIGO burst group injections with Q's calculated from choosing frequency as the limiting factor.
-The other paramters can then be evaluated based on the Q relation.
+defined in~\cref{Tab:training_parms} and a sample of training waveforms are also shown in \cref{fig:training_waveforms}.
+\jordan{These priors are based on LIGO-VIRGO injections with quality factors, Q, calculated from choosing frequency as the limiting factor.
+The ranges of frequency chosen are based on the paramters of the standard injections/simulations in used in \cite{PhysRevD.85.122007}.
+The other parameters can then be evaluated based on the Q relation.
 For the BBH waveforms we restrict the mass to be above 30 as lower mass systems would produce longer duration waveforms than typical bursts.} All training data is rescaled such that their amplitudes peak at 1.
@@
 \hline
- Waveform & Central frequency  & Decay & Central time epoch & Mass range \\
- & (Hz) & (s) & (s) & ($\textrm{M}_{\odot}$) \\
+ Waveform & Central frequency  & Decay & Central epoch & Component \\
+ & (Hz) & (s) & (s) & Mass ($\textrm{M}_{\odot}$) \\
 \mr
@@
 Ringdown & 70 - 250 & 0.004 - 0.03 & 0.4 - 0.6 & - \\
-white noise burst & 70 - 250 & 0.004 - 0.03 & 0.4 - 0.6 & -  \\
+White noise burst & 70 - 250 & 0.004 - 0.03 & 0.4 - 0.6 & -  \\
 Gaussian pulse & - & 0.004 - 0.03 & 0.4 - 0.6 & -  \\
@@
 
-With the exception of the binary black hole waveforms, the signal classes described above are analytic proxy waveforms to gravitational wave signals expected from various burst gravitational wave sources.
-For example, numerical relativity simulations show that rapidly rotating stellar core collapse emit gravitational waves that look like sine gaussians with small time constants (low Q).
-Additionally, gravitational waves from hyperbolic black hole encounters look very similar to sine gaussians and gaussian pulses.
+With the exception of the binary black hole waveforms, the signal classes described above are analytic proxy waveforms of gravitational wave signals expected from various burst gravitational wave sources.
+For example, numerical relativity simulations show that a rapidly rotating stellar core collapse emits gravitational waves that look like sine Gaussians with small time constants (low Q).
+Additionally, gravitational waves from hyperbolic black hole encounters look very similar to sine Gaussians and Gaussian pulses.
 Ringdown signals can be emitted by excited isolated neutron stars, for example, after a pulsar glitch and white noise burst signals mimic the stochastic nature of gravitational wave signals emitted by neutrino driven stellar core collapse.
@@
 that the \ac{GAN} performed better with both networks having the same number of
-layers and neurons which encourages even
+layers and neurons, which encourages even
 competition between the generator and discriminator.  After tuning the multiple
@@
 
+As \acp{GAN} are trained by updating one model at the expense of the other, they can be hard to train. GANs attempting to replicate complicated structures that do not
+have the necessary architecture either struggle to produce results at all or
+fall into the common failure mode known as mode collapse; where the generator
+produces a small variety of samples or simply memorises the training set.
+The goal of \ac{GAN} training is to find an equilibrium between the two models, if this cannot be found then it is said that the \ac{GAN} has failed to converge.
+One way to diagnose problems, such as mode collapse, when training \acp{GAN} is to keep track of the loss and accuracy over time.
+These loss plots can help to identify common failure modes or to check if the \ac{GAN} has indeed converged.
+Accuracy is another metric that may be used to monitor convergence and is defined as the number of correct predictions made divided by total number of predictions.
+There is currently no notion of early stopping in \acp{GAN}, instead, training is halted after convergence and by visually inspecting the generations.
+\cref{fig:lossplot} shows the loss and accuracy during the training process for the GAN used in this work.
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width=0.85\textwidth]{figures/losses.png}
+    \caption{Plot of the discriminator and generator loss and accuracy as a function of epochs.
+Early in training the losses oscillate as both models attempt to find their equilibrium, after which, both losses vary around a point which signifies stable training.
+Accuracies on the real and fake data are similar, showing that neither model is stronger than the other.}
+    \label{fig:lossplot}
+\end{figure}
+
 All models were designed with the Python Keras library \cite{chollet2015keras} and TensorFlow \cite{tensorflow2015-whitepaper} and trained on a GeForce RTX 2080 Ti GPU.
-We train the networks for 500 epochs which takes $\mathcal{O}(10)$ hours and save the model at each epoch.
+We train the network for 500 epochs which takes $\mathcal{O}(10)$ hours and save the model at each epoch.
 We choose an appropriate model by visually inspecting the generations at a point of convergence on the loss plot.
@@
 label, the GAN is able to generate burst-like waveforms generalised from the
-training set. We set out by describing the quality of generated waveforms and
+training set. We set out by describing the quality of the generated waveforms and
 how they compare to the training set. We then explore the structure of the
@@
 During training the network should have learned how to smoothly represent the underlying features of a signal as a function of latent space location.
-For example, the linearly interpolated transition through the latent space for the Gaussian pulse signal shows a shift to earlier epoch and larger decay timescale.
-In contrast, the transition for the ringdown signal appears to pass through a localised region of latent space consistent with higher central frequency.
+For example, the linearly interpolated transition through the latent space for the Gaussian pulse signal shows a shift to an earlier epoch and a larger decay timescale.
+In contrast, the transition for the ringdown signal appears to pass through a localised region of the latent space consistent with a higher central frequency.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 While the \ac{GAN} is trained on distinct one-hot encoded classes, we may test arbitrary points in the \ndimensional{5} class space to produce indistinct or hybrid waveforms.
-In order to explore the class space, in \cref{fig:c_interp} we show results where the latent vector is held constant but we instead linearly
-interpolate within the one-hot encoded class space between pairs of the well-defined training class locations.
-In this scenario we highlight that the \ac{GAN} has not yet probed this intermediate class space during its training and therefore we are reliant on the generator having learned any underlying class space relationships between the 5 training classes.
+In order to explore the class space, in \cref{fig:c_interp} we show results where the latent vector is held constant, but we instead linearly
+interpolate within the one-hot encoded class space between pairs of well-defined training class locations.
+In this scenario, we highlight that the \ac{GAN} has not yet probed this intermediate class space during its training and therefore we are reliant on the generator having learned any underlying class space relationships between the 5 training classes.
 The results show that for each case that the generated signals show distinct characteristics of the respective class pairs at most stages of the transition.
@@
 \subsection{General points within the class space}
-We have shown that the \acp{GAN} latent space and class space have structure that can be navigated via interpolation between pairs of locations within each respective space.
+We have shown that the \acp{GAN} latent space and class space have a structure that can be navigated via interpolation between pairs of locations within each respective space.
 Taking a step further, we can sample from the class space in novel ways to create new inputs for the generator.
@@
 Similarly \cref{fig:uniform_samples} shows generations conditioned on class vectors drawn uniformly in the unit hyper-cube.
-These types of generations tend to exhibit more noise and some tend to be generated with very low amplitude prior to being re-scaled to have maximum amplitude of unity.
-Both methods of generating hybrid waveforms, however, do produce signals that appear to share characteristics from the training set but still be distinct in signal morphology.
-Upon inspection of a larger collection of waveform generations from both methods we do see a tendency for the uniform hyper-cube approach to generate a wider variety of hybrid waveforms that are more visually distinct from the training set.
+These types of generations tend to exhibit more noise and some tend to be generated with very low amplitude prior to being rescaled to have a maximum amplitude of unity.
+Both methods of generating hybrid waveforms, however, do produce signals that appear to share characteristics with the training set but still are distinct in signal morphology.
+Upon inspection of a larger collection of waveform generations from both methods, we do see a tendency for the uniform hyper-cube approach to generate a wider variety of hybrid waveforms that are more visually distinct from the training set.
 This is to be expected given that the simplex class space is a subset of the hyper-cube and does not explore regions of the class space as far from the training set vertices.
@@
 \section{CNN burst classifier} \label{cnn classifier}
-In this section we develop a basic search analysis using a \ac{CNN} in order to compare the sensitivity of such a search using different \ac{GAN} generated waveforms in additive noise.
+In this section, we develop a basic search analysis using a \ac{CNN} in order to compare the sensitivity of such a search using different \ac{GAN} generated waveforms in additive noise.
 We train a \ac{CNN} to perform simple classification and to distinguish between two classes: signals in additive Gaussian noise and Gaussian noise only.
@@
 All of the training data used is whitened using the Advanced LIGO design sensitivity \ac{PSD} \cite{designcurve,observing-prospects}, such that there is equal noise power at each frequency.
-Signal network \acp{SNR} is drawn uniformly in the range $[1,16]$ and is controlled by an amplitude scaling applied to the waveform.
+To generate  signals at a chosen optimal (network) \ac{SNR} $\rho_{\text{opt}}$, we first compute $\rho_{\text{opt}}$ for each generated waveform, defined in~\cite{PhysRevD.87.024033} as
+\begin{equation}
+    \rho^2_{\text{opt}} = \sum_{i=\text{H1,L1}}4\int_{f_\text{min}}^{f_\text{max}} \frac{|\Tilde{h}^{(i)}(f)|^2}{S^{(i)}_{n} (f)} df
+\end{equation}
+where $\Tilde{h}^{(i)}(f)$ and $S^{(i)}_{n}(f)$ are the Fourier transform of the GW strain in the frequency domain and the detector noise \ac{PSD} for the $i$th detector respectively.
+We then sample the target optimal \ac{SNR} uniformly \michael{on $\textrm{U}[1, 16]$} and rescale the waveform amplitudes in order to achieve the desired value.
+
 Each 1 second duration time-series input to the \ac{CNN} is represented by a \ndimensional{1} 1024 sample vector with 2 channels representing each detector.
@@
 We used dropout in the final dense layer and used a selection of different activation functions including the swish activation \cite{ramachandran2017searching} which improved overall performance, and a sigmoid activation for the output layer.
-We used binary cross-entropy \cref{eqn:crossentropy} as the loss function and Adam as an optimizer with learning rate set to $10^{-3}$.
+We used binary cross-entropy \cref{eqn:crossentropy} as the loss function and Adam \cite{DBLP:journals/corr/KingmaB14} as an optimizer with learning rate set to $10^{-3}$.
 In total we train three separate \acp{CNN} on the vertex, uniform and simplex datasets respectively.
@@
 We now compare the \ac{CNN} results between the datasets by first training three \acp{CNN} on the vertex, simplex, and uniform datasets and then using these models to make predictions on the other testing data that is unseen during the network training process.
-We compare results for the different permutations in \cref{fig:eff_curves}.
-In this figure the top panel presents results for the three different networks tested on the vertex data and shows that each model confidently detects all the signals with $\text{\acp{SNR}} >13$.
+We compare results for the different permutations using efficiency curves as shown in \cref{fig:eff_curves}.
+\jordan{The efficiency curves are computed by fixing the false alarm probability (FAP) and plotting the true alarm probability (TAP) against optimal \ac{SNR} for a direct comparison between CNN approaches.
+False alarm probability is the fraction of noise-only samples that are incorrectly identified as signals whereas true alarm probability is the fraction of signals correctly identified as signals.
+However, since the distribution of \acp{SNR} is continuous, we cannot compute the TAP using the method described previously in \cite{Gabbard2017}.
+Instead, we compute the TAP at specific \acp{SNR} by considering all of the signals weighted by a Gaussian window with standard deviation 0.3 centred on each \ac{SNR}.} A classifier model performs better than another when it achieves a higher TAP for a fixed FAP at a given optimal SNR.
+In \cref{fig:eff_curves}, the top panel presents results for the three different networks tested on the vertex data and shows that each model confidently detects all the signals with $\text{\acp{SNR}} >13$.
 At lower \acp{SNR} the vertex and uniform datasets perform similarly, however, at $\rho_{\text{opt}}\sim 10$ the simplex trained model has slightly worse performance, dropping in true alarm probability by a few percent.
@@
 This suggests that the uniform method of sampling the class space for training or characterising a search algorithm is the most robust and sensitive approach given the intrinsically unknown nature of GW burst signals.
-Furthermore, since the uniform trained model performs equally as well as the vertex trained model when applied to  vertex test data, we can conclude that the inclusion of the unmodelled signals does not negatively affect the model's performance on modelled signals.
+Furthermore, since the uniform trained model performs equally as well as the vertex trained model when applied to  vertex test data, we can conclude that the inclusion of the unmodelled signals does not negatively affect the model's performance on the modelled signals.
 
@@
 %
-Whilst we have trained our \ac{CGAN} on 5 discrete signal classes, each having its own signal parameter space, we have shown that we can subsequently sample from the continuous class space to generate hybrid burst waveforms.
+While we have trained our \ac{CGAN} on 5 discrete signal classes, each having its own signal parameter space, we have shown that we can subsequently sample from the continuous class space to generate hybrid burst waveforms.
 This novel aspect of our analysis takes advantage of the learned mapping between individual discrete signal classes.
@@
 %
-To provide a practical example of the usage of these waveforms we have concluded our analysis with a simple search for signals in additive Gaussian noise.
+To provide a practical example of the usage of these waveforms, we have concluded our analysis with a simple search for signals in additive Gaussian noise.
 We have suggested 3 variations of how to sample from the \ac{CGAN} signal class space and have trained a basic \ac{CNN} separately on those data in order to classify whether a signal was present in the noisy data versus only Gaussian noise.
@@
 Our approach allows us to explicitly control the mixing of different signal training classes but the variation within the space of signal properties is determined randomly through sampling of the abstract latent space.
-In the future, as development in \acp{GAN} and generative machine learning advances it is expected that we will gain greater control over targeted generation of signal features.
+In the future, as development in \acp{GAN} and generative \ac{ML} advances it is expected that we will gain greater control over targeted generation of signal features.
 It will also be important to extend our models to train on, and generate, longer duration waveforms, higher sampling rates, and to be conditioned on additional classes.
